### 2018-02-22 comparing_05222017.tex
Added files via upload

\RequirePackage{fix-cm}

\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%

\usepackage{graphicx}
\usepackage{mathptmx}      
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{cite}
\usepackage{caption}
\usepackage{natbib}

\journalname{Sankhya B}

\begin{document}

\title{Comparing Different Planned Missingness Designs in Longitudinal Studies}

\author{Nicholas Illenberger \and Jennifer Pellowski \and Ofer Harel}

\institute{N. Illenberger \and O. Harel 
				\at University of Connecticut \\
						215 Glennbrook Rd. Unit 420\\
						Storrs CT, 06269-4120 USA
              Tel: (860)486-6989 \\
		      \email{ofer.harel@uconn.edu}  
					\and
					J. Pellowski
					\at International Health Institute\\ 
					Brown School of Public Health 
					\and J. Pellowski 
					\at Department of Psychiatry and Human Behavior\\
					The Warren Alpert Medical School of Brown University.  
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Planned Missingness (PM) designs, in which researchers deliberately collect only partial data, have enjoyed a recent growth in popularity. Among other benefits these designs have been proven capable of reducing the study costs and alleviating participant burden. Past research has shown that Split Form PM designs can be effective in simplifying complex surveys while Wave Missingness PM designs act similarly for Longitudinal studies. However, less work has been done to inform how to implement PM structures into studies which incorporate elements of both survey and longitudinal designs. Specifically, in studies where a questionnaire is given to participants at multiple measurement occasions the best way to design missingness is still unclear. To address this deficiency, data in this hybrid format was simulated under both Split Form and Wave Missingness PM structures. Multiple Imputation techniques were applied to estimate a multilevel logistic model in each of the simulations. Estimated parameters were compared to the true values to see which PM design allowed us to best capture the true model. The results of this study indicate that, compared to the Split Form Design, the Wave Missingness design consistently performed less effectively in capturing the multilevel model. Thus, in the context of longitudinal surveys this study recommends the use of Split Form missingness designs, which performs well under a number of different conditions.

\keywords{Planned Missingness \and Split Form \and Multiform \and Wave Missingness \and Multiple Imputation \and Missing Data.}
\end{abstract}

\section{Introduction}
\label{intro}
Planned Missingness (PM) designs are a type of experimental design in which some of the data is predetermined to be missing. While it may seem counterproductive to deliberately omit data from the collection process, PM designs have been shown to reduce both participant burden \citep{graham2006planned, saris20048} and the costs of a study \citep{graham2001planned}. Moreover, PM designs can actually increase the quality of collected data by increasing the breadth of a study \citep{little2013planned} as well as decreasing the effects of assessment reactivity and rates of unplanned missingness \cite{harel2015designed}. We further note that while PM designs decrease the efficiency of estimators \citep{rhemtulla2016asymptotic}, decreasing the cost per participant may allow researchers to enroll more participants in a study, offsetting some of the efficiency loss. \par

There have been many different incarnations of the PM design, each crafted to best suit the study at hand. For example, PM designs have been used in the study of longitudinal growth curves \citep{graham2001planned, mcardle1997expanding}, business research \citep{shoemaker1973principles}, behavioral studies \citep{harel2015designed}, biostatistics \citep{andres2006partial, wacholder1994partial}, and in educational assessments \citep{zeger1997efficient, sirotnik1977incidence}. This paper focuses on two of the simplest and most applicable PM designs, the Split Form design \citep{raghunathan1995split} and the Wave Missingness design \citep{little2013planned}. While this paper covers these designs in more detail later, broadly speaking, the Split Form design entails measuring fewer points at a single measurement occasion \citep{raghunathan1995split}. The Wave Missingness design, on the other hand, would require missing out on entire measurement occasion within a longitudinal study \citep{graham2001planned}.

The issue we concern ourselves with arises when a longitudinal study requires multiple items to be collected at each measurement occasion. When a multi-level regression model is the analysis of interest, we would like to see if it is more efficient to design missingness using the Split Form design or the Wave Missingness design. Previous research indicates that for the estimation of correlated latent growth curve models use of the three-form PM design, a special case of Split Form designs \citep{raghunathan1995split}, resulted in low bias on parameter estimates or standard error and high efficiency when compared with wave missingness designs \citep{rhemtulla2014planned}. Because our model of interest is a mixed effects model, though, we can not be sure that this result will hold. \par

To answer our question we performed a simulation study based on data obtained in longitudinal research on HIV medication adherence and alcohol-interactivity beliefs \citep{pellowski2016alcohol}. For each of the PM designs mentioned we simulated sample data conforming to that particular design and then used multiple imputation (MI) \citep{little2014statistical}  techniques to analyze our data. We subsequently evaluated the PM methodologies using the average bias, percent bias, mean squared error, coverage rates, confidence interval length, and estimated fraction of missing information (FMI) \citep{little2014statistical} for parameter estimates in a multilevel model. To make our results more generalizable the experiment was repeated under a few different scenarios: increased sample size, low inter-survey correlation, and high time effect. \par

To delineate the remainder of this paper, in Section 2 we go into more depth on the two PM designs previously mentioned and then move into a discussion on the modern Multiple Imputation technique for dealing with missing data. Next, in Section 3 we briefly describe the dataset we worked with and our method of simulation before moving on to the results of our analyses in Section 4 and a discussion in the final section. \par

\section{Designs and Methods}
\label{sec:1}
\subsection{Split Form Design}
\label{sec:1.1}

Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are so named because of the way in which they are implemented. Instead of giving participants one large survey, researchers will create multiple “forms”, each containing only a subset of the full survey’s questions. A common setup is the three-form design \citep{graham1996maximizing}. In the three-form design the full survey is split into four blocks, X, A, B, and C. Each form of the survey includes the X block as well as two of the other three blocks. This leaves us with the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded. We note that every block is paired together in at least one of the forms. By designing our forms in this manner we are able to estimate the relationship between any given items regardless of which blocks they are in. That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows us to do that. \par

\begin{table}[h!]
	\centering
	\caption{The Three Form PM Design}
	\label{tab:table10}
	\setlength{\tabcolsep}{1cm}
	\begin{tabular}{c|cccc}
		\toprule
		& \multicolumn{4}{c}{Block} \\
		Form & X & A & B & C \\
		\midrule
		1 & 1 & 1 & 1 & 0 \\
		2 & 1 & 1 & 0 & 1 \\
		3 & 1 & 0 & 1 & 1 \\
		\bottomrule
	\end{tabular}
\end{table}

An important consideration when designing a Split Form survey is deciding which items to put into which blocks. The X-block, being included in every form, should contain either those variables which are of greatest interest or those with the most predictive ability.
Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}. On the other hand, placing the most predictive variables in the X-block allows Multiple Imputation to more effectively impute missing values from the other blocks \citep{gottschall2012comparison}. For the same reason it is good practice to place variables which are predictive of each other in to separate blocks \citep{gottschall2012comparison}. We note that when groupings are not as obvious as in the previous example pilot studies can help determine the predictive potential of variables. We may also wish to consider the cost and burden associated with an item when deciding which block to place it in. Even if a specific item is critical to our analysis, if it is overly expensive or invasive we may be better off excluding it from the X-block \citep{little2013planned}. \par

More than deciding which blocks should contain which items, we also need to consider how many blocks we should use. Including more blocks in our design can allow us to further increase missingness \citep{graham2006planned}. For example, imagine two groups of researchers, the first group divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey, and the second uses an X-block and nine others with 10\% of the items each. The researchers make the decision that any given pair of blocks should be asked together in at least one of the forms to ensure efficient estimations. Based on this requirement, the first group can only reduce the length of their survey by 25\% while the second group can decrease the length of their survey by up to 70\%. \par

While this increase in missingness may allow for further reductions in burden and cost researchers must consider the trade-offs of using more blocks. Besides the fact that greater missingness will lead to less efficient estimation \citep{rhemtulla2016asymptotic} there is the added complication that more blocks means more forms. If the second group of researchers in our example, for instance, did decide that each form would contain the X-block and two of the other blocks, then they would be left with 36 total forms. For traditional paper surveys this can make increasing the number of blocks unwieldy. However, for electronic surveys, where form randomization can be automated, this is not an issue. Oftentimes, Researchers using electronic surveys will give each participant a random sample of all the survey items, in a way treating each item as its own block \citep{silvia2014planned}. Using this method researchers can reap the benefits of increased forms without the difficulty caused by manually building these forms. \par

\subsection{Wave Missingness Design}
\label{sec:1.2}
While Split Form missingness can be applied to many different experimental designs, the Wave Missingness design \citep{little2013planned} is unique to studies with multiple measurement occasions or waves. Unlike the Split Form design, where participants were assigned to miss a subset of items in a single measurement occasion, the Wave Design entails randomizing participants to miss an entire measurement occasion. An example of a Wave Missing design in which data is collected every month for five months but each participant is only measured at three of these occasions as shown in Table \ref{tab:table11}. Again, "1" indicates that a given wave is included while "0" indicates that it is excluded. Subject two, for instance, is randomly assigned to be measured only at the first, second, and fourth month. \par

\begin{table}[b!]
	\centering
	\caption{The Wave Missingness PM Design}
	\label{tab:table11}
	\setlength{\tabcolsep}{0.75cm}
	\begin{tabular}{c|ccccc}
		\toprule
		& \multicolumn{5}{c}{Month} \\
		Participant & 1 & 2 & 3 & 4 & 5 \\
		\midrule
		1 & 1 & 0 & 1 & 0 & 1 \\
		2 & 1 & 1 & 0 & 1 & 0 \\
		3 & 0 & 0 & 1 & 1 & 1 \\
		4 & 1 & 1 & 1 & 0 & 0 \\
		\bottomrule
	\end{tabular}
\end{table}

A relative advantage of the Wave Missingness design over the Split form design is that researchers can have more control over the level of missingness. For studies with many measurement occasions it is easy to make small changes to the amount of missing data. The data described by \citet{pellowski2016alcohol}. \citet{pellowski2016alcohol} for instance has daily measurements for 45 days. Missing eleven days here would result in 24.4\% missingness while missing twelve gives us 26.7\%. Further, Wave Missingness designs have the ability to eclipse Split Form designs in terms of cost reduction \citep{little2013planned}. \par

Another advantage of this design is that many common longitudinal study designs already make use of the Wave Missingness structure \citep{little2013planned}. Cohort Sequential Designs are a type of study where cohorts of different ages are recruited and followed longitudinally in such a way that we can use information from one cohort to impute values for another \citep{little2013longitudinal, duncan2013introduction}. Say, for example, we had three cohorts of ages 10, 11, and 12 at baseline and we measured them annually for four years. Although measurement only occurs at four waves we can frame this as a six-wave study where the 10-year old cohort has missing values at waves five and six, the 11-year old cohort at waves one and six, and the 12-year old cohort at waves one and two. Because the 10-year old cohort is the only group observed at the first wave we use it to impute missing values for the other groups. By continuing in this manner we are able to take the data that was collected over a four year period and extend it to cover six years, accelerating the study. The setup of this type of study is demonstrated in Table \ref{tab:table12}, where "1" and "0" respectively indicate an included and excluded wave. \par

\begin{table}[t!]
	\centering
	\caption{Cohort Sequential Design}
	\label{tab:table12}
	\setlength{\tabcolsep}{0.5cm}
	\begin{tabular}{c|cccccc}
		\toprule
		& \multicolumn{6}{c}{Age} \\
		Participant & 10 & 11 & 12 & 13 & 14 & 15 \\
		\midrule
		1 & 1 & 1 & 1 & 1 & 0 & 0\\
		2 & 0 & 1 & 1 & 1 & 1 & 0\\
		3 & 0 & 0 & 1 & 1 & 1 & 1\\
		\bottomrule
	\end{tabular}
\end{table}

Developmental time-lag models \citep{mcardle1997expanding} also make use of the Wave Missingness structure. As shown in Table \ref{tab:table13}, researchers here observe participants at only two measurement occasions, varying the length between occasions for each participant, and then treat this two-time-point data as multi-time-point data with missing values. Under this framework they are able to use missing data techniques to impute these missing values and estimate growth curve models. Estimating this type of model would normally require measuring participants at many time points however, under the Wave Missingness design we can accomplish this task with only two measurement occasions per participant. These designs exemplify how useful the Wave Missingness structure can be in accelerating longitudinal studies. \par

\begin{table}[b!]
	\centering
	\caption{Developmental Time-Lag Setup}
	\label{tab:table13}
	\setlength{\tabcolsep}{0.75cm}
	\begin{tabular}{c|cccc}
		\toprule
		& \multicolumn{4}{c}{Wave} \\
		Participant & 1 & 2 & 3 & 4 \\
		\midrule
		1 & 1 & 1 & 0 & 0 \\
		2 & 1 & 0 & 1 & 0 \\
		3 & 1 & 0 & 0 & 1 \\
		\bottomrule
	\end{tabular}
\end{table}

\subsection{Multiple Imputation}
\label{sec:1.3}
\subsubsection{Missing Data Mechanisms}
\label{sec:1.3.1}
Before describing Multiple Imputation and how it can be applied to PM designs it is important to first understand how data become incomplete. Suppose we have a dataset, $Y_{com}$, with some missing values. We define the missingness, $R$, to be an indicator variable which equals 0 where $Y_{com}$ is observed and 1 where the corresponding value in $Y_{com}$ is missing. Missing data mechanisms describe the supposed probabilistic relationship between $R$ and the values in $Y_{com}$, observed or unobserved \citep{little2014statistical}. \par

The first missing data mechanism, missing at random (MAR), was defined by \citet{rubin1976inference}. Data are considered MAR when the missingness does not depend on unobserved values but may depend upon other observed variables. For instance, if men are less likely to report their incomes than women but the level of income itself does not affect the probability of reporting, then we can say the missingness govern income is MAR. \par

Later, \citet{little2014statistical} described two additional mechanisms which lead to missing values: missing completely at random (MCAR) and missing not at random (MNAR) \citep{little2014statistical}. The first, MCAR, is used to describe a situation in which the missingness is independent of the observed or unobserved data. That is, the missing values are simply a random subset of the full data. On the other hand, data is said to be MNAR when the missingness is related to the unobserved data; in a survey people may be less willing to provide their income if it is extremely high or low, for example. \par

If we have prior knowledge concerning the relationship between unobserved values, indicated by $R$, and the observed values, then Multiple Imputation can yield efficient estimates even under MNAR \citep{harel2007multiple}. However, because this is not typically the case MI is most often implemented when data is MCAR or MAR \citep{little2014statistical}. \par 
As a consequence of allowing researchers to decide which values in a dataset are observed and unobserved, PM designs grant control over the missing data mechanism. Because of this, MI is an appealing option for researchers utilizing a PM design. If implemented properly, data should conform to either the MCAR or MAR assumption. For instance, if medical researchers decide not to collect blood pressure on a completely random subset of patients there is no reason to believe the missing blood pressures differ significantly from the observed ones. This fact allows for the use of MI and other modern missing data techniques such as the Full Information Maximum Likelihood approach \citep{dempster1977maximum} \par

\subsubsection{The Multiple Imputation Procedure}
\label{sec:1.3.2}
Multiple Imputation is used to obtain statistically valid inferences in spite of missing data. MI works by replacing unobserved values with a set of plausible values in a way which allows us to account for uncertainty in the imputation process. Repeatedly using some imputation technique every missing value in the incomplete dataset is replaced with a fixed number of imputed values. This process allows for the creation of multiple complete datasets, on which users can run complete-data procedures. If, for instance, we imputed $M$ possible values for every missing value we would obtain $M$ different completed datasets. Once these datasets have been created, we can run the analysis of interest on each of them and, using rules defined by \citet{little2014statistical} and \citet{rubin2004multiple}, combine our results to obtain a single inference. \par

Suppose we are interested in estimating a certain parameter such as the mean of a variable or a regression coefficient. If $\theta$ is the parameter of interest, let $\widehat{\theta_1}, \widehat{\theta_2}, ... \widehat{\theta_M}$ be the estimates of $\theta$ and let $S_1, S_2, ... S_M$ be the corresponding estimated standard errors from the $M$ imputed datasets. We can aggregate these results using the combining rules specified by \citet{little2014statistical} and \citet{rubin2004multiple}. \par
The overall MI estimate of $\theta$ is defined as,

\begin{equation}
\widehat{\theta} = \sum_{n=1}^{M} \widehat{\theta_n}.
\end{equation}

From here we can compute the sampling variance of this estimate by first calculating the between-imputation component, $B_M = \sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2 / (M-1)$, and a within-imputation component, $W_M = \sum_{n=1}^{M} S_n^2 / M$. These components are combined to obtain the overall sampling variance of our MI estimate as follows:

\begin{equation}
T_M = W_M + (1+1/M)*B_M.
\end{equation}

These equations form the basis of Rubin's combining rules and should provide parameter estimates which are unbiased while accounting for the inherent uncertainty in the imputation process \citep{raghunathan2015missing}. For a more in depth explanation of these methods we refer readers to \citet{little2014statistical}. \par

When using Multiple Imputation researchers must decide on the number of imputations, $M$, to use. Generally speaking, the lower the level of missingness is the fewer imputations are needed. If less than 20\% of the requisite data is missing, for instance, ten or even five imputations will suffice \citep{raghunathan2015missing}. However, at its roots MI is a simulation technique and thus, the greater $M$ is the more stable our estimates become \citep{harel2007inferences}. \citet{graham2007many} recommend that if computational power is not a limiting factor, then setting $M=100$ is good practice. \par

\section{Data and Simulations}
\label{sec:2}
\subsection{Data}
\label{sec:2.1}
The dataset we based our simulations on came from a study by \citet{pellowski2016alcohol} and more in depth information on it can be found there. However, to give a brief overview, the data was collected in an attempt to determine the day-level relationship between alcohol use, interactive toxicity beliefs, and adherence to antiretroviral therapy (ART) amongst patients with HIV. Previous studies noted that alcohol use combined with the perception that mixing alcohol and ARTs can cause adverse effects, correlated with non-adherence to ARTs \citep{kalichman2009prevalence, kalichman2012alcohol}. However, \citet{pellowski2016alcohol} pointed out that past research had collected data over extended periods of time preventing the identification a day-level interaction. Unlike others, this study was able to determine whether alcohol use and missed medication doses occurred on the same day. \par

The study employed an observational cohort design, following sixty participants over forty-five days and sending them a daily questionnaire. Questions in the survey concerned livelihood insecurities from the previous day as well as alcohol use. The analysis used eight particular questions, two binary questions on housing insecurity, four binary questions on food insecurity, and two questions concerning alcohol use  (one binary variable and one count variable). The exact questions can be found in Table \ref{tab:table1}. \par
\begin{table}[t]
	\centering
	\caption{Survey Questions}
	\label{tab:table1}
	\begin{tabular}{cp{6.5cm}c}
		\toprule
		Item Number & Question & Responses\\
		\midrule
		1 & I worried about having a place to stay yesterday. & 1.Yes $\>$ 2.No \\
		2 & I could not get to where I needed to go yesterday. & 1.Yes $\>$ 2.No \\
		3 & I worried about my food running out yesterday. & 1.Yes $\>$ 2.No \\
		4 & I ate less than I needed to yesterday. & 1.Yes $\>$ 2.No \\
		5 & I was hungry, but did not eat because I couldn't afford food. & 1.Yes $\>$ 2.No \\
		6 & I got food from a pantry, church, agency, friend or the street yesterday. & 1.Yes $\>$ 2.No \\
		7 & Did you drink alcohol yesterday? & 1.Yes $\>$ 2.No \\
		8 & How many alcohol drinks did you have yesterday? & 0-20 \\
		\bottomrule
	\end{tabular}
\end{table}

Beyond the daily questionnaire, data was also collected through a computer-assisted interview on behavioral, psychosocial, and cognitive factors (ex. Income, alcohol-toxicity beliefs, education, etc.) which have been shown to be associated with medication adherence. These values were only collected at baseline and are considered time independent. The variables from this assessment used in our analysis concerned education level, income, age, beliefs about the interactivity of alcohol with ART medication, depression, and alcohol abuse. \par

\subsection{Simulations}
\label{sec:2.2}
The first step in the process of creating our simulated datasets was to use the data from \citet{pellowski2016alcohol} and obtain parameter estimates to quantify the relationships between variables. We then treated these estimated relationships as the “true” relationships and drew two-hundred samples using these parameters. While we would have liked to simulate a larger number of samples we were limited by computational ability. Our purpose in simulating these datasets was to see how well they would be able to capture the true relationship between medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score). Specifically, our model of interest is the random intercept model with time effect found below: \\

\begin{align*}
logit(MissedDose) &= \beta_{0j} + \beta_1*DrinkYN + \beta_2*ZAlcTox +\beta_3*Day \\
Level 2: \beta_{0j} &= \gamma_0 + \epsilon_j
\end{align*}
where, \\ \\
$MissedDose = 1$ if the participant did not adhere to the ART, 0 otherwise. \\
$DrinkYN = 1$ if the participant drank on a given day, 0 otherwise.\\
$ZAlcTox =$ Z-transformed score on an alcohol-antiretroviral interactive toxicity scale developed by Kalichman \cite{kalichman2009prevalence}. \\
$Day =$ The number of days since the study began, 0-44. \\
$j =$ participant index, 1-60. \\
$\epsilon_j  \sim N(0, \sigma^2)$. \\ \\

The true values of the parameters, $\gamma_0, \beta_1, \beta_2$, $\beta_3$, and $\sigma^2$ were set to -2.3, 0.56, 1.28, 0.2, and 1.0 respectively. \par
Once our samples were drawn we imposed three different missingness structures on each of the samples corresponding to three possible PM designs. These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed. To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Table \ref{tab:table14}. As in the previous tables, "1" indicates an observed occasion while "0" indicates a missing one. We see that the Split Form design entails missing two items on each of the days. The altered Split Form, while similar, is fully measured on two of the measurement occasions. Because there are days which are fully observed the relationships between variables may be clearer, allowing the imputation procedure to run more effectively. On the other hand, the Wave Missingness design shows two days in which no questions are asked but the full questionnaire is given on the remaining days. \par

\begin{table}[t!]
	\centering
	\caption{Different Planned Missingness Designs}
	\setlength{\tabcolsep}{0.45cm}
	\label{tab:table14}
	\hspace*{-1cm}
	\begin{tabular}{c|c|ccccc}
		\toprule
		Design & Day & Q1 & Q2 & Q3 & Q4 & Q5 \\
		\midrule
		\multirow{5}{*}{Split Form}
		& 1 & 1 & 1 & 0 & 0 & 1 \\
		& 2 & 0 & 0 & 1 & 1 & 1 \\
		& 3 & 0 & 1 & 1 & 0 & 1 \\
		& 4 & 1 & 0 & 1 & 1 & 0 \\
		& 5 & 1 & 1 & 0 & 1 & 1 \\
		\midrule
		\midrule
		\multirow{5}{*}{Altered Split Form}
		& 1 & 1 & 1 & 1 & 1 & 1 \\
		& 2 & 1 & 1 & 1 & 1 & 1 \\
		& 3 & 0 & 0 & 1 & 1 & 1 \\
		& 4 & 1 & 1 & 0 & 1 & 0 \\
		& 5 & 0 & 1 & 1 & 0 & 1 \\
		\midrule
		\midrule
		\multirow{5}{*}{Wave Missingness}
		& 1 & 1 & 1 & 1 & 1 & 1 \\
		& 2 & 0 & 0 & 0 & 0 & 0 \\
		& 3 & 1 & 1 & 1 & 1 & 1 \\
		& 4 & 1 & 1 & 1 & 1 & 1 \\
		& 5 & 0 & 0 & 0 & 0 & 0 \\
		\bottomrule
	\end{tabular}
	\hspace*{-1cm}	
\end{table}

Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 25\%, 50\%, and 75\% missing data. Previous work by \citet{rhemtulla2014planned} has found that for low levels of missingness (25\%) the Three-Form design outperforms the Wave Missingness design in its ability to capture latent growth curve model parameters. However, because only low-levels of missingness are tested we do not know if this relationship holds at moderate or high levels. We hope that by including these different levels of missingness we will be able to see how these designs perform at all levels of the missingness spectrum. \par
Once missingness was created we used Multiple Imputation techniques to estimate the relationship between Medication Adherence and the other variables in our model. Because we have control over the missing data mechanism, we know the data is MCAR. This fact allows for the principled use of MI techniques. Using the R package $\{$mice$\}$ \citep{mice2011imputation} our binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching. \par

After imputations the logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}. From here, the results from each PM design were evaluated based on bias, percent bias, mean squared error (MSE), coverage, confidence interval (CI) length, and the fraction of missing information (FMI). The FMI is a measure of how much of the MI sampling variance comes from differences between imputations. Besides comparing the results between each of the PM designs we also included the results of these same analyses taken from before missingness was imposed. \par

When determining if the PM designs are performing sufficiently well it is important to consider how well the simulated samples performed before we added a missingness structure. For example, imagine we have two full data samples with respective biases on the $\beta_1$ estimate of 0.13 and 0.15. Further, after imposing different PM design structures on these samples we obtained the average biases of 0.14 and 0.15 respectively. It would be unfair to claim that the first
PM design performed better than the second because, by chance, it was based off of a more representative sample. We kept this fact in mind when determining our evaluation criteria. \par

For bias, percent bias, and MSE we claimed that an increase of more than 40\% in these measurements after imposing missingness indicates that the PM design is inappropriate. For instance, if the complete data shows a percent bias of 10\%, anything higher than 14\% ($0.1*1.4$) would be unacceptable. An increase of this size has the ability to negatively effect efficiency of our estimation. Based on the work of \citet{collins2001comparison} we also regard coverages of less than 90\% as unacceptable. If a 95\% CI has a true coverage of 90\% than the Type I error rate is double what it should be. Because MI accounts for uncertainty in the imputation process coverages should have been similar despite the added missingness. In terms of confidence interval lengths, if one PM design provides similar rates of coverage to another while maintaining shorter intervals than this is considered the better of the two methods. For equal coverage rates, shorter intervals imply more power. The FMI, which quantifies the uncertainty in our imputation process, is simply reported for each PM design. While less uncertainty in the imputations can be beneficial, less variation does not necessarily imply accuracy. Thus, FMI should be taken in the context of the other measurements. \par

We repeated this process under three modified simulation scenarios mentioned in the following sections. We note that while typically these PM designs would be compared against the results obtained using a complete case analysis \citep{rhemtulla2016asymptotic} we decided against this approach because it would fundamentally alter the form of our data. To be more concrete, complete case analysis on the Split Form design would remove all observations (all observations have some missing values). In the Wave Missingness setup, complete case analysis would shorten the length of the longitudinal study. If a participant was missing values on 11 of the 45 days, then complete case analysis would have made the data resemble a longitudinal study held over 34 days. Hence, this comparison is invalid. \par

\subsubsection{Increased Sample Size}
In order to evaluate the impact of sample size on estimation we took the format of the original data, which included sixty participants, and expanded it to include one-hundred and twenty. The rest of the simulation process was carried out as before. We noted earlier that cost savings created from the PM designs could allow us to enroll more participants. Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, then researchers can design missingness in whichever method is most convenient. We further note, that because Wave Missingness allows for greater savings an increase in sample size is more reasonable for that type of Missingness. \par
\subsubsection{Low Inter-Survey Correlation}
For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best. To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days. While this fact was accounted for in the original simulations, it was not in this set of simulations. If the probability of answering “yes” on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations then in this scenario it is a function of only the baseline variables. This implies that each of the questions are conditionally independent of each other given the baseline variables. If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal. \par
\subsubsection{High Time Effect}
In this final scenario we hoped to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable. To do this we changed the value of the parameters $\gamma_0, \beta_1, \beta_2,$ and $\beta_3$ to -4.6, 0.28, 0.64, and 0.2 respectively. We note that instead of increasing the value of $\beta_3$, the slope for time effect, we decreased all the other parameters. We did this because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1. By decreasing the other variables effects we were able to ensure that time has a disproportionate effect without incurring this problem. The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point. \par

\section{Results}
\label{sec:3}
\subsection{Primary Simulation}
\label{sec:3.1}
The first set of simulations we ran had the parameters in our random-intercept logistic model set as $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$. The effects of the variables here are comparable to those found in the original dataset. This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design. Before we imposed a missingness structure on our two-hundred simulated samples we obtained the full data results shown in Table \ref{tab:table2}. We note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.

\begin{table}[b!]
	\centering
	\caption{Results of Analysis before imposing Missingness in each Scenario}
	\setlength{\tabcolsep}{0.1cm}
	\label{tab:table2}
	\begin{tabular}{cc|ccccc}
		\toprule
		Scenario & Parameter & Bias & Percent Bias & MSE & Coverage & CI Length \\
		\midrule
		\multirow{4}{*}{\parbox{2cm}{Primary \\ Analysis (N=60)}} 
		& $\gamma_0$ & 0.151 & 6.55\% & 0.037 & 99.0\% & 0.750 \\
		& $\beta_1$ & 0.133 & 23.75\% & 0.028 & 95.5\% & 0.652 \\
		& $\beta_2$ & 0.120 & 9.40\% & 0.022 & 97.5\% & 0.610 \\
		& $\beta_3$ & 0.007 & 3.42\% & 7.11$*10^-5$ & 97.0\% & 0.034 \\
		\midrule
		\midrule
		\multirow{4}{*}{\parbox{2cm}{Increased \\ Sample (N=120)}} 
		& $\gamma_0$ & 0.106 & 4.61\% & 0.018 & 98.0\% & 0.528 \\
		& $\beta_1$ & 0.099 & 17.63\% & 0.016 & 93.0\% & 0.460 \\
		& $\beta_2$ & 0.091 & 7.12\% & 0.013 & 95.5\% & 0.429 \\
		& $\beta_3$ & 0.005 & 2.34\% & 3.52$*10^-5$ & 96.5\% & 0.024 \\
		\midrule
		\midrule
		\multirow{4}{*}{\parbox{2cm}{Low \\Inter-Survey Correlation (N=60)}} 
		& $\gamma_0$ & 0.145 & 6.29\% & 0.033 & 99.0\% & 0.747 \\
		& $\beta_1$ & 0.130 & 23.27\% & 0.027 & 94.5\% & 0.651 \\
		& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 94.0\% & 0.611 \\
		& $\beta_3$ & 0.007 & 3.69\% & 8.88$*10^-5$ & 93.0\% & 0.034 \\
		\midrule
		\midrule
		\multirow{4}{*}{\parbox{2cm}{High \\Time Effect (N=60)}}
		& $\gamma_0$ & 0.170 & 3.69\% & 0.045 & 98.5\% & 0.888 \\
		& $\beta_1$ & 0.123 & 43.86\% & 0.024 & 96.0\% & 0.598 \\
		& $\beta_2$ & 0.124 & 19.35\% & 0.025 & 93.5\% & 0.575 \\
		& $\beta_3$ & 0.006 & 2.95\% & 5.50$*10^-5$ & 95.5\% & 0.030 \\
		\bottomrule
	\end{tabular}
\end{table}

Of note in the complete-data primary analysis is that the coverage of our 95\% CIs is larger than expected for our parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large. This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}. Nevertheless, we should keep this in mind when analyzing our results from the PM designs provided in Table \ref{tab:table3}. In Table \ref{tab:table3} as in Tables \ref{tab:table4}, \ref{tab:table5}, and \ref{tab:table6} bold values indicate "Unacceptable" results. That is, a Bias, Percent Bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.

\begin{table}[p]
	\centering
	\caption{Primary Simulation Results (N=60)}
	\setlength{\tabcolsep}{0.1cm}
	\label{tab:table3}
	\hspace*{-1cm}
	\begin{tabular}{c|c|c|cccccc}
		\toprule
		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
		\midrule
		\multirow{12}{*}{Split Form}
		& \multirow{4}{*}{Low(25\%)}
		& $\gamma_0$ & 0.151 & 6.59\% & 0.037 & 99.5\% & 0.753 & 0.009 \\
		&& $\beta_1$ & 0.139 & 24.78\% & 0.029 & 96.0\% & 0.693 & 0.112 \\
		&& $\beta_2$ & 0.120 & 9.41\% & 0.022 & 97.0\% & 0.610 & 0.002 \\
		&& $\beta_3$ & 0.007 & 3.42\% & 7.12$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(50\%)}
		& $\gamma_0$ & 0.153 & 6.67\% & 0.037 & 99.0\% & 0.765 & 0.040 \\
		&& $\beta_1$ & 0.162 & 28.93\% & 0.041 & 95.5\% & 0.869 & 0.390 \\
		&& $\beta_2$ & 0.121 & 9.51\% & 0.022 & 97.0\% & 0.616 & 0.007 \\
		&& $\beta_3$ & 0.007 & 3.40\% & 6.99$*10^-5$ & 98.5\% & 0.034 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(75\%)}
		& $\gamma_0$ & 0.154 & 6.70\% & 0.039 & 98.5\% & 0.818 & 0.147 \\
		&& $\beta_1$ & \textbf{0.225} & \textbf{40.16}\% & \textbf{0.076} & 97.5\% & 1.464 & 0.710 \\
		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 97.5\% & 0.611 & 0.022 \\
		&& $\beta_3$ & 0.007 & 3.42\% & 7.02$*10^-5$ & 98.0\% & 0.035 & 0.032 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
		& \multirow{4}{*}{Low(23.9\%)}
		& $\gamma_0$ & 0.151 & 6.57\% & 0.037 & 98.0\% & 0.753 & 0.008 \\
		&& $\beta_1$ & 0.137 & 24.55\% & 0.030 & 96.0\% & 0.690 & 0.105 \\
		&& $\beta_2$ & 0.120 & 9.39\% & 0.022 & 97.5\% & 0.611 & 0.002 \\
		&& $\beta_3$ & 0.007 & 3.42\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(47.8\%)}
		& $\gamma_0$ & 0.153 & 6.67\% & 0.038 & 99.5\% & 0.760 & 0.030 \\
		&& $\beta_1$ & 0.151 & 26.93\% & 0.036 & 96.0\% & 0.811 & 0.324 \\
		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 96.0\% & 0.611 & 0.006 \\
		&& $\beta_3$ & 0.007 & 3.44\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(71.7\%)}
		& $\gamma_0$ & 0.164 & 7.13\% & 0.042 & 98.0\% & 0.799 & 0.105 \\
		&& $\beta_1$ & \textbf{0.225} & \textbf{40.14\%} & \textbf{0.080} & 96.0\% & 1.265 & 0.640 \\
		&& $\beta_2$ & 0.117 & 9.13\% & 0.021 & 97.5\% & 0.615 & 0.019 \\
		&& $\beta_3$ & 0.007 & 3.46\% & 7.07$*10^-5$ & 98.0\% & 0.034 & 0.023 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
		& \multirow{4}{*}{Low(24.4\%)}
		& $\gamma_0$ & 0.152 & 6.61\% & 0.037 & 99.5\% & 0.757 & 0.023 \\
		&& $\beta_1$ & 0.147 & 26.25\% & 0.033 & 96.0\% & 0.767 & 0.270 \\
		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 96.0\% & 0.610 & 0.004 \\
		&& $\beta_3$ & 0.007 & 3.41\% & 6.97$*10^-5$ & 98.0\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(48.9\%)}
		& $\gamma_0$ & 0.157 & 6.84\% & 0.039 & 100.0\% & 0.767 & 0.052 \\
		&& $\beta_1$ & \textbf{0.190} & \textbf{33.95\%} & \textbf{0.058} & 94.5\% & 0.934 & 0.465 \\
		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 97.5\% & 0.609 & 0.008 \\
		&& $\beta_3$ & 0.007 & 3.34\% & 6.80$*10^-5$ & 98.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(73.3\%)}
		& $\gamma_0$ & 0.168 & 7.30\% & 0.045 & 99.5\% & 0.807 & 0.129 \\
		&& $\beta_1$ & \textbf{0.290} & \textbf{51.77\%} & \textbf{0.132} & \textbf{88.5\%} & 1.335 & 0.680 \\
		&& $\beta_2$ & 0.119 & 9.32\% & 0.022 & 96.0\% & 0.614 & 0.017 \\
		&& $\beta_3$ & 0.007 & 3.40\% & 6.96$*10^-5$ & 98.5\% & 0.034 & 0.025 \\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}[p]
	\centering
	\caption{Increased Sample Size simulation Results (N=120)}
	\setlength{\tabcolsep}{0.1cm}
	\label{tab:table4}
	\hspace*{-1cm}
	\begin{tabular}{c|c|c|cccccc}
		\toprule
		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
		\midrule
		\multirow{12}{*}{Split Form}
		& \multirow{4}{*}{Low(25\%)}
		& $\gamma_0$ & 0.106 & 4.60\% & 0.017 & 98.5\% & 0.533 & 0.022 \\
		&& $\beta_1$ & 0.106 & 18.96\% & 0.018 & 96.0\% & 0.548 & 0.263 \\
		&& $\beta_2$ & 0.091 & 7.14\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
		&& $\beta_3$ & 0.005 & 2.33\% & 3.47$*10^-5$ & 96.5\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(50\%)}
		& $\gamma_0$ & 0.112 & 4.85\% & 0.019 & 98.0\% & 0.542 & 0.057 \\
		&& $\beta_1$ & 0.134 & 23.86\% & \textbf{0.027} & 95.0\% & 0.696 & 0.489 \\
		&& $\beta_2$ & 0.092 & 7.15\% & 0.013 & 96.5\% & 0.430 & 0.009 \\
		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(75\%)}
		& $\gamma_0$ & 0.110 & 4.80\% & 0.019 & 99.5\% & 0.575 & 0.153 \\
		&& $\beta_1$ & \textbf{0.194} & \textbf{34.59\%} & \textbf{0.057} & 94.5\% & 1.088 & 0.742 \\
		&& $\beta_2$ & 0.092 & 7.20\% & 0.013 & 95.0\% & 0.432 & 0.021 \\
		&& $\beta_3$ & 0.005 & 2.31\% & 3.42$*10^-5$ & 97.5\% & 0.024 & 0.026 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
		& \multirow{4}{*}{Low(23.9\%)}
		& $\gamma_0$ & 0.107 & 4.64\% & 0.017 & 98.0\% & 0.533 & 0.022 \\
		&& $\beta_1$ & 0.111 & 19.80\% & 0.020 & 94.5\% & 0.545 & 0.263 \\
		&& $\beta_2$ & 0.091 & 7.08\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(47.8\%)}
		& $\gamma_0$ & 0.115 & 4.99\% & 0.020 & 98.0\% & 0.542 & 0.056 \\
		&& $\beta_1$ & 0.138 & 24.65\% & \textbf{0.028} & 94.5\% & 0.693 & 0.494 \\
		&& $\beta_2$ & 0.091 & 7.24\% & 0.013 & 96.0\% & 0.430 & 0.008 \\
		&& $\beta_3$ & 0.005 & 2.34\% & 3.54$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(71.7\%)}
		& $\gamma_0$ & 0.115 & 5.01\% & 0.020 & 99.0\% & 0.563 & 0.119 \\
		&& $\beta_1$ & \textbf{0.188} & \textbf{33.65\%} & \textbf{0.058} & 91.5\% & 0.958 & 0.681 \\
		&& $\beta_2$ & 0.092 & 7.16\% & 0.013 & 96.0\% & 0.432 & 0.018 \\
		&& $\beta_3$ & 0.005 & 2.30\% & 3.44$*10^-5$ & 96.0\% & 0.024 & 0.020 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
		& \multirow{4}{*}{Low(24.4\%)}
		& $\gamma_0$ & 0.108 & 4.72\% & 0.018 & 98.0\% & 0.533 & 0.024 \\
		&& $\beta_1$ & 0.123 & 21.90\% & \textbf{0.024} & 92.0\% & 0.551 & 0.287 \\
		&& $\beta_2$ & 0.092 & 7.18\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
		&& $\beta_3$ & 0.005 & 2.35\% & 3.51$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(48.9\%)}
		& $\gamma_0$ & 0.111 & 4.84\% & 0.019 & 99.0\% & 0.540 & 0.052 \\
		&& $\beta_1$ & \textbf{0.168} & \textbf{30.02\%} & \textbf{0.043} & \textbf{85.5\%} & 0.671 & 0.489 \\
		&& $\beta_2$ & 0.092 & 7.22\% & 0.013 & 95.0\% & 0.429 & 0.007 \\
		&& $\beta_3$ & 0.005 & 2.32\% & 3.42$*10^-5$ & 97.0\% & 0.024 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(73.3\%)}
		& $\gamma_0$ & 0.123 & 5.33\% & 0.023 & 99.0\% & 0.558 & 0.108 \\
		&& $\beta_1$ & \textbf{0.248} & \textbf{44.26\%} & \textbf{0.099} & \textbf{82.0\%} & 0.894 & 0.666 \\
		&& $\beta_2$ & 0.094 & 7.36\% & 0.014 & 96.0\% & 0.430 & 0.013 \\
		&& $\beta_3$ & 0.005 & 2.36\% & 3.53$*10^-5$ & 96.0\% & 0.024 & 0.015 \\
		\bottomrule
	\end{tabular}	
\end{table}
\begin{table}[p]
	\centering
	\caption{Low Inter-Survey Correlation Simulation Results (N=60)}
	\label{tab:table5}
	\setlength{\tabcolsep}{0.1cm}
	\hspace*{-1cm}
	\begin{tabular}{c|c|c|cccccc}
		\toprule
		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
		\midrule
		\multirow{12}{*}{Split Form}
		& \multirow{4}{*}{Low(25\%)}
		& $\gamma_0$ & 0.146 & 6.34\% & 0.033 & 99.0\% & 0.755 & 0.025 \\
		&& $\beta_1$ & 0.150 & 26.82\% & 0.034 & 95.5\% & 0.782 & 0.278 \\
		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.612 & 0.004 \\
		&& $\beta_3$ & 0.007 & 3.64\% & 8.68$*10^-5$ & 92.5\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(50\%)}
		& $\gamma_0$ & 0.148 & 6.43\% & 0.034 & 99.0\% & 0.772 & 0.067 \\
		&& $\beta_1$ & \textbf{0.183} & \textbf{32.65\%} & \textbf{0.053} & 95.0\% & 1.032 & 0.526 \\
		&& $\beta_2$ & 0.125 & 9.80\% & 0.026 & 94.0\% & 0.613 & 0.010 \\
		&& $\beta_3$ & 0.007 & 3.63\% & 8.73$*10^-5$ & 92.5\% & 0.035 & 0.015 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(75\%)}
		& $\gamma_0$ & 0.155 & 6.74\% & 0.036 & 99.5\% & 0.825 & 0.166 \\
		&& $\beta_1$ & \textbf{0.276} & \textbf{49.31\%} & \textbf{0.116} & 95.0\% & 1.567 & 0.749 \\
		&& $\beta_2$ & 0.124 & 9.71\% & 0.025 & 94.0\% & 0.618 & 0.025 \\
		&& $\beta_3$ & 0.007 & 3.61\% & 8.73$*10^-5$ & 93.5\% & 0.035 & 0.034 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
		& \multirow{4}{*}{Low(23.9\%)}
		& $\gamma_0$ & 0.141 & 6.13\% & 0.031 & 99.0\% & 0.754 & 0.023 \\
		&& $\beta_1$ & 0.139 & 25.80\% & 0.030 & 95.5\% & 0.772 & 0.260 \\
		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.612 & 0.004 \\
		&& $\beta_3$ & 0.007 & 3.61\% & 8.55$*10^-5$ & 92.5\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(47.8\%)}
		& $\gamma_0$ & 0.149 & 6.48\% & 0.035 & 99.5\% & 0.767 & 0.056 \\
		&& $\beta_1$ & 0.170 & 30.44\% & \textbf{0.044} & 97.0\% & 0.968 & 0.486 \\
		&& $\beta_2$ & 0.125 & 9.79\% & 0.025 & 93.5\% & 0.612 & 0.009 \\
		&& $\beta_3$ & 0.007 & 3.64\% & 8.58$*10^-5$ & 92.5\% & 0.034 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(71.7\%)}
		& $\gamma_0$ & 0.149 & 6.47\% & 0.036 & 98.5\% & 0.809 & 0.139 \\
		&& $\beta_1$ & \textbf{0.228} & \textbf{40.70\%} & \textbf{0.088} & 96.0\% & 1.425 & 0.708 \\
		&& $\beta_2$ & 0.125 & 9.74\% & 0.026 & 94.0\% & 0.617 & 0.021 \\
		&& $\beta_3$ & 0.007 & 3.62\% & 8.65$*10^-5$ & 93.5\% & 0.035 & 0.027 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
		& \multirow{4}{*}{Low(24.4\%)}
		& $\gamma_0$ & 0.138 & 6.02\% & 0.031 & 99.5\% & 0.754 & 0.025 \\
		&& $\beta_1$ & 0.158 & 28.17\% & 0.036 & 96.5\% & 0.776 & 0.286 \\
		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.611 & 0.004 \\
		&& $\beta_3$ & 0.007 & 3.61\% & 8.50$*10^-5$ & 92.5\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(48.9\%)}
		& $\gamma_0$ & 0.148 & 6.43\% & 0.034 & 99.5\% & 0.765 & 0.053 \\
		&& $\beta_1$ & \textbf{0.197} & \textbf{35.14\%} & \textbf{0.059} & 91.0\% & 0.939 & 0.472 \\
		&& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 93.5\% & 0.611 & 0.007 \\
		&& $\beta_3$ & 0.007 & 3.60\% & 8.48$*10^-5$ & 92.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(73.3\%)}
		& $\gamma_0$ & 0.158 & 6.86\% & 0.040 & 98.5\% & 0.799 & 0.122 \\
		&& $\beta_1$ & \textbf{0.303} & \textbf{54.18\%} &\textbf{0.148} & \textbf{89.5\%} & 1.290 & 0.676 \\
		&& $\beta_2$ & 0.127 & 9.94\% & 0.027 & 95.5\% & 0.615 & 0.015 \\
		&& $\beta_3$ & 0.007 & 3.62\% & 8.77$*10^-5$ & 93.5\% & 0.035 & 0.021 \\
		\bottomrule
	\end{tabular}	
\end{table}
\begin{table}[p]
	\centering
	\caption{High Time Effect Simulation Results (N=60)}
	\label{tab:table6}
	\setlength{\tabcolsep}{0.1cm}
	\hspace*{-1cm}
	\begin{tabular}{c|c|c|cccccc}
		\toprule
		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
		\midrule
		\multirow{12}{*}{Split Form}
		& \multirow{4}{*}{Low(25\%)}
		& $\gamma_0$ & 0.169 & 3.67\% & 0.045 & 99.0\% & 0.895 & 0.015 \\
		&& $\beta_1$ & 0.133 & 47.54\% & 0.029 & 96.0\% & 0.708 & 0.262 \\
		&& $\beta_2$ & 0.124 & 19.33\% & 0.025 & 93.5\% & 0.576 & 0.003 \\
		&& $\beta_3$ & 0.006 & 2.96\% & 5.50$*10^-5$ & 94.5\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(50\%)}
		& $\gamma_0$ & 0.174 & 3.77\% & 0.047 & 98.5\% & 0.912 & 0.050 \\
		&& $\beta_1$ & \textbf{0.181} & \textbf{64.59\%} & \textbf{0.049} & 96.0\% & 0.981 & 0.554 \\
		&& $\beta_2$ & 0.124 & 19.44\% & 0.025 & 94.0\% & 0.578 & 0.007 \\
		&& $\beta_3$ & 0.006 & 2.97\% & 5.55$*10^-5$ & 96.0\% & 0.030 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(75\%)}
		& $\gamma_0$ & 0.177 & 3.85\% & 0.049 & 98.0\% & 0.954 & 0.117 \\
		&& $\beta_1$ & \textbf{0.243} & \textbf{86.63\%} & \textbf{0.097} & 93.0\% & 1.433 & 0.729 \\
		&& $\beta_2$ & 0.124 & 19.37\% & 0.025 & 94.0\% & 0.581 & 0.016 \\
		&& $\beta_3$ & 0.006 & 2.97\% & 5.70$*10^-5$ & 94.0\% & 0.030 & 0.025 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
		& \multirow{4}{*}{Low(23.9\%)}
		& $\gamma_0$ & 0.171 & 3.72\% & 0.046 & 99.0\% & 0.895 & 0.015 \\
		&& $\beta_1$ & 0.142 & 50.55\% & 0.033 & 94.5\% & 0.717 & 0.272 \\
		&& $\beta_2$ & 0.124 & 19.36\% & 0.025 & 93.5\% & 0.577 & 0.002 \\
		&& $\beta_3$ & 0.006 & 2.95\% & 5.48$*10^-5$ & 95.5\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(47.8\%)}
		& $\gamma_0$ & 0.176 & 3.82\% & 0.048 & 99.0\% & 0.905 & 0.038 \\
		&& $\beta_1$ & 0.168 & 60.10\% & \textbf{0.043} & 95.5\% & 0.903 & 0.486 \\
		&& $\beta_2$ & 0.124 & 19.36\% & 0.025 & 93.5\% & 0.581 & 0.006 \\
		&& $\beta_3$ & 0.006 & 2.95\% & 5.60$*10^-5$ & 95.0\% & 0.030 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(71.7\%)}
		& $\gamma_0$ & 0.177 & 3.84\% & 0.051 & 99.5\% & 0.947 & 0.108 \\
		&& $\beta_1$ & \textbf{0.257} & \textbf{91.96\%} & \textbf{0.097} & 94.5\% & 1.381 & 0.714 \\
		&& $\beta_2$ & 0.124 & 19.34\% & 0.025 & 94.5\% & 0.581 & 0.014 \\
		&& $\beta_3$ & 0.006 & 3.01\% & 5.76$*10^-5$ & 95.0\% & 0.030 & 0.023 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
		& \multirow{4}{*}{Low(24.4\%)}
		& $\gamma_0$ & 0.170 & 3.70\% & 0.046 & 99.0\% & 0.895 & 0.016 \\
		&& $\beta_1$ & 0.135 & 48.11\% & 0.026 & 96.5\% & 0.720 & 0.290 \\
		&& $\beta_2$ & 0.124 & 19.40\% & 0.025 & 93.5\% & 0.576 & 0.002 \\
		&& $\beta_3$ & 0.006 & 2.94\% & 5.50$*10^-5$ & 95.0\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(48.9\%)}
		& $\gamma_0$ & 0.173 & 3.77\% & 0.047 & 99.0\% & 0.904 & 0.035 \\
		&& $\beta_1$ & \textbf{0.186} & \textbf{66.53\%} & \textbf{0.052} & 92.0\% & 0.864 & 0.466 \\
		&& $\beta_2$ & 0.124 & 19.40\% & 0.025 & 93.5\% & 0.576 & 0.004 \\
		&& $\beta_3$ & 0.006 & 2.94\% & 5.50$*10^-5$ & 96.0\% & 0.030 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(73.3\%)}
		& $\gamma_0$ & 0.188 & 4.09\% & 0.055 & 98.5\% & 0.946 & 0.105 \\
		&& $\beta_1$ & \textbf{0.322} & \textbf{115.10\%} & \textbf{0.149} & \textbf{85.5\%} & 1.306 & 0.712 \\
		&& $\beta_2$ & 0.127 & 19.87\% & 0.026 & 93.5\% & 0.580 & 0.011 \\
		&& $\beta_3$ & 0.006 & 3.02\% & 5.75$*10^-5$ & 95.0\% & 0.030 & 0.025 \\
		\bottomrule
	\end{tabular}
\end{table}

For the Split Form and Altered Split Form designs seen in Table \ref{tab:table3}, we note that the greatest loss in efficiency was on the $\beta_1$ estimate. While the CI coverage remained high at all levels of missingness for the two designs the bias, percent bias, and MSE reached unacceptable levels at the high missingness level. We also point out that the Altered Split Form design did not perform significantly better than the regular Split Form design. While some individual measurements outperformed those from the Split Form design, bias on $\beta_1$ for example, it underperformed in others, such as percent bias on $\beta_3$. In reference to the FMI on the $\beta_1$ estimate, we can see that at low and medium missingness both Split Form designs performed well. That is to say, there was less variance in the results from our imputed datasets than we expected given the amount of missing data.\par

Towards the bottom of Table \ref{tab:table3} we see that the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at medium and high levels of missingness. Moreover, at high levels of missingness even coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.  Additionally, we see that CI length for the $\beta_1$ estimate was roughly equal across all designs, despite the fact that the Wave Missingness design provided more biased estimates. \par

\subsection{Increased Sample Size}
\label{sec:3.2}
The next simulation scenario we tested was under an increased sample size. All parameter values were held the same as in the original set of simulations but instead of simulating data for 60 participants here we used 120 participants. Table \ref{tab:table2}, again, contains the results of our analysis before applying any PM design. \par

We compare the results from the full-data simulations to those obtained from the PM designs, shown in Table \ref{tab:table4}. The first thing we notice is that the bias on all parameters is lower than it was in the smaller sample size simulations. Next, the Split Form design performed similarly well under this simulation scenario as in the first. At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable. However, the CI length here is relatively far from the complete-data measurement in Table \ref{tab:table2}. The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088. We also point out that the percent bias on the $\beta_1$ estimate is not seriously different from that obtained in the small sample scenario. For example, at medium levels of missingness the percent bias on $\beta_1$ here is 23.86\% while for the smaller sample it was 23.75\%.
Similarly to the Split Form design, the Altered Split Form Design also provided unacceptable results for the MSE of the $\beta_1$ estimate at medium missingness and unacceptable bias, percent bias, and MSE at high levels.  \par
For the Wave Missingness design we continue to see the issues pointed out in the small sample simulations. That is, for the $\beta_1$ estimate we have unacceptable measurements at medium and high levels of missingness and a steep drop off in coverage probability for our 95\% CIs. In fact, at medium and high levels of missingness we find coverages of 85.5\% and 82.0\%. We also continue to see that the $\gamma_0$ parameter is being estimated poorly at high levels of missing data under the Wave Missingness design. \par

\subsection{Low Inter-Survey Correlation}
\label{sec:3.3}
For the next set of simulations we returned to the smaller sample size but decreased the level of inter-survey correlation. As mentioned in section 3.2.2 we made sure that there was no direct predictive relationship between questions in our survey. The results obtained from our full data simulations are provided in Table \ref{tab:table2} while the results from our PM designs are given in Table \ref{tab:table5}. \par

For the Split Form design it is important to notice that the efficiency of the $\beta_1$ estimate decreases much more rapidly than in our first set of simulations where survey questions were predictive of one another. For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be 0.150 and 0.276 at high levels. This left us with an increase in average bias of 0.126. If we check the same increase in the original simulations we see that the bias only increased by 0.071. This loss in efficiency is seen in the other measurements on the $\beta_1$ estimate as well. Moreover, we note that the Split Form design performs unacceptably in terms of bias, percent bias, and MSE at medium levels of missingness. This was not the case in the other missingness scenarios. \par

In the Altered Split Form design at medium levels of missingness the MSE is outside of the acceptable range and at high levels bias, are percent bias are unacceptable as well. We further note that the coverage of the $\beta_1$ CIs was quite a bit higher than in the full-data simulations. That is, while the coverage probability obtained in the full-data simulations was 94.5\%, under this Altered Split Form design we obtained coverages of 95.5\%, 97.0\%, and 96.0\% at low, medium, and high levels of missingness respectively. \par

Concerning the Wave Missingness design we, again, see the issues of unacceptable bias, percent bias and MSE. However, at low levels of missingness the coverage of our $\beta_1$ estimate was fairly good (96.5\% compared to 94.5\% in the full data). This positive coverage did not hold throughout the other levels of missingness as coverage dropped to 89.5\% in the high missingness scenario. As in other scenarios, the CI lengths produced under the Wave Missingness design are similar to those produced in the Split Form designs despite an increase in bias. However, this increase in bias is less dramatic than in other scenarios. For example, at high levels of missingness in the original simulations the average bias on the $\beta_1$ estimate was 0.065 higher for the Wave Missingness design (at 0.290) than in the Split Form design (0.225). In this simulation scenario that same difference was only 0.027. Moreover, while the estimation of $\gamma_0$ was unacceptable at high levels of missingness in the other simulation scenarios, here it was in the acceptable range.\par

\subsection{High Time Effect}
\label{sec:3.4}
In the final scenario we tested to see how the PM designs would capture a model where time had a disproportionately large effect. In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$. The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:table6}. \par

The effects of imposing Split Form missingness in this high time effect scenario are similar to those under the low inter-survey correlation scenario. At low levels of missingness bias, percent bias, MSE, and coverage for $\beta_1$ are all within the acceptable range. At medium and high levels of missingness bias, percent bias, and MSE are unacceptably high. \par

The Altered Split Form design performed slightly better than the normal Split Form design under this simulation scenario. We do note, though, that while the normal Split Form design provided unacceptable bias and percent bias for the $\beta_1$ estimate at medium levels of missingness, this was not true in the Altered Split Form design. Additionally, we point out that at medium and high levels of missingness we saw an improvement from the Split Form design in the CI lengths for the $\beta_1$ estimate. In the Split Form design the CI lengths were recorded as 0.981 and 1.433 at medium and high missingness. Under the Altered Split Form design these measurements were 0.903 and 1.381. \par

Under this simulation scenario, at low levels of missingness we see that the Wave Missingness Design performs similarly to the Split Form and Altered Split Form designs. The bias, percent bias, MSE, and CI coverage for $\beta_1$ all performed acceptably using the Wave Missingness design at low levels of missingness. Moreover, as missingness increases this design shows itself to be unsuitable in terms of estimating $\beta_1$ for the same reasons noted in the other scenarios. \par

\subsection{Interpretation}
\label{sec:3.5}
We note two commonalities throughout our simulation scenarios. The first is that the Altered Split Form design consistently failed to produce better results than the normal Split Form design. Secondly, the Wave Missingness Design resulted in unacceptably poor estimation for anything but low levels of missingness. \par

This first result, the lack of improvement seen in the Altered Split form design is surprising. By keeping a small number of measurement occasions fully observed we would have expected the imputation process to perform more effectively and improve our estimates. However, even factoring in the slight decrease in overall missingness, this design performed only equally as well as the normal Split Form design. This may be a result of the fact that the number of observations we left fully observed was small, only two out of the forty-five days (or about 4.4\% of days) were fully observed. While it may be interesting to see if the inclusion of more fully observed days is capable of improving our estimates, perhaps keeping five days (11.1\%) fully observed, we would need to be careful about raising this number too high. If the cost or burden of observations is a limiting factor then collecting full data on even 10\% of the days may be unnecessarily burdensome. \par

Of larger concern, though, is the steep drop-off in estimating quality of the Wave Missingness design as missingness increased. In every scenario we tested, the Wave Missingness design produced unacceptable bias, percent bias, and MSE at medium and high levels of missingness. We also note that despite increased bias on estimates with missing values, the length of confidence intervals for these estimates remained the same as in the Split Form design. This implies that there is an underestimation of our variances occurring at some point in the imputation process. This is supported by the fact that, generally, the fraction of missing information estimated in the Wave Missingness design tended to be smaller than that of the corresponding Split Form design. This can also explain the low confidence interval coverages we obtained using this design. At high levels of missingness none of the scenarios allowed the Wave Missingness design to obtain coverages above 90\%. This leads us to believe that many of the imputations are producing datasets which are similar in terms of the relationships between variables but that are not representative of the true relationships. Because of this we cannot recommend the use of Wave Missingness designs for anything but small levels of missing data. \par

Additionally, all PM designs under all scenarios performed within acceptable ranges when measuring the effects of variables which had no missing values ($\gamma_0, \beta_2, \beta_3$). This fact makes the increased sample size scenario promising for researchers. While our estimation of $\beta_1$ was similar in this scenario as in others, the estimation of the other model parameters improved by leaps and bounds. If a PM design is able to reduce costs by 50\% by introducing missingness, using these extra funds to recruit more participants may be a good idea for researchers who's analysis of interest involves variables that will not have missing values. \par

\section{Discussion}
\label{4}
In this paper we performed a simulation study to test the ability of different PM designs to capture a multilevel logistic model under a longitudinal framework. We found that for low levels of planned missing data (about 25\% missingness) variations of the Split Form design and the Wave Missingness designs are all capable of estimating the parameters of the multilevel model reasonably well. As the level of missing data increases to 50\% and 75\%, though, the quality of estimates in all of the tested PM designs become unacceptable as we see rising parameter biases and confidence interval lengths. Moreover, we found that the quality of the Wave Missingness design depreciates much more rapidly than the other PM designs, providing higher parameter biases than the corresponding Split Form estimates and low confidence interval coverages (95\% confidence intervals with less than 90\% coverage in some cases). \par

These facts lead us to recommend against the use of Wave Missingness designs when the Split Form design can be easily substituted. If Wave Missingness must be used, as in the Cohort Sequential and Developmental Time-Lag designs, we suggest that the design minimizes the amount of missing data. For instance, in a Cohort Sequential design which attempts to stretch four-year data to cover a span of six years each cohort will have missing values at two of the six measurement occasions. This would result in about 33.3\% missingness. To ensure that the researcher's analyses are accurate, we would recommend an increase in the amount of time they follow participants, using five-year data instead of four-year data to cover the same period. While the recommendation to use low levels of missing data is especially true for Wave Missingness designs it also holds for the Split Form designs. While these designs tended to perform well for all parameters in the multilevel model at low levels of missingness this was not true when missingness was increased to around 50\%. \par

For future research it may be useful to test a wider range of missingness. That is, while our study showed that the PM designs performed well when missingness was around 25\% and sometimes performed poorly when it was around 50\% we do not know exactly when the estimation procedure breaks down. While we can only recommend 25\% missing data here, if it was shown that these designs performed well at 40\% missingness, then researchers could substantially increase cost reduction and decrease participant burden beyond what our recommendations allow. Another worthwhile pursuit may be to see how hybrid PM designs perform. While we found that Wave Missingness designs performed underwhelmingly it would be interesting to see how a design which had some days fully missing and the remaining days missing on some values would have performed. In particular, looking into this result may be useful to researchers who wish to implement an accelerated longitudinal design but also have measures that are costly or burdensome which they would like to limit the collection of. \par

To conclude we discuss the limitations of this analysis. The results we obtained from our PM designs were obtained through multiple imputation with five imputations. While this may be sufficient for low levels of missingness, it is not appropriate for some of the high levels of missingness that we tested. We chose to use such a low number of imputations because of the size of the data we had and our computational limitations. Simulating two hundred samples, each with ten variants, and then imputing five completed datasets for every variant with a missing value resulted in 9200 datasets. Then, under the four different simulation scenarios this number grew to 36,800 datasets. Factoring in the fact that each of these datasets contained at least 2700 observations (60 participants for 45 days, more for the large sample scenario) we were left with more than one-hundred million rows of data to analyze. This also led to another of the limitations we faced, using only two hundred simulated samples. While using more simulations would have allowed us to obtain more stable estimates on bias or coverage, adding in more would have added to our computational difficulties. In the future, this problem could be alleviated through the use of parallel computing through a computer cluster. \par

We hope that the results of this paper will serve to help researchers decide which PM design is most appropriate for their studies' needs. By illuminating the weaknesses of the Wave Missingness design we hope that when Wave missingness is not explicitly required researchers will opt instead to use a Split Form design. Moreover, when researchers do implement a PM design we hope they follow our recommendation to err on the side of caution and keep the amount of missing data relatively low. \par

%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliographystyle{plainnat}
\bibliography{citations}   % name your BibTeX data base

\end{document}

### 2018-02-22 1-25.R

@@ -1,0 +1,46 @@
+library(mice)
+library(lme4)
+library(mvtnorm)
+library(lmerTest)
+
+Daily <- read.csv("C:/Users/Josie/Dropbox/DesignedMissingness/Daily with Tox.csv")
+
+names(Daily)[1] <- c('PID')
+Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7',
+                  'MissedDose', 'ZEduc', 'ZIncom45', 'Gender','Age', 
+                  'ZAlcTox','ZCESDFU', 'ZAUDIT', 'DrinkYN')]
+
+comp <- complete(mice(Daily, m=1, seed=817236),1)
+comp$Age <- as.numeric(comp$Age)
+comp$Day <- comp$Day-1
+rm(Daily)
+
+comp$Age <- as.numeric(scale(comp$Age))
+comp$Q1 <- as.factor(comp$Q1)
+comp$Q2 <- as.factor(comp$Q2)
+comp$Q3 <- as.factor(comp$Q3)
+comp$Q4 <- as.factor(comp$Q4)
+comp$Q5 <- as.factor(comp$Q5)
+comp$Q6 <- as.factor(comp$Q6)
+comp$Q7 <- as.integer(comp$Q7)
+comp$DrinkYN <- as.factor(comp$DrinkYN)
+comp$MissedDose <- as.factor(comp$MissedDose)
+comp$Gender <- as.factor(comp$Gender)
+
+fitMD <- glm(data=comp, MissedDose ~ DrinkYN + ZAlcTox + Day, family=binomial(link=logit))
+fitranMD <- glmer(data=comp, MissedDose ~ DrinkYN + ZAlcTox + Day + (1|PID), family=binomial(link=logit))
+
+#Find fit to simulate
+fit1 <- glm(data=comp, DrinkYN~ZIncom45+Age+ZAlcTox+ZAUDIT, family=binomial(link=logit))
+fit2<- glm(data=comp, Q1~ZEduc+ZIncom45+ZAlcTox+ZCESDFU, family=binomial(link=logit))
+fit3<- glm(data=comp, Q2~Q1+ZEduc+ZIncom45+Age+ZAlcTox
+           +ZCESDFU+ZAUDIT+Gender, family=binomial(link=logit))
[…]

### 2018-02-22 Code Rework 02-07-18.R

@@ -1,0 +1,147 @@
+
+# Install needed packages, if necessary
+# install.packages(c('lme4','mvtnorm','lmerTest'))
+
+# Set working directory
+setwd("/Users/devjyw/Dropbox/Research/DesignedMissingness/")
+
+# Load necessary libraries
+library(mice)
+library(lme4)
+library(mvtnorm)
+library(lmerTest)
+
+# Read in Daily With Tox CSV data file
+Daily <- read.csv('/Users/devjyw/Dropbox/Research/DesignedMissingness/Daily with Tox.csv')
+
+# Retain desired variables
+Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7'
+                  ,'MissedDose'
+                  , 'ZEduc', 'ZIncom45', 'Gender', 'Age', 'ZAlcTox'
+                  ,'ZCESDFU', 'ZAUDIT', 'DrinkYN')]
+
+# Impute missing values in new dataset, 'comp'...Daily has 4.74% missing (sum(is.na(Daily))/prod(dim(Daily)))
+comp <- complete(mice(Daily, m=1, seed=817236),1)
+# Convert Age to data type 'double'
+comp$Age <- as.numeric(comp$Age)
+# Shift days back 1 day
+comp$Day <- comp$Day-1
+# Remove the Daily dataset from the environment
+#rm(Daily)
+
+#comp$Age <- as.numeric(scale(comp$Age)) # why???
+comp$Q1 <- as.factor(comp$Q1)
+comp$Q2 <- as.factor(comp$Q2)
+comp$Q3 <- as.factor(comp$Q3)
+comp$Q4 <- as.factor(comp$Q4)
+comp$Q5 <- as.factor(comp$Q5)
+comp$Q6 <- as.factor(comp$Q6)
+comp$Q7 <- as.integer(comp$Q7)
+comp$DrinkYN <- as.factor(comp$DrinkYN)
+comp$MissedDose <- as.factor(comp$MissedDose)
+comp$Gender <- as.factor(comp$Gender)
+
+# Correlation Matrix
+# Use model.matrix to convert factor variables to dummy encoding
+# Matches OG matrix!!!
[…]

### 2018-02-22 thesis_code_GREG.R

@@ -1,0 +1,426 @@
+#setwd('C:/Users/Nicholas/Documents/Thesis')
+setwd("/Users/gregorymatthews/Dropbox/DesignedMissingness/")
+library(mice)
+library(lme4)
+library(mvtnorm)
+library(lmerTest)
+
+Daily <- read.csv('Daily with Tox.csv')
+names(Daily)[1] <- c('PID')
+Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7'
+                  ,'MissedDose'
+                  , 'ZEduc', 'ZIncom45', 'Gender', 'Age', 'ZAlcTox'
+                  ,'ZCESDFU', 'ZAUDIT', 'DrinkYN')]
+
+
+comp <- complete(mice(Daily, m=1, seed=817236),1)
+comp$Age <- as.numeric(comp$Age)
+comp$Day <- comp$Day-1
+rm(Daily)
+
+comp$Age <- as.numeric(scale(comp$Age))
+comp$Q1 <- as.factor(comp$Q1)
+comp$Q2 <- as.factor(comp$Q2)
+comp$Q3 <- as.factor(comp$Q3)
+comp$Q4 <- as.factor(comp$Q4)
+comp$Q5 <- as.factor(comp$Q5)
+comp$Q6 <- as.factor(comp$Q6)
+comp$Q7 <- as.integer(comp$Q7)
+comp$DrinkYN <- as.factor(comp$DrinkYN)
+comp$MissedDose <- as.factor(comp$MissedDose)
+comp$Gender <- as.factor(comp$Gender)
+
+#Find fit to simulate
+fit1 <- glm(data=comp, DrinkYN~ZIncom45+Age+ZAlcTox+ZAUDIT, family=binomial(link=logit))
+fit2<- glm(data=comp, Q1~ZEduc+ZIncom45+ZAlcTox+ZCESDFU, family=binomial(link=logit))
+fit3<- glm(data=comp, Q2~Q1+ZEduc+ZIncom45+Age+ZAlcTox
+           +ZCESDFU+ZAUDIT+Gender, family=binomial(link=logit))
+fit4<- glm(data=comp, Q3~Q1+Q2+ZEduc+ZIncom45+ZAlcTox
+           +ZCESDFU+Gender, family=binomial(link=logit))
+fit5<- glm(data=comp, Q4~Q1+Q2+Q3+ZEduc+ZAlcTox
[…]

### 2018-02-22 Code Rework 02-22-18.R
New changes
Changed working directory, attempted to fix the split.form() function, and added the beginnings of a alt.split() function.

@@ -1,0 +1,467 @@
+
+# Install needed packages, if necessary
+# install.packages(c('lme4','mvtnorm','lmerTest'))
+
+# Set working directory
+setwd("~/GitHub/designedmissingness/")
+
+# Load necessary libraries
+library(mice)
+library(lme4)
+library(mvtnorm)
+library(lmerTest)
+
+# Read in Daily With Tox CSV data file
+Daily <- read.csv('~/GitHub/designedmissingness/Daily with Tox.csv')
+
+# Retain desired variables
+names(Daily)[1] <- c('PID')
+Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7'
+                  ,'MissedDose'
+                  , 'ZEduc', 'ZIncom45', 'Gender', 'Age', 'ZAlcTox'
+                  ,'ZCESDFU', 'ZAUDIT', 'DrinkYN')]
+
+# Impute missing values in new dataset, 'comp'...Daily has 4.74% missing (sum(is.na(Daily))/prod(dim(Daily)))
+comp <- complete(mice(Daily, m=1, seed=817236),1)
+# Convert Age to data type 'double'
+comp$Age <- as.numeric(comp$Age)
+# Shift days back 1 day
+comp$Day <- comp$Day-1
+# Remove the Daily dataset from the environment
+rm(Daily)
+
+#comp$Age <- as.numeric(scale(comp$Age)) # why???
+comp$Q1 <- as.factor(comp$Q1)
+comp$Q2 <- as.factor(comp$Q2)
+comp$Q3 <- as.factor(comp$Q3)
+comp$Q4 <- as.factor(comp$Q4)
+comp$Q5 <- as.factor(comp$Q5)
+comp$Q6 <- as.factor(comp$Q6)
+comp$Q7 <- as.integer(comp$Q7)
+comp$DrinkYN <- as.factor(comp$DrinkYN)
+comp$MissedDose <- as.factor(comp$MissedDose)
+comp$Gender <- as.factor(comp$Gender)
+
+# Correlation Matrix
+# Use model.matrix to convert factor variables to dummy encoding
+# Matches OG matrix!!!
[…]

### 2018-02-24 Code Rework.R
Saving .RHistory

@@ -1,0 +1,488 @@
+
+# Install needed packages, if necessary
+# install.packages(c('lme4','mvtnorm','lmerTest'))
+
+# Set working directory
+setwd("~/GitHub/designedmissingness/")
+
+# Load necessary libraries
+library(mice)
+library(lme4)
+library(mvtnorm)
+library(lmerTest)
+
+# Read in Daily With Tox CSV data file
+Daily <- read.csv('~/GitHub/designedmissingness/Daily with Tox.csv')
+
+# Retain desired variables
+names(Daily)[1] <- c('PID')
+Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7'
+                  ,'MissedDose'
+                  , 'ZEduc', 'ZIncom45', 'Gender', 'Age', 'ZAlcTox'
+                  ,'ZCESDFU', 'ZAUDIT', 'DrinkYN')]
+
+# Impute missing values in new dataset, 'comp'...Daily has 4.74% missing (sum(is.na(Daily))/prod(dim(Daily)))
+comp <- complete(mice(Daily, m=1, seed=817236),1)
+# Convert Age to data type 'double'
+comp$Age <- as.numeric(comp$Age)
+# Shift days back 1 day
+comp$Day <- comp$Day-1
+# Remove the Daily dataset from the environment
+rm(Daily)
+
+#comp$Age <- as.numeric(scale(comp$Age)) # why???
+comp$Q1 <- as.factor(comp$Q1)
+comp$Q2 <- as.factor(comp$Q2)
+comp$Q3 <- as.factor(comp$Q3)
+comp$Q4 <- as.factor(comp$Q4)
+comp$Q5 <- as.factor(comp$Q5)
+comp$Q6 <- as.factor(comp$Q6)
+comp$Q7 <- as.integer(comp$Q7)
+comp$DrinkYN <- as.factor(comp$DrinkYN)
+comp$MissedDose <- as.factor(comp$MissedDose)
+comp$Gender <- as.factor(comp$Gender)
+
+# Correlation Matrix
+# Use model.matrix to convert factor variables to dummy encoding
+# Matches OG matrix!!!
[…]

### 2018-03-22 1-25.R
Changes

@@ -1,46 +1,0 @@
-library(mice)
-library(lme4)
-library(mvtnorm)
-library(lmerTest)
-
-Daily <- read.csv("C:/Users/Josie/Dropbox/DesignedMissingness/Daily with Tox.csv")
-
-names(Daily)[1] <- c('PID')
-Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7',
-                  'MissedDose', 'ZEduc', 'ZIncom45', 'Gender','Age', 
-                  'ZAlcTox','ZCESDFU', 'ZAUDIT', 'DrinkYN')]
-
-comp <- complete(mice(Daily, m=1, seed=817236),1)
-comp$Age <- as.numeric(comp$Age)
-comp$Day <- comp$Day-1
-rm(Daily)
-
-comp$Age <- as.numeric(scale(comp$Age))
-comp$Q1 <- as.factor(comp$Q1)
-comp$Q2 <- as.factor(comp$Q2)
-comp$Q3 <- as.factor(comp$Q3)
-comp$Q4 <- as.factor(comp$Q4)
-comp$Q5 <- as.factor(comp$Q5)
-comp$Q6 <- as.factor(comp$Q6)
-comp$Q7 <- as.integer(comp$Q7)
-comp$DrinkYN <- as.factor(comp$DrinkYN)
-comp$MissedDose <- as.factor(comp$MissedDose)
-comp$Gender <- as.factor(comp$Gender)
-
-fitMD <- glm(data=comp, MissedDose ~ DrinkYN + ZAlcTox + Day, family=binomial(link=logit))
-fitranMD <- glmer(data=comp, MissedDose ~ DrinkYN + ZAlcTox + Day + (1|PID), family=binomial(link=logit))
-
-#Find fit to simulate
-fit1 <- glm(data=comp, DrinkYN~ZIncom45+Age+ZAlcTox+ZAUDIT, family=binomial(link=logit))
-fit2<- glm(data=comp, Q1~ZEduc+ZIncom45+ZAlcTox+ZCESDFU, family=binomial(link=logit))
-fit3<- glm(data=comp, Q2~Q1+ZEduc+ZIncom45+Age+ZAlcTox
-           +ZCESDFU+ZAUDIT+Gender, family=binomial(link=logit))
[…]

### 2018-03-22 Code Rework 02-15-18.R

@@ -1,153 +1,0 @@
-
-# Install needed packages, if necessary
-# install.packages(c('lme4','mvtnorm','lmerTest'))
-
-# Set working directory
-setwd("~/Dropbox/Research/DesignedMissingness/")
-
-# Load necessary libraries
-library(mice)
-library(lme4)
-library(mvtnorm)
-library(lmerTest)
-
-# Read in Daily With Tox CSV data file
-Daily <- read.csv('~/Dropbox/Research/DesignedMissingness/Daily with Tox.csv')
-
-# Retain desired variables
-names(Daily)[1] <- c('PID')
-Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7'
-                  ,'MissedDose'
-                  , 'ZEduc', 'ZIncom45', 'Gender', 'Age', 'ZAlcTox'
-                  ,'ZCESDFU', 'ZAUDIT', 'DrinkYN')]
-
-# Impute missing values in new dataset, 'comp'...Daily has 4.74% missing (sum(is.na(Daily))/prod(dim(Daily)))
-comp <- complete(mice(Daily, m=1, seed=817236),1)
-# Convert Age to data type 'double'
-comp$Age <- as.numeric(comp$Age)
-# Shift days back 1 day
-comp$Day <- comp$Day-1
-# Remove the Daily dataset from the environment
-rm(Daily)
-
-#comp$Age <- as.numeric(scale(comp$Age)) # why???
-comp$Q1 <- as.factor(comp$Q1)
-comp$Q2 <- as.factor(comp$Q2)
-comp$Q3 <- as.factor(comp$Q3)
-comp$Q4 <- as.factor(comp$Q4)
-comp$Q5 <- as.factor(comp$Q5)
-comp$Q6 <- as.factor(comp$Q6)
-comp$Q7 <- as.integer(comp$Q7)
-comp$DrinkYN <- as.factor(comp$DrinkYN)
-comp$MissedDose <- as.factor(comp$MissedDose)
-comp$Gender <- as.factor(comp$Gender)
-
-# Correlation Matrix
-# Use model.matrix to convert factor variables to dummy encoding
-# Matches OG matrix!!!
[…]

### 2018-03-22 Code/Code Rework 02-15-18.R

@@ -1,0 +1,153 @@
+
+# Install needed packages, if necessary
+# install.packages(c('lme4','mvtnorm','lmerTest'))
+
+# Set working directory
+setwd("~/Dropbox/Research/DesignedMissingness/")
+
+# Load necessary libraries
+library(mice)
+library(lme4)
+library(mvtnorm)
+library(lmerTest)
+
+# Read in Daily With Tox CSV data file
+Daily <- read.csv('~/Dropbox/Research/DesignedMissingness/Daily with Tox.csv')
+
+# Retain desired variables
+names(Daily)[1] <- c('PID')
+Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7'
+                  ,'MissedDose'
+                  , 'ZEduc', 'ZIncom45', 'Gender', 'Age', 'ZAlcTox'
+                  ,'ZCESDFU', 'ZAUDIT', 'DrinkYN')]
+
+# Impute missing values in new dataset, 'comp'...Daily has 4.74% missing (sum(is.na(Daily))/prod(dim(Daily)))
+comp <- complete(mice(Daily, m=1, seed=817236),1)
+# Convert Age to data type 'double'
+comp$Age <- as.numeric(comp$Age)
+# Shift days back 1 day
+comp$Day <- comp$Day-1
+# Remove the Daily dataset from the environment
+rm(Daily)
+
+#comp$Age <- as.numeric(scale(comp$Age)) # why???
+comp$Q1 <- as.factor(comp$Q1)
+comp$Q2 <- as.factor(comp$Q2)
+comp$Q3 <- as.factor(comp$Q3)
+comp$Q4 <- as.factor(comp$Q4)
+comp$Q5 <- as.factor(comp$Q5)
+comp$Q6 <- as.factor(comp$Q6)
+comp$Q7 <- as.integer(comp$Q7)
+comp$DrinkYN <- as.factor(comp$DrinkYN)
+comp$MissedDose <- as.factor(comp$MissedDose)
+comp$Gender <- as.factor(comp$Gender)
+
+# Correlation Matrix
+# Use model.matrix to convert factor variables to dummy encoding
+# Matches OG matrix!!!
[…]

### 2018-03-22 Code/Code Rework.R

@@ -197,11 +197,22 @@ split.pm <- lapply(sim.data,function(x){split.form(x,grps)})
 wave.pm <- lapply(sim.data,function(x){wave.des(x,11)})
 
 # Step 2 - Impute simulated datasets, for both methods
-split.imp <- lapply(split.pm, function(x) {mice(x, m=5)})
-split.data <- lapply(split.imp,function(x) {complete(x,1)})
+split.imp <- lapply(split.pm, function(x) {mice(x, m=5)}) # loop through the split.imps in the complete function
+split.data <- rep(NA,length(split.imp))
+for (i in 1:length(split.imp)){
+  split.data[i] <- list(lapply(split.imp,function(x) {complete(x,i)}))
+}
+
+s1 <- data.frame(split.data[1][1])
+s3 <- data.frame(split.data[3][1]) # very similar, but I guess that is obvious as the missingness isn't a lot
+w1 <- data.frame(wave.data[1][1])
+
 
 wave.imp <- lapply(wave.pm, function(x) {mice(x, m=5)})
-wave.data <- lapply(wave.imp,function(x) {complete(x,1)})
+wave.data <- rep(NA,length(wave.imp))
+for (i in 1:length(wave.imp)){
+  wave.data[i] <- list(lapply(wave.imp,function(x) {complete(x,i)}))
+}
 
 # for(j in c(2,4,6)) { # 2, 4, 6? Why?
 #   new.data <-lapply(sim.data, function(x) {split.form(x, grps)})
@@ -227,29 +238,40 @@ wave.data <- lapply(wave.imp,function(x) {complete(x,1)})
 # }
 
 # Step 3 - Build models from imputed simulation data for both methods
-set.seed(12345)
-splitmods <- list()
-for (i in 1:length(split.data)){
-  dat <- data.frame(split.data[i])
-  model <- glm(MissedDose ~ DrinkYN*Day + ZAlcTox, data = dat, family=binomial(link=logit))
-  # No "+ (1|PID)" because the data doesn't have PID, it indexes the rows as 1,1.1,1.2,...,2,2.1,2.2,...Change this?
-  splitmods[i] <- data.frame(model$coefficients)
+# Result: a list of lists of model coefficients for each method
+# Coefficient order: Intercept, DrinkYN2, Day, ZAlcTox, and DrinkYN2:Day
+
+mod.maker <- function(dat){
+  mods <- NULL
+  for (i in 1:length(split.pm)){
[…]

### 2018-03-22 Code/thesis_code.R

@@ -1,0 +1,424 @@
+setwd('C:/Users/Nicholas/Documents/Thesis')
+library(mice)
+library(lme4)
+library(mvtnorm)
+library(lmerTest)
+
+Daily <- read.csv('Daily with Tox.csv')
+names(Daily)[1] <- c('PID')
+Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7'
+                  ,'MissedDose'
+                  , 'ZEduc', 'ZIncom45', 'Gender', 'Age', 'ZAlcTox'
+                  ,'ZCESDFU', 'ZAUDIT', 'DrinkYN')]
+
+
+comp <- complete(mice(Daily, m=1, seed=817236),1)
+comp$Age <- as.numeric(comp$Age)
+comp$Day <- comp$Day-1
+rm(Daily)
+
+comp$Age <- as.numeric(scale(comp$Age))
+comp$Q1 <- as.factor(comp$Q1)
+comp$Q2 <- as.factor(comp$Q2)
+comp$Q3 <- as.factor(comp$Q3)
+comp$Q4 <- as.factor(comp$Q4)
+comp$Q5 <- as.factor(comp$Q5)
+comp$Q6 <- as.factor(comp$Q6)
+comp$Q7 <- as.integer(comp$Q7)
+comp$DrinkYN <- as.factor(comp$DrinkYN)
+comp$MissedDose <- as.factor(comp$MissedDose)
+comp$Gender <- as.factor(comp$Gender)
+
+#Find fit to simulate
+fit1 <- glm(data=comp, DrinkYN~ZIncom45+Age+ZAlcTox+ZAUDIT, family=binomial(link=logit))
+fit2<- glm(data=comp, Q1~ZEduc+ZIncom45+ZAlcTox+ZCESDFU, family=binomial(link=logit))
+fit3<- glm(data=comp, Q2~Q1+ZEduc+ZIncom45+Age+ZAlcTox
+           +ZCESDFU+ZAUDIT+Gender, family=binomial(link=logit))
+fit4<- glm(data=comp, Q3~Q1+Q2+ZEduc+ZIncom45+ZAlcTox
+           +ZCESDFU+Gender, family=binomial(link=logit))
+fit5<- glm(data=comp, Q4~Q1+Q2+Q3+ZEduc+ZAlcTox
+           +ZCESDFU+ZAUDIT+Gender, family=binomial(link=logit))
[…]

### 2018-03-22 thesis_code.R

@@ -1,424 +1,0 @@
-setwd('C:/Users/Nicholas/Documents/Thesis')
-library(mice)
-library(lme4)
-library(mvtnorm)
-library(lmerTest)
-
-Daily <- read.csv('Daily with Tox.csv')
-names(Daily)[1] <- c('PID')
-Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7'
-                  ,'MissedDose'
-                  , 'ZEduc', 'ZIncom45', 'Gender', 'Age', 'ZAlcTox'
-                  ,'ZCESDFU', 'ZAUDIT', 'DrinkYN')]
-
-
-comp <- complete(mice(Daily, m=1, seed=817236),1)
-comp$Age <- as.numeric(comp$Age)
-comp$Day <- comp$Day-1
-rm(Daily)
-
-comp$Age <- as.numeric(scale(comp$Age))
-comp$Q1 <- as.factor(comp$Q1)
-comp$Q2 <- as.factor(comp$Q2)
-comp$Q3 <- as.factor(comp$Q3)
-comp$Q4 <- as.factor(comp$Q4)
-comp$Q5 <- as.factor(comp$Q5)
-comp$Q6 <- as.factor(comp$Q6)
-comp$Q7 <- as.integer(comp$Q7)
-comp$DrinkYN <- as.factor(comp$DrinkYN)
-comp$MissedDose <- as.factor(comp$MissedDose)
-comp$Gender <- as.factor(comp$Gender)
-
-#Find fit to simulate
-fit1 <- glm(data=comp, DrinkYN~ZIncom45+Age+ZAlcTox+ZAUDIT, family=binomial(link=logit))
-fit2<- glm(data=comp, Q1~ZEduc+ZIncom45+ZAlcTox+ZCESDFU, family=binomial(link=logit))
-fit3<- glm(data=comp, Q2~Q1+ZEduc+ZIncom45+Age+ZAlcTox
-           +ZCESDFU+ZAUDIT+Gender, family=binomial(link=logit))
-fit4<- glm(data=comp, Q3~Q1+Q2+ZEduc+ZIncom45+ZAlcTox
-           +ZCESDFU+Gender, family=binomial(link=logit))
-fit5<- glm(data=comp, Q4~Q1+Q2+Q3+ZEduc+ZAlcTox
-           +ZCESDFU+ZAUDIT+Gender, family=binomial(link=logit))
[…]

### 2018-03-22 thesis_code_GREG.R

@@ -1,426 +1,0 @@
-#setwd('C:/Users/Nicholas/Documents/Thesis')
-setwd("/Users/gregorymatthews/Dropbox/DesignedMissingness/")
-library(mice)
-library(lme4)
-library(mvtnorm)
-library(lmerTest)
-
-Daily <- read.csv('Daily with Tox.csv')
-names(Daily)[1] <- c('PID')
-Daily <- Daily[,c('PID', 'Day', 'Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7'
-                  ,'MissedDose'
-                  , 'ZEduc', 'ZIncom45', 'Gender', 'Age', 'ZAlcTox'
-                  ,'ZCESDFU', 'ZAUDIT', 'DrinkYN')]
-
-
-comp <- complete(mice(Daily, m=1, seed=817236),1)
-comp$Age <- as.numeric(comp$Age)
-comp$Day <- comp$Day-1
-rm(Daily)
-
-comp$Age <- as.numeric(scale(comp$Age))
-comp$Q1 <- as.factor(comp$Q1)
-comp$Q2 <- as.factor(comp$Q2)
-comp$Q3 <- as.factor(comp$Q3)
-comp$Q4 <- as.factor(comp$Q4)
-comp$Q5 <- as.factor(comp$Q5)
-comp$Q6 <- as.factor(comp$Q6)
-comp$Q7 <- as.integer(comp$Q7)
-comp$DrinkYN <- as.factor(comp$DrinkYN)
-comp$MissedDose <- as.factor(comp$MissedDose)
-comp$Gender <- as.factor(comp$Gender)
-
-#Find fit to simulate
-fit1 <- glm(data=comp, DrinkYN~ZIncom45+Age+ZAlcTox+ZAUDIT, family=binomial(link=logit))
-fit2<- glm(data=comp, Q1~ZEduc+ZIncom45+ZAlcTox+ZCESDFU, family=binomial(link=logit))
-fit3<- glm(data=comp, Q2~Q1+ZEduc+ZIncom45+Age+ZAlcTox
-           +ZCESDFU+ZAUDIT+Gender, family=binomial(link=logit))
-fit4<- glm(data=comp, Q3~Q1+Q2+ZEduc+ZIncom45+ZAlcTox
-           +ZCESDFU+Gender, family=binomial(link=logit))
-fit5<- glm(data=comp, Q4~Q1+Q2+Q3+ZEduc+ZAlcTox
[…]

### 2018-05-07 Code/Code Rework.R
Note: Loops are inefficient.

@@ -126,6 +126,8 @@ for (i in 1:no.sim) {print(i)
 rm(comp, sigma, X, b1, b2,b3,b4, fit1, fit2, fit3, fit4, fit5, fit6, fit7,
    i, int, sigmaPID)
 
+save.image("/home/gmatthews1/designedMissingness/simResults20180426.RData")
+
 ## Create MISSINGNESS
 # rremove <- function(nrem, x) { # this literally just randomly removes nrem columns. Like, the entire column. Why???
 #   id <- sample(length(x), nrem)
@@ -154,15 +156,15 @@ wave.des <- function(set, nmiss, ...) { # nmiss is the number of days each perso
 
 # Step 1 - Apply PM methods to simulated datasets
 set.seed(917236)
-split.pm <- mclapply(sim.data,function(x){split.form(x,grps)},mc.cores = 12)
-wave.pm <- mclapply(sim.data,function(x){wave.des(x,11)},mc.cores = 12)
+split.pm <- mclapply(sim.data,function(x){split.form(x,grps)},mc.cores = 18)
+wave.pm <- mclapply(sim.data,function(x){wave.des(x,11)},mc.cores = 18)
 
-
+save.image("/home/gmatthews1/designedMissingness/simResults20180426.RData")
 
 # Step 2 - Impute simulated datasets, for both methods
 
 impute <- function(pm){ # pass split.data
-  imp <- mclapply(pm, function(x) {mice(x, m=no.imp)},mc.cores = 12) # loop through the split.imps in the complete function
+  imp <- mclapply(pm, function(x) {mice(x, m=no.imp)},mc.cores = 18) # loop through the split.imps in the complete function
   res.data <- list()
   for (i in 1:no.sim){
     res.data[[i]] <- list()
@@ -176,10 +178,15 @@ impute <- function(pm){ # pass split.data
 split.data <- impute(split.pm)
 wave.data <- impute(wave.pm)
 
+save.image("/home/gmatthews1/designedMissingness/simResults20180426.RData")
+
 # Step 3 - Build models from imputed simulation data for both methods
 # Result: a list of lists of model coefficients for each method
 # Coefficient order: Intercept, DrinkYN2, Day, ZAlcTox, and DrinkYN2:Day
 
+
+#This should really be changed to run in parallel.  
+#Loops are inefficient.  
 mod.maker <- function(dat){ # passing split.data[[i]]
   modbetas <- list()
[…]

### 2018-05-08 Code/Code Rework.R
Fixed some functions (e.g. FMI, MSE).  Removed interaction effect from model.

@@ -44,14 +44,15 @@ comp$Day <- comp$Day-1
 rm(Daily)
 
 #comp$Age <- as.numeric(scale(comp$Age)) # why???
+#We re-assign drinkYN to be Q7 to match the survey description in the manuscript?  
 comp$Q1 <- as.factor(comp$Q1)
 comp$Q2 <- as.factor(comp$Q2)
 comp$Q3 <- as.factor(comp$Q3)
 comp$Q4 <- as.factor(comp$Q4)
 comp$Q5 <- as.factor(comp$Q5)
 comp$Q6 <- as.factor(comp$Q6)
-comp$Q7 <- as.factor(comp$DrinkYN)
 comp$Q8 <- as.integer(comp$Q7)
+comp$Q7 <- as.factor(comp$DrinkYN)
 comp$MissedDose <- as.factor(comp$MissedDose)
 comp$Gender <- as.factor(comp$Gender)
 
@@ -61,7 +62,9 @@ comp <- comp[,cols.keep]
 
 
 
-pop.mod <- glmer(MissedDose ~ Q7 + ZAlcTox + Day + Q7*Day + (1|PID), data = comp, family=binomial(link=logit))
+pop.mod <- glmer(MissedDose ~ Q7 + ZAlcTox + Day + (1|PID), data = comp, family=binomial(link=logit))
+
+no.var <- nrow(pop.mod.coeffs)
 
 pop.mod.coeffs <- summary(pop.mod)$coef[,1:2]
 
@@ -110,7 +113,7 @@ for (i in 1:no.sim) {print(i)
   X[X$Q7==0,c('Q8')] <- 0
   
   # Make Missed Dose
-  MD <- glmer(MissedDose ~ Q7 + ZAlcTox + Day + Q7*Day + (1|PID), data = comp, family=binomial(link=logit))
+  MD <- glmer(MissedDose ~ Q7 + ZAlcTox + Day + (1|PID), data = comp, family=binomial(link=logit))
   sigmaPID <- MD@theta
   
   X$groupErr <- rnorm(60, mean=0, sd=sigmaPID)[X$PID]
@@ -192,7 +195,7 @@ mod.maker <- function(dat){ # passing split.data[[i]]
   modse <- list()
   for (j in 1:length(dat)){
     df <- data.frame(dat[[j]])
-    try(model <- glmer(MissedDose ~ Q7 + ZAlcTox + Day + Q7*Day + (1|PID), data = df, family=binomial(link=logit)))
[…]

### 2018-05-08 Code/Code Rework.R
SOme notes added.

@@ -7,6 +7,10 @@ library(mvtnorm)
 library(lmerTest)
 library(parallel)
 
+#Settings: 
+#sampling size: 60 and 120 subjects
+#Correlation settings: regular and low
+#Missingness amount: low, medium, high
 start <- Sys.time()
 
 no.sim = 1000 # number of simulated datasets

### 2018-05-09 Code/Code Rework.R
changed hard coded 5 to no.var.

@@ -240,6 +240,17 @@ split.intervals <- TD(splitmods)
 wave.intervals <- TD(wavemods)
 
 coverage <- function(intervals){
+  #How I would have written it.  Results are exactly the same.  
+  # out <- c()
+  # cov <- lapply(intervals, function(x){
+  #   for (j in 1:no.var){
+  #     out[j] <- (pop.mod.coeffs[j,1] >= x[j,2]) & (pop.mod.coeffs[j] <= x[j,3])
+  #   }
+  #   out
+  # })
+  # 
+  # apply(do.call(rbind,cov),2,mean)
+  
   fits <- list() # lists of lists of whether or not a parameter estimate fell in the sim's CI
   for (i in 1:no.sim){
     incl <- list()
@@ -249,7 +260,7 @@ coverage <- function(intervals){
     fits[[i]] <- incl
   }
   
-  fit.mat <- matrix(unlist(fits),5)
+  fit.mat <- matrix(unlist(fits),no.var)
   cover <- apply(fit.mat,1,mean)
   return(list(fit.mat,cover))
 }

### 2018-05-09 Code/Code Rework.R
Generalized the code to run in different format.  Also changed split form to match the paper.  and added altered split form.

@@ -1,4 +1,14 @@
-#nohup R --vanilla CMD BATCH /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar.Rout &
+# #nohup R --vanilla CMD BATCH /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar.Rout &
+# 
+# 
+# nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="low" nmiss=11 nrem=2' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_low.Rout &
+# nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="low" nmiss=11 nrem=2' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar120_1_low.Rout &
+#   
+#   nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="med" nmiss=22 nrem=4' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_med.Rout &
+#   nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="med" nmiss=22 nrem=4' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_med.Rout &
+#   
+#   nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="high" nmiss=33 nrem=6' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_high.Rout &
+#   nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="high" nmiss=33 nrem=6' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_high.Rout &
 
 # Load necessary libraries
 library(mice)
@@ -7,15 +17,33 @@ library(mvtnorm)
 library(lmerTest)
 library(parallel)
 
+#Passing arguments from the command line. 
[…]

### 2018-05-09 Documentation/Block Visualization Scratch.Rmd
Visualizations for PM Methods

---
title: "R Notebook"
output: html_notebook
---

```{r}
# Creating dataframe to visualize - one subject's questions for 5 days

grps <- list(X=c('Q1','Q8'),A=c('Q2','Q3'),B=c('Q4','Q5'),C=c('Q6','Q7'))

split.form <- function(set,grps){
   set$block[sample(1:nrow(set),nrow(set),FALSE)] <- c('A','B','C')
   set[set$block == "A",grps$A] <- NA
   set[set$block == "B",grps$B] <- NA
   set[set$block == "C",grps$C] <- NA
   set
}

wave.des <- function(set, nmiss, ...) { # nmiss is the number of days each person would miss? 11?? Like, miss a fourth of the days?
  id <- sample(2:5, size=nmiss)
  for (i in 1:nmiss) {
    set[set$day %in% id[i], c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')] <- NA
  }
  set
}
```

```{r,warning=FALSE}
cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
fill <- matrix(1, 5, 8)
dat <- data.frame(fill)
colnames(dat) <- cols
dat$day <- seq.int(nrow(dat))
split.dat <- split.form(dat,grps)[1:8]
split.dat
```

```{r,warning=FALSE,message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape2)
datmelt <- split.dat[1:8] %>% is.na %>% melt
colnames(datmelt) <- c("Day","Question","Missing")
datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
```

```{r,warning=FALSE}
cols <- c("A" = "skyblue3", "B" = "skyblue3", "C" = "skyblue3", "X" = "skyblue4", "Missing" = "white")
ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols) + geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white") + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse()
```

```{r}
wave.dat <- wave.des(dat,2)
wave.dat
```

```{r}
library(ggplot2)
library(dplyr)
library(reshape2)
datmelt <- wave.dat[1:8] %>% is.na %>% melt
colnames(datmelt) <- c("Day","Question","Missing")
datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
```

```{r,warning=FALSE}
cols <- c("A" = "skyblue3", "B" = "skyblue3", "C" = "skyblue3", "X" = "skyblue4", "Missing" = "white")
ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols) + geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white") + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse()
```
```

### 2018-05-11 Code/Code Rework.R
Added in high time scenario.

@@ -10,6 +10,27 @@
 #   nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="high" nmiss=33 nrem=6' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_high.Rout &
 #   nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="high" nmiss=33 nrem=6' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_high.Rout &
 
+#hightime == 1
+nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="low" nmiss=11 nrem=2 hightime=1' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_low_highttime.Rout &
+nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="low" nmiss=11 nrem=2 hightime=1' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar120_1_low_highttime.Rout &
+
+  nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="med" nmiss=22 nrem=4 hightime=1' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_med_highttime.Rout &
+  nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="med" nmiss=22 nrem=4 hightime=1' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar120_1_med_highttime.Rout &
+
+  nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="high" nmiss=33 nrem=6 hightime=1' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_high_highttime.Rout &
[…]

### 2018-05-15 Code/Code Rework.R
added percent bias and CI length and code for computing full data coefficients.

@@ -177,6 +177,10 @@ for (i in 1:no.sim) {print(i)
   MD <- glmer(MissedDose ~ Q7 + ZAlcTox + Day + (1|PID), data = comp, family=binomial(link=logit))
   sigmaPID <- MD@theta
   
+  if (hightime == 1){
+    MD@beta <- MD@beta * c(2,0.5,0.5,1)
+  }
+  
   X$groupErr <- rnorm(no.pid, mean=0, sd=sigmaPID)[X$PID]
   X$groupErr2 <- rnorm(no.pid, mean=0, sd=sigmaPID)[X$PID]
   X$MissedDose <- predict(MD,X,allow.new.levels=TRUE)
@@ -185,6 +189,20 @@ for (i in 1:no.sim) {print(i)
   
   sim.data[[i]] <- X
 }
+
+mod.maker.nomiss <- function(dat){ #
+  modbetas <- list()
+  modse <- list()
+  for (i in 1:length(dat)){
+    try(model <- glmer(MissedDose ~ Q7 + ZAlcTox + Day + (1|PID), data = dat[[i]], family=binomial(link=logit)))
+    try(modbetas[[i]] <- summary(model)$coef[,1]) # only take the coefficients of the variables, not the intercept
+    try(modse[[i]] <- summary(model)$coef[,2])
+  }
+  return(list(betas=modbetas,se=modse))
+}
+
+#Get results for the data with no missingess.
+fullmods <- mod.maker.nomiss(sim.data)
 
 #Remove unnecessary before analysis
 rm(comp, sigma, X, b1, b2,b3,b4, fit1, fit2, fit3, fit4, fit5, fit6, fit7,
@@ -347,6 +365,27 @@ split.cover <- coverage(split.intervals)
 altered.split.cover <- coverage(altered.split.intervals)
 wave.cover <- coverage(wave.intervals)
 
+# CI Length #
+
+cilength <- function(intervals){
+  length <- list() # lists of lists of whether or not a parameter estimate fell in the sim's CI
+  for (i in 1:no.sim){
+    len <- list()
+    for (j in 1:no.var){
+      len[[j]] <-  intervals[[i]][j,3] - intervals[[i]][j,2]
+    }
+    length[[i]] <- len
+  }
+  
+  fit.mat <- matrix(unlist(length),no.var)
+  out <- apply(fit.mat,1,mean)
+  return(list(fit.mat,out))
+}
+
+split.length <- cilength(split.intervals)
[…]

### 2018-05-15 Code/Code Rework.R
Updated code.

@@ -1,35 +1,36 @@
 # #nohup R --vanilla CMD BATCH /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar.Rout &
 # 
 # 
-# nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="low" nmiss=11 nrem=2' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_low.Rout &
-# nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="low" nmiss=11 nrem=2' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar120_1_low.Rout &
-#   
-#   nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="med" nmiss=22 nrem=4' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_med.Rout &
-#   nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="med" nmiss=22 nrem=4' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_med.Rout &
-#   
-#   nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="high" nmiss=33 nrem=6' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_high.Rout &
-#   nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="high" nmiss=33 nrem=6' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_high.Rout &
+# Regular Runs: 
+# nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="low" nmiss=11 nrem=2 hightime=0' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_low_highttime0.Rout &
[…]

### 2018-05-15 Documentation/manuscript.Rnw
Manuscript is now being writted in KNITR.

--- 2018-02-22 comparing_05222017.tex
@@
 
-\author{Nicholas Illenberger \and Jennifer Pellowski \and Ofer Harel}
-
-\institute{N. Illenberger \and O. Harel 
+\author{Josephine Wood \and Gregory J. Matthews \and Nicholas Illenberger \and Jennifer Pellowski \and Ofer Harel}
+
+\institute{J. Wood \and G. J. Matthews
+          \at Loyola University Chicago \\
+          1032 W. Sheridan Rd.\\
+          Chicago IL, 60660 USA\\
+          Tel: (773)508-3558
+          \and
+          N. Illenberger \and O. Harel 
 				\at University of Connecticut \\
@@
 
-\begin{table}[h!]
-	\centering
-	\caption{The Three Form PM Design}
-	\label{tab:table10}
-	\setlength{\tabcolsep}{1cm}
-	\begin{tabular}{c|cccc}
-		\toprule
-		& \multicolumn{4}{c}{Block} \\
-		Form & X & A & B & C \\
-		\midrule
-		1 & 1 & 1 & 1 & 0 \\
-		2 & 1 & 1 & 0 & 1 \\
-		3 & 1 & 0 & 1 & 1 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+We need to talk about the other type of split design that we used here which was that X of the 8 questions are randomly omitted on each day.
+
+% \begin{table}[h!]
+% 	\centering
+% 	\caption{The Three Form PM Design}
+% 	\label{tab:table10}
+% 	\setlength{\tabcolsep}{1cm}
+% 	\begin{tabular}{c|cccc}
+% 		\toprule
+% 		& \multicolumn{4}{c}{Block} \\
+% 		Form & X & A & B & C \\
+% 		\midrule
+% 		1 & 1 & 1 & 1 & 0 \\
+% 		2 & 1 & 1 & 0 & 1 \\
+% 		3 & 1 & 0 & 1 & 1 \\
+% 		\bottomrule
+% 	\end{tabular}
+% \end{table}
+
+<<echo = FALSE>>=
+# Creating dataframe to visualize - one subject's questions for 5 days
+split.form <- function(set, nrem = 2, bound = 0){
+
+set[set$Day >= bound, paste0("Q",1:8)] <- t(apply(set[set$Day >= bound,paste0("Q",1:8)], 1, function(x){
+    ind <- sample(1:8, nrem)
+    x[ind] <- NA
+    as.numeric(x)
+  }))
+
+  return(set)
+
+}
+@
+
+<<echo = FALSE>>=
+wave.des <- function(set, nmiss, ...) { # nmiss is the number of days each person would miss? 11?? Like, miss a fourth of the days?
+  id <- sample(2:45, size=nmiss)
+  for (i in 1:nmiss) {
+    set[set$Day %in% id[i], c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')] <- NA
+  }
+  return(set)
+}
+@
+
+<<warning=FALSE, echo = FALSE>>=
+cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
+fill <- matrix(1, 45, 8)
+dat <- data.frame(fill)
+colnames(dat) <- cols
+dat$Day <- seq.int(nrow(dat))
+set.seed(1234)
+split.dat <- split.form(dat)[1:8]
+#split.dat
+@
+
+<<warning=FALSE,message=FALSE,echo=FALSE>>=
+library(ggplot2)
+library(dplyr)
+library(reshape2)
+datmelt <- split.dat[1:8] %>% is.na %>% melt
+colnames(datmelt) <- c("Day","Question","Missing")
+#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
+datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
+
+  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
+@
+
+<<warning=FALSE,echo=FALSE>>=
+cols <- c("Missing" = "red", "Observed" = "skyblue3")
+splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
+
+#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
+@
+
+<<warning=FALSE,echo=FALSE>>=
+cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
+fill <- matrix(1, 45, 8)
+dat <- data.frame(fill)
+colnames(dat) <- cols
+dat$Day <- seq.int(nrow(dat))
+set.seed(1234)
+alternate.split.dat <- split.form(dat, bound = 3)[1:8]
+#alternate.split.dat
+@
+
+<<warning=FALSE,message=FALSE,echo=FALSE>>=
+library(ggplot2)
+library(dplyr)
+library(reshape2)
+datmelt <- alternate.split.dat[1:8] %>% is.na %>% melt
+colnames(datmelt) <- c("Day","Question","Missing")
+#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
+datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
+
+  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
+@
+
+<<warning=FALSE,echo=FALSE>>=
+cols <- c("Missing" = "red", "Observed" = "skyblue3")
+alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
+
+#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
+@
+
+<<echo=FALSE>>=
+set.seed(1234)
+wave.dat <- wave.des(dat,11)
+#wave.dat
+@
+
+<<echo=FALSE>>=
+library(ggplot2)
+library(dplyr)
+library(reshape2)
+datmelt <- wave.dat[1:8] %>% is.na %>% melt
+colnames(datmelt) <- c("Day","Question","Missing")
+#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
+datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
+
+  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
+@
+
+<<echo=FALSE>>=
+cols <- c("Missing" = "red", "Observed" = "skyblue3")
+waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
+@
+
+<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE>>=
+require(gridExtra)
+grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
+@
+
+Figure \ref{fig:misslow} is
 
@@
 \par
+
 \begin{table}[t]
@@
 We note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
+
+<<>>=
+load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high.RData")
+high <- d
+
+load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med.RData")
+med <- d
+
+load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low.RData")
+low <- d
+
+library(xtable)
+print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
+
+load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
+high <- d
+
+load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
+med <- d
+
+load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
+low <- d
+
+library(xtable)
+print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
+
+@
+
+% latex table generated in R 3.5.0 by xtable 1.8-2 package
+% Mon May 14 21:02:34 2018
+\begin{table}[ht]
+\centering
+\begin{tabular}{lllrrrr}
+  \hline
+Design & \% Missingness  & Parameter & Coverage & Bias & MSE & FMI \\ 
+  \hline
+ &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
+   &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
+   &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
+   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
+   \hline
+   &  &  & 0.986 & 0.040 & 0.019 & 0.012 \\ 
+   &  &  & 0.993 & -0.168 & 0.750 & 0.557 \\ 
+   &  &  & 0.932 & 0.008 & 0.024 & 0.002 \\ 
+   &  &  & 0.940 & -0.000 & 0.000 & 0.008 \\ 
+   \hline
+   &  &  & 0.984 & 0.036 & 0.027 & 0.030 \\ 
+   &  &  & 0.991 & -0.713 & 9.933 & 0.625 \\ 
+   &  &  & 0.932 & 0.009 & 0.027 & 0.005 \\ 
+   &  &  & 0.939 & -0.000 & 0.000 & 0.021 \\ 
+   \hline
+   &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
+   &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
+   &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
+   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
+   \hline
+   &  &  & 0.988 & 0.040 & 0.018 & 0.010 \\ 
+   &  &  & 0.994 & -0.167 & 0.782 & 0.549 \\ 
+   &  &  & 0.931 & 0.009 & 0.024 & 0.002 \\ 
+   &  &  & 0.944 & -0.000 & 0.000 & 0.006 \\ 
+   \hline
+   &  &  & 0.983 & 0.036 & 0.022 & 0.027 \\ 
+   &  &  & 0.990 & -0.686 & 10.509 & 0.665 \\ 
+   &  &  & 0.928 & 0.009 & 0.026 & 0.007 \\ 
+   &  &  & 0.946 & -0.000 & 0.000 & 0.023 \\ 
+   \hline
+   &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
+   &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
+   &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
+   &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
+   \hline
+   &  &  & 0.991 & 0.029 & 0.018 & 0.055 \\ 
+   &  &  & 0.988 & -0.112 & 0.345 & 0.752 \\ 
+   &  &  & 0.934 & 0.009 & 0.024 & 0.007 \\ 
+   &  &  & 0.951 & -0.000 & 0.000 & 0.032 \\ 
+   \hline
+   &  &  & 0.994 & -0.003 & 0.022 & 0.258 \\ 
+   &  &  & 0.988 & -0.105 & 0.284 & 0.903 \\ 
+   &  &  & 0.937 & 0.011 & 0.025 & 0.039 \\ 
+   &  &  & 0.960 & -0.000 & 0.000 & 0.175 \\ 
+   \hline
+\end{tabular}
+\end{table}
 

### 2018-05-15 Code/Code Rework.R
I removed model fits that are clearly results of non convergence.
I also added confidence interval length and percent bias.

@@ -2,14 +2,14 @@
 # 
 # 
 # Regular Runs: 
-# nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="low" nmiss=11 nrem=2 hightime=0' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_low_highttime0.Rout &
-# nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="low" nmiss=11 nrem=2 hightime=0' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar120_1_low_highttime0.Rout &
-# 
-#   nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="med" nmiss=22 nrem=4 hightime=0' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_med_highttime0.Rout &
-#   nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="med" nmiss=22 nrem=4 hightime=0' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar120_1_med_highttime0.Rout &
-# 
-#   nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="high" nmiss=33 nrem=6 hightime=0' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_high_highttime0.Rout &
-#   nohup R --vanilla CMD BATCH '--args no.pid=120 corr.scale=1 howmuch="high" nmiss=33 nrem=6 hightime=0' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar120_1_high_highttime0.Rout &
+nohup R --vanilla CMD BATCH '--args no.pid=60 corr.scale=1 howmuch="low" nmiss=11 nrem=2 hightime=0' /home/gmatthews1/designedMissingness/simulationPar.R /home/gmatthews1/designedMissingness/simulationPar60_1_low_highttime0.Rout &
[…]

### 2018-05-16 Documentation/comparing_05222017.tex
Changes
Added new authors.
Documentation Updates

--- 2018-02-22 comparing_05222017.tex
@@
 
-\author{Nicholas Illenberger \and Jennifer Pellowski \and Ofer Harel}
+\author{Josephine Wood \and Gregory J. Matthews \and Nicholas Illenberger \and Jennifer Pellowski \and Ofer Harel}
 
-\institute{N. Illenberger \and O. Harel 
+\institute{J. Wood \and G. J. Matthews
+          \at Loyola University Chicago \\
+          1032 W. Sheridan Rd.\\
+          Chicago IL, 60660 USA\\
+          Tel: (773)508-3558
+          \and
+          N. Illenberger \and O. Harel 
 				\at University of Connecticut \\
@@
 There have been many different incarnations of the PM design, each crafted to best suit the study at hand.
-For example, PM designs have been used in the study of longitudinal growth curves \citep{graham2001planned, mcardle1997expanding}, business research \citep{shoemaker1973principles}, behavioral studies \citep{harel2015designed}, biostatistics \citep{andres2006partial, wacholder1994partial}, and in educational assessments \citep{zeger1997efficient, sirotnik1977incidence}.
-This paper focuses on two of the simplest and most applicable PM designs, the Split Form design \citep{raghunathan1995split} and the Wave Missingness design \citep{little2013planned}.
-While this paper covers these designs in more detail later, broadly speaking, the Split Form design entails measuring fewer points at a single measurement occasion \citep{raghunathan1995split}.
-The Wave Missingness design, on the other hand, would require missing out on entire measurement occasion within a longitudinal study \citep{graham2001planned}.
+For example, PM designs have been used in the study of longitudinal growth curves \citep{graham2001planned, mcardle1997expanding}, business research \citep{shoemaker1973principles}, behavioral studies \citep{harel2015designed}, biostatistics \citep{andres2006partial, wacholder1994partial}, and educational assessments \citep{zeger1997efficient, sirotnik1977incidence}.
+This paper focuses on two of the simplest and most applicable PM designs; the Split Form design \citep{raghunathan1995split} and the Wave Missingness design \citep{little2013planned}.
+While this paper covers these designs in more detail later, broadly speaking, the Split Form design entails measuring fewer points on a single measurement occasion \citep{raghunathan1995split}.
+The Wave Missingness design, on the other hand, requires missing an entire measurement occasion within a longitudinal study \citep{graham2001planned}.
 
 The issue we concern ourselves with arises when a longitudinal study requires multiple items to be collected at each measurement occasion.
-When a multi-level regression model is the analysis of interest, we would like to see if it is more efficient to design missingness using the Split Form design or the Wave Missingness design.
+When implementing a multi-level regression model in this situation, we investigate which planned missingess design is more efficient and accurate.
 Previous research indicates that for the estimation of correlated latent growth curve models use of the three-form PM design, a special case of Split Form designs \citep{raghunathan1995split}, resulted in low bias on parameter estimates or standard error and high efficiency when compared with wave missingness designs \citep{rhemtulla2014planned}.
-Because our model of interest is a mixed effects model, though, we can not be sure that this result will hold.
+As our model of interest is a mixed effects model, however, we can not be sure that this result will hold.
 \par
 
-To answer our question we performed a simulation study based on data obtained in longitudinal research on HIV medication adherence and alcohol-interactivity beliefs \citep{pellowski2016alcohol}.
-For each of the PM designs mentioned we simulated sample data conforming to that particular design and then used multiple imputation (MI) \citep{little2014statistical}  techniques to analyze our data.
-We subsequently evaluated the PM methodologies using the average bias, percent bias, mean squared error, coverage rates, confidence interval length, and estimated fraction of missing information (FMI) \citep{little2014statistical} for parameter estimates in a multilevel model.
-To make our results more generalizable the experiment was repeated under a few different scenarios: increased sample size, low inter-survey correlation, and high time effect.
+To answer our question we performed a simulation study from data obtained in longitudinal research on HIV medication adherence and alcohol-interactivity beliefs \citep{pellowski2016alcohol}.
+For the PM designs mentioned we simulated sample data and then used multiple imputation (MI) \citep{little2014statistical}  techniques to analyze the data.
+The PM methods were subsequently evaluated through the assessmemt of the average bias, percent bias, mean squared error, coverage rates, confidence interval length, and estimated fraction of missing information (FMI) \citep{little2014statistical} for parameter estimates in a multilevel model.
+To make the results generalizable, the experiment was repeated under multiple scenarios: increased sample size, low inter-survey correlation, and high time effect.
 \par
@@
 
-Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are so named because of the way in which they are implemented.
-Instead of giving participants one large survey, researchers will create multiple “forms”, each containing only a subset of the full survey’s questions.
-A common setup is the three-form design \citep{graham1996maximizing}.
-In the three-form design the full survey is split into four blocks, X, A, B, and C.
-Each form of the survey includes the X block as well as two of the other three blocks.
-This leaves us with the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded.
-We note that every block is paired together in at least one of the forms.
-By designing our forms in this manner we are able to estimate the relationship between any given items regardless of which blocks they are in.
+Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are very aptly named.
+Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey’s questions.
+A common form setup is the three-form design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C.
+Each form of the survey includes the X block as well as two of the remaining blocks.
+This leaves the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded.
+Note that every block appears in at least one form.
+By designing the forms in this manner we are able to estimate the relationship between any chosen items regardless of their blocks.
 That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows us to do that.
@@
 
-An important consideration when designing a Split Form survey is deciding which items to put into which blocks.
-The X-block, being included in every form, should contain either those variables which are of greatest interest or those with the most predictive ability.
+An important consideration when designing a Split Form survey is question distribution.
+The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
 Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}.
 On the other hand, placing the most predictive variables in the X-block allows Multiple Imputation to more effectively impute missing values from the other blocks \citep{gottschall2012comparison}.
-For the same reason it is good practice to place variables which are predictive of each other in to separate blocks \citep{gottschall2012comparison}.
-We note that when groupings are not as obvious as in the previous example pilot studies can help determine the predictive potential of variables.
+Similarly, it is good practice to place variables which are predictive of each other in separate blocks \citep{gottschall2012comparison}.
+Note that when groupings are not as obvious, as in the previous example, pilot studies can help determine the predictive potential of variables.
 We may also wish to consider the cost and burden associated with an item when deciding which block to place it in.
-Even if a specific item is critical to our analysis, if it is overly expensive or invasive we may be better off excluding it from the X-block \citep{little2013planned}.
+For example, if a critical item is overly expensive or difficult to obtain we may be better off excluding it from the X-block \citep{little2013planned}.
 \par
 
-More than deciding which blocks should contain which items, we also need to consider how many blocks we should use.
-Including more blocks in our design can allow us to further increase missingness \citep{graham2006planned}.
-For example, imagine two groups of researchers, the first group divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey, and the second uses an X-block and nine others with 10\% of the items each.
-The researchers make the decision that any given pair of blocks should be asked together in at least one of the forms to ensure efficient estimations.
+In additon, the number of blocks must be determined.
+Including more blocks in the design allows further increased missingness \citep{graham2006planned}.
+For example, consider two groups of researchers.
+The first group divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey, and the second uses an X-block and nine others with 10\% of the items each.
+The researchers decide that a pair of blocks will be asked together in at least one of the forms to ensure efficient estimations.
 Based on this requirement, the first group can only reduce the length of their survey by 25\% while the second group can decrease the length of their survey by up to 70\%.
@@
 
-While this increase in missingness may allow for further reductions in burden and cost researchers must consider the trade-offs of using more blocks.
-Besides the fact that greater missingness will lead to less efficient estimation \citep{rhemtulla2016asymptotic} there is the added complication that more blocks means more forms.
-If the second group of researchers in our example, for instance, did decide that each form would contain the X-block and two of the other blocks, then they would be left with 36 total forms.
-For traditional paper surveys this can make increasing the number of blocks unwieldy.
-However, for electronic surveys, where form randomization can be automated, this is not an issue.
-Oftentimes, Researchers using electronic surveys will give each participant a random sample of all the survey items, in a way treating each item as its own block \citep{silvia2014planned}.
-Using this method researchers can reap the benefits of increased forms without the difficulty caused by manually building these forms.
+While increasing missingness may allow for further reductions in burden and cost, researchers must consider the disadvantages of more blocks.
+Inevitably, greater missingness leads to less efficient estimation \citep{rhemtulla2016asymptotic} but there is the added complication as more blocks introduce additional forms.
+If the second group of researchers in the example, for instance, decide that each form would contain the X-block and two of the other blocks, then they would be left with 36 total forms.
+For traditional paper surveys, this can make administering the survey difficult.
+However, for electronic questionaires, where form randomization can be automated, this is not an issue.
+Often, researchers using electronic surveys will give each participant a random sample of all survey items, in a way treating each item as its own block \citep{silvia2014planned}.
+Using this method, researchers reap the benefits of increased forms without the difficulty caused by manually building and administering these forms.
 \par
@@
 \label{sec:1.2}
-While Split Form missingness can be applied to many different experimental designs, the Wave Missingness design \citep{little2013planned} is unique to studies with multiple measurement occasions or waves.
-Unlike the Split Form design, where participants were assigned to miss a subset of items in a single measurement occasion, the Wave Design entails randomizing participants to miss an entire measurement occasion.
-An example of a Wave Missing design in which data is collected every month for five months but each participant is only measured at three of these occasions as shown in Table \ref{tab:table11}.
-Again, "1" indicates that a given wave is included while "0" indicates that it is excluded.
-Subject two, for instance, is randomly assigned to be measured only at the first, second, and fourth month.
+While Split Form missingness can be applied to many experimental designs, the Wave Missingness design \citep{little2013planned} is unique to studies with multiple measurement occasions, or "waves".
+Unlike the Split Form design, where participants miss a subset of items in a single measurement occasion, the Wave Design entails randomizing participants to miss a measurement occasion entirely.
+An example of a Wave Missing design is shown in Table \ref{tab:table11} where data is collected monthly over the course of 5 months.
+However, each participant is only measured at three of these occasions.
 \par
@@
 
-A relative advantage of the Wave Missingness design over the Split form design is that researchers can have more control over the level of missingness.
-For studies with many measurement occasions it is easy to make small changes to the amount of missing data.
-The data described by \citet{pellowski2016alcohol}.
-\citet{pellowski2016alcohol} for instance has daily measurements for 45 days.
+A relative advantage of the Wave Missingness design over the Split form design is increased control over the level of missingness.
+For studies with many measurement occasions, it is easy to make small changes to the amount of missing data.
+For example, the data described by \citet{pellowski2016alcohol} records measurements for 45 days.
 Missing eleven days here would result in 24.4\% missingness while missing twelve gives us 26.7\%.
-Further, Wave Missingness designs have the ability to eclipse Split Form designs in terms of cost reduction \citep{little2013planned}.
+Further, Wave Missingness designs eclipse Split Form designs in terms of cost reduction \citep{little2013planned}.
 \par
 
-Another advantage of this design is that many common longitudinal study designs already make use of the Wave Missingness structure \citep{little2013planned}.
-Cohort Sequential Designs are a type of study where cohorts of different ages are recruited and followed longitudinally in such a way that we can use information from one cohort to impute values for another \citep{little2013longitudinal, duncan2013introduction}.
-Say, for example, we had three cohorts of ages 10, 11, and 12 at baseline and we measured them annually for four years.
+Another advantage of this design is many longitudinal study designs already use the Wave Missingness structure \citep{little2013planned}.
+Cohort Sequential Designs require cohorts of different ages to be followed longitudinally in such a way that the information from one cohort can be used to impute values for another \citep{little2013longitudinal, duncan2013introduction}.
+For example, there were three cohorts of ages 10, 11, and 12 at baseline and measured annually for four years.
 Although measurement only occurs at four waves we can frame this as a six-wave study where the 10-year old cohort has missing values at waves five and six, the 11-year old cohort at waves one and six, and the 12-year old cohort at waves one and two.
-Because the 10-year old cohort is the only group observed at the first wave we use it to impute missing values for the other groups.
-By continuing in this manner we are able to take the data that was collected over a four year period and extend it to cover six years, accelerating the study.
+Because the 10-year old cohort is the only group observed at the first wave, the missing values for the other groups are imputed using this information.
+By continuing in this manner the data that was collected over a four year period is extended it to cover six years, accelerating the study.
 The setup of this type of study is demonstrated in Table \ref{tab:table12}, where "1" and "0" respectively indicate an included and excluded wave.
@@
 Developmental time-lag models \citep{mcardle1997expanding} also make use of the Wave Missingness structure.
-As shown in Table \ref{tab:table13}, researchers here observe participants at only two measurement occasions, varying the length between occasions for each participant, and then treat this two-time-point data as multi-time-point data with missing values.
-Under this framework they are able to use missing data techniques to impute these missing values and estimate growth curve models.
-Estimating this type of model would normally require measuring participants at many time points however, under the Wave Missingness design we can accomplish this task with only two measurement occasions per participant.
-These designs exemplify how useful the Wave Missingness structure can be in accelerating longitudinal studies.
+As shown in Table \ref{tab:table13}, researchers observe participants at only two measurement occasions, varying the length between occasions for each participant, and then treat this two-time-point data as multi-time-point data with missing values.
+Under this framework they impute these missing values and estimate growth curve models.
+Estimating this type of model would normally require measuring participants at many time points.
+However, under the Wave Missingness design this is accomplished with only two measurement occasions per participant.
+These designs exemplify how useful the Wave Missingness structure is in accelerating longitudinal studies.
 \par
@@
 We define the missingness, $R$, to be an indicator variable which equals 0 where $Y_{com}$ is observed and 1 where the corresponding value in $Y_{com}$ is missing.
-Missing data mechanisms describe the supposed probabilistic relationship between $R$ and the values in $Y_{com}$, observed or unobserved \citep{little2014statistical}.
+Missing data mechanisms describe the proposed probabilistic relationship between $R$ and the values in $Y_{com}$, observed or unobserved \citep{little2014statistical}.
 \par
@@
 If we have prior knowledge concerning the relationship between unobserved values, indicated by $R$, and the observed values, then Multiple Imputation can yield efficient estimates even under MNAR \citep{harel2007multiple}.
-However, because this is not typically the case MI is most often implemented when data is MCAR or MAR \citep{little2014statistical}.
+However, because this is not typically the case, MI is most often implemented when data is MCAR or MAR \citep{little2014statistical}.
 \par
@@
 MI works by replacing unobserved values with a set of plausible values in a way which allows us to account for uncertainty in the imputation process.
-Repeatedly using some imputation technique every missing value in the incomplete dataset is replaced with a fixed number of imputed values.
+Repeatedly using an imputation technique, every missing value in the incomplete dataset is replaced with a fixed number of imputed values.
 This process allows for the creation of multiple complete datasets, on which users can run complete-data procedures.
 If, for instance, we imputed $M$ possible values for every missing value we would obtain $M$ different completed datasets.
-Once these datasets have been created, we can run the analysis of interest on each of them and, using rules defined by \citet{little2014statistical} and \citet{rubin2004multiple}, combine our results to obtain a single inference.
+Once created, the analysis of interest can be performed on each of them and, using rules defined by \citet{little2014statistical} and \citet{rubin2004multiple}, combine the results to obtain a single inference.
 \par
@@
 
-From here we can compute the sampling variance of this estimate by first calculating the between-imputation component, $B_M = \sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2 / (M-1)$, and a within-imputation component, $W_M = \sum_{n=1}^{M} S_n^2 / M$.
-These components are combined to obtain the overall sampling variance of our MI estimate as follows:
+From here we can compute the sample variance of this estimate by calculating the between-imputation component, $B_M = \sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2 / (M-1)$, and the within-imputation component, $W_M = \sum_{n=1}^{M} S_n^2 / M$.
+These components are combined to obtain the overall sample variance of our MI estimate as follows:
 
@@
 
-These equations form the basis of Rubin's combining rules and should provide parameter estimates which are unbiased while accounting for the inherent uncertainty in the imputation process \citep{raghunathan2015missing}.
+These equations form the basis of Rubin's combining rules and provide unbiased parameter estimates accounting for the inherent uncertainty in the imputation process \citep{raghunathan2015missing}.
 For a more in depth explanation of these methods we refer readers to \citet{little2014statistical}.
@@
 
-When using Multiple Imputation researchers must decide on the number of imputations, $M$, to use.
-Generally speaking, the lower the level of missingness is the fewer imputations are needed.
-If less than 20\% of the requisite data is missing, for instance, ten or even five imputations will suffice \citep{raghunathan2015missing}.
-However, at its roots MI is a simulation technique and thus, the greater $M$ is the more stable our estimates become \citep{harel2007inferences}.
+When using Multiple Imputation, researchers must decide on the number of imputations, $M$, to use.
+Generally, as the level of missingness decreases the number of imputations needed does as well.
+If less than 20\% of the requisite data is missing, for instance, five or tien imputations will suffice \citep{raghunathan2015missing}.
+However, at its roots, MI is a simulation technique and thus, the greater $M$ is the more stable our estimates become \citep{harel2007inferences}.
 \citet{graham2007many} recommend that if computational power is not a limiting factor, then setting $M=100$ is good practice.
@@
 \label{sec:2.1}
-The dataset we based our simulations on came from a study by \citet{pellowski2016alcohol} and more in depth information on it can be found there.
-However, to give a brief overview, the data was collected in an attempt to determine the day-level relationship between alcohol use, interactive toxicity beliefs, and adherence to antiretroviral therapy (ART) amongst patients with HIV.
-Previous studies noted that alcohol use combined with the perception that mixing alcohol and ARTs can cause adverse effects, correlated with non-adherence to ARTs \citep{kalichman2009prevalence, kalichman2012alcohol}.
-However, \citet{pellowski2016alcohol} pointed out that past research had collected data over extended periods of time preventing the identification a day-level interaction.
+The dataset the simulations are based on originated in a study by \citet{pellowski2016alcohol}.
+The data was collected in an attempt to determine the day-level relationship between alcohol use, its interactive toxicity beliefs, and adherence to antiretroviral therapy (ART) amongst patients with HIV.
+Previous studies note that alcohol use combined with the perception that mixing alcohol and ARTs can cause adverse effects, correlated with non-adherence to ARTs \citep{kalichman2009prevalence, kalichman2012alcohol}.
+However, \citet{pellowski2016alcohol} pointed out that past research collected data over extended periods of time, preventing the identification a day-level interaction.
 Unlike others, this study was able to determine whether alcohol use and missed medication doses occurred on the same day.
@@
 
-The study employed an observational cohort design, following sixty participants over forty-five days and sending them a daily questionnaire.
+The study employed an observational cohort design, following sixty participants over forty-five consequtive days via a daily questionnaire.
 Questions in the survey concerned livelihood insecurities from the previous day as well as alcohol use.
-The analysis used eight particular questions, two binary questions on housing insecurity, four binary questions on food insecurity, and two questions concerning alcohol use  (one binary variable and one count variable).
+The analysis included eight particular questions: two binary questions on housing insecurity, four binary questions on food insecurity, and two questions concerning alcohol use (one binary variable and one count variable).
 The exact questions can be found in Table \ref{tab:table1}.
@@
 \label{sec:2.2}
-The first step in the process of creating our simulated datasets was to use the data from \citet{pellowski2016alcohol} and obtain parameter estimates to quantify the relationships between variables.
-We then treated these estimated relationships as the “true” relationships and drew two-hundred samples using these parameters.
-While we would have liked to simulate a larger number of samples we were limited by computational ability.
-Our purpose in simulating these datasets was to see how well they would be able to capture the true relationship between medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score).
+
+The first step in the process of creating the simulated datasets was to obtain parameter estimates from \citet{pellowski2016alcohol} and to quantify the relationships between variables.
+These estimated relationships were treated as the “true” relationships and one thousand samples were drawn using these parameters.
+The purpose of simulating these datasets was to see how well they captured the true relationship between daily medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score).
 Specifically, our model of interest is the random intercept model with time effect found below: \\
@@
 
-The true values of the parameters, $\gamma_0, \beta_1, \beta_2$, $\beta_3$, and $\sigma^2$ were set to -2.3, 0.56, 1.28, 0.2, and 1.0 respectively. \par
-Once our samples were drawn we imposed three different missingness structures on each of the samples corresponding to three possible PM designs.
+Based on the observed data, the true values of the parameters, $\gamma_0, \beta_1, \beta_2$, $\beta_3$, and $\sigma^2$ were found to be -2.3, 0.56, 1.28, 0.2, and 1.0 respectively. \par
+Once the samples were drawn, they were transformed under the three different missingness structures.
 These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed.
@@
 The altered Split Form, while similar, is fully measured on two of the measurement occasions.
-Because there are days which are fully observed the relationships between variables may be clearer, allowing the imputation procedure to run more effectively.
+Because there are days which are fully observed, the relationships between variables may be clearer, allowing the imputation procedure to run more effectively.
 On the other hand, the Wave Missingness design shows two days in which no questions are asked but the full questionnaire is given on the remaining days.
@@
 Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 25\%, 50\%, and 75\% missing data.
-Previous work by \citet{rhemtulla2014planned} has found that for low levels of missingness (25\%) the Three-Form design outperforms the Wave Missingness design in its ability to capture latent growth curve model parameters.
-However, because only low-levels of missingness are tested we do not know if this relationship holds at moderate or high levels.
+Previous work by \citet{rhemtulla2014planned} found that for low levels of missingness (25\%) the Three-Form design outperforms the Wave Missingness design in capturing latent growth curve model parameters.
+However, because only low-levels of missingness are tested it is unknown whether this relationship holds at moderate or high levels.
 We hope that by including these different levels of missingness we will be able to see how these designs perform at all levels of the missingness spectrum.
 \par
-Once missingness was created we used Multiple Imputation techniques to estimate the relationship between Medication Adherence and the other variables in our model.
+Once missingness was created, Multiple Imputation techniques were applied to estimate the relationship between medication adherence and the other variables in our model.
 Because we have control over the missing data mechanism, we know the data is MCAR.
@@
 
-After imputations the logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}.
+After imputating, a logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}.
 From here, the results from each PM design were evaluated based on bias, percent bias, mean squared error (MSE), coverage, confidence interval (CI) length, and the fraction of missing information (FMI).
-The FMI is a measure of how much of the MI sampling variance comes from differences between imputations.
-Besides comparing the results between each of the PM designs we also included the results of these same analyses taken from before missingness was imposed.
+The FMI is a measure of how much of the MI sample variance comes from differences between imputations.
+In addition to comparing the results between each of the PM designs, the same analyses were also performed before missingness was imposed.
 \par
 
-When determining if the PM designs are performing sufficiently well it is important to consider how well the simulated samples performed before we added a missingness structure.
-For example, imagine we have two full data samples with respective biases on the $\beta_1$ estimate of 0.13 and 0.15.
-Further, after imposing different PM design structures on these samples we obtained the average biases of 0.14 and 0.15 respectively.
-It would be unfair to claim that the first
-PM design performed better than the second because, by chance, it was based off of a more representative sample. We kept this fact in mind when determining our evaluation criteria. \par
+When determining if the PM designs are performing sufficiently, it is important to consider how well the simulated samples performed before adding a missingness structure.
+For example, consider two full data samples with respective biases on the $\beta_1$ estimate of 0.13 and 0.15.
+Further, after imposing different PM design structures on these samples, the average biases are 0.14 and 0.15 respectively.
+It would be unfair to claim that the first PM design performed better than the second because, by chance, it was based off of a more representative sample.
+This fact was considered when determining the evaluation criteria.
+\par
 
 For bias, percent bias, and MSE we claimed that an increase of more than 40\% in these measurements after imposing missingness indicates that the PM design is inappropriate.
-For instance, if the complete data shows a percent bias of 10\%, anything higher than 14\% ($0.1*1.4$) would be unacceptable.
+For instance, if the complete data shows a percent bias of 10\%, anything higher than 14\% would be unacceptable.
 An increase of this size has the ability to negatively effect efficiency of our estimation.
@@
 If a 95\% CI has a true coverage of 90\% than the Type I error rate is double what it should be.
-Because MI accounts for uncertainty in the imputation process coverages should have been similar despite the added missingness.
+Because MI accounts for uncertainty in the imputation process, coverages should be similar despite the added missingness.
 In terms of confidence interval lengths, if one PM design provides similar rates of coverage to another while maintaining shorter intervals than this is considered the better of the two methods.
@@
 
-We repeated this process under three modified simulation scenarios mentioned in the following sections.
-We note that while typically these PM designs would be compared against the results obtained using a complete case analysis \citep{rhemtulla2016asymptotic} we decided against this approach because it would fundamentally alter the form of our data.
-To be more concrete, complete case analysis on the Split Form design would remove all observations (all observations have some missing values).
+This process was repeated under the three modified simulation scenarios mentioned in the following sections.
+Note that while typically these PM designs would be compared against the results obtained using a complete case analysis \citep{rhemtulla2016asymptotic}, this approach was avoided as it would fundamentally alter the form of the data.
+Specifically, complete case analysis removes any observation with any missing values.
+Then, for the Split Form design this would remove all observations.
 In the Wave Missingness setup, complete case analysis would shorten the length of the longitudinal study.
@@
 \subsubsection{Increased Sample Size}
-In order to evaluate the impact of sample size on estimation we took the format of the original data, which included sixty participants, and expanded it to include one-hundred and twenty.
+In order to evaluate the impact of sample size on estimation, the original sample size of 60 participants was expanded to 120.
 The rest of the simulation process was carried out as before.
-We noted earlier that cost savings created from the PM designs could allow us to enroll more participants.
-Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, then researchers can design missingness in whichever method is most convenient.
-We further note, that because Wave Missingness allows for greater savings an increase in sample size is more reasonable for that type of Missingness.
+As noted earlier, the cost savings gleaned from the PM designs could allow us to enroll more participants.
+Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, researchers can design missingness in whichever method is most convenient.
+Furthermore, because Wave Missingness allows for greater savings, an increase in sample size is more reasonable for that type of missingness.
 \par
@@
 While this fact was accounted for in the original simulations, it was not in this set of simulations.
-If the probability of answering “yes” on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations then in this scenario it is a function of only the baseline variables.
+If the probability of answering “yes” on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables.
 This implies that each of the questions are conditionally independent of each other given the baseline variables.
@@
 \subsubsection{High Time Effect}
-In this final scenario we hoped to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable.
+In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable.
 To do this we changed the value of the parameters $\gamma_0, \beta_1, \beta_2,$ and $\beta_3$ to -4.6, 0.28, 0.64, and 0.2 respectively.
-We note that instead of increasing the value of $\beta_3$, the slope for time effect, we decreased all the other parameters.
-We did this because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1.
-By decreasing the other variables effects we were able to ensure that time has a disproportionate effect without incurring this problem.
+Note that instead of increasing the value of $\beta_3$, the slope for time effect, all the other parameters were decreased.
+This was done because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1.
+Decreasing the other variables effects ensured that time has a disproportionate effect without this problem.
 The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point.
@@
 \label{sec:3.1}
-The first set of simulations we ran had the parameters in our random-intercept logistic model set as $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$.
+The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$.
 The effects of the variables here are comparable to those found in the original dataset.
 This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design.
-Before we imposed a missingness structure on our two-hundred simulated samples we obtained the full data results shown in Table \ref{tab:table2}.
-We note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
+Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:table2}.
+Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
 

### 2018-05-16 Documentation/manuscript.tex
Paper edits in Manuscript.RNW

--- 2018-02-22 comparing_05222017.tex
@@
 
+\usepackage{Sweave}
 \begin{document}
+\input{manuscript-concordance}
 
@@
 
-Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are so named because of the way in which they are implemented.
-Instead of giving participants one large survey, researchers will create multiple “forms”, each containing only a subset of the full survey’s questions.
-A common setup is the three-form design \citep{graham1996maximizing}.
-In the three-form design the full survey is split into four blocks, X, A, B, and C.
-Each form of the survey includes the X block as well as two of the other three blocks.
-This leaves us with the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded.
-We note that every block is paired together in at least one of the forms.
-By designing our forms in this manner we are able to estimate the relationship between any given items regardless of which blocks they are in.
-That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows us to do that.
-\par
+NA
 
-\begin{table}[h!]
-	\centering
-	\caption{The Three Form PM Design}
-	\label{tab:table10}
-	\setlength{\tabcolsep}{1cm}
-	\begin{tabular}{c|cccc}
-		\toprule
-		& \multicolumn{4}{c}{Block} \\
-		Form & X & A & B & C \\
-		\midrule
-		1 & 1 & 1 & 1 & 0 \\
-		2 & 1 & 1 & 0 & 1 \\
-		3 & 1 & 0 & 1 & 1 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+We need to talk about the other type of split design that we used here which was that X of the 8 questions are randomly omitted on each day.
+
+% \begin{table}[h!]
+% 	\centering
+% 	\caption{The Three Form PM Design}
+% 	\label{tab:table10}
+% 	\setlength{\tabcolsep}{1cm}
+% 	\begin{tabular}{c|cccc}
+% 		\toprule
+% 		& \multicolumn{4}{c}{Block} \\
+% 		Form & X & A & B & C \\
+% 		\midrule
+% 		1 & 1 & 1 & 1 & 0 \\
+% 		2 & 1 & 1 & 0 & 1 \\
+% 		3 & 1 & 0 & 1 & 1 \\
+% 		\bottomrule
+% 	\end{tabular}
+% \end{table}
+
+Figure \ref{fig:misslow} is
 
@@
 \label{sec:2.2}
-The first step in the process of creating our simulated datasets was to use the data from \citet{pellowski2016alcohol} and obtain parameter estimates to quantify the relationships between variables.
-We then treated these estimated relationships as the “true” relationships and drew two-hundred samples using these parameters.
-While we would have liked to simulate a larger number of samples we were limited by computational ability.
-Our purpose in simulating these datasets was to see how well they would be able to capture the true relationship between medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score).
-Specifically, our model of interest is the random intercept model with time effect found below: \\
+NA
 
@@
 \subsubsection{Low Inter-Survey Correlation}
-For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best.
-To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days.
-While this fact was accounted for in the original simulations, it was not in this set of simulations.
-If the probability of answering “yes” on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations then in this scenario it is a function of only the baseline variables.
-This implies that each of the questions are conditionally independent of each other given the baseline variables.
-If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal.
-\par
+NA
 \subsubsection{High Time Effect}
@@
 
-\begin{table}[b!]
+\begin{Schunk}
+\begin{Sinput}
+> load("C:/Users/Josie/Documents/GitHub/designedmissingness/Results/tables20180509_60_1_high.RData")
+> high <- d
+> load("C:/Users/Josie/Documents/GitHub/designedmissingness/Results/tables20180509_60_1_med.RData")
+> med <- d
+> load("C:/Users/Josie/Documents/GitHub/designedmissingness/Results/tables20180509_60_1_low.RData")
+> low <- d
+> library(xtable)
+> print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
+\end{Sinput}
+\begin{Soutput}
+% latex table generated in R 3.4.1 by xtable 1.8-2 package
+% Wed May 16 16:26:28 2018
+\begin{table}[ht]
 \centering
-	\caption{Results of Analysis before imposing Missingness in each Scenario}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table2}
-	\begin{tabular}{cc|ccccc}
-		\toprule
-		Scenario & Parameter & Bias & Percent Bias & MSE & Coverage & CI Length \\
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Primary \\ Analysis (N=60)}} 
-		& $\gamma_0$ & 0.151 & 6.55\% & 0.037 & 99.0\% & 0.750 \\
-		& $\beta_1$ & 0.133 & 23.75\% & 0.028 & 95.5\% & 0.652 \\
-		& $\beta_2$ & 0.120 & 9.40\% & 0.022 & 97.5\% & 0.610 \\
-		& $\beta_3$ & 0.007 & 3.42\% & 7.11$*10^-5$ & 97.0\% & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Increased \\ Sample (N=120)}} 
-		& $\gamma_0$ & 0.106 & 4.61\% & 0.018 & 98.0\% & 0.528 \\
-		& $\beta_1$ & 0.099 & 17.63\% & 0.016 & 93.0\% & 0.460 \\
-		& $\beta_2$ & 0.091 & 7.12\% & 0.013 & 95.5\% & 0.429 \\
-		& $\beta_3$ & 0.005 & 2.34\% & 3.52$*10^-5$ & 96.5\% & 0.024 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Low \\Inter-Survey Correlation (N=60)}} 
-		& $\gamma_0$ & 0.145 & 6.29\% & 0.033 & 99.0\% & 0.747 \\
-		& $\beta_1$ & 0.130 & 23.27\% & 0.027 & 94.5\% & 0.651 \\
-		& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 94.0\% & 0.611 \\
-		& $\beta_3$ & 0.007 & 3.69\% & 8.88$*10^-5$ & 93.0\% & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{High \\Time Effect (N=60)}}
-		& $\gamma_0$ & 0.170 & 3.69\% & 0.045 & 98.5\% & 0.888 \\
-		& $\beta_1$ & 0.123 & 43.86\% & 0.024 & 96.0\% & 0.598 \\
-		& $\beta_2$ & 0.124 & 19.35\% & 0.025 & 93.5\% & 0.575 \\
-		& $\beta_3$ & 0.006 & 2.95\% & 5.50$*10^-5$ & 95.5\% & 0.030 \\
-		\bottomrule
+\begin{tabular}{lllrrrr}
+  \hline
+"" & "" & "" & Coverage & Bias & MSE & FMI \\ 
+  \hline
+ &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
+   &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
+   &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
+   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
+   &  &  & 0.986 & 0.040 & 0.019 & 0.012 \\ 
+   &  &  & 0.993 & -0.168 & 0.750 & 0.557 \\ 
+   &  &  & 0.932 & 0.008 & 0.024 & 0.002 \\ 
+   &  &  & 0.940 & -0.000 & 0.000 & 0.008 \\ 
+   &  &  & 0.984 & 0.036 & 0.027 & 0.030 \\ 
+   &  &  & 0.991 & -0.713 & 9.933 & 0.625 \\ 
+   &  &  & 0.932 & 0.009 & 0.027 & 0.005 \\ 
+   &  &  & 0.939 & -0.000 & 0.000 & 0.021 \\ 
+   &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
+   &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
+   &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
+   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
+   &  &  & 0.988 & 0.040 & 0.018 & 0.010 \\ 
+   &  &  & 0.994 & -0.167 & 0.782 & 0.549 \\ 
+   &  &  & 0.931 & 0.009 & 0.024 & 0.002 \\ 
+   &  &  & 0.944 & -0.000 & 0.000 & 0.006 \\ 
+   &  &  & 0.983 & 0.036 & 0.022 & 0.027 \\ 
+   &  &  & 0.990 & -0.686 & 10.509 & 0.665 \\ 
+   &  &  & 0.928 & 0.009 & 0.026 & 0.007 \\ 
+   &  &  & 0.946 & -0.000 & 0.000 & 0.023 \\ 
+   &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
+   &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
+   &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
+   &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
+   &  &  & 0.991 & 0.029 & 0.018 & 0.055 \\ 
+   &  &  & 0.988 & -0.112 & 0.345 & 0.752 \\ 
+   &  &  & 0.934 & 0.009 & 0.024 & 0.007 \\ 
+   &  &  & 0.951 & -0.000 & 0.000 & 0.032 \\ 
+   &  &  & 0.994 & -0.003 & 0.022 & 0.258 \\ 
+   &  &  & 0.988 & -0.105 & 0.284 & 0.903 \\ 
+   &  &  & 0.937 & 0.011 & 0.025 & 0.039 \\ 
+   &  &  & 0.960 & -0.000 & 0.000 & 0.175 \\ 
+   \hline
 \end{tabular}
 \end{table}
-
-Of note in the complete-data primary analysis is that the coverage of our 95\% CIs is larger than expected for our parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large.
-This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}.
-Nevertheless, we should keep this in mind when analyzing our results from the PM designs provided in Table \ref{tab:table3}.
-In Table \ref{tab:table3} as in Tables \ref{tab:table4}, \ref{tab:table5}, and \ref{tab:table6} bold values indicate "Unacceptable" results.
-That is, a Bias, Percent Bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
-
-\begin{table}[p]
-	\centering
-	\caption{Primary Simulation Results (N=60)}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table3}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.151 & 6.59\% & 0.037 & 99.5\% & 0.753 & 0.009 \\
-		&& $\beta_1$ & 0.139 & 24.78\% & 0.029 & 96.0\% & 0.693 & 0.112 \\
-		&& $\beta_2$ & 0.120 & 9.41\% & 0.022 & 97.0\% & 0.610 & 0.002 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.12$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.153 & 6.67\% & 0.037 & 99.0\% & 0.765 & 0.040 \\
-		&& $\beta_1$ & 0.162 & 28.93\% & 0.041 & 95.5\% & 0.869 & 0.390 \\
-		&& $\beta_2$ & 0.121 & 9.51\% & 0.022 & 97.0\% & 0.616 & 0.007 \\
-		&& $\beta_3$ & 0.007 & 3.40\% & 6.99$*10^-5$ & 98.5\% & 0.034 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.154 & 6.70\% & 0.039 & 98.5\% & 0.818 & 0.147 \\
-		&& $\beta_1$ & \textbf{0.225} & \textbf{40.16}\% & \textbf{0.076} & 97.5\% & 1.464 & 0.710 \\
-		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 97.5\% & 0.611 & 0.022 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.02$*10^-5$ & 98.0\% & 0.035 & 0.032 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.151 & 6.57\% & 0.037 & 98.0\% & 0.753 & 0.008 \\
-		&& $\beta_1$ & 0.137 & 24.55\% & 0.030 & 96.0\% & 0.690 & 0.105 \\
-		&& $\beta_2$ & 0.120 & 9.39\% & 0.022 & 97.5\% & 0.611 & 0.002 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.153 & 6.67\% & 0.038 & 99.5\% & 0.760 & 0.030 \\
-		&& $\beta_1$ & 0.151 & 26.93\% & 0.036 & 96.0\% & 0.811 & 0.324 \\
-		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 96.0\% & 0.611 & 0.006 \\
-		&& $\beta_3$ & 0.007 & 3.44\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.164 & 7.13\% & 0.042 & 98.0\% & 0.799 & 0.105 \\
-		&& $\beta_1$ & \textbf{0.225} & \textbf{40.14\%} & \textbf{0.080} & 96.0\% & 1.265 & 0.640 \\
-		&& $\beta_2$ & 0.117 & 9.13\% & 0.021 & 97.5\% & 0.615 & 0.019 \\
-		&& $\beta_3$ & 0.007 & 3.46\% & 7.07$*10^-5$ & 98.0\% & 0.034 & 0.023 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.152 & 6.61\% & 0.037 & 99.5\% & 0.757 & 0.023 \\
-		&& $\beta_1$ & 0.147 & 26.25\% & 0.033 & 96.0\% & 0.767 & 0.270 \\
-		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 96.0\% & 0.610 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.41\% & 6.97$*10^-5$ & 98.0\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.157 & 6.84\% & 0.039 & 100.0\% & 0.767 & 0.052 \\
-		&& $\beta_1$ & \textbf{0.190} & \textbf{33.95\%} & \textbf{0.058} & 94.5\% & 0.934 & 0.465 \\
-		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 97.5\% & 0.609 & 0.008 \\
-		&& $\beta_3$ & 0.007 & 3.34\% & 6.80$*10^-5$ & 98.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.168 & 7.30\% & 0.045 & 99.5\% & 0.807 & 0.129 \\
-		&& $\beta_1$ & \textbf{0.290} & \textbf{51.77\%} & \textbf{0.132} & \textbf{88.5\%} & 1.335 & 0.680 \\
-		&& $\beta_2$ & 0.119 & 9.32\% & 0.022 & 96.0\% & 0.614 & 0.017 \\
-		&& $\beta_3$ & 0.007 & 3.40\% & 6.96$*10^-5$ & 98.5\% & 0.034 & 0.025 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{Increased Sample Size simulation Results (N=120)}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table4}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.106 & 4.60\% & 0.017 & 98.5\% & 0.533 & 0.022 \\
-		&& $\beta_1$ & 0.106 & 18.96\% & 0.018 & 96.0\% & 0.548 & 0.263 \\
-		&& $\beta_2$ & 0.091 & 7.14\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.33\% & 3.47$*10^-5$ & 96.5\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.112 & 4.85\% & 0.019 & 98.0\% & 0.542 & 0.057 \\
-		&& $\beta_1$ & 0.134 & 23.86\% & \textbf{0.027} & 95.0\% & 0.696 & 0.489 \\
-		&& $\beta_2$ & 0.092 & 7.15\% & 0.013 & 96.5\% & 0.430 & 0.009 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.110 & 4.80\% & 0.019 & 99.5\% & 0.575 & 0.153 \\
-		&& $\beta_1$ & \textbf{0.194} & \textbf{34.59\%} & \textbf{0.057} & 94.5\% & 1.088 & 0.742 \\
-		&& $\beta_2$ & 0.092 & 7.20\% & 0.013 & 95.0\% & 0.432 & 0.021 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.42$*10^-5$ & 97.5\% & 0.024 & 0.026 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.107 & 4.64\% & 0.017 & 98.0\% & 0.533 & 0.022 \\
-		&& $\beta_1$ & 0.111 & 19.80\% & 0.020 & 94.5\% & 0.545 & 0.263 \\
-		&& $\beta_2$ & 0.091 & 7.08\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.115 & 4.99\% & 0.020 & 98.0\% & 0.542 & 0.056 \\
-		&& $\beta_1$ & 0.138 & 24.65\% & \textbf{0.028} & 94.5\% & 0.693 & 0.494 \\
-		&& $\beta_2$ & 0.091 & 7.24\% & 0.013 & 96.0\% & 0.430 & 0.008 \\
-		&& $\beta_3$ & 0.005 & 2.34\% & 3.54$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.115 & 5.01\% & 0.020 & 99.0\% & 0.563 & 0.119 \\
-		&& $\beta_1$ & \textbf{0.188} & \textbf{33.65\%} & \textbf{0.058} & 91.5\% & 0.958 & 0.681 \\
-		&& $\beta_2$ & 0.092 & 7.16\% & 0.013 & 96.0\% & 0.432 & 0.018 \\
-		&& $\beta_3$ & 0.005 & 2.30\% & 3.44$*10^-5$ & 96.0\% & 0.024 & 0.020 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.108 & 4.72\% & 0.018 & 98.0\% & 0.533 & 0.024 \\
-		&& $\beta_1$ & 0.123 & 21.90\% & \textbf{0.024} & 92.0\% & 0.551 & 0.287 \\
-		&& $\beta_2$ & 0.092 & 7.18\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.35\% & 3.51$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.111 & 4.84\% & 0.019 & 99.0\% & 0.540 & 0.052 \\
-		&& $\beta_1$ & \textbf{0.168} & \textbf{30.02\%} & \textbf{0.043} & \textbf{85.5\%} & 0.671 & 0.489 \\
-		&& $\beta_2$ & 0.092 & 7.22\% & 0.013 & 95.0\% & 0.429 & 0.007 \\
-		&& $\beta_3$ & 0.005 & 2.32\% & 3.42$*10^-5$ & 97.0\% & 0.024 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.123 & 5.33\% & 0.023 & 99.0\% & 0.558 & 0.108 \\
-		&& $\beta_1$ & \textbf{0.248} & \textbf{44.26\%} & \textbf{0.099} & \textbf{82.0\%} & 0.894 & 0.666 \\
-		&& $\beta_2$ & 0.094 & 7.36\% & 0.014 & 96.0\% & 0.430 & 0.013 \\
-		&& $\beta_3$ & 0.005 & 2.36\% & 3.53$*10^-5$ & 96.0\% & 0.024 & 0.015 \\
-		\bottomrule
-	\end{tabular}	
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{Low Inter-Survey Correlation Simulation Results (N=60)}
-	\label{tab:table5}
-	\setlength{\tabcolsep}{0.1cm}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.146 & 6.34\% & 0.033 & 99.0\% & 0.755 & 0.025 \\
-		&& $\beta_1$ & 0.150 & 26.82\% & 0.034 & 95.5\% & 0.782 & 0.278 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.612 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.64\% & 8.68$*10^-5$ & 92.5\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.148 & 6.43\% & 0.034 & 99.0\% & 0.772 & 0.067 \\
-		&& $\beta_1$ & \textbf{0.183} & \textbf{32.65\%} & \textbf{0.053} & 95.0\% & 1.032 & 0.526 \\
-		&& $\beta_2$ & 0.125 & 9.80\% & 0.026 & 94.0\% & 0.613 & 0.010 \\
-		&& $\beta_3$ & 0.007 & 3.63\% & 8.73$*10^-5$ & 92.5\% & 0.035 & 0.015 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.155 & 6.74\% & 0.036 & 99.5\% & 0.825 & 0.166 \\
-		&& $\beta_1$ & \textbf{0.276} & \textbf{49.31\%} & \textbf{0.116} & 95.0\% & 1.567 & 0.749 \\
-		&& $\beta_2$ & 0.124 & 9.71\% & 0.025 & 94.0\% & 0.618 & 0.025 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.73$*10^-5$ & 93.5\% & 0.035 & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.141 & 6.13\% & 0.031 & 99.0\% & 0.754 & 0.023 \\
-		&& $\beta_1$ & 0.139 & 25.80\% & 0.030 & 95.5\% & 0.772 & 0.260 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.612 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.55$*10^-5$ & 92.5\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.149 & 6.48\% & 0.035 & 99.5\% & 0.767 & 0.056 \\
-		&& $\beta_1$ & 0.170 & 30.44\% & \textbf{0.044} & 97.0\% & 0.968 & 0.486 \\
-		&& $\beta_2$ & 0.125 & 9.79\% & 0.025 & 93.5\% & 0.612 & 0.009 \\
-		&& $\beta_3$ & 0.007 & 3.64\% & 8.58$*10^-5$ & 92.5\% & 0.034 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.149 & 6.47\% & 0.036 & 98.5\% & 0.809 & 0.139 \\
-		&& $\beta_1$ & \textbf{0.228} & \textbf{40.70\%} & \textbf{0.088} & 96.0\% & 1.425 & 0.708 \\
-		&& $\beta_2$ & 0.125 & 9.74\% & 0.026 & 94.0\% & 0.617 & 0.021 \\
-		&& $\beta_3$ & 0.007 & 3.62\% & 8.65$*10^-5$ & 93.5\% & 0.035 & 0.027 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.138 & 6.02\% & 0.031 & 99.5\% & 0.754 & 0.025 \\
-		&& $\beta_1$ & 0.158 & 28.17\% & 0.036 & 96.5\% & 0.776 & 0.286 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.611 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.50$*10^-5$ & 92.5\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.148 & 6.43\% & 0.034 & 99.5\% & 0.765 & 0.053 \\
-		&& $\beta_1$ & \textbf{0.197} & \textbf{35.14\%} & \textbf{0.059} & 91.0\% & 0.939 & 0.472 \\
-		&& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 93.5\% & 0.611 & 0.007 \\
-		&& $\beta_3$ & 0.007 & 3.60\% & 8.48$*10^-5$ & 92.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.158 & 6.86\% & 0.040 & 98.5\% & 0.799 & 0.122 \\
-		&& $\beta_1$ & \textbf{0.303} & \textbf{54.18\%} &\textbf{0.148} & \textbf{89.5\%} & 1.290 & 0.676 \\
-		&& $\beta_2$ & 0.127 & 9.94\% & 0.027 & 95.5\% & 0.615 & 0.015 \\
-		&& $\beta_3$ & 0.007 & 3.62\% & 8.77$*10^-5$ & 93.5\% & 0.035 & 0.021 \\
-		\bottomrule
-	\end{tabular}	
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{High Time Effect Simulation Results (N=60)}
-	\label{tab:table6}
-	\setlength{\tabcolsep}{0.1cm}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.169 & 3.67\% & 0.045 & 99.0\% & 0.895 & 0.015 \\
-		&& $\beta_1$ & 0.133 & 47.54\% & 0.029 & 96.0\% & 0.708 & 0.262 \\
-		&& $\beta_2$ & 0.124 & 19.33\% & 0.025 & 93.5\% & 0.576 & 0.003 \\
-		&& $\beta_3$ & 0.006 & 2.96\% & 5.50$*10^-5$ & 94.5\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.174 & 3.77\% & 0.047 & 98.5\% & 0.912 & 0.050 \\
-		&& $\beta_1$ & \textbf{0.181} & \textbf{64.59\%} & \textbf{0.049} & 96.0\% & 0.981 & 0.554 \\
-		&& $\beta_2$ & 0.124 & 19.44\% & 0.025 & 94.0\% & 0.578 & 0.007 \\
-		&& $\beta_3$ & 0.006 & 2.97\% & 5.55$*10^-5$ & 96.0\% & 0.030 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.177 & 3.85\% & 0.049 & 98.0\% & 0.954 & 0.117 \\
-		&& $\beta_1$ & \textbf{0.243} & \textbf{86.63\%} & \textbf{0.097} & 93.0\% & 1.433 & 0.729 \\
-		&& $\beta_2$ & 0.124 & 19.37\% & 0.025 & 94.0\% & 0.581 & 0.016 \\
-		&& $\beta_3$ & 0.006 & 2.97\% & 5.70$*10^-5$ & 94.0\% & 0.030 & 0.025 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.171 & 3.72\% & 0.046 & 99.0\% & 0.895 & 0.015 \\
-		&& $\beta_1$ & 0.142 & 50.55\% & 0.033 & 94.5\% & 0.717 & 0.272 \\
-		&& $\beta_2$ & 0.124 & 19.36\% & 0.025 & 93.5\% & 0.577 & 0.002 \\
-		&& $\beta_3$ & 0.006 & 2.95\% & 5.48$*10^-5$ & 95.5\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.176 & 3.82\% & 0.048 & 99.0\% & 0.905 & 0.038 \\
-		&& $\beta_1$ & 0.168 & 60.10\% & \textbf{0.043} & 95.5\% & 0.903 & 0.486 \\
-		&& $\beta_2$ & 0.124 & 19.36\% & 0.025 & 93.5\% & 0.581 & 0.006 \\
-		&& $\beta_3$ & 0.006 & 2.95\% & 5.60$*10^-5$ & 95.0\% & 0.030 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.177 & 3.84\% & 0.051 & 99.5\% & 0.947 & 0.108 \\
-		&& $\beta_1$ & \textbf{0.257} & \textbf{91.96\%} & \textbf{0.097} & 94.5\% & 1.381 & 0.714 \\
-		&& $\beta_2$ & 0.124 & 19.34\% & 0.025 & 94.5\% & 0.581 & 0.014 \\
-		&& $\beta_3$ & 0.006 & 3.01\% & 5.76$*10^-5$ & 95.0\% & 0.030 & 0.023 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.170 & 3.70\% & 0.046 & 99.0\% & 0.895 & 0.016 \\
-		&& $\beta_1$ & 0.135 & 48.11\% & 0.026 & 96.5\% & 0.720 & 0.290 \\
-		&& $\beta_2$ & 0.124 & 19.40\% & 0.025 & 93.5\% & 0.576 & 0.002 \\
-		&& $\beta_3$ & 0.006 & 2.94\% & 5.50$*10^-5$ & 95.0\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.173 & 3.77\% & 0.047 & 99.0\% & 0.904 & 0.035 \\
-		&& $\beta_1$ & \textbf{0.186} & \textbf{66.53\%} & \textbf{0.052} & 92.0\% & 0.864 & 0.466 \\
-		&& $\beta_2$ & 0.124 & 19.40\% & 0.025 & 93.5\% & 0.576 & 0.004 \\
-		&& $\beta_3$ & 0.006 & 2.94\% & 5.50$*10^-5$ & 96.0\% & 0.030 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.188 & 4.09\% & 0.055 & 98.5\% & 0.946 & 0.105 \\
-		&& $\beta_1$ & \textbf{0.322} & \textbf{115.10\%} & \textbf{0.149} & \textbf{85.5\%} & 1.306 & 0.712 \\
-		&& $\beta_2$ & 0.127 & 19.87\% & 0.026 & 93.5\% & 0.580 & 0.011 \\
-		&& $\beta_3$ & 0.006 & 3.02\% & 5.75$*10^-5$ & 95.0\% & 0.030 & 0.025 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-For the Split Form and Altered Split Form designs seen in Table \ref{tab:table3}, we note that the greatest loss in efficiency was on the $\beta_1$ estimate.
-While the CI coverage remained high at all levels of missingness for the two designs the bias, percent bias, and MSE reached unacceptable levels at the high missingness level.
-We also point out that the Altered Split Form design did not perform significantly better than the regular Split Form design.
-While some individual measurements outperformed those from the Split Form design, bias on $\beta_1$ for example, it underperformed in others, such as percent bias on $\beta_3$.
-In reference to the FMI on the $\beta_1$ estimate, we can see that at low and medium missingness both Split Form designs performed well.
-That is to say, there was less variance in the results from our imputed datasets than we expected given the amount of missing data.\par
-
-Towards the bottom of Table \ref{tab:table3} we see that the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at medium and high levels of missingness.
-Moreover, at high levels of missingness even coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.
-Additionally, we see that CI length for the $\beta_1$ estimate was roughly equal across all designs, despite the fact that the Wave Missingness design provided more biased estimates.
-\par
-
-\subsection{Increased Sample Size}
-\label{sec:3.2}
-The next simulation scenario we tested was under an increased sample size.
-All parameter values were held the same as in the original set of simulations but instead of simulating data for 60 participants here we used 120 participants.
-Table \ref{tab:table2}, again, contains the results of our analysis before applying any PM design.
-\par
-
-We compare the results from the full-data simulations to those obtained from the PM designs, shown in Table \ref{tab:table4}.
-The first thing we notice is that the bias on all parameters is lower than it was in the smaller sample size simulations.
-Next, the Split Form design performed similarly well under this simulation scenario as in the first.
-At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable.
-However, the CI length here is relatively far from the complete-data measurement in Table \ref{tab:table2}.
-The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088.
-We also point out that the percent bias on the $\beta_1$ estimate is not seriously different from that obtained in the small sample scenario.
-For example, at medium levels of missingness the percent bias on $\beta_1$ here is 23.86\% while for the smaller sample it was 23.75\%.
-Similarly to the Split Form design, the Altered Split Form Design also provided unacceptable results for the MSE of the $\beta_1$ estimate at medium missingness and unacceptable bias, percent bias, and MSE at high levels.
-\par
-For the Wave Missingness design we continue to see the issues pointed out in the small sample simulations.
-That is, for the $\beta_1$ estimate we have unacceptable measurements at medium and high levels of missingness and a steep drop off in coverage probability for our 95\% CIs.
-In fact, at medium and high levels of missingness we find coverages of 85.5\% and 82.0\%.
-We also continue to see that the $\gamma_0$ parameter is being estimated poorly at high levels of missing data under the Wave Missingness design.
-\par
-
-\subsection{Low Inter-Survey Correlation}
-\label{sec:3.3}
-For the next set of simulations we returned to the smaller sample size but decreased the level of inter-survey correlation.
-As mentioned in section 3.2.2 we made sure that there was no direct predictive relationship between questions in our survey.
-The results obtained from our full data simulations are provided in Table \ref{tab:table2} while the results from our PM designs are given in Table \ref{tab:table5}.
-\par
-
-For the Split Form design it is important to notice that the efficiency of the $\beta_1$ estimate decreases much more rapidly than in our first set of simulations where survey questions were predictive of one another.
-For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be 0.150 and 0.276 at high levels.
-This left us with an increase in average bias of 0.126.
-If we check the same increase in the original simulations we see that the bias only increased by 0.071.
-This loss in efficiency is seen in the other measurements on the $\beta_1$ estimate as well.
-Moreover, we note that the Split Form design performs unacceptably in terms of bias, percent bias, and MSE at medium levels of missingness.
-This was not the case in the other missingness scenarios.
-\par
-
-In the Altered Split Form design at medium levels of missingness the MSE is outside of the acceptable range and at high levels bias, are percent bias are unacceptable as well.
-We further note that the coverage of the $\beta_1$ CIs was quite a bit higher than in the full-data simulations.
-That is, while the coverage probability obtained in the full-data simulations was 94.5\%, under this Altered Split Form design we obtained coverages of 95.5\%, 97.0\%, and 96.0\% at low, medium, and high levels of missingness respectively.
-\par
-
-Concerning the Wave Missingness design we, again, see the issues of unacceptable bias, percent bias and MSE.
-However, at low levels of missingness the coverage of our $\beta_1$ estimate was fairly good (96.5\% compared to 94.5\% in the full data).
-This positive coverage did not hold throughout the other levels of missingness as coverage dropped to 89.5\% in the high missingness scenario.
-As in other scenarios, the CI lengths produced under the Wave Missingness design are similar to those produced in the Split Form designs despite an increase in bias.
-However, this increase in bias is less dramatic than in other scenarios.
-For example, at high levels of missingness in the original simulations the average bias on the $\beta_1$ estimate was 0.065 higher for the Wave Missingness design (at 0.290) than in the Split Form design (0.225).
-In this simulation scenario that same difference was only 0.027.
-Moreover, while the estimation of $\gamma_0$ was unacceptable at high levels of missingness in the other simulation scenarios, here it was in the acceptable range.\par
-
-\subsection{High Time Effect}
-\label{sec:3.4}
-In the final scenario we tested to see how the PM designs would capture a model where time had a disproportionately large effect.
-In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$.
-The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:table6}.
-\par
-
-The effects of imposing Split Form missingness in this high time effect scenario are similar to those under the low inter-survey correlation scenario.
-At low levels of missingness bias, percent bias, MSE, and coverage for $\beta_1$ are all within the acceptable range.
-At medium and high levels of missingness bias, percent bias, and MSE are unacceptably high.
-\par
-
-The Altered Split Form design performed slightly better than the normal Split Form design under this simulation scenario.
-We do note, though, that while the normal Split Form design provided unacceptable bias and percent bias for the $\beta_1$ estimate at medium levels of missingness, this was not true in the Altered Split Form design.
-Additionally, we point out that at medium and high levels of missingness we saw an improvement from the Split Form design in the CI lengths for the $\beta_1$ estimate.
-In the Split Form design the CI lengths were recorded as 0.981 and 1.433 at medium and high missingness.
-Under the Altered Split Form design these measurements were 0.903 and 1.381.
-\par
-
-Under this simulation scenario, at low levels of missingness we see that the Wave Missingness Design performs similarly to the Split Form and Altered Split Form designs.
-The bias, percent bias, MSE, and CI coverage for $\beta_1$ all performed acceptably using the Wave Missingness design at low levels of missingness.
-Moreover, as missingness increases this design shows itself to be unsuitable in terms of estimating $\beta_1$ for the same reasons noted in the other scenarios.
-\par
-
-\subsection{Interpretation}
-\label{sec:3.5}
-We note two commonalities throughout our simulation scenarios.
-The first is that the Altered Split Form design consistently failed to produce better results than the normal Split Form design.
-Secondly, the Wave Missingness Design resulted in unacceptably poor estimation for anything but low levels of missingness.
-\par
-
-This first result, the lack of improvement seen in the Altered Split form design is surprising.
-By keeping a small number of measurement occasions fully observed we would have expected the imputation process to perform more effectively and improve our estimates.
-However, even factoring in the slight decrease in overall missingness, this design performed only equally as well as the normal Split Form design.
-This may be a result of the fact that the number of observations we left fully observed was small, only two out of the forty-five days (or about 4.4\% of days) were fully observed.
-While it may be interesting to see if the inclusion of more fully observed days is capable of improving our estimates, perhaps keeping five days (11.1\%) fully observed, we would need to be careful about raising this number too high.
-If the cost or burden of observations is a limiting factor then collecting full data on even 10\% of the days may be unnecessarily burdensome.
-\par
-
-Of larger concern, though, is the steep drop-off in estimating quality of the Wave Missingness design as missingness increased.
-In every scenario we tested, the Wave Missingness design produced unacceptable bias, percent bias, and MSE at medium and high levels of missingness.
-We also note that despite increased bias on estimates with missing values, the length of confidence intervals for these estimates remained the same as in the Split Form design.
-This implies that there is an underestimation of our variances occurring at some point in the imputation process.
-This is supported by the fact that, generally, the fraction of missing information estimated in the Wave Missingness design tended to be smaller than that of the corresponding Split Form design.
-This can also explain the low confidence interval coverages we obtained using this design.
-At high levels of missingness none of the scenarios allowed the Wave Missingness design to obtain coverages above 90\%.
-This leads us to believe that many of the imputations are producing datasets which are similar in terms of the relationships between variables but that are not representative of the true relationships.
-Because of this we cannot recommend the use of Wave Missingness designs for anything but small levels of missing data.
-\par
-
-Additionally, all PM designs under all scenarios performed within acceptable ranges when measuring the effects of variables which had no missing values ($\gamma_0, \beta_2, \beta_3$).
-This fact makes the increased sample size scenario promising for researchers.
-While our estimation of $\beta_1$ was similar in this scenario as in others, the estimation of the other model parameters improved by leaps and bounds.
-If a PM design is able to reduce costs by 50\% by introducing missingness, using these extra funds to recruit more participants may be a good idea for researchers who's analysis of interest involves variables that will not have missing values.
-\par
-
-\section{Discussion}
-\label{4}
-In this paper we performed a simulation study to test the ability of different PM designs to capture a multilevel logistic model under a longitudinal framework.
-We found that for low levels of planned missing data (about 25\% missingness) variations of the Split Form design and the Wave Missingness designs are all capable of estimating the parameters of the multilevel model reasonably well.
-As the level of missing data increases to 50\% and 75\%, though, the quality of estimates in all of the tested PM designs become unacceptable as we see rising parameter biases and confidence interval lengths.
-Moreover, we found that the quality of the Wave Missingness design depreciates much more rapidly than the other PM designs, providing higher parameter biases than the corresponding Split Form estimates and low confidence interval coverages (95\% confidence intervals with less than 90\% coverage in some cases).
-\par
-
-These facts lead us to recommend against the use of Wave Missingness designs when the Split Form design can be easily substituted.
-If Wave Missingness must be used, as in the Cohort Sequential and Developmental Time-Lag designs, we suggest that the design minimizes the amount of missing data.
-For instance, in a Cohort Sequential design which attempts to stretch four-year data to cover a span of six years each cohort will have missing values at two of the six measurement occasions.
-This would result in about 33.3\% missingness.
-To ensure that the researcher's analyses are accurate, we would recommend an increase in the amount of time they follow participants, using five-year data instead of four-year data to cover the same period.
-While the recommendation to use low levels of missing data is especially true for Wave Missingness designs it also holds for the Split Form designs.
-While these designs tended to perform well for all parameters in the multilevel model at low levels of missingness this was not true when missingness was increased to around 50\%.
-\par
-
-For future research it may be useful to test a wider range of missingness.
-That is, while our study showed that the PM designs performed well when missingness was around 25\% and sometimes performed poorly when it was around 50\% we do not know exactly when the estimation procedure breaks down.
-While we can only recommend 25\% missing data here, if it was shown that these designs performed well at 40\% missingness, then researchers could substantially increase cost reduction and decrease participant burden beyond what our recommendations allow.
-Another worthwhile pursuit may be to see how hybrid PM designs perform.
-While we found that Wave Missingness designs performed underwhelmingly it would be interesting to see how a design which had some days fully missing and the remaining days missing on some values would have performed.
-In particular, looking into this result may be useful to researchers who wish to implement an accelerated longitudinal design but also have measures that are costly or burdensome which they would like to limit the collection of.
-\par
-
-To conclude we discuss the limitations of this analysis.
-The results we obtained from our PM designs were obtained through multiple imputation with five imputations.
-While this may be sufficient for low levels of missingness, it is not appropriate for some of the high levels of missingness that we tested.
-We chose to use such a low number of imputations because of the size of the data we had and our computational limitations.
-Simulating two hundred samples, each with ten variants, and then imputing five completed datasets for every variant with a missing value resulted in 9200 datasets.
-Then, under the four different simulation scenarios this number grew to 36,800 datasets.
-Factoring in the fact that each of these datasets contained at least 2700 observations (60 participants for 45 days, more for the large sample scenario) we were left with more than one-hundred million rows of data to analyze.
-This also led to another of the limitations we faced, using only two hundred simulated samples.
-While using more simulations would have allowed us to obtain more stable estimates on bias or coverage, adding in more would have added to our computational difficulties.
-In the future, this problem could be alleviated through the use of parallel computing through a computer cluster.
-\par
-
-We hope that the results of this paper will serve to help researchers decide which PM design is most appropriate for their studies' needs.
-By illuminating the weaknesses of the Wave Missingness design we hope that when Wave missingness is not explicitly required researchers will opt instead to use a Split Form design.
-Moreover, when researchers do implement a PM design we hope they follow our recommendation to err on the side of caution and keep the amount of missing data relatively low.
-\par
-
-%\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-\bibliographystyle{plainnat}
-\bibliography{citations}   % name your BibTeX data base
-
-\end{document}
+\end{Soutput}
+\begin{Sinput}
+> load("C:/Users/Josie/Documents/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime1.RData")

### 2018-05-16 Documentation/manuscript.tex
h

--- 2018-02-22 comparing_05222017.tex
@@
 
-\documentclass{svjour3}                     % onecolumn (standard format)
+\documentclass{svjour3}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}                     % onecolumn (standard format)
 %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
@@
 \journalname{Sankhya B}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
-\begin{table}[h!]
-	\centering
-	\caption{The Three Form PM Design}
-	\label{tab:table10}
-	\setlength{\tabcolsep}{1cm}
-	\begin{tabular}{c|cccc}
-		\toprule
-		& \multicolumn{4}{c}{Block} \\
-		Form & X & A & B & C \\
-		\midrule
-		1 & 1 & 1 & 1 & 0 \\
-		2 & 1 & 1 & 0 & 1 \\
-		3 & 1 & 0 & 1 & 1 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+We need to talk about the other type of split design that we used here which was that X of the 8 questions are randomly omitted on each day.
+
+% \begin{table}[h!]
+% 	\centering
+% 	\caption{The Three Form PM Design}
+% 	\label{tab:table10}
+% 	\setlength{\tabcolsep}{1cm}
+% 	\begin{tabular}{c|cccc}
+% 		\toprule
+% 		& \multicolumn{4}{c}{Block} \\
+% 		Form & X & A & B & C \\
+% 		\midrule
+% 		1 & 1 & 1 & 1 & 0 \\
+% 		2 & 1 & 1 & 0 & 1 \\
+% 		3 & 1 & 0 & 1 & 1 \\
+% 		\bottomrule
+% 	\end{tabular}
+% \end{table}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/misslow-1} \caption[Low missingness]{Low missingness}\label{fig:misslow}
+\end{figure}
+
+\end{knitrout}
+
+Figure \ref{fig:misslow} is
 
@@
 We note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high.RData"}\hlstd{)}
+\hlstd{high} \hlkwb{<-} \hlstd{d}
+
+\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med.RData"}\hlstd{)}
+\hlstd{med} \hlkwb{<-} \hlstd{d}
+
+\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low.RData"}\hlstd{)}
+\hlstd{low} \hlkwb{<-} \hlstd{d}
+
+\hlkwd{library}\hlstd{(xtable)}
+\hlkwd{print}\hlstd{(}\hlkwd{xtable}\hlstd{(}\hlkwd{cbind}\hlstd{(}\hlstr{""}\hlstd{,}\hlstr{""}\hlstd{,}\hlstr{""}\hlstd{,}\hlkwd{rbind}\hlstd{(low[[}\hlnum{1}\hlstd{]],med[[}\hlnum{1}\hlstd{]],high[[}\hlnum{1}\hlstd{]],low[[}\hlnum{2}\hlstd{]],med[[}\hlnum{2}\hlstd{]],high[[}\hlnum{2}\hlstd{]],low[[}\hlnum{3}\hlstd{]],med[[}\hlnum{3}\hlstd{]],high[[}\hlnum{3}\hlstd{]])),}\hlkwc{digits}\hlstd{=} \hlnum{3}\hlstd{),}\hlkwc{include.rownames}\hlstd{=}\hlnum{FALSE}\hlstd{)}
+\end{alltt}
+\begin{verbatim}
+## % latex table generated in R 3.5.0 by xtable 1.8-2 package
+## % Tue May 15 15:43:01 2018
+## \begin{table}[ht]
+## \centering
+## \begin{tabular}{lllrrrr}
+##   \hline
+## "" & "" & "" & Coverage & Bias & MSE & FMI \\ 
+##   \hline
+##  &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
+##    &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
+##    &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
+##    &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
+##    &  &  & 0.986 & 0.040 & 0.019 & 0.012 \\ 
+##    &  &  & 0.993 & -0.168 & 0.750 & 0.557 \\ 
+##    &  &  & 0.932 & 0.008 & 0.024 & 0.002 \\ 
+##    &  &  & 0.940 & -0.000 & 0.000 & 0.008 \\ 
+##    &  &  & 0.984 & 0.036 & 0.027 & 0.030 \\ 
+##    &  &  & 0.991 & -0.713 & 9.933 & 0.625 \\ 
+##    &  &  & 0.932 & 0.009 & 0.027 & 0.005 \\ 
+##    &  &  & 0.939 & -0.000 & 0.000 & 0.021 \\ 
+##    &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
+##    &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
+##    &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
+##    &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
+##    &  &  & 0.988 & 0.040 & 0.018 & 0.010 \\ 
+##    &  &  & 0.994 & -0.167 & 0.782 & 0.549 \\ 
+##    &  &  & 0.931 & 0.009 & 0.024 & 0.002 \\ 
+##    &  &  & 0.944 & -0.000 & 0.000 & 0.006 \\ 
+##    &  &  & 0.983 & 0.036 & 0.022 & 0.027 \\ 
+##    &  &  & 0.990 & -0.686 & 10.509 & 0.665 \\ 
+##    &  &  & 0.928 & 0.009 & 0.026 & 0.007 \\ 
+##    &  &  & 0.946 & -0.000 & 0.000 & 0.023 \\ 
+##    &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
+##    &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
+##    &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
+##    &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
+##    &  &  & 0.991 & 0.029 & 0.018 & 0.055 \\ 
+##    &  &  & 0.988 & -0.112 & 0.345 & 0.752 \\ 
+##    &  &  & 0.934 & 0.009 & 0.024 & 0.007 \\ 
+##    &  &  & 0.951 & -0.000 & 0.000 & 0.032 \\ 
+##    &  &  & 0.994 & -0.003 & 0.022 & 0.258 \\ 
+##    &  &  & 0.988 & -0.105 & 0.284 & 0.903 \\ 
+##    &  &  & 0.937 & 0.011 & 0.025 & 0.039 \\ 
+##    &  &  & 0.960 & -0.000 & 0.000 & 0.175 \\ 
+##    \hline
+## \end{tabular}
+## \end{table}
+\end{verbatim}
+\begin{alltt}
+\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high_hightime1.RData"}\hlstd{)}
+\end{alltt}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in readChar(con, 5L, useBytes = TRUE): cannot open compressed file '/Users/gregorymatthews/Dropbox/designedMissingnessGit/Results/tables20180509\_60\_1\_high\_hightime1.RData', probable reason 'No such file or directory'}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}\begin{alltt}
+\hlstd{high} \hlkwb{<-} \hlstd{d}
+
+\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med_hightime1.RData"}\hlstd{)}
+\hlstd{med} \hlkwb{<-} \hlstd{d}
+
+\hlkwd{load}\hlstd{(}\hlstr{"~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low_hightime1.RData"}\hlstd{)}
+\hlstd{low} \hlkwb{<-} \hlstd{d}
+
+\hlkwd{library}\hlstd{(xtable)}
+\hlkwd{print}\hlstd{(}\hlkwd{xtable}\hlstd{(}\hlkwd{cbind}\hlstd{(}\hlstr{""}\hlstd{,}\hlstr{""}\hlstd{,}\hlstr{""}\hlstd{,}\hlkwd{rbind}\hlstd{(low[[}\hlnum{1}\hlstd{]],med[[}\hlnum{1}\hlstd{]],high[[}\hlnum{1}\hlstd{]],low[[}\hlnum{2}\hlstd{]],med[[}\hlnum{2}\hlstd{]],high[[}\hlnum{2}\hlstd{]],low[[}\hlnum{3}\hlstd{]],med[[}\hlnum{3}\hlstd{]],high[[}\hlnum{3}\hlstd{]])),}\hlkwc{digits}\hlstd{=} \hlnum{3}\hlstd{),}\hlkwc{include.rownames}\hlstd{=}\hlnum{FALSE}\hlstd{)}
+\end{alltt}
+\begin{verbatim}
+## % latex table generated in R 3.5.0 by xtable 1.8-2 package
+## % Tue May 15 15:43:01 2018
+## \begin{table}[ht]
+## \centering
+## \begin{tabular}{lllrrrr}
+##   \hline
+## "" & "" & "" & Coverage & Bias & MSE & FMI \\ 
+##   \hline
+##  &  &  & 0.000 & 2.328 & 5.437 & 0.002 \\ 
+##    &  &  & 0.969 & 0.040 & 0.514 & 0.252 \\ 
+##    &  &  & 0.411 & 0.327 & 0.131 & 0.000 \\ 
+##    &  &  & 0.944 & -0.000 & 0.000 & 0.001 \\ 
+##    &  &  & 0.000 & 2.326 & 5.427 & 0.012 \\ 
+##    &  &  & 0.989 & -0.046 & 1.196 & 0.554 \\ 
+##    &  &  & 0.409 & 0.327 & 0.131 & 0.002 \\ 
+##    &  &  & 0.942 & -0.000 & 0.000 & 0.007 \\ 
+##    &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
+##    &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
+##    &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
+##    &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
+##    &  &  & 0.000 & 2.328 & 5.437 & 0.002 \\ 
+##    &  &  & 0.969 & 0.059 & 0.427 & 0.242 \\ 
+##    &  &  & 0.409 & 0.327 & 0.131 & 0.000 \\ 
+##    &  &  & 0.944 & -0.000 & 0.000 & 0.001 \\ 
+##    &  &  & 0.000 & 2.326 & 5.428 & 0.010 \\ 
+##    &  &  & 0.988 & 0.019 & 0.485 & 0.547 \\ 
+##    &  &  & 0.413 & 0.327 & 0.131 & 0.002 \\ 
+##    &  &  & 0.941 & -0.000 & 0.000 & 0.005 \\ 
+##    &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
+##    &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
+##    &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
+##    &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
+##    &  &  & 0.000 & 2.327 & 5.430 & 0.006 \\ 
+##    &  &  & 0.980 & 0.047 & 0.289 & 0.464 \\ 
+##    &  &  & 0.411 & 0.327 & 0.131 & 0.001 \\ 
+##    &  &  & 0.944 & -0.000 & 0.000 & 0.003 \\ 
+##    &  &  & 0.000 & 2.315 & 5.375 & 0.054 \\ 
+##    &  &  & 0.972 & 0.035 & 0.279 & 0.741 \\ 
+##    &  &  & 0.416 & 0.328 & 0.132 & 0.007 \\ 
+##    &  &  & 0.947 & -0.000 & 0.000 & 0.032 \\ 
+##    &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
+##    &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
+##    &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
+##    &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
+##    \hline
+## \end{tabular}
+## \end{table}
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+% latex table generated in R 3.5.0 by xtable 1.8-2 package
+% Mon May 14 21:02:34 2018
+\begin{table}[ht]
+\centering
+\begin{tabular}{lllrrrr}
+  \hline
+Design & \% Missingness  & Parameter & Coverage & Bias & MSE & FMI \\ 
+  \hline
+ &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
+   &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
+   &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
+   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
+   \hline
+   &  &  & 0.986 & 0.040 & 0.019 & 0.012 \\ 
+   &  &  & 0.993 & -0.168 & 0.750 & 0.557 \\ 
+   &  &  & 0.932 & 0.008 & 0.024 & 0.002 \\ 
+   &  &  & 0.940 & -0.000 & 0.000 & 0.008 \\ 
+   \hline
+   &  &  & 0.984 & 0.036 & 0.027 & 0.030 \\ 
+   &  &  & 0.991 & -0.713 & 9.933 & 0.625 \\ 
+   &  &  & 0.932 & 0.009 & 0.027 & 0.005 \\ 
+   &  &  & 0.939 & -0.000 & 0.000 & 0.021 \\ 
+   \hline
+   &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
+   &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
+   &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
+   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
+   \hline
+   &  &  & 0.988 & 0.040 & 0.018 & 0.010 \\ 
+   &  &  & 0.994 & -0.167 & 0.782 & 0.549 \\ 
+   &  &  & 0.931 & 0.009 & 0.024 & 0.002 \\ 
+   &  &  & 0.944 & -0.000 & 0.000 & 0.006 \\ 
+   \hline
+   &  &  & 0.983 & 0.036 & 0.022 & 0.027 \\ 
+   &  &  & 0.990 & -0.686 & 10.509 & 0.665 \\ 
+   &  &  & 0.928 & 0.009 & 0.026 & 0.007 \\ 
+   &  &  & 0.946 & -0.000 & 0.000 & 0.023 \\ 
+   \hline
+   &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
+   &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
+   &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
+   &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
+   \hline
+   &  &  & 0.991 & 0.029 & 0.018 & 0.055 \\ 
+   &  &  & 0.988 & -0.112 & 0.345 & 0.752 \\ 
+   &  &  & 0.934 & 0.009 & 0.024 & 0.007 \\ 
+   &  &  & 0.951 & -0.000 & 0.000 & 0.032 \\ 
+   \hline
+   &  &  & 0.994 & -0.003 & 0.022 & 0.258 \\ 
+   &  &  & 0.988 & -0.105 & 0.284 & 0.903 \\ 
+   &  &  & 0.937 & 0.011 & 0.025 & 0.039 \\ 
+   &  &  & 0.960 & -0.000 & 0.000 & 0.175 \\ 
+   \hline
+\end{tabular}
+\end{table}
 

### 2018-05-16 Documentation/manuscript.Rnw
manuscript.

@@
 \begin{document}
+\SweaveOpts{concordance=TRUE}
 
@@
 There have been many different incarnations of the PM design, each crafted to best suit the study at hand.
-For example, PM designs have been used in the study of longitudinal growth curves \citep{graham2001planned, mcardle1997expanding}, business research \citep{shoemaker1973principles}, behavioral studies \citep{harel2015designed}, biostatistics \citep{andres2006partial, wacholder1994partial}, and in educational assessments \citep{zeger1997efficient, sirotnik1977incidence}.
-This paper focuses on two of the simplest and most applicable PM designs, the Split Form design \citep{raghunathan1995split} and the Wave Missingness design \citep{little2013planned}.
-While this paper covers these designs in more detail later, broadly speaking, the Split Form design entails measuring fewer points at a single measurement occasion \citep{raghunathan1995split}.
-The Wave Missingness design, on the other hand, would require missing out on entire measurement occasion within a longitudinal study \citep{graham2001planned}.
+For example, PM designs have been used in the study of longitudinal growth curves \citep{graham2001planned, mcardle1997expanding}, business research \citep{shoemaker1973principles}, behavioral studies \citep{harel2015designed}, biostatistics \citep{andres2006partial, wacholder1994partial}, and educational assessments \citep{zeger1997efficient, sirotnik1977incidence}.
+This paper focuses on two of the simplest and most applicable PM designs; the Split Form design \citep{raghunathan1995split} and the Wave Missingness design \citep{little2013planned}.
+While this paper covers these designs in more detail later, broadly speaking, the Split Form design entails measuring fewer points on a single measurement occasion \citep{raghunathan1995split}.
+The Wave Missingness design, on the other hand, requires missing an entire measurement occasion within a longitudinal study \citep{graham2001planned}.
 
 The issue we concern ourselves with arises when a longitudinal study requires multiple items to be collected at each measurement occasion.
-When a multi-level regression model is the analysis of interest, we would like to see if it is more efficient to design missingness using the Split Form design or the Wave Missingness design.
+When implementing a multi-level regression model in this situation, we investigate which planned missingess design is more efficient and accurate.
 Previous research indicates that for the estimation of correlated latent growth curve models use of the three-form PM design, a special case of Split Form designs \citep{raghunathan1995split}, resulted in low bias on parameter estimates or standard error and high efficiency when compared with wave missingness designs \citep{rhemtulla2014planned}.
-Because our model of interest is a mixed effects model, though, we can not be sure that this result will hold.
-\par
-
-To answer our question we performed a simulation study based on data obtained in longitudinal research on HIV medication adherence and alcohol-interactivity beliefs \citep{pellowski2016alcohol}.
-For each of the PM designs mentioned we simulated sample data conforming to that particular design and then used multiple imputation (MI) \citep{little2014statistical}  techniques to analyze our data.
-We subsequently evaluated the PM methodologies using the average bias, percent bias, mean squared error, coverage rates, confidence interval length, and estimated fraction of missing information (FMI) \citep{little2014statistical} for parameter estimates in a multilevel model.
-To make our results more generalizable the experiment was repeated under a few different scenarios: increased sample size, low inter-survey correlation, and high time effect.
+As our model of interest is a mixed effects model, however, we can not be sure that this result will hold.
+\par
+
+To answer our question we performed a simulation study from data obtained in longitudinal research on HIV medication adherence and alcohol-interactivity beliefs \citep{pellowski2016alcohol}.
+For the PM designs mentioned we simulated sample data and then used multiple imputation (MI) \citep{little2014statistical}  techniques to analyze the data.
+The PM methods were subsequently evaluated through the assessmemt of the average bias, percent bias, mean squared error, coverage rates, confidence interval length, and estimated fraction of missing information (FMI) \citep{little2014statistical} for parameter estimates in a multilevel model.
+To make the results generalizable, the experiment was repeated under multiple scenarios: increased sample size, low inter-survey correlation, and high time effect.
 \par
@@
 
-Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are so named because of the way in which they are implemented.
-Instead of giving participants one large survey, researchers will create multiple “forms”, each containing only a subset of the full survey’s questions.
-A common setup is the three-form design \citep{graham1996maximizing}.
-In the three-form design the full survey is split into four blocks, X, A, B, and C.
-Each form of the survey includes the X block as well as two of the other three blocks.
-This leaves us with the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded.
-We note that every block is paired together in at least one of the forms.
-By designing our forms in this manner we are able to estimate the relationship between any given items regardless of which blocks they are in.
-That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows us to do that.
+Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are very aptly named.
+Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions.
+A common form setup is the three-form design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C.
+Each form of the survey includes the X block as well as two of the remaining blocks.
+This leaves the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded.
+Note that every block appears in at least one form.
+By designing the forms in this manner we are able to estimate the relationship between any chosen items regardless of their blocks.
+That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows this.
 \par
@@
 
-An important consideration when designing a Split Form survey is deciding which items to put into which blocks.
-The X-block, being included in every form, should contain either those variables which are of greatest interest or those with the most predictive ability.
+An important consideration when designing a Split Form survey is question distribution.
+The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
 Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}.
 On the other hand, placing the most predictive variables in the X-block allows Multiple Imputation to more effectively impute missing values from the other blocks \citep{gottschall2012comparison}.
-For the same reason it is good practice to place variables which are predictive of each other in to separate blocks \citep{gottschall2012comparison}.
-We note that when groupings are not as obvious as in the previous example pilot studies can help determine the predictive potential of variables.
+Similarly, it is good practice to place variables which are predictive of each other in separate blocks \citep{gottschall2012comparison}.
+Note that when groupings are not as obvious, as in the previous example, pilot studies can help determine the predictive potential of variables.
 We may also wish to consider the cost and burden associated with an item when deciding which block to place it in.
-Even if a specific item is critical to our analysis, if it is overly expensive or invasive we may be better off excluding it from the X-block \citep{little2013planned}.
-\par
-
-More than deciding which blocks should contain which items, we also need to consider how many blocks we should use.
-Including more blocks in our design can allow us to further increase missingness \citep{graham2006planned}.
-For example, imagine two groups of researchers, the first group divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey, and the second uses an X-block and nine others with 10\% of the items each.
-The researchers make the decision that any given pair of blocks should be asked together in at least one of the forms to ensure efficient estimations.
+For example, if a critical item is overly expensive or difficult to obtain we may be better off excluding it from the X-block \citep{little2013planned}.
+\par
+
+In additon, the number of blocks must be determined.
+Including more blocks in the design allows further increased missingness \citep{graham2006planned}.
+For example, consider two groups of researchers.
+The first group divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey, and the second uses an X-block and nine others with 10\% of the items each.
+The researchers decide that a pair of blocks will be asked together in at least one of the forms to ensure efficient estimations.
 Based on this requirement, the first group can only reduce the length of their survey by 25\% while the second group can decrease the length of their survey by up to 70\%.
@@
 
-A relative advantage of the Wave Missingness design over the Split form design is that researchers can have more control over the level of missingness.
-For studies with many measurement occasions it is easy to make small changes to the amount of missing data.
-The data described by \citet{pellowski2016alcohol}.
-\citet{pellowski2016alcohol} for instance has daily measurements for 45 days.
+A relative advantage of the Wave Missingness design over the Split form design is increased control over the level of missingness.
+For studies with many measurement occasions, it is easy to make small changes to the amount of missing data.
+For example, the data described by \citet{pellowski2016alcohol} records measurements for 45 days.
 Missing eleven days here would result in 24.4\% missingness while missing twelve gives us 26.7\%.
-Further, Wave Missingness designs have the ability to eclipse Split Form designs in terms of cost reduction \citep{little2013planned}.
-\par
-
-Another advantage of this design is that many common longitudinal study designs already make use of the Wave Missingness structure \citep{little2013planned}.
-Cohort Sequential Designs are a type of study where cohorts of different ages are recruited and followed longitudinally in such a way that we can use information from one cohort to impute values for another \citep{little2013longitudinal, duncan2013introduction}.
-Say, for example, we had three cohorts of ages 10, 11, and 12 at baseline and we measured them annually for four years.
+Further, Wave Missingness designs eclipse Split Form designs in terms of cost reduction \citep{little2013planned}.
+\par
+
+Another advantage of this design is many longitudinal study designs already use the Wave Missingness structure \citep{little2013planned}.
+Cohort Sequential Designs require cohorts of different ages to be followed longitudinally in such a way that the information from one cohort can be used to impute values for another \citep{little2013longitudinal, duncan2013introduction}.
+For example, there were three cohorts of ages 10, 11, and 12 at baseline and measured annually for four years.
 Although measurement only occurs at four waves we can frame this as a six-wave study where the 10-year old cohort has missing values at waves five and six, the 11-year old cohort at waves one and six, and the 12-year old cohort at waves one and two.
-Because the 10-year old cohort is the only group observed at the first wave we use it to impute missing values for the other groups.
-By continuing in this manner we are able to take the data that was collected over a four year period and extend it to cover six years, accelerating the study.
+Because the 10-year old cohort is the only group observed at the first wave, the missing values for the other groups are imputed using this information.
+By continuing in this manner the data that was collected over a four year period is extended it to cover six years, accelerating the study.
 The setup of this type of study is demonstrated in Table \ref{tab:table12}, where "1" and "0" respectively indicate an included and excluded wave.
@@
 If we have prior knowledge concerning the relationship between unobserved values, indicated by $R$, and the observed values, then Multiple Imputation can yield efficient estimates even under MNAR \citep{harel2007multiple}.
-However, because this is not typically the case MI is most often implemented when data is MCAR or MAR \citep{little2014statistical}.
-\par
+However, because this is not typically the case, MI is most often implemented when data is MCAR or MAR \citep{little2014statistical}.
+\par
+
 As a consequence of allowing researchers to decide which values in a dataset are observed and unobserved, PM designs grant control over the missing data mechanism.
@@
 \label{sec:2.2}
-The first step in the process of creating our simulated datasets was to use the data from \citet{pellowski2016alcohol} and obtain parameter estimates to quantify the relationships between variables.
-We then treated these estimated relationships as the “true” relationships and drew two-hundred samples using these parameters.
-While we would have liked to simulate a larger number of samples we were limited by computational ability.
-Our purpose in simulating these datasets was to see how well they would be able to capture the true relationship between medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score).
+The first step in the process of creating the simulated datasets was to obtain parameter estimates from \citet{pellowski2016alcohol} and to quantify the relationships between variables.
+These estimated relationships were treated as the "true" relationships and one thousand samples were drawn using these parameters.
+The purpose of simulating these datasets was to see how well they captured the true relationship between daily medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score).
 Specifically, our model of interest is the random intercept model with time effect found below: \\
@@
 
-After imputations the logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}.
+After imputating, a logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}.
 From here, the results from each PM design were evaluated based on bias, percent bias, mean squared error (MSE), coverage, confidence interval (CI) length, and the fraction of missing information (FMI).
-The FMI is a measure of how much of the MI sampling variance comes from differences between imputations.
-Besides comparing the results between each of the PM designs we also included the results of these same analyses taken from before missingness was imposed.
-\par
-
-When determining if the PM designs are performing sufficiently well it is important to consider how well the simulated samples performed before we added a missingness structure.
-For example, imagine we have two full data samples with respective biases on the $\beta_1$ estimate of 0.13 and 0.15.
-Further, after imposing different PM design structures on these samples we obtained the average biases of 0.14 and 0.15 respectively.
-It would be unfair to claim that the first
-PM design performed better than the second because, by chance, it was based off of a more representative sample. We kept this fact in mind when determining our evaluation criteria. \par
+The FMI is a measure of how much of the MI sample variance comes from differences between imputations.
+In addition to comparing the results between each of the PM designs, the same analyses were also performed before missingness was imposed.
+\par
+
+When determining if the PM designs are performing sufficiently, it is important to consider how well the simulated samples performed before adding a missingness structure.
+For example, consider two full data samples with respective biases on the $\beta_1$ estimate of 0.13 and 0.15.
+Further, after imposing different PM design structures on these samples, the average biases are 0.14 and 0.15 respectively.
+It would be unfair to claim that the first PM design performed better than the second because, by chance, it was based off of a more representative sample.
+This fact was considered when determining the evaluation criteria.
+\par
 
 For bias, percent bias, and MSE we claimed that an increase of more than 40\% in these measurements after imposing missingness indicates that the PM design is inappropriate.
-For instance, if the complete data shows a percent bias of 10\%, anything higher than 14\% ($0.1*1.4$) would be unacceptable.
+For instance, if the complete data shows a percent bias of 10\%, anything higher than 14\% would be unacceptable.
 An increase of this size has the ability to negatively effect efficiency of our estimation.
@@
 While this fact was accounted for in the original simulations, it was not in this set of simulations.
-If the probability of answering “yes” on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations then in this scenario it is a function of only the baseline variables.
+If the probability of answering "yes" on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables.
 This implies that each of the questions are conditionally independent of each other given the baseline variables.
@@
 \label{sec:3.1}
-The first set of simulations we ran had the parameters in our random-intercept logistic model set as $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$.
+The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$.
 The effects of the variables here are comparable to those found in the original dataset.
 This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design.
-Before we imposed a missingness structure on our two-hundred simulated samples we obtained the full data results shown in Table \ref{tab:table2}.
-We note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
+Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:table2}.
+Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
 
 <<>>=
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high.RData")
+load("~/designedmissingnessGit/Results/tables20180509_60_1_high.RData")
 high <- d
 
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med.RData")
+load("~/designedmissingnessGit/Results/tables20180509_60_1_med.RData")
 med <- d
 
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low.RData")
+load("~/designedmissingnessGit/Results/tables20180509_60_1_low.RData")
 low <- d
@@
 
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
+load("~/designedmissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
 high <- d
 
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
+load("~/designedmissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
 med <- d
 
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
+load("~/designedmissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
 low <- d
@@
 
-Of note in the complete-data primary analysis is that the coverage of our 95\% CIs is larger than expected for our parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large.
+Of note in the complete-data primary analysis is that the coverage of the 95\% CIs is larger than expected for the parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large.
 This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}.
@@
 In Table \ref{tab:table3} as in Tables \ref{tab:table4}, \ref{tab:table5}, and \ref{tab:table6} bold values indicate "Unacceptable" results.
-That is, a Bias, Percent Bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
+That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
 
@@
 
-For the Split Form and Altered Split Form designs seen in Table \ref{tab:table3}, we note that the greatest loss in efficiency was on the $\beta_1$ estimate.
-While the CI coverage remained high at all levels of missingness for the two designs the bias, percent bias, and MSE reached unacceptable levels at the high missingness level.
+For the Split Form and Altered Split Form designs seen in Table \ref{tab:table3}, note that the greatest loss in efficiency was on the $\beta_1$ estimate.
+While the CI coverage remained high at all levels of missingness for the two designs, the bias, percent bias, and MSE reached unacceptable levels at the high missingness level.
 We also point out that the Altered Split Form design did not perform significantly better than the regular Split Form design.
@@
 In reference to the FMI on the $\beta_1$ estimate, we can see that at low and medium missingness both Split Form designs performed well.
-That is to say, there was less variance in the results from our imputed datasets than we expected given the amount of missing data.\par
-
-Towards the bottom of Table \ref{tab:table3} we see that the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at medium and high levels of missingness.
-Moreover, at high levels of missingness even coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.
+That is, there was less variance in the results from th imputed datasets than we expected given the amount of missing data.\par
+
+Towards the bottom of Table \ref{tab:table3}, the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at both medium and high levels of missingness.
+Moreover, at high levels of missingness coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.
 Additionally, we see that CI length for the $\beta_1$ estimate was roughly equal across all designs, despite the fact that the Wave Missingness design provided more biased estimates.
@@
 \label{sec:3.2}
-The next simulation scenario we tested was under an increased sample size.
-All parameter values were held the same as in the original set of simulations but instead of simulating data for 60 participants here we used 120 participants.
-Table \ref{tab:table2}, again, contains the results of our analysis before applying any PM design.
-\par
-
-We compare the results from the full-data simulations to those obtained from the PM designs, shown in Table \ref{tab:table4}.
-The first thing we notice is that the bias on all parameters is lower than it was in the smaller sample size simulations.
-Next, the Split Form design performed similarly well under this simulation scenario as in the first.
+In the next simulation scenario the sample size was increased to 120 participants.
+All parameter values were held the same as in the original simulation.
+Table \ref{tab:table2}, again, contains the results of the analysis before applying any PM design.
+\par
+
+The results of the full-data simulations are compared to those obtained from the PM designs, shown in Table \ref{tab:table4}.
+First notice the bias of all parameters is lower than in the smaller sample size simulations.
+Next, the Split Form design performed similarly well as in the first.
 At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable.
-However, the CI length here is relatively far from the complete-data measurement in Table \ref{tab:table2}.
+However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:table2}.
 The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088.
-We also point out that the percent bias on the $\beta_1$ estimate is not seriously different from that obtained in the small sample scenario.
-For example, at medium levels of missingness the percent bias on $\beta_1$ here is 23.86\% while for the smaller sample it was 23.75\%.
+Furthermore, the percent bias on the $\beta_1$ estimate is not seriously different from that obtained in the small sample scenario.
+For example, at medium levels of missingness the percent bias on $\beta_1$ is 23.86\% while for the smaller sample it was 23.75\%.
 Similarly to the Split Form design, the Altered Split Form Design also provided unacceptable results for the MSE of the $\beta_1$ estimate at medium missingness and unacceptable bias, percent bias, and MSE at high levels.
 \par
-For the Wave Missingness design we continue to see the issues pointed out in the small sample simulations.
-That is, for the $\beta_1$ estimate we have unacceptable measurements at medium and high levels of missingness and a steep drop off in coverage probability for our 95\% CIs.
-In fact, at medium and high levels of missingness we find coverages of 85.5\% and 82.0\%.
-We also continue to see that the $\gamma_0$ parameter is being estimated poorly at high levels of missing data under the Wave Missingness design.
+For the Wave Missingness design we continue to see the issues observed in the small sample simulations.
+That is, for the $\beta_1$ estimate the measurements at medium and high levels of missingness are unacceptable and a steep drop off in coverage probability occurs for the 95\% CIs.
+In fact, at medium and high levels of missingness the coverages drop to 85.5\% and 82.0\%.
+The $\gamma_0$ parameter also continues to be estimated poorly at high levels of missing data under the Wave Missingness design.
 \par
@@
 \label{sec:3.3}
-For the next set of simulations we returned to the smaller sample size but decreased the level of inter-survey correlation.
-As mentioned in section 3.2.2 we made sure that there was no direct predictive relationship between questions in our survey.
-The results obtained from our full data simulations are provided in Table \ref{tab:table2} while the results from our PM designs are given in Table \ref{tab:table5}.
-\par
-
-For the Split Form design it is important to notice that the efficiency of the $\beta_1$ estimate decreases much more rapidly than in our first set of simulations where survey questions were predictive of one another.
+For the next set of simulations sample size returned to 60 participants but the level of inter-survey correlation decreased.
+The results obtained from the full data simulations are provided in Table \ref{tab:table2} while the results from the PM designs are given in Table \ref{tab:table5}.
+\par
+
+For the Split Form design it is important to notice that the efficiency of the $\beta_1$ estimate decreases much more rapidly than in the original simulations where survey questions were predictive of one another.
 For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be 0.150 and 0.276 at high levels.
 This left us with an increase in average bias of 0.126.
-If we check the same increase in the original simulations we see that the bias only increased by 0.071.
+Looking at the same increase in the original simulations, note that the bias only increased by 0.071.
 This loss in efficiency is seen in the other measurements on the $\beta_1$ estimate as well.
-Moreover, we note that the Split Form design performs unacceptably in terms of bias, percent bias, and MSE at medium levels of missingness.
+Moreover, note that the Split Form design performs unacceptably in terms of bias, percent bias, and MSE at medium levels of missingness.
 This was not the case in the other missingness scenarios.
@@
 
-In the Altered Split Form design at medium levels of missingness the MSE is outside of the acceptable range and at high levels bias, are percent bias are unacceptable as well.
-We further note that the coverage of the $\beta_1$ CIs was quite a bit higher than in the full-data simulations.
-That is, while the coverage probability obtained in the full-data simulations was 94.5\%, under this Altered Split Form design we obtained coverages of 95.5\%, 97.0\%, and 96.0\% at low, medium, and high levels of missingness respectively.
-\par
-
-Concerning the Wave Missingness design we, again, see the issues of unacceptable bias, percent bias and MSE.
-However, at low levels of missingness the coverage of our $\beta_1$ estimate was fairly good (96.5\% compared to 94.5\% in the full data).
-This positive coverage did not hold throughout the other levels of missingness as coverage dropped to 89.5\% in the high missingness scenario.
+The Altered Split Form design at medium levels of missingness yielded an MSE outside of the acceptable range and at high levels bias, the percent bias are unacceptable as well.
+Additionally, the coverage of the $\beta_1$ CIs was quite a bit higher than in the full-data simulations.
+That is, while the coverage probability obtained in the full-data simulations was 94.5\%, under this Altered Split Form design the coverages are 95.5\%, 97.0\%, and 96.0\% at low, medium, and high levels of missingness respectively.
+\par
+
+Under Wave Missingness the issues of unacceptable bias, percent bias and MSE occur.
+However, at low levels of missingness, the coverage of the $\beta_1$ estimate was fairly good (96.5\% compared to 94.5\% in the full data).
+Sufficient coverage did not hold through increased missingness as coverage dropped to 89.5\% in the high missingness scenario.
 As in other scenarios, the CI lengths produced under the Wave Missingness design are similar to those produced in the Split Form designs despite an increase in bias.
-However, this increase in bias is less dramatic than in other scenarios.
+However, here the increase in bias is less dramatic than in other scenarios.
 For example, at high levels of missingness in the original simulations the average bias on the $\beta_1$ estimate was 0.065 higher for the Wave Missingness design (at 0.290) than in the Split Form design (0.225).
@@
 \label{sec:3.4}
-In the final scenario we tested to see how the PM designs would capture a model where time had a disproportionately large effect.
+In the final scenario we tested to see how the PM designs would capture a model where time had a disproportionately large effect on Missed Dose.
 In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$.
@@
 The Altered Split Form design performed slightly better than the normal Split Form design under this simulation scenario.
-We do note, though, that while the normal Split Form design provided unacceptable bias and percent bias for the $\beta_1$ estimate at medium levels of missingness, this was not true in the Altered Split Form design.
-Additionally, we point out that at medium and high levels of missingness we saw an improvement from the Split Form design in the CI lengths for the $\beta_1$ estimate.
+Note, however, that while the normal Split Form design provided unacceptable bias and percent bias for the $\beta_1$ estimate at medium levels of missingness, this was not true of the Altered Split Form design.
+Additionally, observe that at medium and high levels of missingness there was an improvement under the Split Form design in the CI lengths for the $\beta_1$ estimate.
 In the Split Form design the CI lengths were recorded as 0.981 and 1.433 at medium and high missingness.
@@
 
-Under this simulation scenario, at low levels of missingness we see that the Wave Missingness Design performs similarly to the Split Form and Altered Split Form designs.
+In this simulation scenario, the Wave Missingness Design performs similarly to the Split Form and Altered Split Form designs at low levels of missingness.
 The bias, percent bias, MSE, and CI coverage for $\beta_1$ all performed acceptably using the Wave Missingness design at low levels of missingness.
-Moreover, as missingness increases this design shows itself to be unsuitable in terms of estimating $\beta_1$ for the same reasons noted in the other scenarios.
+However, as missingness increases this design shows itself to be unsuitable in terms of estimating $\beta_1$ for the same reasons noted in the other scenarios.
 \par
@@
 However, even factoring in the slight decrease in overall missingness, this design performed only equally as well as the normal Split Form design.
-This may be a result of the fact that the number of observations we left fully observed was small, only two out of the forty-five days (or about 4.4\% of days) were fully observed.
+This may be a result of the fact that the number of observations we left fully observed was small; only two out of the forty-five days (approximately 4.4\% of days).
 While it may be interesting to see if the inclusion of more fully observed days is capable of improving our estimates, perhaps keeping five days (11.1\%) fully observed, we would need to be careful about raising this number too high.
-If the cost or burden of observations is a limiting factor then collecting full data on even 10\% of the days may be unnecessarily burdensome.
-\par
-
-Of larger concern, though, is the steep drop-off in estimating quality of the Wave Missingness design as missingness increased.
-In every scenario we tested, the Wave Missingness design produced unacceptable bias, percent bias, and MSE at medium and high levels of missingness.
-We also note that despite increased bias on estimates with missing values, the length of confidence intervals for these estimates remained the same as in the Split Form design.
-This implies that there is an underestimation of our variances occurring at some point in the imputation process.
+If the cost or burden of observations is a limiting factor, then collecting full data on even 10\% of the days may be unnecessarily burdensome.
+\par
+
+Of larger concern, however, is the steep drop-off in estimating quality of the Wave Missingness design as missingness increased.
+In every scenario tested, the Wave Missingness design produced unacceptable bias, percent bias, and MSE at medium and high levels of missingness.
+In addition, despite increased bias on estimates with missing values, the length of confidence intervals for these estimates remained the same as in the Split Form design.
+This implies that there is an underestimation of the variances occurring at some point in the imputation process.
 This is supported by the fact that, generally, the fraction of missing information estimated in the Wave Missingness design tended to be smaller than that of the corresponding Split Form design.
-This can also explain the low confidence interval coverages we obtained using this design.
+This can also explain the lower confidence interval coverages obtained using this design.
 At high levels of missingness none of the scenarios allowed the Wave Missingness design to obtain coverages above 90\%.
-This leads us to believe that many of the imputations are producing datasets which are similar in terms of the relationships between variables but that are not representative of the true relationships.
-Because of this we cannot recommend the use of Wave Missingness designs for anything but small levels of missing data.
+This leads to the belief that many of the imputations are producing datasets which are similar in terms of the relationships between variables but that are not representative of the true relationships.
+Because of this, the use of Wave Missingness designs for anything but small levels of missing data cannot be recommended.
 \par
@@
 While our estimation of $\beta_1$ was similar in this scenario as in others, the estimation of the other model parameters improved by leaps and bounds.
-If a PM design is able to reduce costs by 50\% by introducing missingness, using these extra funds to recruit more participants may be a good idea for researchers who's analysis of interest involves variables that will not have missing values.
+If a PM design is able to reduce costs by 50\% by introducing missingness, using these extra funds to recruit more participants may be a good idea for researchers whose analysis of interest involves variables that will not have missing values.
 \par
@@
 In this paper we performed a simulation study to test the ability of different PM designs to capture a multilevel logistic model under a longitudinal framework.
-We found that for low levels of planned missing data (about 25\% missingness) variations of the Split Form design and the Wave Missingness designs are all capable of estimating the parameters of the multilevel model reasonably well.
-As the level of missing data increases to 50\% and 75\%, though, the quality of estimates in all of the tested PM designs become unacceptable as we see rising parameter biases and confidence interval lengths.
+We found that for low levels of planned missing data (about 25\% missingness), variations of the Split Form design and the Wave Missingness designs are all capable of estimating the parameters of the multilevel model reasonably well.
+As the level of missing data increases to 50\% and 75\%, however, the quality of estimates in all of the tested PM designs become unacceptable as we see rising parameter biases and confidence interval lengths.
 Moreover, we found that the quality of the Wave Missingness design depreciates much more rapidly than the other PM designs, providing higher parameter biases than the corresponding Split Form estimates and low confidence interval coverages (95\% confidence intervals with less than 90\% coverage in some cases).
@@
 
-These facts lead us to recommend against the use of Wave Missingness designs when the Split Form design can be easily substituted.
-If Wave Missingness must be used, as in the Cohort Sequential and Developmental Time-Lag designs, we suggest that the design minimizes the amount of missing data.
-For instance, in a Cohort Sequential design which attempts to stretch four-year data to cover a span of six years each cohort will have missing values at two of the six measurement occasions.
+These facts warn against the use of Wave Missingness designs when the Split Form design can be easily substituted.
+If Wave Missingness must be used, as in the cohort sequential and developmental timelLag designs, the design must minimize the amount of missing data.
+For instance, in a cohort sequential design which attempts to stretch four-year data to cover a span of six years each cohort will have missing values at two of the six measurement occasions.
 This would result in about 33.3\% missingness.
@@
 For future research it may be useful to test a wider range of missingness.
-That is, while our study showed that the PM designs performed well when missingness was around 25\% and sometimes performed poorly when it was around 50\% we do not know exactly when the estimation procedure breaks down.
-While we can only recommend 25\% missing data here, if it was shown that these designs performed well at 40\% missingness, then researchers could substantially increase cost reduction and decrease participant burden beyond what our recommendations allow.
+That is, while this study showed that the PM designs performed well when missingness was around 25\% and sometimes performed poorly when it was around 50\% it is unknown exactly when the estimation procedure breaks down.
+While only 25\% missing data is suggested here, if it was shown that these designs performed well at 40\% missingness, then researchers could substantially increase cost reduction and decrease participant burden beyond what our recommendations allow.
 Another worthwhile pursuit may be to see how hybrid PM designs perform.
-While we found that Wave Missingness designs performed underwhelmingly it would be interesting to see how a design which had some days fully missing and the remaining days missing on some values would have performed.
-In particular, looking into this result may be useful to researchers who wish to implement an accelerated longitudinal design but also have measures that are costly or burdensome which they would like to limit the collection of.
-\par
-
-To conclude we discuss the limitations of this analysis.
-The results we obtained from our PM designs were obtained through multiple imputation with five imputations.
-While this may be sufficient for low levels of missingness, it is not appropriate for some of the high levels of missingness that we tested.
-We chose to use such a low number of imputations because of the size of the data we had and our computational limitations.
-Simulating two hundred samples, each with ten variants, and then imputing five completed datasets for every variant with a missing value resulted in 9200 datasets.
-Then, under the four different simulation scenarios this number grew to 36,800 datasets.
-Factoring in the fact that each of these datasets contained at least 2700 observations (60 participants for 45 days, more for the large sample scenario) we were left with more than one-hundred million rows of data to analyze.
-This also led to another of the limitations we faced, using only two hundred simulated samples.
-While using more simulations would have allowed us to obtain more stable estimates on bias or coverage, adding in more would have added to our computational difficulties.
-In the future, this problem could be alleviated through the use of parallel computing through a computer cluster.
-\par
-
-We hope that the results of this paper will serve to help researchers decide which PM design is most appropriate for their studies' needs.
-By illuminating the weaknesses of the Wave Missingness design we hope that when Wave missingness is not explicitly required researchers will opt instead to use a Split Form design.
-Moreover, when researchers do implement a PM design we hope they follow our recommendation to err on the side of caution and keep the amount of missing data relatively low.
+While it was found that Wave Missingness designs performed underwhelmingly, it would be interesting to investigatte a design containing fully missing days with the remaining days missing on some values would perform.
+This investigation may be particularly useful to researchers who wish to implement an accelerated longitudinal design but also have measures that are costly or burdensome which they would like to limit the collection of.
+\par
+
+To conclude we discuss the limitations of this analysis. DIFFERENT LIMITATIONS. NOT COMPUTING POWER.
+
+Hopefully, the results of this paper will serve to help researchers decide which PM design is most appropriate for their studies' needs.
+By illuminating the weaknesses of the Wave Missingness design, it is hoped that, unless it is explicitly required, researchers will opt instead to use a Split Form design.
+Furthermore, when researchers do implement a PM design we hope they follow our recommendation to err on the side of caution and keep the amount of missing data relatively low.
 \par

### 2018-05-16 Documentation/manuscript.Rnw
paper edits

@@
 
-<<>>=
-load("~/designedmissingnessGit/Results/tables20180509_60_1_high.RData")
+<<echo=FALSE>>=
+d <- file("~/GitHub/designedmissingness/Results/tables20180509_60_1_high.RData")
 high <- d
 
-load("~/designedmissingnessGit/Results/tables20180509_60_1_med.RData")
+d <- file("~/GitHub/designedmissingness/Results/tables20180509_60_1_med.RData")
 med <- d
 
-load("~/designedmissingnessGit/Results/tables20180509_60_1_low.RData")
+d <- file("~/GitHub/designedmissingness/Results/tables20180509_60_1_low.RData")
 low <- d
@@
 library(xtable)
-print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
-
-load("~/designedmissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
+print(xtable(cbind("","","",rbind(low[1],med[1],high[1],low[2],med[2],high[2],low[3],med[3],high[3])),digits= 3),include.rownames=FALSE)
+
+d <- file("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime1.RData")
 high <- d
 
-load("~/designedmissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
+d <- file("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime1.RData")
 med <- d
 
-load("~/designedmissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
+d <- file("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime1.RData")
 low <- d
@@
 library(xtable)
-print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
+print(xtable(cbind("","","",rbind(low[1],med[1],high[1],low[2],med[2],high[2],low[3],med[3],high[3])),digits= 3),include.rownames=FALSE)
 

### 2018-05-16 Documentation/manuscript.tex
paper edits

--- 2018-05-15 Documentation/manuscript.Rnw
@@
 
-<<echo = FALSE>>=
-# Creating dataframe to visualize - one subject's questions for 5 days
-split.form <- function(set, nrem = 2, bound = 0){
-
-set[set$Day >= bound, paste0("Q",1:8)] <- t(apply(set[set$Day >= bound,paste0("Q",1:8)], 1, function(x){
-    ind <- sample(1:8, nrem)
-    x[ind] <- NA
-    as.numeric(x)
-  }))
-
-  return(set)
-
-}
-@
-
-<<echo = FALSE>>=
-wave.des <- function(set, nmiss, ...) { # nmiss is the number of days each person would miss? 11?? Like, miss a fourth of the days?
-  id <- sample(2:45, size=nmiss)
-  for (i in 1:nmiss) {
-    set[set$Day %in% id[i], c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')] <- NA
-  }
-  return(set)
-}
-@
-
-<<warning=FALSE, echo = FALSE>>=
-cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
-fill <- matrix(1, 45, 8)
-dat <- data.frame(fill)
-colnames(dat) <- cols
-dat$Day <- seq.int(nrow(dat))
-set.seed(1234)
-split.dat <- split.form(dat)[1:8]
-#split.dat
-@
-
-<<warning=FALSE,message=FALSE,echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- split.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-
-#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
-fill <- matrix(1, 45, 8)
-dat <- data.frame(fill)
-colnames(dat) <- cols
-dat$Day <- seq.int(nrow(dat))
-set.seed(1234)
-alternate.split.dat <- split.form(dat, bound = 3)[1:8]
-#alternate.split.dat
-@
-
-<<warning=FALSE,message=FALSE,echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- alternate.split.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-
-#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
-@
-
-<<echo=FALSE>>=
-set.seed(1234)
-wave.dat <- wave.des(dat,11)
-#wave.dat
-@
-
-<<echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- wave.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-@
-
-<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE>>=
-require(gridExtra)
-grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
-@
-
 Figure \ref{fig:misslow} is
 
-An important consideration when designing a Split Form survey is deciding which items to put into which blocks.
-The X-block, being included in every form, should contain either those variables which are of greatest interest or those with the most predictive ability.
+An important consideration when designing a Split Form survey is question distribution.
+The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
 Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}.
 On the other hand, placing the most predictive variables in the X-block allows Multiple Imputation to more effectively impute missing values from the other blocks \citep{gottschall2012comparison}.
-For the same reason it is good practice to place variables which are predictive of each other in to separate blocks \citep{gottschall2012comparison}.
-We note that when groupings are not as obvious as in the previous example pilot studies can help determine the predictive potential of variables.
+Similarly, it is good practice to place variables which are predictive of each other in separate blocks \citep{gottschall2012comparison}.
+Note that when groupings are not as obvious, as in the previous example, pilot studies can help determine the predictive potential of variables.
 We may also wish to consider the cost and burden associated with an item when deciding which block to place it in.
-Even if a specific item is critical to our analysis, if it is overly expensive or invasive we may be better off excluding it from the X-block \citep{little2013planned}.
-\par
-
-More than deciding which blocks should contain which items, we also need to consider how many blocks we should use.
-Including more blocks in our design can allow us to further increase missingness \citep{graham2006planned}.
-For example, imagine two groups of researchers, the first group divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey, and the second uses an X-block and nine others with 10\% of the items each.
-The researchers make the decision that any given pair of blocks should be asked together in at least one of the forms to ensure efficient estimations.
+For example, if a critical item is overly expensive or difficult to obtain we may be better off excluding it from the X-block \citep{little2013planned}.
+\par
+
+In additon, the number of blocks must be determined.
+Including more blocks in the design allows further increased missingness \citep{graham2006planned}.
+For example, consider two groups of researchers.
+The first group divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey, and the second uses an X-block and nine others with 10\% of the items each.
+The researchers decide that a pair of blocks will be asked together in at least one of the forms to ensure efficient estimations.
 Based on this requirement, the first group can only reduce the length of their survey by 25\% while the second group can decrease the length of their survey by up to 70\%.
@@
 \label{sec:3.1}
-The first set of simulations we ran had the parameters in our random-intercept logistic model set as $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$.
+The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$.
 The effects of the variables here are comparable to those found in the original dataset.
 This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design.
-Before we imposed a missingness structure on our two-hundred simulated samples we obtained the full data results shown in Table \ref{tab:table2}.
-We note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
-
-<<>>=
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high.RData")
-high <- d
-
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med.RData")
-med <- d
-
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low.RData")
-low <- d
-
-library(xtable)
-print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
-
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
-high <- d
-
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
-med <- d
-
-load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
-low <- d
-
-library(xtable)
-print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
-
-@
+Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:table2}.
+Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
+
+\begin{Schunk}
+\begin{Soutput}
+% latex table generated in R 3.4.1 by xtable 1.8-2 package
+% Wed May 16 17:31:14 2018
+\begin{table}[ht]
+\centering
+\begin{tabular}{llll}
+  \hline
+1 & 2 & 3 & 4 \\ 
+  \hline
+ &  &  & 7 \\ 
+   &  &  & 6 \\ 
+   &  &  & 5 \\ 
+   &  &  &  \\ 
+   &  &  &  \\ 
+   &  &  &  \\ 
+   &  &  &  \\ 
+   &  &  &  \\ 
+   &  &  &  \\ 
+   \hline
+\end{tabular}
+\end{table}
+\end{Soutput}
+\begin{Soutput}
+% latex table generated in R 3.4.1 by xtable 1.8-2 package
+% Wed May 16 17:31:14 2018
+\begin{table}[ht]
+\centering
+\begin{tabular}{llll}
+  \hline
+1 & 2 & 3 & 4 \\ 
+  \hline
+ &  &  & 10 \\ 
+   &  &  & 9 \\ 
+   &  &  & 8 \\ 
+   &  &  &  \\ 
+   &  &  &  \\ 
+   &  &  &  \\ 
+   &  &  &  \\ 
+   &  &  &  \\ 
+   &  &  &  \\ 
+   \hline
+\end{tabular}
+\end{table}
+\end{Soutput}
+\end{Schunk}
 

### 2018-05-17 Documentation/manuscript.Rnw
Manuscript edits.

--- 2018-05-16 Documentation/manuscript.Rnw
@@
   return(set)
-
 }
@@
 
-<<>>=
-load("~/designedmissingnessGit/Results/tables20180509_60_1_high.RData")
+<<echo=FALSE>>=
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high.RData")
 high <- d
 
-load("~/designedmissingnessGit/Results/tables20180509_60_1_med.RData")
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med.RData")
 med <- d
 
-load("~/designedmissingnessGit/Results/tables20180509_60_1_low.RData")
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low.RData")
 low <- d
@@
 library(xtable)
-print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
-
-load("~/designedmissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
+print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),type="latex", comment = FALSE)
+
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime1.RData")
 high <- d
 
-load("~/designedmissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime1.RData")
 med <- d
 
-load("~/designedmissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime1.RData")
 low <- d

### 2018-05-17 Documentation/manuscript.tex
Manuscript edits.
Manuscript table edits

@@
 \journalname{Sankhya B}
-
-\usepackage{Sweave}
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
-\input{manuscript-concordance}
+%\SweaveOpts{concordance=TRUE}
 
@@
 
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/misslow-1} \caption[Low missingness]{Low missingness}\label{fig:misslow}
+\end{figure}
+
+\end{knitrout}
+
 Figure \ref{fig:misslow} is
@@
 
-\begin{Schunk}
-\begin{Soutput}
-% latex table generated in R 3.4.1 by xtable 1.8-2 package
-% Wed May 16 17:31:14 2018
-\begin{table}[ht]
-\centering
-\begin{tabular}{llll}
-  \hline
-1 & 2 & 3 & 4 \\ 
-  \hline
- &  &  & 7 \\ 
-   &  &  & 6 \\ 
-   &  &  & 5 \\ 
-   &  &  &  \\ 
-   &  &  &  \\ 
-   &  &  &  \\ 
-   &  &  &  \\ 
-   &  &  &  \\ 
-   &  &  &  \\ 
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\begin{tabular}{l|l|l|r|r|r|r|r|r}
+\hline
+Design & Missingness & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
+\hline
+ &  & $\gamma_0$ & 0.042 & -1.817 & 0.018 & 0.988 & 0.702 & 0.002\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.071 & -25.122 & 0.269 & 0.983 & 2.534 & 0.236\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.008 & 1.253 & 0.024 & 0.932 & 0.585 & 0.000\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.886 & 0.000 & 0.944 & 0.017 & 0.001\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.039 & -1.684 & 0.018 & 0.990 & 0.709 & 0.011\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.102 & -36.186 & 0.271 & 0.998 & 3.500 & 0.534\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.008 & 1.207 & 0.024 & 0.933 & 0.586 & 0.002\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.419 & 0.000 & 0.946 & 0.017 & 0.007\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.028 & -1.242 & 0.027 & 0.985 & 0.791 & 0.030\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.107 & -38.054 & 0.418 & 0.988 & 4.268 & 0.630\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.012 & 1.869 & 0.027 & 0.932 & 0.613 & 0.005\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.471 & 0.000 & 0.946 & 0.020 & 0.020\\
+\cline{1-9}
+ &  & $\gamma_0$ & 0.042 & -1.832 & 0.018 & 0.990 & 0.701 & 0.001\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.069 & -24.401 & 0.283 & 0.983 & 2.508 & 0.218\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.008 & 1.272 & 0.024 & 0.933 & 0.585 & 0.000\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.949 & 0.000 & 0.944 & 0.017 & 0.001\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.040 & -1.760 & 0.018 & 0.988 & 0.704 & 0.007\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.117 & -41.573 & 0.277 & 0.990 & 3.385 & 0.508\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.008 & 1.286 & 0.024 & 0.931 & 0.585 & 0.002\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.986 & 0.000 & 0.945 & 0.017 & 0.005\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.036 & -1.592 & 0.021 & 0.989 & 0.742 & 0.022\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.158 & -56.111 & 0.394 & 0.992 & 4.336 & 0.662\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.012 & 1.809 & 0.026 & 0.934 & 0.601 & 0.006\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.487 & 0.000 & 0.941 & 0.018 & 0.021\\
+\cline{1-9}
+ &  & $\gamma_0$ & 0.040 & -1.765 & 0.018 & 0.988 & 0.703 & 0.005\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.094 & -33.425 & 0.238 & 0.993 & 2.995 & 0.433\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.008 & 1.251 & 0.024 & 0.934 & 0.585 & 0.001\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.875 & 0.000 & 0.943 & 0.017 & 0.002\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.028 & -1.223 & 0.018 & 0.995 & 0.744 & 0.051\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.088 & -31.121 & 0.240 & 0.992 & 3.497 & 0.718\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.009 & 1.436 & 0.024 & 0.933 & 0.588 & 0.006\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.326 & 0.000 & 0.946 & 0.017 & 0.025\\
+\cline{2-9}
+ &  & $\gamma_0$ & -0.004 & 0.194 & 0.020 & 0.995 & 0.962 & 0.224\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.080 & -28.263 & 0.234 & 0.985 & 3.791 & 0.886\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.011 & 1.700 & 0.024 & 0.938 & 0.607 & 0.032\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -3.304 & 0.000 & 0.970 & 0.020 & 0.148\\
 \hline
 \end{tabular}
-\end{table}
-\end{Soutput}
-\begin{Soutput}
-% latex table generated in R 3.4.1 by xtable 1.8-2 package
-% Wed May 16 17:31:14 2018
-\begin{table}[ht]
-\centering
-\begin{tabular}{llll}
-  \hline
-1 & 2 & 3 & 4 \\ 
-  \hline
- &  &  & 10 \\ 
-   &  &  & 9 \\ 
-   &  &  & 8 \\ 
-   &  &  &  \\ 
-   &  &  &  \\ 
-   &  &  &  \\ 
-   &  &  &  \\ 
-   &  &  &  \\ 
-   &  &  &  \\ 
-   \hline
-\end{tabular}
-\end{table}
-\end{Soutput}
-\end{Schunk}
+
+\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in column\_spec(1, width = "{}30em"{}): argument "{}column"{} is missing, with no default}}\begin{verbatim}
+## % latex table generated in R 3.4.1 by xtable 1.8-2 package
+## % Thu May 17 15:47:48 2018
+## \begin{table}[ht]
+## \centering
+## \begin{tabular}{lllrrrrrr}
+##   \hline
+## "" & "" & "" & Coverage & Bias & MSE & FMI & CI Length & Pct Bias \\ 
+##   \hline
+##  &  &  & 0.968 & -0.023 & 0.120 & 0.018 & 1.414 & 0.498 \\ 
+##    &  &  & 0.973 & 0.604 & 0.669 & 0.271 & 4.812 & 429.053 \\ 
+##    &  &  & 0.955 & 0.010 & 0.048 & 0.003 & 0.827 & 3.263 \\ 
+##    &  &  & 0.945 & -0.000 & 0.000 & 0.004 & 0.039 & -2.671 \\ 
+##    &  &  & 0.972 & -0.048 & 0.128 & 0.059 & 1.506 & 1.060 \\ 
+##    &  &  & 0.988 & 0.724 & 0.898 & 0.499 & 5.933 & 513.940 \\ 
+##    &  &  & 0.958 & 0.025 & 0.047 & 0.013 & 0.834 & 7.927 \\ 
+##    &  &  & 0.938 & -0.000 & 0.000 & 0.017 & 0.039 & -2.867 \\ 
+##    &  &  & 0.984 & -0.178 & 0.370 & 0.132 & 2.050 & 3.882 \\ 
+##    &  &  & 0.955 & 0.997 & 1.573 & 0.610 & 6.822 & 708.287 \\ 
+##    &  &  & 0.965 & 0.044 & 0.060 & 0.036 & 0.966 & 13.650 \\ 
+##    &  &  & 0.955 & -0.000 & 0.000 & 0.060 & 0.048 & -0.787 \\ 
+##    &  &  & 0.966 & -0.019 & 0.119 & 0.011 & 1.401 & 0.415 \\ 
+##    &  &  & 0.966 & 0.603 & 0.638 & 0.239 & 4.616 & 428.601 \\ 
+##    &  &  & 0.956 & 0.014 & 0.048 & 0.002 & 0.827 & 4.254 \\ 
+##    &  &  & 0.944 & -0.000 & 0.000 & 0.003 & 0.039 & -3.004 \\ 
+##    &  &  & 0.978 & -0.045 & 0.124 & 0.053 & 1.493 & 0.988 \\ 
+##    &  &  & 0.974 & 0.728 & 0.879 & 0.504 & 5.976 & 517.389 \\ 
+##    &  &  & 0.954 & 0.024 & 0.051 & 0.011 & 0.838 & 7.437 \\ 
+##    &  &  & 0.946 & -0.001 & 0.000 & 0.018 & 0.039 & -4.550 \\ 
+##    &  &  & 0.984 & -0.117 & 0.196 & 0.112 & 1.759 & 2.557 \\ 
+##    &  &  & 0.968 & 0.876 & 1.305 & 0.650 & 6.913 & 622.327 \\ 
+##    &  &  & 0.963 & 0.026 & 0.051 & 0.034 & 0.892 & 8.265 \\ 
+##    &  &  & 0.949 & -0.001 & 0.000 & 0.055 & 0.043 & -5.340 \\ 
+##    &  &  & 0.968 & -0.057 & 0.127 & 0.038 & 1.454 & 1.249 \\ 
+##    &  &  & 0.974 & 0.853 & 1.003 & 0.510 & 5.629 & 606.148 \\ 
+##    &  &  & 0.959 & 0.006 & 0.046 & 0.006 & 0.831 & 1.804 \\ 
+##    &  &  & 0.945 & -0.000 & 0.000 & 0.011 & 0.039 & -3.051 \\ 
+##    &  &  & 0.979 & -0.182 & 0.166 & 0.183 & 1.813 & 3.981 \\ 
+##    &  &  & 0.967 & 0.979 & 1.325 & 0.782 & 6.758 & 695.352 \\ 
+##    &  &  & 0.956 & 0.020 & 0.050 & 0.037 & 0.871 & 6.425 \\ 
+##    &  &  & 0.955 & -0.001 & 0.000 & 0.068 & 0.042 & -4.466 \\ 
+##    &  &  & 0.987 & -0.403 & 0.345 & 0.440 & 2.789 & 8.803 \\ 
+##    &  &  & 0.951 & 1.050 & 1.504 & 0.887 & 7.357 & 745.735 \\ 
+##    &  &  & 0.973 & 0.019 & 0.050 & 0.099 & 0.960 & 5.848 \\ 
+##    &  &  & 0.975 & -0.003 & 0.000 & 0.200 & 0.052 & -18.904 \\ 
+##    \hline
+## \end{tabular}
+## \end{table}
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 

### 2018-05-17 Documentation/manuscript.Rnw

@@
 \begin{document}
-\SweaveOpts{concordance=TRUE}
+%\SweaveOpts{concordance=TRUE}
 
@@
 
-<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE>>=
+<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig = TRUE>>=
 require(gridExtra)
@@
 
-<<echo=FALSE>>=
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high.RData")
-high <- d
-
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med.RData")
-med <- d
-
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low.RData")
-low <- d
-
-library(xtable)
-print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),type="latex", comment = FALSE)
+<<echo=FALSE, warning=FALSE>>=
+# if (Sys.info()[8] == "Josie"){
+#   setwd("~/GitHub/designedmissingness")
+# }
+# if (Sys.info()[8] == "gregorymatthews"){
+#   setwd("~/Dropbox/designedmissingnessGit")
+# }
+
+# Table 7
+library(kableExtra)
+library(dplyr)
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime0.RData")
+high_8 <- d
+
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime0.RData")
+med_8 <- d
+
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime0.RData")
+low_8 <- d
+
+c8 <- rbind(low_8[[1]],med_8[[1]],high_8[[1]],low_8[[2]],med_8[[2]],high_8[[2]],low_8[[3]],med_8[[3]],high_8[[3]])
+
+df_8 <- data.frame(Design = rep(c("Split Form","Altered Split Form", "Wave Missingness"), each = 12), Missingness = rep(rep(c("Low","Medium", "High"), each = 4),3), Parameter = rep(c("$\\gamma_0$", "$\\beta_1$", "$\\beta_2$", "$\\beta_3$"),9), Bias = unlist(c8["Bias"]), unlist(c8["Pct Bias"]), MSE = unlist(c8["MSE"]), Coverage = c8["Coverage"], c8["CI Length"], FMI = c8["FMI"])
+
+df_8[,4:9] <- apply(df_8[,4:9], 2, round, digits = 3)
+
+names(df_8) <- c("Design", "Missingness", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
+row.names(df_8) <- NULL
+kable(df_8, escape = FALSE, format ="latex") %>%
+  collapse_rows(columns = 1:2, latex_hline = "full")
+  column_spec(1, width = "30em")
+
+# library(knitr)
+# kable(cbind("","","",rbind(low_8[[1]],med_8[[1]],high_8[[1]],low_8[[2]],med_8[[2]],high_8[[2]],low_8[[3]],med_8[[3]],high_8[[3]])),format="latex")
 

### 2018-05-22 Documentation/manuscript.Rnw
Manuscript changes.

@@
 \usepackage{natbib}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage[table]{xcolor}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+% \usepackage{threeparttable}
+% \usepackage{threeparttablex}
+% \usepackage[normalem]{ulem}
+% \usepackage{makecell}
 
@@
 Each form of the survey includes the X block as well as two of the remaining blocks.
-This leaves the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded.
+This leaves the configurations seen in Table \\ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded.
 Note that every block appears in at least one form.
@@
 
-<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig = TRUE>>=
+<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig.keep = TRUE>>=
 require(gridExtra)
@@
 
-names(df_8) <- c("Design", "Missingness", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
+names(df_8) <- c("Design", "Level", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
 row.names(df_8) <- NULL
 kable(df_8, escape = FALSE, format ="latex") %>%
-  collapse_rows(columns = 1:2, latex_hline = "full")
-  column_spec(1, width = "30em")
+  collapse_rows(columns = 1:2, latex_hline = "full") %>%
+  kable_styling(latex_options = "scale_down")
 
@@
 low <- d
-
-library(xtable)
-print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
-
 @

### 2018-05-22 Documentation/manuscript.tex
Manuscript changes.

@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\begin{tabular}{l|l|l|r|r|r|r|r|r}
-\hline
-Design & Missingness & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[H]
+\centering
+\resizebox{\linewidth}{!}{\begin{tabular}{l|l|l|r|r|r|r|r|r}
+\hline
+Design & Level & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
 \hline
@@
 \hline
-\end{tabular}
-
-\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in column\_spec(1, width = "{}30em"{}): argument "{}column"{} is missing, with no default}}\begin{verbatim}
-## % latex table generated in R 3.4.1 by xtable 1.8-2 package
-## % Thu May 17 15:47:48 2018
-## \begin{table}[ht]
-## \centering
-## \begin{tabular}{lllrrrrrr}
-##   \hline
-## "" & "" & "" & Coverage & Bias & MSE & FMI & CI Length & Pct Bias \\ 
-##   \hline
-##  &  &  & 0.968 & -0.023 & 0.120 & 0.018 & 1.414 & 0.498 \\ 
-##    &  &  & 0.973 & 0.604 & 0.669 & 0.271 & 4.812 & 429.053 \\ 
-##    &  &  & 0.955 & 0.010 & 0.048 & 0.003 & 0.827 & 3.263 \\ 
-##    &  &  & 0.945 & -0.000 & 0.000 & 0.004 & 0.039 & -2.671 \\ 
-##    &  &  & 0.972 & -0.048 & 0.128 & 0.059 & 1.506 & 1.060 \\ 
-##    &  &  & 0.988 & 0.724 & 0.898 & 0.499 & 5.933 & 513.940 \\ 
-##    &  &  & 0.958 & 0.025 & 0.047 & 0.013 & 0.834 & 7.927 \\ 
-##    &  &  & 0.938 & -0.000 & 0.000 & 0.017 & 0.039 & -2.867 \\ 
-##    &  &  & 0.984 & -0.178 & 0.370 & 0.132 & 2.050 & 3.882 \\ 
-##    &  &  & 0.955 & 0.997 & 1.573 & 0.610 & 6.822 & 708.287 \\ 
-##    &  &  & 0.965 & 0.044 & 0.060 & 0.036 & 0.966 & 13.650 \\ 
-##    &  &  & 0.955 & -0.000 & 0.000 & 0.060 & 0.048 & -0.787 \\ 
-##    &  &  & 0.966 & -0.019 & 0.119 & 0.011 & 1.401 & 0.415 \\ 
-##    &  &  & 0.966 & 0.603 & 0.638 & 0.239 & 4.616 & 428.601 \\ 
-##    &  &  & 0.956 & 0.014 & 0.048 & 0.002 & 0.827 & 4.254 \\ 
-##    &  &  & 0.944 & -0.000 & 0.000 & 0.003 & 0.039 & -3.004 \\ 
-##    &  &  & 0.978 & -0.045 & 0.124 & 0.053 & 1.493 & 0.988 \\ 
-##    &  &  & 0.974 & 0.728 & 0.879 & 0.504 & 5.976 & 517.389 \\ 
-##    &  &  & 0.954 & 0.024 & 0.051 & 0.011 & 0.838 & 7.437 \\ 
-##    &  &  & 0.946 & -0.001 & 0.000 & 0.018 & 0.039 & -4.550 \\ 
-##    &  &  & 0.984 & -0.117 & 0.196 & 0.112 & 1.759 & 2.557 \\ 
-##    &  &  & 0.968 & 0.876 & 1.305 & 0.650 & 6.913 & 622.327 \\ 
-##    &  &  & 0.963 & 0.026 & 0.051 & 0.034 & 0.892 & 8.265 \\ 
-##    &  &  & 0.949 & -0.001 & 0.000 & 0.055 & 0.043 & -5.340 \\ 
-##    &  &  & 0.968 & -0.057 & 0.127 & 0.038 & 1.454 & 1.249 \\ 
-##    &  &  & 0.974 & 0.853 & 1.003 & 0.510 & 5.629 & 606.148 \\ 
-##    &  &  & 0.959 & 0.006 & 0.046 & 0.006 & 0.831 & 1.804 \\ 
-##    &  &  & 0.945 & -0.000 & 0.000 & 0.011 & 0.039 & -3.051 \\ 
-##    &  &  & 0.979 & -0.182 & 0.166 & 0.183 & 1.813 & 3.981 \\ 
-##    &  &  & 0.967 & 0.979 & 1.325 & 0.782 & 6.758 & 695.352 \\ 
-##    &  &  & 0.956 & 0.020 & 0.050 & 0.037 & 0.871 & 6.425 \\ 
-##    &  &  & 0.955 & -0.001 & 0.000 & 0.068 & 0.042 & -4.466 \\ 
-##    &  &  & 0.987 & -0.403 & 0.345 & 0.440 & 2.789 & 8.803 \\ 
-##    &  &  & 0.951 & 1.050 & 1.504 & 0.887 & 7.357 & 745.735 \\ 
-##    &  &  & 0.973 & 0.019 & 0.050 & 0.099 & 0.960 & 5.848 \\ 
-##    &  &  & 0.975 & -0.003 & 0.000 & 0.200 & 0.052 & -18.904 \\ 
-##    \hline
-## \end{tabular}
-## \end{table}
-\end{verbatim}
-\end{kframe}
+\end{tabular}}
+\end{table}
+
 \end{knitrout}

### 2018-05-22 Documentation/Original Tables and Figures.Rnw
Manuscript edits.

--- 2018-05-17 Documentation/manuscript.Rnw
@@
-\RequirePackage{fix-cm}
-
-\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-
-\usepackage{graphicx}
-\usepackage{mathptmx}      
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{cite}
-\usepackage{caption}
-\usepackage{natbib}
-
-\journalname{Sankhya B}
+\documentclass{article}
 
 \begin{document}
-%\SweaveOpts{concordance=TRUE}
 
-\title{Comparing Different Planned Missingness Designs in Longitudinal Studies}
+% Original Tables and Figures
 
-\author{Josephine Wood \and Gregory J. Matthews \and Nicholas Illenberger \and Jennifer Pellowski \and Ofer Harel}
-
-\institute{J. Wood \and G. J. Matthews
-          \at Loyola University Chicago \\
-          1032 W. Sheridan Rd.\\
-          Chicago IL, 60660 USA\\
-          Tel: (773)508-3558
-          \and
-          N. Illenberger \and O. Harel 
-				\at University of Connecticut \\
-						215 Glennbrook Rd. Unit 420\\
-						Storrs CT, 06269-4120 USA
-              Tel: (860)486-6989 \\
-		      \email{ofer.harel@uconn.edu}  
-					\and
-					J. Pellowski
-					\at International Health Institute\\ 
-					Brown School of Public Health 
-					\and J. Pellowski 
-					\at Department of Psychiatry and Human Behavior\\
-					The Warren Alpert Medical School of Brown University.  
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-Planned Missingness (PM) designs, in which researchers deliberately collect only partial data, have enjoyed a recent growth in popularity.
-Among other benefits these designs have been proven capable of reducing the study costs and alleviating participant burden.
-Past research has shown that Split Form PM designs can be effective in simplifying complex surveys while Wave Missingness PM designs act similarly for Longitudinal studies.
-However, less work has been done to inform how to implement PM structures into studies which incorporate elements of both survey and longitudinal designs.
-Specifically, in studies where a questionnaire is given to participants at multiple measurement occasions the best way to design missingness is still unclear.
-To address this deficiency, data in this hybrid format was simulated under both Split Form and Wave Missingness PM structures.
-Multiple Imputation techniques were applied to estimate a multilevel logistic model in each of the simulations.
-Estimated parameters were compared to the true values to see which PM design allowed us to best capture the true model.
-The results of this study indicate that, compared to the Split Form Design, the Wave Missingness design consistently performed less effectively in capturing the multilevel model.
-Thus, in the context of longitudinal surveys this study recommends the use of Split Form missingness designs, which performs well under a number of different conditions.
-
-\keywords{Planned Missingness \and Split Form \and Multiform \and Wave Missingness \and Multiple Imputation \and Missing Data.}
-\end{abstract}
-
-\section{Introduction}
-\label{intro}
-Planned Missingness (PM) designs are a type of experimental design in which some of the data is predetermined to be missing.
-While it may seem counterproductive to deliberately omit data from the collection process, PM designs have been shown to reduce both participant burden \citep{graham2006planned, saris20048} and the costs of a study \citep{graham2001planned}.
-Moreover, PM designs can actually increase the quality of collected data by increasing the breadth of a study \citep{little2013planned} as well as decreasing the effects of assessment reactivity and rates of unplanned missingness \cite{harel2015designed}.
-We further note that while PM designs decrease the efficiency of estimators \citep{rhemtulla2016asymptotic}, decreasing the cost per participant may allow researchers to enroll more participants in a study, offsetting some of the efficiency loss.
-\par
-
-There have been many different incarnations of the PM design, each crafted to best suit the study at hand.
-For example, PM designs have been used in the study of longitudinal growth curves \citep{graham2001planned, mcardle1997expanding}, business research \citep{shoemaker1973principles}, behavioral studies \citep{harel2015designed}, biostatistics \citep{andres2006partial, wacholder1994partial}, and educational assessments \citep{zeger1997efficient, sirotnik1977incidence}.
-This paper focuses on two of the simplest and most applicable PM designs; the Split Form design \citep{raghunathan1995split} and the Wave Missingness design \citep{little2013planned}.
-While this paper covers these designs in more detail later, broadly speaking, the Split Form design entails measuring fewer points on a single measurement occasion \citep{raghunathan1995split}.
-The Wave Missingness design, on the other hand, requires missing an entire measurement occasion within a longitudinal study \citep{graham2001planned}.
-
-The issue we concern ourselves with arises when a longitudinal study requires multiple items to be collected at each measurement occasion.
-When implementing a multi-level regression model in this situation, we investigate which planned missingess design is more efficient and accurate.
-Previous research indicates that for the estimation of correlated latent growth curve models use of the three-form PM design, a special case of Split Form designs \citep{raghunathan1995split}, resulted in low bias on parameter estimates or standard error and high efficiency when compared with wave missingness designs \citep{rhemtulla2014planned}.
-As our model of interest is a mixed effects model, however, we can not be sure that this result will hold.
-\par
-
-To answer our question we performed a simulation study from data obtained in longitudinal research on HIV medication adherence and alcohol-interactivity beliefs \citep{pellowski2016alcohol}.
-For the PM designs mentioned we simulated sample data and then used multiple imputation (MI) \citep{little2014statistical}  techniques to analyze the data.
-The PM methods were subsequently evaluated through the assessmemt of the average bias, percent bias, mean squared error, coverage rates, confidence interval length, and estimated fraction of missing information (FMI) \citep{little2014statistical} for parameter estimates in a multilevel model.
-To make the results generalizable, the experiment was repeated under multiple scenarios: increased sample size, low inter-survey correlation, and high time effect.
-\par
-
-To delineate the remainder of this paper, in Section 2 we go into more depth on the two PM designs previously mentioned and then move into a discussion on the modern Multiple Imputation technique for dealing with missing data.
-Next, in Section 3 we briefly describe the dataset we worked with and our method of simulation before moving on to the results of our analyses in Section 4 and a discussion in the final section.
-\par
-
-\section{Designs and Methods}
-\label{sec:1}
-\subsection{Split Form Design}
-\label{sec:1.1}
-
-Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are very aptly named.
-Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions.
-A common form setup is the three-form design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C.
-Each form of the survey includes the X block as well as two of the remaining blocks.
-This leaves the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded.
-Note that every block appears in at least one form.
-By designing the forms in this manner we are able to estimate the relationship between any chosen items regardless of their blocks.
-That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows this.
-\par
-
-We need to talk about the other type of split design that we used here which was that X of the 8 questions are randomly omitted on each day.
+% Table 10
 
@@
 
-<<echo = FALSE>>=
-# Creating dataframe to visualize - one subject's questions for 5 days
-split.form <- function(set, nrem = 2, bound = 0){
+% Table 11
 
-set[set$Day >= bound, paste0("Q",1:8)] <- t(apply(set[set$Day >= bound,paste0("Q",1:8)], 1, function(x){
-    ind <- sample(1:8, nrem)
-    x[ind] <- NA
-    as.numeric(x)
-  }))
-
-  return(set)
-}
-@
-
-<<echo = FALSE>>=
-wave.des <- function(set, nmiss, ...) { # nmiss is the number of days each person would miss? 11?? Like, miss a fourth of the days?
-  id <- sample(2:45, size=nmiss)
-  for (i in 1:nmiss) {
-    set[set$Day %in% id[i], c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')] <- NA
-  }
-  return(set)
-}
-@
-
-<<warning=FALSE, echo = FALSE>>=
-cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
-fill <- matrix(1, 45, 8)
-dat <- data.frame(fill)
-colnames(dat) <- cols
-dat$Day <- seq.int(nrow(dat))
-set.seed(1234)
-split.dat <- split.form(dat)[1:8]
-#split.dat
-@
-
-<<warning=FALSE,message=FALSE,echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- split.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-
-#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
-fill <- matrix(1, 45, 8)
-dat <- data.frame(fill)
-colnames(dat) <- cols
-dat$Day <- seq.int(nrow(dat))
-set.seed(1234)
-alternate.split.dat <- split.form(dat, bound = 3)[1:8]
-#alternate.split.dat
-@
-
-<<warning=FALSE,message=FALSE,echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- alternate.split.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-
-#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
-@
-
-<<echo=FALSE>>=
-set.seed(1234)
-wave.dat <- wave.des(dat,11)
-#wave.dat
-@
-
-<<echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- wave.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-@
-
-<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig = TRUE>>=
-require(gridExtra)
-grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
-@
-
-Figure \ref{fig:misslow} is
-
-An important consideration when designing a Split Form survey is question distribution.
-The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
-Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}.
-On the other hand, placing the most predictive variables in the X-block allows Multiple Imputation to more effectively impute missing values from the other blocks \citep{gottschall2012comparison}.
-Similarly, it is good practice to place variables which are predictive of each other in separate blocks \citep{gottschall2012comparison}.
-Note that when groupings are not as obvious, as in the previous example, pilot studies can help determine the predictive potential of variables.
-We may also wish to consider the cost and burden associated with an item when deciding which block to place it in.
-For example, if a critical item is overly expensive or difficult to obtain we may be better off excluding it from the X-block \citep{little2013planned}.
-\par
-
-In additon, the number of blocks must be determined.
-Including more blocks in the design allows further increased missingness \citep{graham2006planned}.
-For example, consider two groups of researchers.
-The first group divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey, and the second uses an X-block and nine others with 10\% of the items each.
-The researchers decide that a pair of blocks will be asked together in at least one of the forms to ensure efficient estimations.
-Based on this requirement, the first group can only reduce the length of their survey by 25\% while the second group can decrease the length of their survey by up to 70\%.
-\par
-
-While increasing missingness may allow for further reductions in burden and cost, researchers must consider the disadvantages of more blocks.
-Inevitably, greater missingness leads to less efficient estimation \citep{rhemtulla2016asymptotic} but there is the added complication as more blocks introduce additional forms.
-If the second group of researchers in the example, for instance, decide that each form would contain the X-block and two of the other blocks, then they would be left with 36 total forms.
-For traditional paper surveys, this can make administering the survey difficult.
-However, for electronic questionaires, where form randomization can be automated, this is not an issue.
-Often, researchers using electronic surveys will give each participant a random sample of all survey items, in a way treating each item as its own block \citep{silvia2014planned}.
-Using this method, researchers reap the benefits of increased forms without the difficulty caused by manually building and administering these forms.
-\par
-
-\subsection{Wave Missingness Design}
-\label{sec:1.2}
-While Split Form missingness can be applied to many experimental designs, the Wave Missingness design \citep{little2013planned} is unique to studies with multiple measurement occasions, or "waves".
-Unlike the Split Form design, where participants miss a subset of items in a single measurement occasion, the Wave Design entails randomizing participants to miss a measurement occasion entirely.
-An example of a Wave Missing design is shown in Table \ref{tab:table11} where data is collected monthly over the course of 5 months.
-However, each participant is only measured at three of these occasions.
-\par
-
-\begin{table}[b!]
-	\centering
-	\caption{The Wave Missingness PM Design}
-	\label{tab:table11}
-	\setlength{\tabcolsep}{0.75cm}
-	\begin{tabular}{c|ccccc}
-		\toprule
-		& \multicolumn{5}{c}{Month} \\
-		Participant & 1 & 2 & 3 & 4 & 5 \\
-		\midrule
-		1 & 1 & 0 & 1 & 0 & 1 \\
-		2 & 1 & 1 & 0 & 1 & 0 \\
-		3 & 0 & 0 & 1 & 1 & 1 \\
-		4 & 1 & 1 & 1 & 0 & 0 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-A relative advantage of the Wave Missingness design over the Split form design is increased control over the level of missingness.
-For studies with many measurement occasions, it is easy to make small changes to the amount of missing data.
-For example, the data described by \citet{pellowski2016alcohol} records measurements for 45 days.
-Missing eleven days here would result in 24.4\% missingness while missing twelve gives us 26.7\%.
-Further, Wave Missingness designs eclipse Split Form designs in terms of cost reduction \citep{little2013planned}.
-\par
-
-Another advantage of this design is many longitudinal study designs already use the Wave Missingness structure \citep{little2013planned}.
-Cohort Sequential Designs require cohorts of different ages to be followed longitudinally in such a way that the information from one cohort can be used to impute values for another \citep{little2013longitudinal, duncan2013introduction}.
-For example, there were three cohorts of ages 10, 11, and 12 at baseline and measured annually for four years.
-Although measurement only occurs at four waves we can frame this as a six-wave study where the 10-year old cohort has missing values at waves five and six, the 11-year old cohort at waves one and six, and the 12-year old cohort at waves one and two.
-Because the 10-year old cohort is the only group observed at the first wave, the missing values for the other groups are imputed using this information.
-By continuing in this manner the data that was collected over a four year period is extended it to cover six years, accelerating the study.
-The setup of this type of study is demonstrated in Table \ref{tab:table12}, where "1" and "0" respectively indicate an included and excluded wave.
-\par
-
-\begin{table}[t!]
-	\centering
-	\caption{Cohort Sequential Design}
-	\label{tab:table12}
-	\setlength{\tabcolsep}{0.5cm}
-	\begin{tabular}{c|cccccc}
-		\toprule
-		& \multicolumn{6}{c}{Age} \\
-		Participant & 10 & 11 & 12 & 13 & 14 & 15 \\
-		\midrule
-		1 & 1 & 1 & 1 & 1 & 0 & 0\\
-		2 & 0 & 1 & 1 & 1 & 1 & 0\\
-		3 & 0 & 0 & 1 & 1 & 1 & 1\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Developmental time-lag models \citep{mcardle1997expanding} also make use of the Wave Missingness structure.
-As shown in Table \ref{tab:table13}, researchers observe participants at only two measurement occasions, varying the length between occasions for each participant, and then treat this two-time-point data as multi-time-point data with missing values.
-Under this framework they impute these missing values and estimate growth curve models.
-Estimating this type of model would normally require measuring participants at many time points.
-However, under the Wave Missingness design this is accomplished with only two measurement occasions per participant.
-These designs exemplify how useful the Wave Missingness structure is in accelerating longitudinal studies.
-\par
-
-\begin{table}[b!]
-	\centering
-	\caption{Developmental Time-Lag Setup}
-	\label{tab:table13}
-	\setlength{\tabcolsep}{0.75cm}
-	\begin{tabular}{c|cccc}
-		\toprule
-		& \multicolumn{4}{c}{Wave} \\
-		Participant & 1 & 2 & 3 & 4 \\
-		\midrule
-		1 & 1 & 1 & 0 & 0 \\
-		2 & 1 & 0 & 1 & 0 \\
-		3 & 1 & 0 & 0 & 1 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\subsection{Multiple Imputation}
-\label{sec:1.3}
-\subsubsection{Missing Data Mechanisms}
-\label{sec:1.3.1}
-Before describing Multiple Imputation and how it can be applied to PM designs it is important to first understand how data become incomplete.
-Suppose we have a dataset, $Y_{com}$, with some missing values.
-We define the missingness, $R$, to be an indicator variable which equals 0 where $Y_{com}$ is observed and 1 where the corresponding value in $Y_{com}$ is missing.
-Missing data mechanisms describe the proposed probabilistic relationship between $R$ and the values in $Y_{com}$, observed or unobserved \citep{little2014statistical}.
-\par
-
-The first missing data mechanism, missing at random (MAR), was defined by \citet{rubin1976inference}.
-Data are considered MAR when the missingness does not depend on unobserved values but may depend upon other observed variables.
-For instance, if men are less likely to report their incomes than women but the level of income itself does not affect the probability of reporting, then we can say the missingness govern income is MAR.
-\par
-
-Later, \citet{little2014statistical} described two additional mechanisms which lead to missing values: missing completely at random (MCAR) and missing not at random (MNAR) \citep{little2014statistical}.
-The first, MCAR, is used to describe a situation in which the missingness is independent of the observed or unobserved data.
-That is, the missing values are simply a random subset of the full data.
-On the other hand, data is said to be MNAR when the missingness is related to the unobserved data; in a survey people may be less willing to provide their income if it is extremely high or low, for example.
-\par
-
-If we have prior knowledge concerning the relationship between unobserved values, indicated by $R$, and the observed values, then Multiple Imputation can yield efficient estimates even under MNAR \citep{harel2007multiple}.
-However, because this is not typically the case, MI is most often implemented when data is MCAR or MAR \citep{little2014statistical}.
-\par
-
-As a consequence of allowing researchers to decide which values in a dataset are observed and unobserved, PM designs grant control over the missing data mechanism.
-Because of this, MI is an appealing option for researchers utilizing a PM design.
-If implemented properly, data should conform to either the MCAR or MAR assumption.
-For instance, if medical researchers decide not to collect blood pressure on a completely random subset of patients there is no reason to believe the missing blood pressures differ significantly from the observed ones.
-This fact allows for the use of MI and other modern missing data techniques such as the Full Information Maximum Likelihood approach \citep{dempster1977maximum} \par
-
-\subsubsection{The Multiple Imputation Procedure}
-\label{sec:1.3.2}
-Multiple Imputation is used to obtain statistically valid inferences in spite of missing data.
-MI works by replacing unobserved values with a set of plausible values in a way which allows us to account for uncertainty in the imputation process.
-Repeatedly using an imputation technique, every missing value in the incomplete dataset is replaced with a fixed number of imputed values.
-This process allows for the creation of multiple complete datasets, on which users can run complete-data procedures.
-If, for instance, we imputed $M$ possible values for every missing value we would obtain $M$ different completed datasets.
-Once created, the analysis of interest can be performed on each of them and, using rules defined by \citet{little2014statistical} and \citet{rubin2004multiple}, combine the results to obtain a single inference.
-\par
-
-Suppose we are interested in estimating a certain parameter such as the mean of a variable or a regression coefficient.
-If $\theta$ is the parameter of interest, let $\widehat{\theta_1}, \widehat{\theta_2}, ...
-\widehat{\theta_M}$ be the estimates of $\theta$ and let $S_1, S_2, ...
-S_M$ be the corresponding estimated standard errors from the $M$ imputed datasets.
-We can aggregate these results using the combining rules specified by \citet{little2014statistical} and \citet{rubin2004multiple}.
-\par
-The overall MI estimate of $\theta$ is defined as,
-
-\begin{equation}
-\widehat{\theta} = \sum_{n=1}^{M} \widehat{\theta_n}.
-\end{equation}
-
-From here we can compute the sample variance of this estimate by calculating the between-imputation component, $B_M = \sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2 / (M-1)$, and the within-imputation component, $W_M = \sum_{n=1}^{M} S_n^2 / M$.
-These components are combined to obtain the overall sample variance of our MI estimate as follows:
-
-\begin{equation}
-T_M = W_M + (1+1/M)*B_M.
-\end{equation}
-
-These equations form the basis of Rubin's combining rules and provide unbiased parameter estimates accounting for the inherent uncertainty in the imputation process \citep{raghunathan2015missing}.
-For a more in depth explanation of these methods we refer readers to \citet{little2014statistical}.
-\par
-
-When using Multiple Imputation, researchers must decide on the number of imputations, $M$, to use.
-Generally, as the level of missingness decreases the number of imputations needed does as well.
-If less than 20\% of the requisite data is missing, for instance, five or tien imputations will suffice \citep{raghunathan2015missing}.
-However, at its roots, MI is a simulation technique and thus, the greater $M$ is the more stable our estimates become \citep{harel2007inferences}.
-\citet{graham2007many} recommend that if computational power is not a limiting factor, then setting $M=100$ is good practice.
-\par
-
-\section{Data and Simulations}
-\label{sec:2}
-\subsection{Data}
-\label{sec:2.1}
-The dataset the simulations are based on originated in a study by \citet{pellowski2016alcohol}.
-The data was collected in an attempt to determine the day-level relationship between alcohol use, its interactive toxicity beliefs, and adherence to antiretroviral therapy (ART) amongst patients with HIV.
-Previous studies note that alcohol use combined with the perception that mixing alcohol and ARTs can cause adverse effects, correlated with non-adherence to ARTs \citep{kalichman2009prevalence, kalichman2012alcohol}.
-However, \citet{pellowski2016alcohol} pointed out that past research collected data over extended periods of time, preventing the identification a day-level interaction.
-Unlike others, this study was able to determine whether alcohol use and missed medication doses occurred on the same day.
-\par
-
-The study employed an observational cohort design, following sixty participants over forty-five consequtive days via a daily questionnaire.
-Questions in the survey concerned livelihood insecurities from the previous day as well as alcohol use.
-The analysis included eight particular questions: two binary questions on housing insecurity, four binary questions on food insecurity, and two questions concerning alcohol use (one binary variable and one count variable).
-The exact questions can be found in Table \ref{tab:table1}.
-\par
-
-\begin{table}[t]
-	\centering
-	\caption{Survey Questions}
-	\label{tab:table1}
-	\begin{tabular}{cp{6.5cm}c}
-		\toprule
-		Item Number & Question & Responses\\
-		\midrule
-		1 & I worried about having a place to stay yesterday. & 1.Yes $\>$ 2.No \\
-		2 & I could not get to where I needed to go yesterday. & 1.Yes $\>$ 2.No \\
-		3 & I worried about my food running out yesterday. & 1.Yes $\>$ 2.No \\
-		4 & I ate less than I needed to yesterday. & 1.Yes $\>$ 2.No \\
-		5 & I was hungry, but did not eat because I couldn't afford food. & 1.Yes $\>$ 2.No \\
-		6 & I got food from a pantry, church, agency, friend or the street yesterday. & 1.Yes $\>$ 2.No \\
-		7 & Did you drink alcohol yesterday? & 1.Yes $\>$ 2.No \\
-		8 & How many alcohol drinks did you have yesterday? & 0-20 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Beyond the daily questionnaire, data was also collected through a computer-assisted interview on behavioral, psychosocial, and cognitive factors (ex.
-Income, alcohol-toxicity beliefs, education, etc.) which have been shown to be associated with medication adherence.
-These values were only collected at baseline and are considered time independent.
-The variables from this assessment used in our analysis concerned education level, income, age, beliefs about the interactivity of alcohol with ART medication, depression, and alcohol abuse.
-\par
-
-\subsection{Simulations}
-\label{sec:2.2}
-The first step in the process of creating the simulated datasets was to obtain parameter estimates from \citet{pellowski2016alcohol} and to quantify the relationships between variables.
-These estimated relationships were treated as the "true" relationships and one thousand samples were drawn using these parameters.
-The purpose of simulating these datasets was to see how well they captured the true relationship between daily medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score).
-Specifically, our model of interest is the random intercept model with time effect found below: \\
-
-\begin{align*}
-logit(MissedDose) &= \beta_{0j} + \beta_1*DrinkYN + \beta_2*ZAlcTox +\beta_3*Day \\
-Level 2: \beta_{0j} &= \gamma_0 + \epsilon_j
-\end{align*}
-where, \\ \\
-$MissedDose = 1$ if the participant did not adhere to the ART, 0 otherwise. \\
-$DrinkYN = 1$ if the participant drank on a given day, 0 otherwise.\\
-$ZAlcTox =$ Z-transformed score on an alcohol-antiretroviral interactive toxicity scale developed by Kalichman \cite{kalichman2009prevalence}. \\
-$Day =$ The number of days since the study began, 0-44. \\
-$j =$ participant index, 1-60. \\
-$\epsilon_j  \sim N(0, \sigma^2)$. \\ \\
-
-Based on the observed data, the true values of the parameters, $\gamma_0, \beta_1, \beta_2$, $\beta_3$, and $\sigma^2$ were found to be -2.3, 0.56, 1.28, 0.2, and 1.0 respectively. \par
-Once the samples were drawn, they were transformed under the three different missingness structures.
-These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed.
-To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Table \ref{tab:table14}.
-As in the previous tables, "1" indicates an observed occasion while "0" indicates a missing one.
-We see that the Split Form design entails missing two items on each of the days.
-The altered Split Form, while similar, is fully measured on two of the measurement occasions.
-Because there are days which are fully observed, the relationships between variables may be clearer, allowing the imputation procedure to run more effectively.
-On the other hand, the Wave Missingness design shows two days in which no questions are asked but the full questionnaire is given on the remaining days.
-\par
-
-\begin{table}[t!]
-	\centering
-	\caption{Different Planned Missingness Designs}
-	\setlength{\tabcolsep}{0.45cm}
-	\label{tab:table14}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|ccccc}
-		\toprule
-		Design & Day & Q1 & Q2 & Q3 & Q4 & Q5 \\
-		\midrule
-		\multirow{5}{*}{Split Form}
-		& 1 & 1 & 1 & 0 & 0 & 1 \\
-		& 2 & 0 & 0 & 1 & 1 & 1 \\
-		& 3 & 0 & 1 & 1 & 0 & 1 \\
-		& 4 & 1 & 0 & 1 & 1 & 0 \\
-		& 5 & 1 & 1 & 0 & 1 & 1 \\
-		\midrule
-		\midrule
-		\multirow{5}{*}{Altered Split Form}
-		& 1 & 1 & 1 & 1 & 1 & 1 \\
-		& 2 & 1 & 1 & 1 & 1 & 1 \\
-		& 3 & 0 & 0 & 1 & 1 & 1 \\
-		& 4 & 1 & 1 & 0 & 1 & 0 \\
-		& 5 & 0 & 1 & 1 & 0 & 1 \\
-		\midrule
-		\midrule
-		\multirow{5}{*}{Wave Missingness}
-		& 1 & 1 & 1 & 1 & 1 & 1 \\
-		& 2 & 0 & 0 & 0 & 0 & 0 \\
-		& 3 & 1 & 1 & 1 & 1 & 1 \\
-		& 4 & 1 & 1 & 1 & 1 & 1 \\
-		& 5 & 0 & 0 & 0 & 0 & 0 \\
-		\bottomrule
-	\end{tabular}
-	\hspace*{-1cm}	
-\end{table}
-
-Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 25\%, 50\%, and 75\% missing data.
-Previous work by \citet{rhemtulla2014planned} found that for low levels of missingness (25\%) the Three-Form design outperforms the Wave Missingness design in capturing latent growth curve model parameters.
-However, because only low-levels of missingness are tested it is unknown whether this relationship holds at moderate or high levels.
-We hope that by including these different levels of missingness we will be able to see how these designs perform at all levels of the missingness spectrum.
-\par
-Once missingness was created, Multiple Imputation techniques were applied to estimate the relationship between medication adherence and the other variables in our model.
-Because we have control over the missing data mechanism, we know the data is MCAR.
-This fact allows for the principled use of MI techniques.
-Using the R package $\{$mice$\}$ \citep{mice2011imputation} our binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching.
-\par
-
-After imputating, a logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}.
-From here, the results from each PM design were evaluated based on bias, percent bias, mean squared error (MSE), coverage, confidence interval (CI) length, and the fraction of missing information (FMI).
-The FMI is a measure of how much of the MI sample variance comes from differences between imputations.
-In addition to comparing the results between each of the PM designs, the same analyses were also performed before missingness was imposed.
-\par
-
-When determining if the PM designs are performing sufficiently, it is important to consider how well the simulated samples performed before adding a missingness structure.
-For example, consider two full data samples with respective biases on the $\beta_1$ estimate of 0.13 and 0.15.
-Further, after imposing different PM design structures on these samples, the average biases are 0.14 and 0.15 respectively.
-It would be unfair to claim that the first PM design performed better than the second because, by chance, it was based off of a more representative sample.
-This fact was considered when determining the evaluation criteria.
-\par
-
-For bias, percent bias, and MSE we claimed that an increase of more than 40\% in these measurements after imposing missingness indicates that the PM design is inappropriate.
-For instance, if the complete data shows a percent bias of 10\%, anything higher than 14\% would be unacceptable.
-An increase of this size has the ability to negatively effect efficiency of our estimation.
-Based on the work of \citet{collins2001comparison} we also regard coverages of less than 90\% as unacceptable.
-If a 95\% CI has a true coverage of 90\% than the Type I error rate is double what it should be.
-Because MI accounts for uncertainty in the imputation process, coverages should be similar despite the added missingness.
-In terms of confidence interval lengths, if one PM design provides similar rates of coverage to another while maintaining shorter intervals than this is considered the better of the two methods.
-For equal coverage rates, shorter intervals imply more power.
-The FMI, which quantifies the uncertainty in our imputation process, is simply reported for each PM design.
-While less uncertainty in the imputations can be beneficial, less variation does not necessarily imply accuracy.
-Thus, FMI should be taken in the context of the other measurements.
-\par
-
-This process was repeated under the three modified simulation scenarios mentioned in the following sections.
-Note that while typically these PM designs would be compared against the results obtained using a complete case analysis \citep{rhemtulla2016asymptotic}, this approach was avoided as it would fundamentally alter the form of the data.
-Specifically, complete case analysis removes any observation with any missing values.
-Then, for the Split Form design this would remove all observations.
-In the Wave Missingness setup, complete case analysis would shorten the length of the longitudinal study.
-If a participant was missing values on 11 of the 45 days, then complete case analysis would have made the data resemble a longitudinal study held over 34 days.
-Hence, this comparison is invalid.
-\par
-
-\subsubsection{Increased Sample Size}
-In order to evaluate the impact of sample size on estimation, the original sample size of 60 participants was expanded to 120.
-The rest of the simulation process was carried out as before.
-As noted earlier, the cost savings gleaned from the PM designs could allow us to enroll more participants.
-Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, researchers can design missingness in whichever method is most convenient.
-Furthermore, because Wave Missingness allows for greater savings, an increase in sample size is more reasonable for that type of missingness.
-\par
-\subsubsection{Low Inter-Survey Correlation}
-For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best.
-To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days.
-While this fact was accounted for in the original simulations, it was not in this set of simulations.
-If the probability of answering "yes" on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables.
-This implies that each of the questions are conditionally independent of each other given the baseline variables.
-If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal.
-\par
-\subsubsection{High Time Effect}
-In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable.
-To do this we changed the value of the parameters $\gamma_0, \beta_1, \beta_2,$ and $\beta_3$ to -4.6, 0.28, 0.64, and 0.2 respectively.
-Note that instead of increasing the value of $\beta_3$, the slope for time effect, all the other parameters were decreased.
-This was done because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1.
-Decreasing the other variables effects ensured that time has a disproportionate effect without this problem.
-The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point.
-\par
-
-\section{Results}
-\label{sec:3}
-\subsection{Primary Simulation}
-\label{sec:3.1}
-The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$.
-The effects of the variables here are comparable to those found in the original dataset.
-This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design.
-Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:table2}.
-Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
-
-<<echo=FALSE, warning=FALSE>>=
-# if (Sys.info()[8] == "Josie"){
-#   setwd("~/GitHub/designedmissingness")
-# }
-# if (Sys.info()[8] == "gregorymatthews"){
-#   setwd("~/Dropbox/designedmissingnessGit")
-# }
-
-# Table 7
+% \begin{table}[!h]
+% 	\centering
+% 	\caption{The Wave Missingness PM Design}
+% 	\label{tab:table11}
+% 	\setlength{\tabcolsep}{0.75cm}
+% 	\begin{tabular}{c|ccccc}
+% 		\toprule
+% 		& \multicolumn{5}{c}{Month} \\
+% 		Participant & 1 & 2 & 3 & 4 & 5 \\
+% 		\midrule
+% 		1 & 1 & 0 & 1 & 0 & 1 \\
+% 		2 & 1 & 1 & 0 & 1 & 0 \\
+% 		3 & 0 & 0 & 1 & 1 & 1 \\
+% 		4 & 1 & 1 & 1 & 0 & 0 \\
+% 		\bottomrule
+% 	\end{tabular}
+% \end{table}
+<<>>=
 library(kableExtra)
@@
 
-names(df_8) <- c("Design", "Missingness", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
+names(df_8) <- c("Design", "Level", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
 row.names(df_8) <- NULL
 kable(df_8, escape = FALSE, format ="latex") %>%
-  collapse_rows(columns = 1:2, latex_hline = "full")
-  column_spec(1, width = "30em")
-
-# library(knitr)
-# kable(cbind("","","",rbind(low_8[[1]],med_8[[1]],high_8[[1]],low_8[[2]],med_8[[2]],high_8[[2]],low_8[[3]],med_8[[3]],high_8[[3]])),format="latex")
-
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime1.RData")
-high <- d
-
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime1.RData")
-med <- d
-
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime1.RData")
-low <- d
-
-library(xtable)
-print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
-
+  collapse_rows(columns = 1:2, latex_hline = "full") %>%
+  kable_styling(latex_options = "scale_down")
 @
-
-% latex table generated in R 3.5.0 by xtable 1.8-2 package
-% Mon May 14 21:02:34 2018
-\begin{table}[ht]
-\centering
-\begin{tabular}{lllrrrr}
-  \hline
-Design & \% Missingness  & Parameter & Coverage & Bias & MSE & FMI \\ 
-  \hline
- &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
-   &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
-   &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
-   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
-   \hline
-   &  &  & 0.986 & 0.040 & 0.019 & 0.012 \\ 
-   &  &  & 0.993 & -0.168 & 0.750 & 0.557 \\ 
-   &  &  & 0.932 & 0.008 & 0.024 & 0.002 \\ 
-   &  &  & 0.940 & -0.000 & 0.000 & 0.008 \\ 
-   \hline
-   &  &  & 0.984 & 0.036 & 0.027 & 0.030 \\ 
-   &  &  & 0.991 & -0.713 & 9.933 & 0.625 \\ 
-   &  &  & 0.932 & 0.009 & 0.027 & 0.005 \\ 
-   &  &  & 0.939 & -0.000 & 0.000 & 0.021 \\ 
-   \hline
-   &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
-   &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
-   &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
-   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
-   \hline
-   &  &  & 0.988 & 0.040 & 0.018 & 0.010 \\ 
-   &  &  & 0.994 & -0.167 & 0.782 & 0.549 \\ 
-   &  &  & 0.931 & 0.009 & 0.024 & 0.002 \\ 
-   &  &  & 0.944 & -0.000 & 0.000 & 0.006 \\ 
-   \hline
-   &  &  & 0.983 & 0.036 & 0.022 & 0.027 \\ 
-   &  &  & 0.990 & -0.686 & 10.509 & 0.665 \\ 
-   &  &  & 0.928 & 0.009 & 0.026 & 0.007 \\ 
-   &  &  & 0.946 & -0.000 & 0.000 & 0.023 \\ 
-   \hline
-   &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
-   &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
-   &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
-   &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
-   \hline
-   &  &  & 0.991 & 0.029 & 0.018 & 0.055 \\ 
-   &  &  & 0.988 & -0.112 & 0.345 & 0.752 \\ 
-   &  &  & 0.934 & 0.009 & 0.024 & 0.007 \\ 
-   &  &  & 0.951 & -0.000 & 0.000 & 0.032 \\ 
-   \hline
-   &  &  & 0.994 & -0.003 & 0.022 & 0.258 \\ 
-   &  &  & 0.988 & -0.105 & 0.284 & 0.903 \\ 
-   &  &  & 0.937 & 0.011 & 0.025 & 0.039 \\ 
-   &  &  & 0.960 & -0.000 & 0.000 & 0.175 \\ 
-   \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[b!]
-	\centering
-	\caption{Results of Analysis before imposing Missingness in each Scenario}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table2}
-	\begin{tabular}{cc|ccccc}
-		\toprule
-		Scenario & Parameter & Bias & Percent Bias & MSE & Coverage & CI Length \\
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Primary \\ Analysis (N=60)}} 
-		& $\gamma_0$ & 0.151 & 6.55\% & 0.037 & 99.0\% & 0.750 \\
-		& $\beta_1$ & 0.133 & 23.75\% & 0.028 & 95.5\% & 0.652 \\
-		& $\beta_2$ & 0.120 & 9.40\% & 0.022 & 97.5\% & 0.610 \\
-		& $\beta_3$ & 0.007 & 3.42\% & 7.11$*10^-5$ & 97.0\% & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Increased \\ Sample (N=120)}} 
-		& $\gamma_0$ & 0.106 & 4.61\% & 0.018 & 98.0\% & 0.528 \\
-		& $\beta_1$ & 0.099 & 17.63\% & 0.016 & 93.0\% & 0.460 \\
-		& $\beta_2$ & 0.091 & 7.12\% & 0.013 & 95.5\% & 0.429 \\
-		& $\beta_3$ & 0.005 & 2.34\% & 3.52$*10^-5$ & 96.5\% & 0.024 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Low \\Inter-Survey Correlation (N=60)}} 
-		& $\gamma_0$ & 0.145 & 6.29\% & 0.033 & 99.0\% & 0.747 \\
-		& $\beta_1$ & 0.130 & 23.27\% & 0.027 & 94.5\% & 0.651 \\
-		& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 94.0\% & 0.611 \\
-		& $\beta_3$ & 0.007 & 3.69\% & 8.88$*10^-5$ & 93.0\% & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{High \\Time Effect (N=60)}}
-		& $\gamma_0$ & 0.170 & 3.69\% & 0.045 & 98.5\% & 0.888 \\
-		& $\beta_1$ & 0.123 & 43.86\% & 0.024 & 96.0\% & 0.598 \\
-		& $\beta_2$ & 0.124 & 19.35\% & 0.025 & 93.5\% & 0.575 \\
-		& $\beta_3$ & 0.006 & 2.95\% & 5.50$*10^-5$ & 95.5\% & 0.030 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Of note in the complete-data primary analysis is that the coverage of the 95\% CIs is larger than expected for the parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large.
-This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}.
-Nevertheless, we should keep this in mind when analyzing our results from the PM designs provided in Table \ref{tab:table3}.
-In Table \ref{tab:table3} as in Tables \ref{tab:table4}, \ref{tab:table5}, and \ref{tab:table6} bold values indicate "Unacceptable" results.
-That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
-
-\begin{table}[p]
-	\centering
-	\caption{Primary Simulation Results (N=60)}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table3}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.151 & 6.59\% & 0.037 & 99.5\% & 0.753 & 0.009 \\
-		&& $\beta_1$ & 0.139 & 24.78\% & 0.029 & 96.0\% & 0.693 & 0.112 \\
-		&& $\beta_2$ & 0.120 & 9.41\% & 0.022 & 97.0\% & 0.610 & 0.002 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.12$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.153 & 6.67\% & 0.037 & 99.0\% & 0.765 & 0.040 \\
-		&& $\beta_1$ & 0.162 & 28.93\% & 0.041 & 95.5\% & 0.869 & 0.390 \\
-		&& $\beta_2$ & 0.121 & 9.51\% & 0.022 & 97.0\% & 0.616 & 0.007 \\
-		&& $\beta_3$ & 0.007 & 3.40\% & 6.99$*10^-5$ & 98.5\% & 0.034 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.154 & 6.70\% & 0.039 & 98.5\% & 0.818 & 0.147 \\
-		&& $\beta_1$ & \textbf{0.225} & \textbf{40.16}\% & \textbf{0.076} & 97.5\% & 1.464 & 0.710 \\
-		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 97.5\% & 0.611 & 0.022 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.02$*10^-5$ & 98.0\% & 0.035 & 0.032 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.151 & 6.57\% & 0.037 & 98.0\% & 0.753 & 0.008 \\
-		&& $\beta_1$ & 0.137 & 24.55\% & 0.030 & 96.0\% & 0.690 & 0.105 \\
-		&& $\beta_2$ & 0.120 & 9.39\% & 0.022 & 97.5\% & 0.611 & 0.002 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.153 & 6.67\% & 0.038 & 99.5\% & 0.760 & 0.030 \\
-		&& $\beta_1$ & 0.151 & 26.93\% & 0.036 & 96.0\% & 0.811 & 0.324 \\
-		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 96.0\% & 0.611 & 0.006 \\
-		&& $\beta_3$ & 0.007 & 3.44\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.164 & 7.13\% & 0.042 & 98.0\% & 0.799 & 0.105 \\
-		&& $\beta_1$ & \textbf{0.225} & \textbf{40.14\%} & \textbf{0.080} & 96.0\% & 1.265 & 0.640 \\
-		&& $\beta_2$ & 0.117 & 9.13\% & 0.021 & 97.5\% & 0.615 & 0.019 \\
-		&& $\beta_3$ & 0.007 & 3.46\% & 7.07$*10^-5$ & 98.0\% & 0.034 & 0.023 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.152 & 6.61\% & 0.037 & 99.5\% & 0.757 & 0.023 \\
-		&& $\beta_1$ & 0.147 & 26.25\% & 0.033 & 96.0\% & 0.767 & 0.270 \\
-		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 96.0\% & 0.610 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.41\% & 6.97$*10^-5$ & 98.0\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.157 & 6.84\% & 0.039 & 100.0\% & 0.767 & 0.052 \\
-		&& $\beta_1$ & \textbf{0.190} & \textbf{33.95\%} & \textbf{0.058} & 94.5\% & 0.934 & 0.465 \\
-		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 97.5\% & 0.609 & 0.008 \\
-		&& $\beta_3$ & 0.007 & 3.34\% & 6.80$*10^-5$ & 98.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.168 & 7.30\% & 0.045 & 99.5\% & 0.807 & 0.129 \\
-		&& $\beta_1$ & \textbf{0.290} & \textbf{51.77\%} & \textbf{0.132} & \textbf{88.5\%} & 1.335 & 0.680 \\
-		&& $\beta_2$ & 0.119 & 9.32\% & 0.022 & 96.0\% & 0.614 & 0.017 \\
-		&& $\beta_3$ & 0.007 & 3.40\% & 6.96$*10^-5$ & 98.5\% & 0.034 & 0.025 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{Increased Sample Size simulation Results (N=120)}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table4}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.106 & 4.60\% & 0.017 & 98.5\% & 0.533 & 0.022 \\
-		&& $\beta_1$ & 0.106 & 18.96\% & 0.018 & 96.0\% & 0.548 & 0.263 \\
-		&& $\beta_2$ & 0.091 & 7.14\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.33\% & 3.47$*10^-5$ & 96.5\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.112 & 4.85\% & 0.019 & 98.0\% & 0.542 & 0.057 \\
-		&& $\beta_1$ & 0.134 & 23.86\% & \textbf{0.027} & 95.0\% & 0.696 & 0.489 \\
-		&& $\beta_2$ & 0.092 & 7.15\% & 0.013 & 96.5\% & 0.430 & 0.009 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.110 & 4.80\% & 0.019 & 99.5\% & 0.575 & 0.153 \\
-		&& $\beta_1$ & \textbf{0.194} & \textbf{34.59\%} & \textbf{0.057} & 94.5\% & 1.088 & 0.742 \\
-		&& $\beta_2$ & 0.092 & 7.20\% & 0.013 & 95.0\% & 0.432 & 0.021 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.42$*10^-5$ & 97.5\% & 0.024 & 0.026 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.107 & 4.64\% & 0.017 & 98.0\% & 0.533 & 0.022 \\
-		&& $\beta_1$ & 0.111 & 19.80\% & 0.020 & 94.5\% & 0.545 & 0.263 \\
-		&& $\beta_2$ & 0.091 & 7.08\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.115 & 4.99\% & 0.020 & 98.0\% & 0.542 & 0.056 \\
-		&& $\beta_1$ & 0.138 & 24.65\% & \textbf{0.028} & 94.5\% & 0.693 & 0.494 \\
-		&& $\beta_2$ & 0.091 & 7.24\% & 0.013 & 96.0\% & 0.430 & 0.008 \\
-		&& $\beta_3$ & 0.005 & 2.34\% & 3.54$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.115 & 5.01\% & 0.020 & 99.0\% & 0.563 & 0.119 \\
-		&& $\beta_1$ & \textbf{0.188} & \textbf{33.65\%} & \textbf{0.058} & 91.5\% & 0.958 & 0.681 \\
-		&& $\beta_2$ & 0.092 & 7.16\% & 0.013 & 96.0\% & 0.432 & 0.018 \\
-		&& $\beta_3$ & 0.005 & 2.30\% & 3.44$*10^-5$ & 96.0\% & 0.024 & 0.020 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.108 & 4.72\% & 0.018 & 98.0\% & 0.533 & 0.024 \\
-		&& $\beta_1$ & 0.123 & 21.90\% & \textbf{0.024} & 92.0\% & 0.551 & 0.287 \\
-		&& $\beta_2$ & 0.092 & 7.18\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.35\% & 3.51$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.111 & 4.84\% & 0.019 & 99.0\% & 0.540 & 0.052 \\
-		&& $\beta_1$ & \textbf{0.168} & \textbf{30.02\%} & \textbf{0.043} & \textbf{85.5\%} & 0.671 & 0.489 \\
-		&& $\beta_2$ & 0.092 & 7.22\% & 0.013 & 95.0\% & 0.429 & 0.007 \\
-		&& $\beta_3$ & 0.005 & 2.32\% & 3.42$*10^-5$ & 97.0\% & 0.024 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.123 & 5.33\% & 0.023 & 99.0\% & 0.558 & 0.108 \\
-		&& $\beta_1$ & \textbf{0.248} & \textbf{44.26\%} & \textbf{0.099} & \textbf{82.0\%} & 0.894 & 0.666 \\
-		&& $\beta_2$ & 0.094 & 7.36\% & 0.014 & 96.0\% & 0.430 & 0.013 \\
-		&& $\beta_3$ & 0.005 & 2.36\% & 3.53$*10^-5$ & 96.0\% & 0.024 & 0.015 \\
-		\bottomrule
-	\end{tabular}	
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{Low Inter-Survey Correlation Simulation Results (N=60)}
-	\label{tab:table5}
-	\setlength{\tabcolsep}{0.1cm}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.146 & 6.34\% & 0.033 & 99.0\% & 0.755 & 0.025 \\
-		&& $\beta_1$ & 0.150 & 26.82\% & 0.034 & 95.5\% & 0.782 & 0.278 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.612 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.64\% & 8.68$*10^-5$ & 92.5\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.148 & 6.43\% & 0.034 & 99.0\% & 0.772 & 0.067 \\
-		&& $\beta_1$ & \textbf{0.183} & \textbf{32.65\%} & \textbf{0.053} & 95.0\% & 1.032 & 0.526 \\
-		&& $\beta_2$ & 0.125 & 9.80\% & 0.026 & 94.0\% & 0.613 & 0.010 \\
-		&& $\beta_3$ & 0.007 & 3.63\% & 8.73$*10^-5$ & 92.5\% & 0.035 & 0.015 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.155 & 6.74\% & 0.036 & 99.5\% & 0.825 & 0.166 \\
-		&& $\beta_1$ & \textbf{0.276} & \textbf{49.31\%} & \textbf{0.116} & 95.0\% & 1.567 & 0.749 \\
-		&& $\beta_2$ & 0.124 & 9.71\% & 0.025 & 94.0\% & 0.618 & 0.025 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.73$*10^-5$ & 93.5\% & 0.035 & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.141 & 6.13\% & 0.031 & 99.0\% & 0.754 & 0.023 \\
-		&& $\beta_1$ & 0.139 & 25.80\% & 0.030 & 95.5\% & 0.772 & 0.260 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.612 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.55$*10^-5$ & 92.5\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.149 & 6.48\% & 0.035 & 99.5\% & 0.767 & 0.056 \\
-		&& $\beta_1$ & 0.170 & 30.44\% & \textbf{0.044} & 97.0\% & 0.968 & 0.486 \\
-		&& $\beta_2$ & 0.125 & 9.79\% & 0.025 & 93.5\% & 0.612 & 0.009 \\
-		&& $\beta_3$ & 0.007 & 3.64\% & 8.58$*10^-5$ & 92.5\% & 0.034 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.149 & 6.47\% & 0.036 & 98.5\% & 0.809 & 0.139 \\
-		&& $\beta_1$ & \textbf{0.228} & \textbf{40.70\%} & \textbf{0.088} & 96.0\% & 1.425 & 0.708 \\
-		&& $\beta_2$ & 0.125 & 9.74\% & 0.026 & 94.0\% & 0.617 & 0.021 \\
-		&& $\beta_3$ & 0.007 & 3.62\% & 8.65$*10^-5$ & 93.5\% & 0.035 & 0.027 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.138 & 6.02\% & 0.031 & 99.5\% & 0.754 & 0.025 \\
-		&& $\beta_1$ & 0.158 & 28.17\% & 0.036 & 96.5\% & 0.776 & 0.286 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.611 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.50$*10^-5$ & 92.5\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.148 & 6.43\% & 0.034 & 99.5\% & 0.765 & 0.053 \\
-		&& $\beta_1$ & \textbf{0.197} & \textbf{35.14\%} & \textbf{0.059} & 91.0\% & 0.939 & 0.472 \\
-		&& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 93.5\% & 0.611 & 0.007 \\
-		&& $\beta_3$ & 0.007 & 3.60\% & 8.48$*10^-5$ & 92.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.158 & 6.86\% & 0.040 & 98.5\% & 0.799 & 0.122 \\
-		&& $\beta_1$ & \textbf{0.303} & \textbf{54.18\%} &\textbf{0.148} & \textbf{89.5\%} & 1.290 & 0.676 \\
-		&& $\beta_2$ & 0.127 & 9.94\% & 0.027 & 95.5\% & 0.615 & 0.015 \\
-		&& $\beta_3$ & 0.007 & 3.62\% & 8.77$*10^-5$ & 93.5\% & 0.035 & 0.021 \\
-		\bottomrule
-	\end{tabular}	
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{High Time Effect Simulation Results (N=60)}
-	\label{tab:table6}
-	\setlength{\tabcolsep}{0.1cm}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.169 & 3.67\% & 0.045 & 99.0\% & 0.895 & 0.015 \\
-		&& $\beta_1$ & 0.133 & 47.54\% & 0.029 & 96.0\% & 0.708 & 0.262 \\
-		&& $\beta_2$ & 0.124 & 19.33\% & 0.025 & 93.5\% & 0.576 & 0.003 \\
-		&& $\beta_3$ & 0.006 & 2.96\% & 5.50$*10^-5$ & 94.5\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.174 & 3.77\% & 0.047 & 98.5\% & 0.912 & 0.050 \\
-		&& $\beta_1$ & \textbf{0.181} & \textbf{64.59\%} & \textbf{0.049} & 96.0\% & 0.981 & 0.554 \\
-		&& $\beta_2$ & 0.124 & 19.44\% & 0.025 & 94.0\% & 0.578 & 0.007 \\
-		&& $\beta_3$ & 0.006 & 2.97\% & 5.55$*10^-5$ & 96.0\% & 0.030 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.177 & 3.85\% & 0.049 & 98.0\% & 0.954 & 0.117 \\
-		&& $\beta_1$ & \textbf{0.243} & \textbf{86.63\%} & \textbf{0.097} & 93.0\% & 1.433 & 0.729 \\
-		&& $\beta_2$ & 0.124 & 19.37\% & 0.025 & 94.0\% & 0.581 & 0.016 \\
-		&& $\beta_3$ & 0.006 & 2.97\% & 5.70$*10^-5$ & 94.0\% & 0.030 & 0.025 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.171 & 3.72\% & 0.046 & 99.0\% & 0.895 & 0.015 \\
-		&& $\beta_1$ & 0.142 & 50.55\% & 0.033 & 94.5\% & 0.717 & 0.272 \\
-		&& $\beta_2$ & 0.124 & 19.36\% & 0.025 & 93.5\% & 0.577 & 0.002 \\
-		&& $\beta_3$ & 0.006 & 2.95\% & 5.48$*10^-5$ & 95.5\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.176 & 3.82\% & 0.048 & 99.0\% & 0.905 & 0.038 \\
-		&& $\beta_1$ & 0.168 & 60.10\% & \textbf{0.043} & 95.5\% & 0.903 & 0.486 \\
-		&& $\beta_2$ & 0.124 & 19.36\% & 0.025 & 93.5\% & 0.581 & 0.006 \\
-		&& $\beta_3$ & 0.006 & 2.95\% & 5.60$*10^-5$ & 95.0\% & 0.030 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.177 & 3.84\% & 0.051 & 99.5\% & 0.947 & 0.108 \\
-		&& $\beta_1$ & \textbf{0.257} & \textbf{91.96\%} & \textbf{0.097} & 94.5\% & 1.381 & 0.714 \\
-		&& $\beta_2$ & 0.124 & 19.34\% & 0.025 & 94.5\% & 0.581 & 0.014 \\
-		&& $\beta_3$ & 0.006 & 3.01\% & 5.76$*10^-5$ & 95.0\% & 0.030 & 0.023 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.170 & 3.70\% & 0.046 & 99.0\% & 0.895 & 0.016 \\
-		&& $\beta_1$ & 0.135 & 48.11\% & 0.026 & 96.5\% & 0.720 & 0.290 \\
-		&& $\beta_2$ & 0.124 & 19.40\% & 0.025 & 93.5\% & 0.576 & 0.002 \\
-		&& $\beta_3$ & 0.006 & 2.94\% & 5.50$*10^-5$ & 95.0\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.173 & 3.77\% & 0.047 & 99.0\% & 0.904 & 0.035 \\
-		&& $\beta_1$ & \textbf{0.186} & \textbf{66.53\%} & \textbf{0.052} & 92.0\% & 0.864 & 0.466 \\
-		&& $\beta_2$ & 0.124 & 19.40\% & 0.025 & 93.5\% & 0.576 & 0.004 \\
-		&& $\beta_3$ & 0.006 & 2.94\% & 5.50$*10^-5$ & 96.0\% & 0.030 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.188 & 4.09\% & 0.055 & 98.5\% & 0.946 & 0.105 \\
-		&& $\beta_1$ & \textbf{0.322} & \textbf{115.10\%} & \textbf{0.149} & \textbf{85.5\%} & 1.306 & 0.712 \\
-		&& $\beta_2$ & 0.127 & 19.87\% & 0.026 & 93.5\% & 0.580 & 0.011 \\
-		&& $\beta_3$ & 0.006 & 3.02\% & 5.75$*10^-5$ & 95.0\% & 0.030 & 0.025 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-For the Split Form and Altered Split Form designs seen in Table \ref{tab:table3}, note that the greatest loss in efficiency was on the $\beta_1$ estimate.
-While the CI coverage remained high at all levels of missingness for the two designs, the bias, percent bias, and MSE reached unacceptable levels at the high missingness level.
-We also point out that the Altered Split Form design did not perform significantly better than the regular Split Form design.
-While some individual measurements outperformed those from the Split Form design, bias on $\beta_1$ for example, it underperformed in others, such as percent bias on $\beta_3$.
-In reference to the FMI on the $\beta_1$ estimate, we can see that at low and medium missingness both Split Form designs performed well.
-That is, there was less variance in the results from th imputed datasets than we expected given the amount of missing data.\par
-
-Towards the bottom of Table \ref{tab:table3}, the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at both medium and high levels of missingness.
-Moreover, at high levels of missingness coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.
-Additionally, we see that CI length for the $\beta_1$ estimate was roughly equal across all designs, despite the fact that the Wave Missingness design provided more biased estimates.
-\par
-
-\subsection{Increased Sample Size}
-\label{sec:3.2}
-In the next simulation scenario the sample size was increased to 120 participants.
-All parameter values were held the same as in the original simulation.
-Table \ref{tab:table2}, again, contains the results of the analysis before applying any PM design.
-\par
-
-The results of the full-data simulations are compared to those obtained from the PM designs, shown in Table \ref{tab:table4}.
-First notice the bias of all parameters is lower than in the smaller sample size simulations.
-Next, the Split Form design performed similarly well as in the first.
-At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable.
-However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:table2}.
-The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088.
-Furthermore, the percent bias on the $\beta_1$ estimate is not seriously different from that obtained in the small sample scenario.
-For example, at medium levels of missingness the percent bias on $\beta_1$ is 23.86\% while for the smaller sample it was 23.75\%.
-Similarly to the Split Form design, the Altered Split Form Design also provided unacceptable results for the MSE of the $\beta_1$ estimate at medium missingness and unacceptable bias, percent bias, and MSE at high levels.
-\par
-For the Wave Missingness design we continue to see the issues observed in the small sample simulations.
-That is, for the $\beta_1$ estimate the measurements at medium and high levels of missingness are unacceptable and a steep drop off in coverage probability occurs for the 95\% CIs.
-In fact, at medium and high levels of missingness the coverages drop to 85.5\% and 82.0\%.
-The $\gamma_0$ parameter also continues to be estimated poorly at high levels of missing data under the Wave Missingness design.
-\par
-
-\subsection{Low Inter-Survey Correlation}
-\label{sec:3.3}
-For the next set of simulations sample size returned to 60 participants but the level of inter-survey correlation decreased.
-The results obtained from the full data simulations are provided in Table \ref{tab:table2} while the results from the PM designs are given in Table \ref{tab:table5}.
-\par
-
-For the Split Form design it is important to notice that the efficiency of the $\beta_1$ estimate decreases much more rapidly than in the original simulations where survey questions were predictive of one another.
-For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be 0.150 and 0.276 at high levels.
-This left us with an increase in average bias of 0.126.
-Looking at the same increase in the original simulations, note that the bias only increased by 0.071.
-This loss in efficiency is seen in the other measurements on the $\beta_1$ estimate as well.
-Moreover, note that the Split Form design performs unacceptably in terms of bias, percent bias, and MSE at medium levels of missingness.
-This was not the case in the other missingness scenarios.
-\par
-
-The Altered Split Form design at medium levels of missingness yielded an MSE outside of the acceptable range and at high levels bias, the percent bias are unacceptable as well.
-Additionally, the coverage of the $\beta_1$ CIs was quite a bit higher than in the full-data simulations.
-That is, while the coverage probability obtained in the full-data simulations was 94.5\%, under this Altered Split Form design the coverages are 95.5\%, 97.0\%, and 96.0\% at low, medium, and high levels of missingness respectively.
-\par
-
-Under Wave Missingness the issues of unacceptable bias, percent bias and MSE occur.
-However, at low levels of missingness, the coverage of the $\beta_1$ estimate was fairly good (96.5\% compared to 94.5\% in the full data).
-Sufficient coverage did not hold through increased missingness as coverage dropped to 89.5\% in the high missingness scenario.
-As in other scenarios, the CI lengths produced under the Wave Missingness design are similar to those produced in the Split Form designs despite an increase in bias.
-However, here the increase in bias is less dramatic than in other scenarios.
-For example, at high levels of missingness in the original simulations the average bias on the $\beta_1$ estimate was 0.065 higher for the Wave Missingness design (at 0.290) than in the Split Form design (0.225).
-In this simulation scenario that same difference was only 0.027.
-Moreover, while the estimation of $\gamma_0$ was unacceptable at high levels of missingness in the other simulation scenarios, here it was in the acceptable range.\par
-
-\subsection{High Time Effect}
-\label{sec:3.4}
-In the final scenario we tested to see how the PM designs would capture a model where time had a disproportionately large effect on Missed Dose.
-In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$.
-The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:table6}.
-\par
-
-The effects of imposing Split Form missingness in this high time effect scenario are similar to those under the low inter-survey correlation scenario.
-At low levels of missingness bias, percent bias, MSE, and coverage for $\beta_1$ are all within the acceptable range.
-At medium and high levels of missingness bias, percent bias, and MSE are unacceptably high.
-\par
-
-The Altered Split Form design performed slightly better than the normal Split Form design under this simulation scenario.
-Note, however, that while the normal Split Form design provided unacceptable bias and percent bias for the $\beta_1$ estimate at medium levels of missingness, this was not true of the Altered Split Form design.
-Additionally, observe that at medium and high levels of missingness there was an improvement under the Split Form design in the CI lengths for the $\beta_1$ estimate.
-In the Split Form design the CI lengths were recorded as 0.981 and 1.433 at medium and high missingness.
-Under the Altered Split Form design these measurements were 0.903 and 1.381.
-\par
-
-In this simulation scenario, the Wave Missingness Design performs similarly to the Split Form and Altered Split Form designs at low levels of missingness.
-The bias, percent bias, MSE, and CI coverage for $\beta_1$ all performed acceptably using the Wave Missingness design at low levels of missingness.
-However, as missingness increases this design shows itself to be unsuitable in terms of estimating $\beta_1$ for the same reasons noted in the other scenarios.
-\par
-
-\subsection{Interpretation}
-\label{sec:3.5}
-We note two commonalities throughout our simulation scenarios.
-The first is that the Altered Split Form design consistently failed to produce better results than the normal Split Form design.
-Secondly, the Wave Missingness Design resulted in unacceptably poor estimation for anything but low levels of missingness.
-\par
-
-This first result, the lack of improvement seen in the Altered Split form design is surprising.
-By keeping a small number of measurement occasions fully observed we would have expected the imputation process to perform more effectively and improve our estimates.
-However, even factoring in the slight decrease in overall missingness, this design performed only equally as well as the normal Split Form design.
-This may be a result of the fact that the number of observations we left fully observed was small; only two out of the forty-five days (approximately 4.4\% of days).
-While it may be interesting to see if the inclusion of more fully observed days is capable of improving our estimates, perhaps keeping five days (11.1\%) fully observed, we would need to be careful about raising this number too high.
-If the cost or burden of observations is a limiting factor, then collecting full data on even 10\% of the days may be unnecessarily burdensome.
-\par
-
-Of larger concern, however, is the steep drop-off in estimating quality of the Wave Missingness design as missingness increased.
-In every scenario tested, the Wave Missingness design produced unacceptable bias, percent bias, and MSE at medium and high levels of missingness.
-In addition, despite increased bias on estimates with missing values, the length of confidence intervals for these estimates remained the same as in the Split Form design.
-This implies that there is an underestimation of the variances occurring at some point in the imputation process.
-This is supported by the fact that, generally, the fraction of missing information estimated in the Wave Missingness design tended to be smaller than that of the corresponding Split Form design.
-This can also explain the lower confidence interval coverages obtained using this design.
-At high levels of missingness none of the scenarios allowed the Wave Missingness design to obtain coverages above 90\%.
-This leads to the belief that many of the imputations are producing datasets which are similar in terms of the relationships between variables but that are not representative of the true relationships.
-Because of this, the use of Wave Missingness designs for anything but small levels of missing data cannot be recommended.
-\par
-
-Additionally, all PM designs under all scenarios performed within acceptable ranges when measuring the effects of variables which had no missing values ($\gamma_0, \beta_2, \beta_3$).
-This fact makes the increased sample size scenario promising for researchers.
-While our estimation of $\beta_1$ was similar in this scenario as in others, the estimation of the other model parameters improved by leaps and bounds.
-If a PM design is able to reduce costs by 50\% by introducing missingness, using these extra funds to recruit more participants may be a good idea for researchers whose analysis of interest involves variables that will not have missing values.
-\par
-
-\section{Discussion}
-\label{4}
-In this paper we performed a simulation study to test the ability of different PM designs to capture a multilevel logistic model under a longitudinal framework.
-We found that for low levels of planned missing data (about 25\% missingness), variations of the Split Form design and the Wave Missingness designs are all capable of estimating the parameters of the multilevel model reasonably well.
-As the level of missing data increases to 50\% and 75\%, however, the quality of estimates in all of the tested PM designs become unacceptable as we see rising parameter biases and confidence interval lengths.
-Moreover, we found that the quality of the Wave Missingness design depreciates much more rapidly than the other PM designs, providing higher parameter biases than the corresponding Split Form estimates and low confidence interval coverages (95\% confidence intervals with less than 90\% coverage in some cases).
-\par
-
-These facts warn against the use of Wave Missingness designs when the Split Form design can be easily substituted.
-If Wave Missingness must be used, as in the cohort sequential and developmental timelLag designs, the design must minimize the amount of missing data.
-For instance, in a cohort sequential design which attempts to stretch four-year data to cover a span of six years each cohort will have missing values at two of the six measurement occasions.
-This would result in about 33.3\% missingness.
-To ensure that the researcher's analyses are accurate, we would recommend an increase in the amount of time they follow participants, using five-year data instead of four-year data to cover the same period.
-While the recommendation to use low levels of missing data is especially true for Wave Missingness designs it also holds for the Split Form designs.
-While these designs tended to perform well for all parameters in the multilevel model at low levels of missingness this was not true when missingness was increased to around 50\%.
-\par
-
-For future research it may be useful to test a wider range of missingness.
-That is, while this study showed that the PM designs performed well when missingness was around 25\% and sometimes performed poorly when it was around 50\% it is unknown exactly when the estimation procedure breaks down.
-While only 25\% missing data is suggested here, if it was shown that these designs performed well at 40\% missingness, then researchers could substantially increase cost reduction and decrease participant burden beyond what our recommendations allow.
-Another worthwhile pursuit may be to see how hybrid PM designs perform.
-While it was found that Wave Missingness designs performed underwhelmingly, it would be interesting to investigatte a design containing fully missing days with the remaining days missing on some values would perform.
-This investigation may be particularly useful to researchers who wish to implement an accelerated longitudinal design but also have measures that are costly or burdensome which they would like to limit the collection of.
-\par
-
-To conclude we discuss the limitations of this analysis. DIFFERENT LIMITATIONS. NOT COMPUTING POWER.
-
-Hopefully, the results of this paper will serve to help researchers decide which PM design is most appropriate for their studies' needs.
-By illuminating the weaknesses of the Wave Missingness design, it is hoped that, unless it is explicitly required, researchers will opt instead to use a Split Form design.
-Furthermore, when researchers do implement a PM design we hope they follow our recommendation to err on the side of caution and keep the amount of missing data relatively low.
-\par
-
-%\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-\bibliographystyle{plainnat}
-\bibliography{citations}   % name your BibTeX data base
-
 \end{document}

### 2018-05-22 Documentation/manuscript.Rnw
Manuscript edits.

--- 2018-05-17 Documentation/manuscript.Rnw
@@
+% Predefine some figures
+
+<<echo = FALSE>>=
+# Creating dataframe to visualize - one subject's questions for 5 days
+split.form <- function(set, nrem = 2, bound = 0){
+
+set[set$Day >= bound, paste0("Q",1:8)] <- t(apply(set[set$Day >= bound,paste0("Q",1:8)], 1, function(x){
+    ind <- sample(1:8, nrem)
+    x[ind] <- NA
+    as.numeric(x)
+  }))
+
+  return(set)
+}
+@
+
+<<echo = FALSE>>=
+wave.des <- function(set, nmiss, ...) { # nmiss is the number of days each person would miss? 11?? Like, miss a fourth of the days?
+  id <- sample(2:45, size=nmiss)
+  for (i in 1:nmiss) {
+    set[set$Day %in% id[i], c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')] <- NA
+  }
+  return(set)
+}
+@
+
+<<warning=FALSE, echo = FALSE>>=
+cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
+fill <- matrix(1, 45, 8)
+dat <- data.frame(fill)
+colnames(dat) <- cols
+dat$Day <- seq.int(nrow(dat))
+set.seed(1234)
+split.dat <- split.form(dat)[1:8]
+#split.dat
+@
+
+<<warning=FALSE,message=FALSE,echo=FALSE>>=
+library(ggplot2)
+library(dplyr)
+library(reshape2)
+datmelt <- split.dat[1:8] %>% is.na %>% melt
+colnames(datmelt) <- c("Day","Question","Missing")
+#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
+datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
+
+  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
+@
+
+<<warning=FALSE,echo=FALSE>>=
+cols <- c("Missing" = "red", "Observed" = "skyblue3")
+splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
+
+#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
+@
+
+<<warning=FALSE,echo=FALSE>>=
+cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
+fill <- matrix(1, 45, 8)
+dat <- data.frame(fill)
+colnames(dat) <- cols
+dat$Day <- seq.int(nrow(dat))
+set.seed(1234)
+alternate.split.dat <- split.form(dat, bound = 3)[1:8]
+#alternate.split.dat
+@
+
+<<warning=FALSE,message=FALSE,echo=FALSE>>=
+library(ggplot2)
+library(dplyr)
+library(reshape2)
+datmelt <- alternate.split.dat[1:8] %>% is.na %>% melt
+colnames(datmelt) <- c("Day","Question","Missing")
+#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
+datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
+
+  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
+@
+
+<<warning=FALSE,echo=FALSE>>=
+cols <- c("Missing" = "red", "Observed" = "skyblue3")
+alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
+
+#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
+@
+
+<<echo=FALSE>>=
+set.seed(1234)
+wave.dat <- wave.des(dat,11)
+#wave.dat
+@
+
+<<echo=FALSE>>=
+library(ggplot2)
+library(dplyr)
+library(reshape2)
+datmelt <- wave.dat[1:8] %>% is.na %>% melt
+colnames(datmelt) <- c("Day","Question","Missing")
+#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
+datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
+
+  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
+@
+
+<<echo=FALSE>>=
+cols <- c("Missing" = "red", "Observed" = "skyblue3")
+waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
+@
+
 \RequirePackage{fix-cm}
@@
 \usepackage{natbib}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage[table]{xcolor}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+% \usepackage{threeparttable}
+% \usepackage{threeparttablex}
+% \usepackage[normalem]{ulem}
+% \usepackage{makecell}
+
+\raggedbottom
 
@@
 \begin{document}
-\SweaveOpts{concordance=TRUE}
+%\SweaveOpts{concordance=TRUE}
+
+<<primary, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
+library(kableExtra)
+library(dplyr)
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime0.RData")
+high <- d
+
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime0.RData")
+med <- d
+
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime0.RData")
+low <- d
+
+r <- rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])
+
+df <- data.frame(Design = rep(c("Split Form","Altered Split Form", "Wave Missingness"), each = 12), Missingness = rep(rep(c("Low","Medium", "High"), each = 4),3), Parameter = rep(c("$\\gamma_0$", "$\\beta_1$", "$\\beta_2$", "$\\beta_3$"),9), Bias = unlist(r["Bias"]), unlist(r["Pct Bias"]), MSE = unlist(r["MSE"]), Coverage = r["Coverage"], r["CI Length"], FMI = r["FMI"])
+
+df[,4:9] <- apply(df[,4:9], 2, round, digits = 3)
+
+names(df) <- c("Design", "Level", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
+row.names(df) <- NULL
+primary <- kable(df, escape = FALSE, format ="latex", caption = "Primary Results (N = 60)") %>%
+  collapse_rows(columns = 1:2, latex_hline = "full") %>%
+  kable_styling(latex_options = c("scale_down","hold_position"))
+@
+
+<<sampsize, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
+library(kableExtra)
+library(dplyr)
+load("~/GitHub/designedmissingness/Results/tables20180509_120_1_high_hightime0.RData")
+high <- d
+
+load("~/GitHub/designedmissingness/Results/tables20180509_120_1_med_hightime0.RData")
+med <- d
+
+load("~/GitHub/designedmissingness/Results/tables20180509_120_1_low_hightime0.RData")
+low <- d
+
+r <- rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])
+
+df <- data.frame(Design = rep(c("Split Form","Altered Split Form", "Wave Missingness"), each = 12), Missingness = rep(rep(c("Low","Medium", "High"), each = 4),3), Parameter = rep(c("$\\gamma_0$", "$\\beta_1$", "$\\beta_2$", "$\\beta_3$"),9), Bias = unlist(r["Bias"]), unlist(r["Pct Bias"]), MSE = unlist(r["MSE"]), Coverage = r["Coverage"], r["CI Length"], FMI = r["FMI"])
+
+df[,4:9] <- apply(df[,4:9], 2, round, digits = 3)
+
+names(df) <- c("Design", "Level", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
+row.names(df) <- NULL
+sampsize <- kable(df, escape = FALSE, format ="latex", caption = "Increased Sample Size Results (N = 120)") %>%
+  collapse_rows(columns = 1:2, latex_hline = "full") %>%
+  kable_styling(latex_options = c("scale_down","hold_position"))
+@
+
+<<hightime, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
+library(kableExtra)
+library(dplyr)
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime1.RData")
+high <- d
+
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime1.RData")
+med <- d
+
+load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime1.RData")
+low <- d
+
+r <- rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])
+
+df <- data.frame(Design = rep(c("Split Form","Altered Split Form", "Wave Missingness"), each = 12), Missingness = rep(rep(c("Low","Medium", "High"), each = 4),3), Parameter = rep(c("$\\gamma_0$", "$\\beta_1$", "$\\beta_2$", "$\\beta_3$"),9), Bias = unlist(r["Bias"]), unlist(r["Pct Bias"]), MSE = unlist(r["MSE"]), Coverage = r["Coverage"], r["CI Length"], FMI = r["FMI"])
+
+df[,4:9] <- apply(df[,4:9], 2, round, digits = 3)
+
+names(df) <- c("Design", "Level", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
+row.names(df) <- NULL
+hightime <- kable(df, escape = FALSE, format ="latex", caption = "High Time Results (N = 60)") %>%
+  collapse_rows(columns = 1:2, latex_hline = "full") %>%
+  kable_styling(latex_options = c("scale_down","hold_position"))
+@
+
+<<lowcorr, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
+library(kableExtra)
+library(dplyr)
+load("~/GitHub/designedmissingness/Results/tables20180509_60_0.5_high_hightime0.RData")
+high <- d
+
+load("~/GitHub/designedmissingness/Results/tables20180509_60_0.5_med_hightime0.RData")
+med <- d
+
+load("~/GitHub/designedmissingness/Results/tables20180509_60_0.5_low_hightime0.RData")
+low <- d
+
+r <- rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])
+
+df <- data.frame(Design = rep(c("Split Form","Altered Split Form", "Wave Missingness"), each = 12), Missingness = rep(rep(c("Low","Medium", "High"), each = 4),3), Parameter = rep(c("$\\gamma_0$", "$\\beta_1$", "$\\beta_2$", "$\\beta_3$"),9), Bias = unlist(r["Bias"]), unlist(r["Pct Bias"]), MSE = unlist(r["MSE"]), Coverage = r["Coverage"], r["CI Length"], FMI = r["FMI"])
+
+df[,4:9] <- apply(df[,4:9], 2, round, digits = 3)
+
+names(df) <- c("Design", "Level", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
+row.names(df) <- NULL
+lowcorr <- kable(df, escape = FALSE, format ="latex", caption = "Low Inter-Survey Correlation Results (N = 60)") %>%
+  collapse_rows(columns = 1:2, latex_hline = "full") %>%
+  kable_styling(latex_options = c("scale_down","hold_position"))
+@
 
@@
 Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions.
-A common form setup is the three-form design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C.
+How these subsets are chosen varies.
+A common form setup is three-form Block Design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C.
 Each form of the survey includes the X block as well as two of the remaining blocks.
-This leaves the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded.
-Note that every block appears in at least one form.
-By designing the forms in this manner we are able to estimate the relationship between any chosen items regardless of their blocks.
-That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows this.
-\par
-
-We need to talk about the other type of split design that we used here which was that X of the 8 questions are randomly omitted on each day.
-
-% \begin{table}[h!]
-% 	\centering
-% 	\caption{The Three Form PM Design}
-% 	\label{tab:table10}
-% 	\setlength{\tabcolsep}{1cm}
-% 	\begin{tabular}{c|cccc}
-% 		\toprule
-% 		& \multicolumn{4}{c}{Block} \\
-% 		Form & X & A & B & C \\
-% 		\midrule
-% 		1 & 1 & 1 & 1 & 0 \\
-% 		2 & 1 & 1 & 0 & 1 \\
-% 		3 & 1 & 0 & 1 & 1 \\
-% 		\bottomrule
-% 	\end{tabular}
-% \end{table}
-
-<<echo = FALSE>>=
-# Creating dataframe to visualize - one subject's questions for 5 days
-split.form <- function(set, nrem = 2, bound = 0){
-
-set[set$Day >= bound, paste0("Q",1:8)] <- t(apply(set[set$Day >= bound,paste0("Q",1:8)], 1, function(x){
-    ind <- sample(1:8, nrem)
-    x[ind] <- NA
-    as.numeric(x)
-  }))
-
-  return(set)
-}
-@
-
-<<echo = FALSE>>=
-wave.des <- function(set, nmiss, ...) { # nmiss is the number of days each person would miss? 11?? Like, miss a fourth of the days?
-  id <- sample(2:45, size=nmiss)
-  for (i in 1:nmiss) {
-    set[set$Day %in% id[i], c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')] <- NA
-  }
-  return(set)
-}
-@
-
-<<warning=FALSE, echo = FALSE>>=
-cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
-fill <- matrix(1, 45, 8)
-dat <- data.frame(fill)
-colnames(dat) <- cols
-dat$Day <- seq.int(nrow(dat))
-set.seed(1234)
-split.dat <- split.form(dat)[1:8]
-#split.dat
-@
-
-<<warning=FALSE,message=FALSE,echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- split.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-
-#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
-fill <- matrix(1, 45, 8)
-dat <- data.frame(fill)
-colnames(dat) <- cols
-dat$Day <- seq.int(nrow(dat))
-set.seed(1234)
-alternate.split.dat <- split.form(dat, bound = 3)[1:8]
-#alternate.split.dat
-@
-
-<<warning=FALSE,message=FALSE,echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- alternate.split.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-
-#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
-@
-
-<<echo=FALSE>>=
-set.seed(1234)
-wave.dat <- wave.des(dat,11)
-#wave.dat
-@
-
-<<echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- wave.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-@
-
-<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE>>=
-require(gridExtra)
-grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
-@
-
-Figure \ref{fig:misslow} is
-
-An important consideration when designing a Split Form survey is question distribution.
-The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
+A participant is then given a different form each day of the study.
+Designing the forms in this manner allows researchers to estimate the relationship between any chosen items, regardless of their blocks.
+For example, this allows the relationship between an item in block A and another in block C to be estimated and examined.
+\par
+
+An important consideration here is question distribution. The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
 Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}.
@@
 Similarly, it is good practice to place variables which are predictive of each other in separate blocks \citep{gottschall2012comparison}.
-Note that when groupings are not as obvious, as in the previous example, pilot studies can help determine the predictive potential of variables.
-We may also wish to consider the cost and burden associated with an item when deciding which block to place it in.
+While this approach provides researchers more freedom when forming the surveys, the puzzle of question distribution introduces new concerns.
+When the question groupings are not obvious, pilot studies may be necessary to determine the predictive potential of and relationships between variables.
+The cost and burden associated with an item must also be considered when deciding which block to place it in.
 For example, if a critical item is overly expensive or difficult to obtain we may be better off excluding it from the X-block \citep{little2013planned}.
@@
 
-In additon, the number of blocks must be determined.
+In addition, the number of blocks must be determined.
 Including more blocks in the design allows further increased missingness \citep{graham2006planned}.
-For example, consider two groups of researchers.
-The first group divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey, and the second uses an X-block and nine others with 10\% of the items each.
-The researchers decide that a pair of blocks will be asked together in at least one of the forms to ensure efficient estimations.
-Based on this requirement, the first group can only reduce the length of their survey by 25\% while the second group can decrease the length of their survey by up to 70\%.
-\par
-
 While increasing missingness may allow for further reductions in burden and cost, researchers must consider the disadvantages of more blocks.
-Inevitably, greater missingness leads to less efficient estimation \citep{rhemtulla2016asymptotic} but there is the added complication as more blocks introduce additional forms.
-If the second group of researchers in the example, for instance, decide that each form would contain the X-block and two of the other blocks, then they would be left with 36 total forms.
-For traditional paper surveys, this can make administering the survey difficult.
-However, for electronic questionaires, where form randomization can be automated, this is not an issue.
-Often, researchers using electronic surveys will give each participant a random sample of all survey items, in a way treating each item as its own block \citep{silvia2014planned}.
-Using this method, researchers reap the benefits of increased forms without the difficulty caused by manually building and administering these forms.
+As more blocks are added, the number of possible forms increases.
+For example, consider two research teams.
+The first team divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey.
+The second uses an X-block and nine others with 10\% of the items each.
+If the teams decide that each form will contain the X-block and two of the other blocks, then the second team will have 36 \textbf{(28?
+8 choose 2?)} total forms while the first team can proceed with 3.
+\textbf{This is all assuming that the blocks represent the optimal question grouping.
+If this is not known, to account for possible relationships and correlation between questions, the teams would need to consider all possible blocks and create forms for every block configuration.
+For a 7 question survey, with any one question X block and the other 6 split into three blocks, there are 75 possible block configurations.
+For each configuration, there are 3 possible forms.
+So, a team would need to consider 225 different forms.
+Instead of creating 225 distinct forms, a research team can follow a alternative Split Form method.} \par
+
+\textbf{This method, hereafter referred to as Split Form planned missingness and illustrated in \ref{fig:formillustration}, involves meaningfully selecting an X block of $n$ questions and then randomly excluding $k$ questions on each day.
+In a way treating each item as its own block \citep{silvia2014planned}.
+This is simple in theory, but for traditional paper surveys this is very difficult to execute.
+Fortunately, recent technological advances have made the use of electronic questionaires more readily accessible.
+In this environment form randomization can be automated and the creation of numerous unique forms is no longer an issue.} Using this method, researchers reap the benefits of including all possible variable relationships through increased forms without the difficulty caused by manually building these forms.
 \par
@@
 Unlike the Split Form design, where participants miss a subset of items in a single measurement occasion, the Wave Design entails randomizing participants to miss a measurement occasion entirely.
-An example of a Wave Missing design is shown in Table \ref{tab:table11} where data is collected monthly over the course of 5 months.
+An example of a Wave Missing design is shown in Figure \ref{fig:formillustration} where data is collected monthly over the course of 5 months.
 However, each participant is only measured at three of these occasions.
 \par
-
-\begin{table}[b!]
-	\centering
-	\caption{The Wave Missingness PM Design}
-	\label{tab:table11}
-	\setlength{\tabcolsep}{0.75cm}
-	\begin{tabular}{c|ccccc}
-		\toprule
-		& \multicolumn{5}{c}{Month} \\
-		Participant & 1 & 2 & 3 & 4 & 5 \\
-		\midrule
-		1 & 1 & 0 & 1 & 0 & 1 \\
-		2 & 1 & 1 & 0 & 1 & 0 \\
-		3 & 0 & 0 & 1 & 1 & 1 \\
-		4 & 1 & 1 & 1 & 0 & 0 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
 
@@
 By continuing in this manner the data that was collected over a four year period is extended it to cover six years, accelerating the study.
-The setup of this type of study is demonstrated in Table \ref{tab:table12}, where "1" and "0" respectively indicate an included and excluded wave.
-\par
-
-\begin{table}[t!]
+The setup of this type of study is demonstrated in Table \ref{tab:cohort}, where "1" and "0" respectively indicate an included and excluded wave.
+\par
+
+\begin{table}[H]
 	\centering
 	\caption{Cohort Sequential Design}
-	\label{tab:table12}
+	\label{tab:cohort}
 	\setlength{\tabcolsep}{0.5cm}
@@
 
-Developmental time-lag models \citep{mcardle1997expanding} also make use of the Wave Missingness structure.
-As shown in Table \ref{tab:table13}, researchers observe participants at only two measurement occasions, varying the length between occasions for each participant, and then treat this two-time-point data as multi-time-point data with missing values.
+Developmental time-lag models \citep{mcardle1997expanding} use the Wave Missingness structure, as well.
+As shown in Table \ref{tab:devtimelag}, researchers observe participants at only two measurement occasions, varying the length between occasions for each participant, and then treat this two-time-point data as multi-time-point data with missing values.
 Under this framework they impute these missing values and estimate growth curve models.
@@
 
-\begin{table}[b!]
+\begin{table}[H]
 	\centering
 	\caption{Developmental Time-Lag Setup}
-	\label{tab:table13}
+	\label{tab:devtimelag}
 	\setlength{\tabcolsep}{0.75cm}
@@
 
+\subsection{Altered Split Form}
+
+The Split Form planned missingness method can be modified to include the benefits of complete cases seen in Wave Missingness in what may be called Altered Split Form.
+In this method, the researcher asks participants all questions on the first $n$ days of the study.
+Thereafter, the survey design reverts to regular Split Form.
+This method allows the researcher to collect $n$ complete cases from each participant, aiding in the imputation process after surveys are administered.
+Altered Split Form, and the other planned missingness methods, is illustrated in Figure \ref{fig:formillustration} below.
+
+<<formillustration, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig.keep = TRUE, fig.pos = "H">>=
+require(gridExtra)
+grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
+@
+
 \subsection{Multiple Imputation}
@@
 
-From here we can compute the sample variance of this estimate by calculating the between-imputation component, $B_M = \sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2 / (M-1)$, and the within-imputation component, $W_M = \sum_{n=1}^{M} S_n^2 / M$.
+From here we can compute the sample variance of this estimate by calculating the between-imputation component, $B_M = \frac{1}{(M-1)}\sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2$, and the within-imputation component, $W_M = \frac{1}{(M)}\sum_{n=1}^{M} S_n^2$.
 These components are combined to obtain the overall sample variance of our MI estimate as follows:
@@
 \begin{equation}
-T_M = W_M + (1+1/M)*B_M.
+T_M = W_M + \frac{M+1}{(M)}B_M.
 \end{equation}
@@
 The analysis included eight particular questions: two binary questions on housing insecurity, four binary questions on food insecurity, and two questions concerning alcohol use (one binary variable and one count variable).
-The exact questions can be found in Table \ref{tab:table1}.
-\par
-
-\begin{table}[t]
+The exact questions can be found in Table \ref{tab:survey_qs}.
+\par
+
+\begin{table}[H]
 	\centering
 	\caption{Survey Questions}
-	\label{tab:table1}
+	\label{tab:survey_qs}
 	\begin{tabular}{cp{6.5cm}c}
@@
 The first step in the process of creating the simulated datasets was to obtain parameter estimates from \citet{pellowski2016alcohol} and to quantify the relationships between variables.
-These estimated relationships were treated as the "true" relationships and one thousand samples were drawn using these parameters.
+These estimated relationships were treated as the "true" relationships and \textbf{one thousand (number or no???)} samples were drawn using these parameters.
 The purpose of simulating these datasets was to see how well they captured the true relationship between daily medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score).
-Specifically, our model of interest is the random intercept model with time effect found below: \\
-
+Specifically, \\
+
+Let $Y_{ij} \sim binomial(n_{ij},p_{ij})$ be whether the $j$th person missed their medication dose on the $i$th day.
+Then the model of interest is the random intercept model with time effect described as follows:
 \begin{align*}
-logit(MissedDose) &= \beta_{0j} + \beta_1*DrinkYN + \beta_2*ZAlcTox +\beta_3*Day \\
-Level 2: \beta_{0j} &= \gamma_0 + \epsilon_j
+logit(p_{ij}) &= \beta_{0j} + \beta_1DrinkYN_i + \beta_2ZAlcTox_i +\beta_3Day
 \end{align*}
-where, \\ \\
-$MissedDose = 1$ if the participant did not adhere to the ART, 0 otherwise. \\
-$DrinkYN = 1$ if the participant drank on a given day, 0 otherwise.\\
-$ZAlcTox =$ Z-transformed score on an alcohol-antiretroviral interactive toxicity scale developed by Kalichman \cite{kalichman2009prevalence}. \\
-$Day =$ The number of days since the study began, 0-44. \\
+where $\beta_{0j} = \gamma_0 + \alpha_j$ and $\alpha_j \sim \mathcal{N}(0,\sigma_\alpha^2)$. \\ \\ 
+Additionally, note: \\ \\
+$p_{ij} = 1$ when participant $p$ did not adhere to the ART on day $i$, 0 otherwise. \\
+$DrinkYN = 1$ if participant $p$  drank on day $i$, 0 otherwise.\\
+$ZAlcTox =$ participant $p$'s Z-transformed score on an alcohol-antiretroviral interactive toxicity scale developed by Kalichman \cite{kalichman2009prevalence}. \\
+$Day =$ Day $i$ of the study, 0-44. \\
 $j =$ participant index, 1-60. \\
-$\epsilon_j  \sim N(0, \sigma^2)$. \\ \\
-
-Based on the observed data, the true values of the parameters, $\gamma_0, \beta_1, \beta_2$, $\beta_3$, and $\sigma^2$ were found to be -2.3, 0.56, 1.28, 0.2, and 1.0 respectively. \par
+
+Based on the observed data, the true values of the parameters, $\gamma_0$, $\beta_1$, $\beta_2$, $\beta_3$, and $\sigma_\alpha^2$ were found to be -2.29, 0.28, 0.64, 0.01, and \textbf{1.0???} respectively.
+\par
 Once the samples were drawn, they were transformed under the three different missingness structures.
 These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed.
-To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Table \ref{tab:table14}.
+To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in \textbf{Table \ref{tab:table14} (do we want the illustration here instead?
+or in both places?)}.
 As in the previous tables, "1" indicates an observed occasion while "0" indicates a missing one.
@@
 
-\begin{table}[t!]
+\begin{table}[H]
 	\centering
@@
 
-Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 25\%, 50\%, and 75\% missing data.
-Previous work by \citet{rhemtulla2014planned} found that for low levels of missingness (25\%) the Three-Form design outperforms the Wave Missingness design in capturing latent growth curve model parameters.
+Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions.
+Previous work by \citet{rhemtulla2014planned} found that for low levels of missingness Split Form design outperforms the Wave Missingness design in capturing latent growth curve model parameters.
 However, because only low-levels of missingness are tested it is unknown whether this relationship holds at moderate or high levels.
-We hope that by including these different levels of missingness we will be able to see how these designs perform at all levels of the missingness spectrum.
+By including these different levels of missingness the performance at all levels of the missingness spectrum will be measured.
 \par
 Once missingness was created, Multiple Imputation techniques were applied to estimate the relationship between medication adherence and the other variables in our model.
-Because we have control over the missing data mechanism, we know the data is MCAR.
+Because the missing data mechanism is controled, the data is known to be MCAR.
 This fact allows for the principled use of MI techniques.
-Using the R package $\{$mice$\}$ \citep{mice2011imputation} our binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching.
-\par
-
-After imputating, a logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}.
+Using the R package $\{$mice$\}$ \citep{mice2011imputation} the binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching \textbf{was it???
+i don't think so, it was in the X block originally but double check!}.
+\par
+
+After imputing, a logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}.
 From here, the results from each PM design were evaluated based on bias, percent bias, mean squared error (MSE), coverage, confidence interval (CI) length, and the fraction of missing information (FMI).
@@
 If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal.
-\par
+To investigate this, the correlation of the variables was scaled by 0.5.\par
 \subsubsection{High Time Effect}
 In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable.
-To do this we changed the value of the parameters $\gamma_0, \beta_1, \beta_2,$ and $\beta_3$ to -4.6, 0.28, 0.64, and 0.2 respectively.
+To do this we changed the value of the parameters $\gamma_0$, $\beta_1$, $\beta_2$, and $\beta_3$ to -4.56, 0.14, 0.32, and 0.01 respectively.
 Note that instead of increasing the value of $\beta_3$, the slope for time effect, all the other parameters were decreased.
@@
 \label{sec:3.1}
-The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$.
+The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.28$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.01$.
 The effects of the variables here are comparable to those found in the original dataset.
 This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design.
-Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:table2}.
+Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:prelim} \textbf{not here yet}.
 Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
 
-<<echo=FALSE>>=
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high.RData")
-high <- d
-
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med.RData")
-med <- d
-
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low.RData")
-low <- d
-
-library(xtable)
-print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),type="latex", comment = FALSE)
-
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime1.RData")
-high <- d
-
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime1.RData")
-med <- d
-
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime1.RData")
-low <- d
-
-library(xtable)
-print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
-
-@
-
-% latex table generated in R 3.5.0 by xtable 1.8-2 package
-% Mon May 14 21:02:34 2018
-\begin{table}[ht]
-\centering
-\begin{tabular}{lllrrrr}
-  \hline
-Design & \% Missingness  & Parameter & Coverage & Bias & MSE & FMI \\ 
-  \hline
- &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
-   &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
-   &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
-   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
-   \hline
-   &  &  & 0.986 & 0.040 & 0.019 & 0.012 \\ 
-   &  &  & 0.993 & -0.168 & 0.750 & 0.557 \\ 
-   &  &  & 0.932 & 0.008 & 0.024 & 0.002 \\ 
-   &  &  & 0.940 & -0.000 & 0.000 & 0.008 \\ 
-   \hline
-   &  &  & 0.984 & 0.036 & 0.027 & 0.030 \\ 
-   &  &  & 0.991 & -0.713 & 9.933 & 0.625 \\ 
-   &  &  & 0.932 & 0.009 & 0.027 & 0.005 \\ 
-   &  &  & 0.939 & -0.000 & 0.000 & 0.021 \\ 
-   \hline
-   &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
-   &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
-   &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
-   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
-   \hline
-   &  &  & 0.988 & 0.040 & 0.018 & 0.010 \\ 
-   &  &  & 0.994 & -0.167 & 0.782 & 0.549 \\ 
-   &  &  & 0.931 & 0.009 & 0.024 & 0.002 \\ 
-   &  &  & 0.944 & -0.000 & 0.000 & 0.006 \\ 
-   \hline
-   &  &  & 0.983 & 0.036 & 0.022 & 0.027 \\ 
-   &  &  & 0.990 & -0.686 & 10.509 & 0.665 \\ 
-   &  &  & 0.928 & 0.009 & 0.026 & 0.007 \\ 
-   &  &  & 0.946 & -0.000 & 0.000 & 0.023 \\ 
-   \hline
-   &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
-   &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
-   &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
-   &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
-   \hline
-   &  &  & 0.991 & 0.029 & 0.018 & 0.055 \\ 
-   &  &  & 0.988 & -0.112 & 0.345 & 0.752 \\ 
-   &  &  & 0.934 & 0.009 & 0.024 & 0.007 \\ 
-   &  &  & 0.951 & -0.000 & 0.000 & 0.032 \\ 
-   \hline
-   &  &  & 0.994 & -0.003 & 0.022 & 0.258 \\ 
-   &  &  & 0.988 & -0.105 & 0.284 & 0.903 \\ 
-   &  &  & 0.937 & 0.011 & 0.025 & 0.039 \\ 
-   &  &  & 0.960 & -0.000 & 0.000 & 0.175 \\ 
-   \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[b!]
-	\centering
-	\caption{Results of Analysis before imposing Missingness in each Scenario}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table2}
-	\begin{tabular}{cc|ccccc}
-		\toprule
-		Scenario & Parameter & Bias & Percent Bias & MSE & Coverage & CI Length \\
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Primary \\ Analysis (N=60)}} 
-		& $\gamma_0$ & 0.151 & 6.55\% & 0.037 & 99.0\% & 0.750 \\
-		& $\beta_1$ & 0.133 & 23.75\% & 0.028 & 95.5\% & 0.652 \\
-		& $\beta_2$ & 0.120 & 9.40\% & 0.022 & 97.5\% & 0.610 \\
-		& $\beta_3$ & 0.007 & 3.42\% & 7.11$*10^-5$ & 97.0\% & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Increased \\ Sample (N=120)}} 
-		& $\gamma_0$ & 0.106 & 4.61\% & 0.018 & 98.0\% & 0.528 \\
-		& $\beta_1$ & 0.099 & 17.63\% & 0.016 & 93.0\% & 0.460 \\
-		& $\beta_2$ & 0.091 & 7.12\% & 0.013 & 95.5\% & 0.429 \\
-		& $\beta_3$ & 0.005 & 2.34\% & 3.52$*10^-5$ & 96.5\% & 0.024 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Low \\Inter-Survey Correlation (N=60)}} 
-		& $\gamma_0$ & 0.145 & 6.29\% & 0.033 & 99.0\% & 0.747 \\
-		& $\beta_1$ & 0.130 & 23.27\% & 0.027 & 94.5\% & 0.651 \\
-		& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 94.0\% & 0.611 \\
-		& $\beta_3$ & 0.007 & 3.69\% & 8.88$*10^-5$ & 93.0\% & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{High \\Time Effect (N=60)}}
-		& $\gamma_0$ & 0.170 & 3.69\% & 0.045 & 98.5\% & 0.888 \\
-		& $\beta_1$ & 0.123 & 43.86\% & 0.024 & 96.0\% & 0.598 \\
-		& $\beta_2$ & 0.124 & 19.35\% & 0.025 & 93.5\% & 0.575 \\
-		& $\beta_3$ & 0.006 & 2.95\% & 5.50$*10^-5$ & 95.5\% & 0.030 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
+#prelim
+@
 
@@
 This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}.
-Nevertheless, we should keep this in mind when analyzing our results from the PM designs provided in Table \ref{tab:table3}.
-In Table \ref{tab:table3} as in Tables \ref{tab:table4}, \ref{tab:table5}, and \ref{tab:table6} bold values indicate "Unacceptable" results.
-That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
-
-\begin{table}[p]
-	\centering
-	\caption{Primary Simulation Results (N=60)}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table3}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.151 & 6.59\% & 0.037 & 99.5\% & 0.753 & 0.009 \\
-		&& $\beta_1$ & 0.139 & 24.78\% & 0.029 & 96.0\% & 0.693 & 0.112 \\
-		&& $\beta_2$ & 0.120 & 9.41\% & 0.022 & 97.0\% & 0.610 & 0.002 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.12$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.153 & 6.67\% & 0.037 & 99.0\% & 0.765 & 0.040 \\
-		&& $\beta_1$ & 0.162 & 28.93\% & 0.041 & 95.5\% & 0.869 & 0.390 \\
-		&& $\beta_2$ & 0.121 & 9.51\% & 0.022 & 97.0\% & 0.616 & 0.007 \\
-		&& $\beta_3$ & 0.007 & 3.40\% & 6.99$*10^-5$ & 98.5\% & 0.034 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.154 & 6.70\% & 0.039 & 98.5\% & 0.818 & 0.147 \\
-		&& $\beta_1$ & \textbf{0.225} & \textbf{40.16}\% & \textbf{0.076} & 97.5\% & 1.464 & 0.710 \\
-		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 97.5\% & 0.611 & 0.022 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.02$*10^-5$ & 98.0\% & 0.035 & 0.032 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.151 & 6.57\% & 0.037 & 98.0\% & 0.753 & 0.008 \\
-		&& $\beta_1$ & 0.137 & 24.55\% & 0.030 & 96.0\% & 0.690 & 0.105 \\
-		&& $\beta_2$ & 0.120 & 9.39\% & 0.022 & 97.5\% & 0.611 & 0.002 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.153 & 6.67\% & 0.038 & 99.5\% & 0.760 & 0.030 \\
-		&& $\beta_1$ & 0.151 & 26.93\% & 0.036 & 96.0\% & 0.811 & 0.324 \\
-		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 96.0\% & 0.611 & 0.006 \\
-		&& $\beta_3$ & 0.007 & 3.44\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.164 & 7.13\% & 0.042 & 98.0\% & 0.799 & 0.105 \\
-		&& $\beta_1$ & \textbf{0.225} & \textbf{40.14\%} & \textbf{0.080} & 96.0\% & 1.265 & 0.640 \\
-		&& $\beta_2$ & 0.117 & 9.13\% & 0.021 & 97.5\% & 0.615 & 0.019 \\
-		&& $\beta_3$ & 0.007 & 3.46\% & 7.07$*10^-5$ & 98.0\% & 0.034 & 0.023 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.152 & 6.61\% & 0.037 & 99.5\% & 0.757 & 0.023 \\
-		&& $\beta_1$ & 0.147 & 26.25\% & 0.033 & 96.0\% & 0.767 & 0.270 \\
-		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 96.0\% & 0.610 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.41\% & 6.97$*10^-5$ & 98.0\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.157 & 6.84\% & 0.039 & 100.0\% & 0.767 & 0.052 \\
-		&& $\beta_1$ & \textbf{0.190} & \textbf{33.95\%} & \textbf{0.058} & 94.5\% & 0.934 & 0.465 \\
-		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 97.5\% & 0.609 & 0.008 \\
-		&& $\beta_3$ & 0.007 & 3.34\% & 6.80$*10^-5$ & 98.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.168 & 7.30\% & 0.045 & 99.5\% & 0.807 & 0.129 \\
-		&& $\beta_1$ & \textbf{0.290} & \textbf{51.77\%} & \textbf{0.132} & \textbf{88.5\%} & 1.335 & 0.680 \\
-		&& $\beta_2$ & 0.119 & 9.32\% & 0.022 & 96.0\% & 0.614 & 0.017 \\
-		&& $\beta_3$ & 0.007 & 3.40\% & 6.96$*10^-5$ & 98.5\% & 0.034 & 0.025 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{Increased Sample Size simulation Results (N=120)}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table4}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.106 & 4.60\% & 0.017 & 98.5\% & 0.533 & 0.022 \\
-		&& $\beta_1$ & 0.106 & 18.96\% & 0.018 & 96.0\% & 0.548 & 0.263 \\
-		&& $\beta_2$ & 0.091 & 7.14\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.33\% & 3.47$*10^-5$ & 96.5\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.112 & 4.85\% & 0.019 & 98.0\% & 0.542 & 0.057 \\
-		&& $\beta_1$ & 0.134 & 23.86\% & \textbf{0.027} & 95.0\% & 0.696 & 0.489 \\
-		&& $\beta_2$ & 0.092 & 7.15\% & 0.013 & 96.5\% & 0.430 & 0.009 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.110 & 4.80\% & 0.019 & 99.5\% & 0.575 & 0.153 \\
-		&& $\beta_1$ & \textbf{0.194} & \textbf{34.59\%} & \textbf{0.057} & 94.5\% & 1.088 & 0.742 \\
-		&& $\beta_2$ & 0.092 & 7.20\% & 0.013 & 95.0\% & 0.432 & 0.021 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.42$*10^-5$ & 97.5\% & 0.024 & 0.026 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.107 & 4.64\% & 0.017 & 98.0\% & 0.533 & 0.022 \\
-		&& $\beta_1$ & 0.111 & 19.80\% & 0.020 & 94.5\% & 0.545 & 0.263 \\
-		&& $\beta_2$ & 0.091 & 7.08\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.115 & 4.99\% & 0.020 & 98.0\% & 0.542 & 0.056 \\
-		&& $\beta_1$ & 0.138 & 24.65\% & \textbf{0.028} & 94.5\% & 0.693 & 0.494 \\
-		&& $\beta_2$ & 0.091 & 7.24\% & 0.013 & 96.0\% & 0.430 & 0.008 \\
-		&& $\beta_3$ & 0.005 & 2.34\% & 3.54$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.115 & 5.01\% & 0.020 & 99.0\% & 0.563 & 0.119 \\
-		&& $\beta_1$ & \textbf{0.188} & \textbf{33.65\%} & \textbf{0.058} & 91.5\% & 0.958 & 0.681 \\
-		&& $\beta_2$ & 0.092 & 7.16\% & 0.013 & 96.0\% & 0.432 & 0.018 \\
-		&& $\beta_3$ & 0.005 & 2.30\% & 3.44$*10^-5$ & 96.0\% & 0.024 & 0.020 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.108 & 4.72\% & 0.018 & 98.0\% & 0.533 & 0.024 \\
-		&& $\beta_1$ & 0.123 & 21.90\% & \textbf{0.024} & 92.0\% & 0.551 & 0.287 \\
-		&& $\beta_2$ & 0.092 & 7.18\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.35\% & 3.51$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.111 & 4.84\% & 0.019 & 99.0\% & 0.540 & 0.052 \\
-		&& $\beta_1$ & \textbf{0.168} & \textbf{30.02\%} & \textbf{0.043} & \textbf{85.5\%} & 0.671 & 0.489 \\
-		&& $\beta_2$ & 0.092 & 7.22\% & 0.013 & 95.0\% & 0.429 & 0.007 \\
-		&& $\beta_3$ & 0.005 & 2.32\% & 3.42$*10^-5$ & 97.0\% & 0.024 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.123 & 5.33\% & 0.023 & 99.0\% & 0.558 & 0.108 \\
-		&& $\beta_1$ & \textbf{0.248} & \textbf{44.26\%} & \textbf{0.099} & \textbf{82.0\%} & 0.894 & 0.666 \\
-		&& $\beta_2$ & 0.094 & 7.36\% & 0.014 & 96.0\% & 0.430 & 0.013 \\
-		&& $\beta_3$ & 0.005 & 2.36\% & 3.53$*10^-5$ & 96.0\% & 0.024 & 0.015 \\
-		\bottomrule
-	\end{tabular}	
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{Low Inter-Survey Correlation Simulation Results (N=60)}
-	\label{tab:table5}
-	\setlength{\tabcolsep}{0.1cm}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.146 & 6.34\% & 0.033 & 99.0\% & 0.755 & 0.025 \\
-		&& $\beta_1$ & 0.150 & 26.82\% & 0.034 & 95.5\% & 0.782 & 0.278 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.612 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.64\% & 8.68$*10^-5$ & 92.5\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.148 & 6.43\% & 0.034 & 99.0\% & 0.772 & 0.067 \\
-		&& $\beta_1$ & \textbf{0.183} & \textbf{32.65\%} & \textbf{0.053} & 95.0\% & 1.032 & 0.526 \\
-		&& $\beta_2$ & 0.125 & 9.80\% & 0.026 & 94.0\% & 0.613 & 0.010 \\
-		&& $\beta_3$ & 0.007 & 3.63\% & 8.73$*10^-5$ & 92.5\% & 0.035 & 0.015 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.155 & 6.74\% & 0.036 & 99.5\% & 0.825 & 0.166 \\
-		&& $\beta_1$ & \textbf{0.276} & \textbf{49.31\%} & \textbf{0.116} & 95.0\% & 1.567 & 0.749 \\
-		&& $\beta_2$ & 0.124 & 9.71\% & 0.025 & 94.0\% & 0.618 & 0.025 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.73$*10^-5$ & 93.5\% & 0.035 & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.141 & 6.13\% & 0.031 & 99.0\% & 0.754 & 0.023 \\
-		&& $\beta_1$ & 0.139 & 25.80\% & 0.030 & 95.5\% & 0.772 & 0.260 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.612 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.55$*10^-5$ & 92.5\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.149 & 6.48\% & 0.035 & 99.5\% & 0.767 & 0.056 \\
-		&& $\beta_1$ & 0.170 & 30.44\% & \textbf{0.044} & 97.0\% & 0.968 & 0.486 \\
-		&& $\beta_2$ & 0.125 & 9.79\% & 0.025 & 93.5\% & 0.612 & 0.009 \\
-		&& $\beta_3$ & 0.007 & 3.64\% & 8.58$*10^-5$ & 92.5\% & 0.034 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.149 & 6.47\% & 0.036 & 98.5\% & 0.809 & 0.139 \\
-		&& $\beta_1$ & \textbf{0.228} & \textbf{40.70\%} & \textbf{0.088} & 96.0\% & 1.425 & 0.708 \\
-		&& $\beta_2$ & 0.125 & 9.74\% & 0.026 & 94.0\% & 0.617 & 0.021 \\
-		&& $\beta_3$ & 0.007 & 3.62\% & 8.65$*10^-5$ & 93.5\% & 0.035 & 0.027 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.138 & 6.02\% & 0.031 & 99.5\% & 0.754 & 0.025 \\
-		&& $\beta_1$ & 0.158 & 28.17\% & 0.036 & 96.5\% & 0.776 & 0.286 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.611 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.50$*10^-5$ & 92.5\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.148 & 6.43\% & 0.034 & 99.5\% & 0.765 & 0.053 \\
-		&& $\beta_1$ & \textbf{0.197} & \textbf{35.14\%} & \textbf{0.059} & 91.0\% & 0.939 & 0.472 \\
-		&& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 93.5\% & 0.611 & 0.007 \\
-		&& $\beta_3$ & 0.007 & 3.60\% & 8.48$*10^-5$ & 92.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.158 & 6.86\% & 0.040 & 98.5\% & 0.799 & 0.122 \\
-		&& $\beta_1$ & \textbf{0.303} & \textbf{54.18\%} &\textbf{0.148} & \textbf{89.5\%} & 1.290 & 0.676 \\
-		&& $\beta_2$ & 0.127 & 9.94\% & 0.027 & 95.5\% & 0.615 & 0.015 \\
-		&& $\beta_3$ & 0.007 & 3.62\% & 8.77$*10^-5$ & 93.5\% & 0.035 & 0.021 \\
-		\bottomrule
-	\end{tabular}	
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{High Time Effect Simulation Results (N=60)}
-	\label{tab:table6}
-	\setlength{\tabcolsep}{0.1cm}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.169 & 3.67\% & 0.045 & 99.0\% & 0.895 & 0.015 \\
-		&& $\beta_1$ & 0.133 & 47.54\% & 0.029 & 96.0\% & 0.708 & 0.262 \\
-		&& $\beta_2$ & 0.124 & 19.33\% & 0.025 & 93.5\% & 0.576 & 0.003 \\
-		&& $\beta_3$ & 0.006 & 2.96\% & 5.50$*10^-5$ & 94.5\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.174 & 3.77\% & 0.047 & 98.5\% & 0.912 & 0.050 \\
-		&& $\beta_1$ & \textbf{0.181} & \textbf{64.59\%} & \textbf{0.049} & 96.0\% & 0.981 & 0.554 \\
-		&& $\beta_2$ & 0.124 & 19.44\% & 0.025 & 94.0\% & 0.578 & 0.007 \\
-		&& $\beta_3$ & 0.006 & 2.97\% & 5.55$*10^-5$ & 96.0\% & 0.030 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.177 & 3.85\% & 0.049 & 98.0\% & 0.954 & 0.117 \\
-		&& $\beta_1$ & \textbf{0.243} & \textbf{86.63\%} & \textbf{0.097} & 93.0\% & 1.433 & 0.729 \\
-		&& $\beta_2$ & 0.124 & 19.37\% & 0.025 & 94.0\% & 0.581 & 0.016 \\
-		&& $\beta_3$ & 0.006 & 2.97\% & 5.70$*10^-5$ & 94.0\% & 0.030 & 0.025 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.171 & 3.72\% & 0.046 & 99.0\% & 0.895 & 0.015 \\
-		&& $\beta_1$ & 0.142 & 50.55\% & 0.033 & 94.5\% & 0.717 & 0.272 \\
-		&& $\beta_2$ & 0.124 & 19.36\% & 0.025 & 93.5\% & 0.577 & 0.002 \\
-		&& $\beta_3$ & 0.006 & 2.95\% & 5.48$*10^-5$ & 95.5\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.176 & 3.82\% & 0.048 & 99.0\% & 0.905 & 0.038 \\
-		&& $\beta_1$ & 0.168 & 60.10\% & \textbf{0.043} & 95.5\% & 0.903 & 0.486 \\
-		&& $\beta_2$ & 0.124 & 19.36\% & 0.025 & 93.5\% & 0.581 & 0.006 \\
-		&& $\beta_3$ & 0.006 & 2.95\% & 5.60$*10^-5$ & 95.0\% & 0.030 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.177 & 3.84\% & 0.051 & 99.5\% & 0.947 & 0.108 \\
-		&& $\beta_1$ & \textbf{0.257} & \textbf{91.96\%} & \textbf{0.097} & 94.5\% & 1.381 & 0.714 \\
-		&& $\beta_2$ & 0.124 & 19.34\% & 0.025 & 94.5\% & 0.581 & 0.014 \\
-		&& $\beta_3$ & 0.006 & 3.01\% & 5.76$*10^-5$ & 95.0\% & 0.030 & 0.023 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.170 & 3.70\% & 0.046 & 99.0\% & 0.895 & 0.016 \\
-		&& $\beta_1$ & 0.135 & 48.11\% & 0.026 & 96.5\% & 0.720 & 0.290 \\
-		&& $\beta_2$ & 0.124 & 19.40\% & 0.025 & 93.5\% & 0.576 & 0.002 \\
-		&& $\beta_3$ & 0.006 & 2.94\% & 5.50$*10^-5$ & 95.0\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.173 & 3.77\% & 0.047 & 99.0\% & 0.904 & 0.035 \\
-		&& $\beta_1$ & \textbf{0.186} & \textbf{66.53\%} & \textbf{0.052} & 92.0\% & 0.864 & 0.466 \\
-		&& $\beta_2$ & 0.124 & 19.40\% & 0.025 & 93.5\% & 0.576 & 0.004 \\
-		&& $\beta_3$ & 0.006 & 2.94\% & 5.50$*10^-5$ & 96.0\% & 0.030 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.188 & 4.09\% & 0.055 & 98.5\% & 0.946 & 0.105 \\
-		&& $\beta_1$ & \textbf{0.322} & \textbf{115.10\%} & \textbf{0.149} & \textbf{85.5\%} & 1.306 & 0.712 \\
-		&& $\beta_2$ & 0.127 & 19.87\% & 0.026 & 93.5\% & 0.580 & 0.011 \\
-		&& $\beta_3$ & 0.006 & 3.02\% & 5.75$*10^-5$ & 95.0\% & 0.030 & 0.025 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+Nevertheless, this must be kept in mind when analyzing the results from the PM designs provided in Table \ref{tab:primary}.
+\textbf{In Table \ref{tab:primary} as in Tables \ref{tab:sampsize}, \ref{tab:lowcorr}, and \ref{tab:hightime} bold values indicate ``unacceptable" results.} That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
+
+<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
+primary
+@
 
@@
 
-Towards the bottom of Table \ref{tab:table3}, the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at both medium and high levels of missingness.
+Towards the bottom of Table \ref{tab:primary}, the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at both medium and high levels of missingness.
 Moreover, at high levels of missingness coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.
@@
 All parameter values were held the same as in the original simulation.
-Table \ref{tab:table2}, again, contains the results of the analysis before applying any PM design.
-\par
-
-The results of the full-data simulations are compared to those obtained from the PM designs, shown in Table \ref{tab:table4}.
+Table \ref{tab:prelim} \textbf{not here yet}, again, contains the results of the analysis before applying any PM design.
+The results of the full-data simulations are compared to those obtained from the PM designs, shown in Table \ref{tab:sampsize}.
+\par
+
+<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
+sampsize
+@
+
 First notice the bias of all parameters is lower than in the smaller sample size simulations.
@@
 At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable.
-However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:table2}.
+However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:prelim} \textbf{not here yet}.
 The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088.
@@
 For the next set of simulations sample size returned to 60 participants but the level of inter-survey correlation decreased.
-The results obtained from the full data simulations are provided in Table \ref{tab:table2} while the results from the PM designs are given in Table \ref{tab:table5}.
-\par
+The results obtained from the full data simulations are provided in Table \ref{tab:prelim} \textbf{not here yet} while the results from the PM designs are given in Table \ref{tab:lowcorr}.
+\par
+
+<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
+lowcorr
+@
 
@@
 In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$.
-The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:table6}.
-\par
+The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:hightime}.
+\par
+
+<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
+hightime
+@
 

### 2018-05-22 Documentation/manuscript.tex
Manuscript edits.

@@
+% Predefine some figures
+
 \RequirePackage{fix-cm}
@@
 
+\raggedbottom
+
 \journalname{Sankhya B}
@@
 Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions.
-A common form setup is the three-form design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C.
+How these subsets are chosen varies.
+A common form setup is three-form Block Design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C.
 Each form of the survey includes the X block as well as two of the remaining blocks.
-This leaves the configurations seen in Table \\ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded.
-Note that every block appears in at least one form.
-By designing the forms in this manner we are able to estimate the relationship between any chosen items regardless of their blocks.
-That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows this.
-\par
-
-We need to talk about the other type of split design that we used here which was that X of the 8 questions are randomly omitted on each day.
-
-% \begin{table}[h!]
-% 	\centering
-% 	\caption{The Three Form PM Design}
-% 	\label{tab:table10}
-% 	\setlength{\tabcolsep}{1cm}
-% 	\begin{tabular}{c|cccc}
-% 		\toprule
-% 		& \multicolumn{4}{c}{Block} \\
-% 		Form & X & A & B & C \\
-% 		\midrule
-% 		1 & 1 & 1 & 1 & 0 \\
-% 		2 & 1 & 1 & 0 & 1 \\
-% 		3 & 1 & 0 & 1 & 1 \\
-% 		\bottomrule
-% 	\end{tabular}
-% \end{table}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/misslow-1} \caption[Low missingness]{Low missingness}\label{fig:misslow}
-\end{figure}
-
-\end{knitrout}
-
-Figure \ref{fig:misslow} is
-
-An important consideration when designing a Split Form survey is question distribution.
-The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
+A participant is then given a different form each day of the study.
+Designing the forms in this manner allows researchers to estimate the relationship between any chosen items, regardless of their blocks.
+For example, this allows the relationship between an item in block A and another in block C to be estimated and examined.
+\par
+
+An important consideration here is question distribution. The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
 Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}.
@@
 
+\subsection{Altered Split Form}
+
+The Split Form planned missingness method can be modified to include the benefits of complete cases seen in Wave Missingness in what may be called Altered Split Form.
+In this method, the researcher asks participants all questions on the first $n$ days of the study.
+Thereafter, the survey design reverts to regular Split Form.
+This method allows the researcher to collect $n$ complete cases from each participant, aiding in the imputation process after surveys are administered.
+Altered Split Form, and the other planned missingness methods, is illustrated in Figure \ref{fig:formillustration} below.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+\includegraphics[width=\maxwidth]{figure/formillustration-1} \caption[Low missingness]{Low missingness}\label{fig:formillustration}
+\end{figure}
+
+\end{knitrout}
+
 \subsection{Multiple Imputation}
@@
 \label{sec:3.1}
-The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$.
+The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.28$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.01$.
 The effects of the variables here are comparable to those found in the original dataset.
 This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design.
-Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:table2}.
+Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:prelim} \textbf{not here yet}.
 Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
 
+Of note in the complete-data primary analysis is that the coverage of the 95\% CIs is larger than expected for the parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large.
+This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}.
+Nevertheless, this must be kept in mind when analyzing the results from the PM designs provided in Table \ref{tab:primary}.
+\textbf{In Table \ref{tab:primary} as in Tables \ref{tab:sampsize}, \ref{tab:lowcorr}, and \ref{tab:hightime} bold values indicate ``unacceptable" results.} That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
+
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[H]
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[!h]
+
+\caption{\label{tab:primary}Primary Results (N = 60)}
 \centering
-\resizebox{\linewidth}{!}{\begin{tabular}{l|l|l|r|r|r|r|r|r}
+\resizebox{\linewidth}{!}{\begin{tabular}[t]{l|l|l|r|r|r|r|r|r}
 \hline
@@
 \end{knitrout}
-
-% latex table generated in R 3.5.0 by xtable 1.8-2 package
-% Mon May 14 21:02:34 2018
-\begin{table}[ht]
-\centering
-\begin{tabular}{lllrrrr}
-  \hline
-Design & \% Missingness  & Parameter & Coverage & Bias & MSE & FMI \\ 
-  \hline
- &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
-   &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
-   &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
-   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
-   \hline
-   &  &  & 0.986 & 0.040 & 0.019 & 0.012 \\ 
-   &  &  & 0.993 & -0.168 & 0.750 & 0.557 \\ 
-   &  &  & 0.932 & 0.008 & 0.024 & 0.002 \\ 
-   &  &  & 0.940 & -0.000 & 0.000 & 0.008 \\ 
-   \hline
-   &  &  & 0.984 & 0.036 & 0.027 & 0.030 \\ 
-   &  &  & 0.991 & -0.713 & 9.933 & 0.625 \\ 
-   &  &  & 0.932 & 0.009 & 0.027 & 0.005 \\ 
-   &  &  & 0.939 & -0.000 & 0.000 & 0.021 \\ 
-   \hline
-   &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
-   &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
-   &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
-   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
-   \hline
-   &  &  & 0.988 & 0.040 & 0.018 & 0.010 \\ 
-   &  &  & 0.994 & -0.167 & 0.782 & 0.549 \\ 
-   &  &  & 0.931 & 0.009 & 0.024 & 0.002 \\ 
-   &  &  & 0.944 & -0.000 & 0.000 & 0.006 \\ 
-   \hline
-   &  &  & 0.983 & 0.036 & 0.022 & 0.027 \\ 
-   &  &  & 0.990 & -0.686 & 10.509 & 0.665 \\ 
-   &  &  & 0.928 & 0.009 & 0.026 & 0.007 \\ 
-   &  &  & 0.946 & -0.000 & 0.000 & 0.023 \\ 
-   \hline
-   &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
-   &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
-   &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
-   &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
-   \hline
-   &  &  & 0.991 & 0.029 & 0.018 & 0.055 \\ 
-   &  &  & 0.988 & -0.112 & 0.345 & 0.752 \\ 
-   &  &  & 0.934 & 0.009 & 0.024 & 0.007 \\ 
-   &  &  & 0.951 & -0.000 & 0.000 & 0.032 \\ 
-   \hline
-   &  &  & 0.994 & -0.003 & 0.022 & 0.258 \\ 
-   &  &  & 0.988 & -0.105 & 0.284 & 0.903 \\ 
-   &  &  & 0.937 & 0.011 & 0.025 & 0.039 \\ 
-   &  &  & 0.960 & -0.000 & 0.000 & 0.175 \\ 
-   \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[b!]
-	\centering
-	\caption{Results of Analysis before imposing Missingness in each Scenario}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table2}
-	\begin{tabular}{cc|ccccc}
-		\toprule
-		Scenario & Parameter & Bias & Percent Bias & MSE & Coverage & CI Length \\
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Primary \\ Analysis (N=60)}} 
-		& $\gamma_0$ & 0.151 & 6.55\% & 0.037 & 99.0\% & 0.750 \\
-		& $\beta_1$ & 0.133 & 23.75\% & 0.028 & 95.5\% & 0.652 \\
-		& $\beta_2$ & 0.120 & 9.40\% & 0.022 & 97.5\% & 0.610 \\
-		& $\beta_3$ & 0.007 & 3.42\% & 7.11$*10^-5$ & 97.0\% & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Increased \\ Sample (N=120)}} 
-		& $\gamma_0$ & 0.106 & 4.61\% & 0.018 & 98.0\% & 0.528 \\
-		& $\beta_1$ & 0.099 & 17.63\% & 0.016 & 93.0\% & 0.460 \\
-		& $\beta_2$ & 0.091 & 7.12\% & 0.013 & 95.5\% & 0.429 \\
-		& $\beta_3$ & 0.005 & 2.34\% & 3.52$*10^-5$ & 96.5\% & 0.024 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{Low \\Inter-Survey Correlation (N=60)}} 
-		& $\gamma_0$ & 0.145 & 6.29\% & 0.033 & 99.0\% & 0.747 \\
-		& $\beta_1$ & 0.130 & 23.27\% & 0.027 & 94.5\% & 0.651 \\
-		& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 94.0\% & 0.611 \\
-		& $\beta_3$ & 0.007 & 3.69\% & 8.88$*10^-5$ & 93.0\% & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{4}{*}{\parbox{2cm}{High \\Time Effect (N=60)}}
-		& $\gamma_0$ & 0.170 & 3.69\% & 0.045 & 98.5\% & 0.888 \\
-		& $\beta_1$ & 0.123 & 43.86\% & 0.024 & 96.0\% & 0.598 \\
-		& $\beta_2$ & 0.124 & 19.35\% & 0.025 & 93.5\% & 0.575 \\
-		& $\beta_3$ & 0.006 & 2.95\% & 5.50$*10^-5$ & 95.5\% & 0.030 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Of note in the complete-data primary analysis is that the coverage of the 95\% CIs is larger than expected for the parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large.
-This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}.
-Nevertheless, we should keep this in mind when analyzing our results from the PM designs provided in Table \ref{tab:table3}.
-In Table \ref{tab:table3} as in Tables \ref{tab:table4}, \ref{tab:table5}, and \ref{tab:table6} bold values indicate "Unacceptable" results.
-That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
-
-\begin{table}[p]
-	\centering
-	\caption{Primary Simulation Results (N=60)}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table3}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.151 & 6.59\% & 0.037 & 99.5\% & 0.753 & 0.009 \\
-		&& $\beta_1$ & 0.139 & 24.78\% & 0.029 & 96.0\% & 0.693 & 0.112 \\
-		&& $\beta_2$ & 0.120 & 9.41\% & 0.022 & 97.0\% & 0.610 & 0.002 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.12$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.153 & 6.67\% & 0.037 & 99.0\% & 0.765 & 0.040 \\
-		&& $\beta_1$ & 0.162 & 28.93\% & 0.041 & 95.5\% & 0.869 & 0.390 \\
-		&& $\beta_2$ & 0.121 & 9.51\% & 0.022 & 97.0\% & 0.616 & 0.007 \\
-		&& $\beta_3$ & 0.007 & 3.40\% & 6.99$*10^-5$ & 98.5\% & 0.034 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.154 & 6.70\% & 0.039 & 98.5\% & 0.818 & 0.147 \\
-		&& $\beta_1$ & \textbf{0.225} & \textbf{40.16}\% & \textbf{0.076} & 97.5\% & 1.464 & 0.710 \\
-		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 97.5\% & 0.611 & 0.022 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.02$*10^-5$ & 98.0\% & 0.035 & 0.032 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.151 & 6.57\% & 0.037 & 98.0\% & 0.753 & 0.008 \\
-		&& $\beta_1$ & 0.137 & 24.55\% & 0.030 & 96.0\% & 0.690 & 0.105 \\
-		&& $\beta_2$ & 0.120 & 9.39\% & 0.022 & 97.5\% & 0.611 & 0.002 \\
-		&& $\beta_3$ & 0.007 & 3.42\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.153 & 6.67\% & 0.038 & 99.5\% & 0.760 & 0.030 \\
-		&& $\beta_1$ & 0.151 & 26.93\% & 0.036 & 96.0\% & 0.811 & 0.324 \\
-		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 96.0\% & 0.611 & 0.006 \\
-		&& $\beta_3$ & 0.007 & 3.44\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.164 & 7.13\% & 0.042 & 98.0\% & 0.799 & 0.105 \\
-		&& $\beta_1$ & \textbf{0.225} & \textbf{40.14\%} & \textbf{0.080} & 96.0\% & 1.265 & 0.640 \\
-		&& $\beta_2$ & 0.117 & 9.13\% & 0.021 & 97.5\% & 0.615 & 0.019 \\
-		&& $\beta_3$ & 0.007 & 3.46\% & 7.07$*10^-5$ & 98.0\% & 0.034 & 0.023 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.152 & 6.61\% & 0.037 & 99.5\% & 0.757 & 0.023 \\
-		&& $\beta_1$ & 0.147 & 26.25\% & 0.033 & 96.0\% & 0.767 & 0.270 \\
-		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 96.0\% & 0.610 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.41\% & 6.97$*10^-5$ & 98.0\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.157 & 6.84\% & 0.039 & 100.0\% & 0.767 & 0.052 \\
-		&& $\beta_1$ & \textbf{0.190} & \textbf{33.95\%} & \textbf{0.058} & 94.5\% & 0.934 & 0.465 \\
-		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 97.5\% & 0.609 & 0.008 \\
-		&& $\beta_3$ & 0.007 & 3.34\% & 6.80$*10^-5$ & 98.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.168 & 7.30\% & 0.045 & 99.5\% & 0.807 & 0.129 \\
-		&& $\beta_1$ & \textbf{0.290} & \textbf{51.77\%} & \textbf{0.132} & \textbf{88.5\%} & 1.335 & 0.680 \\
-		&& $\beta_2$ & 0.119 & 9.32\% & 0.022 & 96.0\% & 0.614 & 0.017 \\
-		&& $\beta_3$ & 0.007 & 3.40\% & 6.96$*10^-5$ & 98.5\% & 0.034 & 0.025 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{Increased Sample Size simulation Results (N=120)}
-	\setlength{\tabcolsep}{0.1cm}
-	\label{tab:table4}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.106 & 4.60\% & 0.017 & 98.5\% & 0.533 & 0.022 \\
-		&& $\beta_1$ & 0.106 & 18.96\% & 0.018 & 96.0\% & 0.548 & 0.263 \\
-		&& $\beta_2$ & 0.091 & 7.14\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.33\% & 3.47$*10^-5$ & 96.5\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.112 & 4.85\% & 0.019 & 98.0\% & 0.542 & 0.057 \\
-		&& $\beta_1$ & 0.134 & 23.86\% & \textbf{0.027} & 95.0\% & 0.696 & 0.489 \\
-		&& $\beta_2$ & 0.092 & 7.15\% & 0.013 & 96.5\% & 0.430 & 0.009 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.110 & 4.80\% & 0.019 & 99.5\% & 0.575 & 0.153 \\
-		&& $\beta_1$ & \textbf{0.194} & \textbf{34.59\%} & \textbf{0.057} & 94.5\% & 1.088 & 0.742 \\
-		&& $\beta_2$ & 0.092 & 7.20\% & 0.013 & 95.0\% & 0.432 & 0.021 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.42$*10^-5$ & 97.5\% & 0.024 & 0.026 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.107 & 4.64\% & 0.017 & 98.0\% & 0.533 & 0.022 \\
-		&& $\beta_1$ & 0.111 & 19.80\% & 0.020 & 94.5\% & 0.545 & 0.263 \\
-		&& $\beta_2$ & 0.091 & 7.08\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.115 & 4.99\% & 0.020 & 98.0\% & 0.542 & 0.056 \\
-		&& $\beta_1$ & 0.138 & 24.65\% & \textbf{0.028} & 94.5\% & 0.693 & 0.494 \\
-		&& $\beta_2$ & 0.091 & 7.24\% & 0.013 & 96.0\% & 0.430 & 0.008 \\
-		&& $\beta_3$ & 0.005 & 2.34\% & 3.54$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.115 & 5.01\% & 0.020 & 99.0\% & 0.563 & 0.119 \\
-		&& $\beta_1$ & \textbf{0.188} & \textbf{33.65\%} & \textbf{0.058} & 91.5\% & 0.958 & 0.681 \\
-		&& $\beta_2$ & 0.092 & 7.16\% & 0.013 & 96.0\% & 0.432 & 0.018 \\
-		&& $\beta_3$ & 0.005 & 2.30\% & 3.44$*10^-5$ & 96.0\% & 0.024 & 0.020 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.108 & 4.72\% & 0.018 & 98.0\% & 0.533 & 0.024 \\
-		&& $\beta_1$ & 0.123 & 21.90\% & \textbf{0.024} & 92.0\% & 0.551 & 0.287 \\
-		&& $\beta_2$ & 0.092 & 7.18\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
-		&& $\beta_3$ & 0.005 & 2.35\% & 3.51$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.111 & 4.84\% & 0.019 & 99.0\% & 0.540 & 0.052 \\
-		&& $\beta_1$ & \textbf{0.168} & \textbf{30.02\%} & \textbf{0.043} & \textbf{85.5\%} & 0.671 & 0.489 \\
-		&& $\beta_2$ & 0.092 & 7.22\% & 0.013 & 95.0\% & 0.429 & 0.007 \\
-		&& $\beta_3$ & 0.005 & 2.32\% & 3.42$*10^-5$ & 97.0\% & 0.024 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.123 & 5.33\% & 0.023 & 99.0\% & 0.558 & 0.108 \\
-		&& $\beta_1$ & \textbf{0.248} & \textbf{44.26\%} & \textbf{0.099} & \textbf{82.0\%} & 0.894 & 0.666 \\
-		&& $\beta_2$ & 0.094 & 7.36\% & 0.014 & 96.0\% & 0.430 & 0.013 \\
-		&& $\beta_3$ & 0.005 & 2.36\% & 3.53$*10^-5$ & 96.0\% & 0.024 & 0.015 \\
-		\bottomrule
-	\end{tabular}	
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{Low Inter-Survey Correlation Simulation Results (N=60)}
-	\label{tab:table5}
-	\setlength{\tabcolsep}{0.1cm}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.146 & 6.34\% & 0.033 & 99.0\% & 0.755 & 0.025 \\
-		&& $\beta_1$ & 0.150 & 26.82\% & 0.034 & 95.5\% & 0.782 & 0.278 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.612 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.64\% & 8.68$*10^-5$ & 92.5\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.148 & 6.43\% & 0.034 & 99.0\% & 0.772 & 0.067 \\
-		&& $\beta_1$ & \textbf{0.183} & \textbf{32.65\%} & \textbf{0.053} & 95.0\% & 1.032 & 0.526 \\
-		&& $\beta_2$ & 0.125 & 9.80\% & 0.026 & 94.0\% & 0.613 & 0.010 \\
-		&& $\beta_3$ & 0.007 & 3.63\% & 8.73$*10^-5$ & 92.5\% & 0.035 & 0.015 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.155 & 6.74\% & 0.036 & 99.5\% & 0.825 & 0.166 \\
-		&& $\beta_1$ & \textbf{0.276} & \textbf{49.31\%} & \textbf{0.116} & 95.0\% & 1.567 & 0.749 \\
-		&& $\beta_2$ & 0.124 & 9.71\% & 0.025 & 94.0\% & 0.618 & 0.025 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.73$*10^-5$ & 93.5\% & 0.035 & 0.034 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.141 & 6.13\% & 0.031 & 99.0\% & 0.754 & 0.023 \\
-		&& $\beta_1$ & 0.139 & 25.80\% & 0.030 & 95.5\% & 0.772 & 0.260 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.612 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.55$*10^-5$ & 92.5\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.149 & 6.48\% & 0.035 & 99.5\% & 0.767 & 0.056 \\
-		&& $\beta_1$ & 0.170 & 30.44\% & \textbf{0.044} & 97.0\% & 0.968 & 0.486 \\
-		&& $\beta_2$ & 0.125 & 9.79\% & 0.025 & 93.5\% & 0.612 & 0.009 \\
-		&& $\beta_3$ & 0.007 & 3.64\% & 8.58$*10^-5$ & 92.5\% & 0.034 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.149 & 6.47\% & 0.036 & 98.5\% & 0.809 & 0.139 \\
-		&& $\beta_1$ & \textbf{0.228} & \textbf{40.70\%} & \textbf{0.088} & 96.0\% & 1.425 & 0.708 \\
-		&& $\beta_2$ & 0.125 & 9.74\% & 0.026 & 94.0\% & 0.617 & 0.021 \\
-		&& $\beta_3$ & 0.007 & 3.62\% & 8.65$*10^-5$ & 93.5\% & 0.035 & 0.027 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.138 & 6.02\% & 0.031 & 99.5\% & 0.754 & 0.025 \\
-		&& $\beta_1$ & 0.158 & 28.17\% & 0.036 & 96.5\% & 0.776 & 0.286 \\
-		&& $\beta_2$ & 0.126 & 9.82\% & 0.026 & 94.0\% & 0.611 & 0.004 \\
-		&& $\beta_3$ & 0.007 & 3.61\% & 8.50$*10^-5$ & 92.5\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.148 & 6.43\% & 0.034 & 99.5\% & 0.765 & 0.053 \\
-		&& $\beta_1$ & \textbf{0.197} & \textbf{35.14\%} & \textbf{0.059} & 91.0\% & 0.939 & 0.472 \\
-		&& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 93.5\% & 0.611 & 0.007 \\
-		&& $\beta_3$ & 0.007 & 3.60\% & 8.48$*10^-5$ & 92.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.158 & 6.86\% & 0.040 & 98.5\% & 0.799 & 0.122 \\
-		&& $\beta_1$ & \textbf{0.303} & \textbf{54.18\%} &\textbf{0.148} & \textbf{89.5\%} & 1.290 & 0.676 \\
-		&& $\beta_2$ & 0.127 & 9.94\% & 0.027 & 95.5\% & 0.615 & 0.015 \\
-		&& $\beta_3$ & 0.007 & 3.62\% & 8.77$*10^-5$ & 93.5\% & 0.035 & 0.021 \\
-		\bottomrule
-	\end{tabular}	
-\end{table}
-\begin{table}[p]
-	\centering
-	\caption{High Time Effect Simulation Results (N=60)}
-	\label{tab:table6}
-	\setlength{\tabcolsep}{0.1cm}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|c|cccccc}
-		\toprule
-		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
-		\midrule
-		\multirow{12}{*}{Split Form}
-		& \multirow{4}{*}{Low(25\%)}
-		& $\gamma_0$ & 0.169 & 3.67\% & 0.045 & 99.0\% & 0.895 & 0.015 \\
-		&& $\beta_1$ & 0.133 & 47.54\% & 0.029 & 96.0\% & 0.708 & 0.262 \\
-		&& $\beta_2$ & 0.124 & 19.33\% & 0.025 & 93.5\% & 0.576 & 0.003 \\
-		&& $\beta_3$ & 0.006 & 2.96\% & 5.50$*10^-5$ & 94.5\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(50\%)}
-		& $\gamma_0$ & 0.174 & 3.77\% & 0.047 & 98.5\% & 0.912 & 0.050 \\
-		&& $\beta_1$ & \textbf{0.181} & \textbf{64.59\%} & \textbf{0.049} & 96.0\% & 0.981 & 0.554 \\
-		&& $\beta_2$ & 0.124 & 19.44\% & 0.025 & 94.0\% & 0.578 & 0.007 \\
-		&& $\beta_3$ & 0.006 & 2.97\% & 5.55$*10^-5$ & 96.0\% & 0.030 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(75\%)}
-		& $\gamma_0$ & 0.177 & 3.85\% & 0.049 & 98.0\% & 0.954 & 0.117 \\
-		&& $\beta_1$ & \textbf{0.243} & \textbf{86.63\%} & \textbf{0.097} & 93.0\% & 1.433 & 0.729 \\
-		&& $\beta_2$ & 0.124 & 19.37\% & 0.025 & 94.0\% & 0.581 & 0.016 \\
-		&& $\beta_3$ & 0.006 & 2.97\% & 5.70$*10^-5$ & 94.0\% & 0.030 & 0.025 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
-		& \multirow{4}{*}{Low(23.9\%)}
-		& $\gamma_0$ & 0.171 & 3.72\% & 0.046 & 99.0\% & 0.895 & 0.015 \\
-		&& $\beta_1$ & 0.142 & 50.55\% & 0.033 & 94.5\% & 0.717 & 0.272 \\
-		&& $\beta_2$ & 0.124 & 19.36\% & 0.025 & 93.5\% & 0.577 & 0.002 \\
-		&& $\beta_3$ & 0.006 & 2.95\% & 5.48$*10^-5$ & 95.5\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(47.8\%)}
-		& $\gamma_0$ & 0.176 & 3.82\% & 0.048 & 99.0\% & 0.905 & 0.038 \\
-		&& $\beta_1$ & 0.168 & 60.10\% & \textbf{0.043} & 95.5\% & 0.903 & 0.486 \\
-		&& $\beta_2$ & 0.124 & 19.36\% & 0.025 & 93.5\% & 0.581 & 0.006 \\
-		&& $\beta_3$ & 0.006 & 2.95\% & 5.60$*10^-5$ & 95.0\% & 0.030 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(71.7\%)}
-		& $\gamma_0$ & 0.177 & 3.84\% & 0.051 & 99.5\% & 0.947 & 0.108 \\
-		&& $\beta_1$ & \textbf{0.257} & \textbf{91.96\%} & \textbf{0.097} & 94.5\% & 1.381 & 0.714 \\
-		&& $\beta_2$ & 0.124 & 19.34\% & 0.025 & 94.5\% & 0.581 & 0.014 \\
-		&& $\beta_3$ & 0.006 & 3.01\% & 5.76$*10^-5$ & 95.0\% & 0.030 & 0.023 \\
-		\midrule
-		\midrule
-		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
-		& \multirow{4}{*}{Low(24.4\%)}
-		& $\gamma_0$ & 0.170 & 3.70\% & 0.046 & 99.0\% & 0.895 & 0.016 \\
-		&& $\beta_1$ & 0.135 & 48.11\% & 0.026 & 96.5\% & 0.720 & 0.290 \\
-		&& $\beta_2$ & 0.124 & 19.40\% & 0.025 & 93.5\% & 0.576 & 0.002 \\
-		&& $\beta_3$ & 0.006 & 2.94\% & 5.50$*10^-5$ & 95.0\% & 0.030 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
-		&\multirow{4}{*}{Medium(48.9\%)}
-		& $\gamma_0$ & 0.173 & 3.77\% & 0.047 & 99.0\% & 0.904 & 0.035 \\
-		&& $\beta_1$ & \textbf{0.186} & \textbf{66.53\%} & \textbf{0.052} & 92.0\% & 0.864 & 0.466 \\
-		&& $\beta_2$ & 0.124 & 19.40\% & 0.025 & 93.5\% & 0.576 & 0.004 \\
-		&& $\beta_3$ & 0.006 & 2.94\% & 5.50$*10^-5$ & 96.0\% & 0.030 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
-		& \multirow{4}{*}{High(73.3\%)}
-		& $\gamma_0$ & 0.188 & 4.09\% & 0.055 & 98.5\% & 0.946 & 0.105 \\
-		&& $\beta_1$ & \textbf{0.322} & \textbf{115.10\%} & \textbf{0.149} & \textbf{85.5\%} & 1.306 & 0.712 \\
-		&& $\beta_2$ & 0.127 & 19.87\% & 0.026 & 93.5\% & 0.580 & 0.011 \\
-		&& $\beta_3$ & 0.006 & 3.02\% & 5.75$*10^-5$ & 95.0\% & 0.030 & 0.025 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
 
@@
 All parameter values were held the same as in the original simulation.
-Table \ref{tab:table2}, again, contains the results of the analysis before applying any PM design.
-\par
-
-The results of the full-data simulations are compared to those obtained from the PM designs, shown in Table \ref{tab:table4}.
+Table \ref{tab:prelim} \textbf{not here yet}, again, contains the results of the analysis before applying any PM design.
+The results of the full-data simulations are compared to those obtained from the PM designs, shown in Table \ref{tab:sampsize}.
+\par
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[!h]
+
+\caption{\label{tab:sampsize}Increased Sample Size Results (N = 120)}
+\centering
+\resizebox{\linewidth}{!}{\begin{tabular}[t]{l|l|l|r|r|r|r|r|r}
+\hline
+Design & Level & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
+\hline
+ &  & $\gamma_0$ & 0.013 & -0.577 & 0.008 & 0.985 & 0.424 & 0.001\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.041 & -14.633 & 0.134 & 0.975 & 1.690 & 0.183\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.006 & 0.867 & 0.007 & 0.944 & 0.319 & 0.000\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.868 & 0.000 & 0.954 & 0.012 & 0.000\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.012 & -0.544 & 0.008 & 0.985 & 0.429 & 0.009\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.073 & -25.973 & 0.148 & 0.991 & 2.366 & 0.449\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.006 & 0.875 & 0.007 & 0.944 & 0.320 & 0.002\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.832 & 0.000 & 0.953 & 0.012 & 0.002\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.004 & -0.179 & 0.011 & 0.973 & 0.465 & 0.025\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.145 & -51.616 & 0.304 & 0.983 & 3.281 & 0.649\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.007 & 1.136 & 0.008 & 0.939 & 0.332 & 0.005\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & 0.243 & 0.000 & 0.944 & 0.013 & 0.010\\
+\cline{1-9}
+ &  & $\gamma_0$ & 0.013 & -0.576 & 0.008 & 0.984 & 0.425 & 0.002\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.032 & -11.186 & 0.129 & 0.980 & 1.677 & 0.173\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.006 & 0.875 & 0.007 & 0.944 & 0.319 & 0.000\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.883 & 0.000 & 0.952 & 0.012 & 0.000\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.013 & -0.553 & 0.008 & 0.983 & 0.426 & 0.005\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.058 & -20.672 & 0.145 & 0.996 & 2.250 & 0.414\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.006 & 0.879 & 0.007 & 0.944 & 0.319 & 0.001\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.917 & 0.000 & 0.951 & 0.012 & 0.002\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.011 & -0.465 & 0.008 & 0.986 & 0.434 & 0.017\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.112 & -39.796 & 0.228 & 0.994 & 3.245 & 0.691\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.006 & 0.886 & 0.007 & 0.940 & 0.321 & 0.004\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.054 & 0.000 & 0.952 & 0.012 & 0.009\\
+\cline{1-9}
+ &  & $\gamma_0$ & 0.013 & -0.575 & 0.008 & 0.985 & 0.426 & 0.004\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.064 & -22.793 & 0.137 & 0.987 & 2.064 & 0.342\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.005 & 0.832 & 0.007 & 0.944 & 0.319 & 0.001\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.906 & 0.000 & 0.952 & 0.012 & 0.001\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.010 & -0.453 & 0.008 & 0.984 & 0.435 & 0.023\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.082 & -29.029 & 0.184 & 0.994 & 2.979 & 0.630\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.006 & 0.890 & 0.007 & 0.943 & 0.320 & 0.004\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.959 & 0.000 & 0.954 & 0.012 & 0.008\\
+\cline{2-9}
+ &  & $\gamma_0$ & -0.010 & 0.428 & 0.010 & 0.988 & 0.554 & 0.179\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.059 & -21.087 & 0.297 & 0.970 & 3.760 & 0.859\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.008 & 1.204 & 0.007 & 0.952 & 0.334 & 0.040\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -2.426 & 0.000 & 0.955 & 0.014 & 0.105\\
+\hline
+\end{tabular}}
+\end{table}
+
+\end{knitrout}
+
 First notice the bias of all parameters is lower than in the smaller sample size simulations.
@@
 For the next set of simulations sample size returned to 60 participants but the level of inter-survey correlation decreased.
-The results obtained from the full data simulations are provided in Table \ref{tab:table2} while the results from the PM designs are given in Table \ref{tab:table5}.
-\par
+The results obtained from the full data simulations are provided in Table \ref{tab:prelim} \textbf{not here yet} while the results from the PM designs are given in Table \ref{tab:lowcorr}.
+\par
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[!h]
+
+\caption{\label{tab:lowcorr}Low Inter-Survey Correlation Results (N = 60)}
+\centering
+\resizebox{\linewidth}{!}{\begin{tabular}[t]{l|l|l|r|r|r|r|r|r}
+\hline
+Design & Level & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
+\hline
+ &  & $\gamma_0$ & 0.042 & -1.856 & 0.018 & 0.990 & 0.702 & 0.002\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.067 & -23.958 & 0.265 & 0.981 & 2.537 & 0.230\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.007 & 1.122 & 0.024 & 0.938 & 0.585 & 0.000\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -1.108 & 0.000 & 0.940 & 0.017 & 0.001\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.041 & -1.774 & 0.018 & 0.992 & 0.708 & 0.010\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.103 & -36.645 & 0.281 & 0.991 & 3.492 & 0.535\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.008 & 1.183 & 0.024 & 0.934 & 0.586 & 0.002\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.031 & 0.000 & 0.939 & 0.017 & 0.006\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.034 & -1.488 & 0.026 & 0.990 & 0.794 & 0.030\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.148 & -52.475 & 0.425 & 0.991 & 4.285 & 0.621\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.011 & 1.791 & 0.028 & 0.935 & 0.613 & 0.005\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.870 & 0.000 & 0.941 & 0.020 & 0.020\\
+\cline{1-9}
+ &  & $\gamma_0$ & 0.043 & -1.874 & 0.018 & 0.989 & 0.701 & 0.001\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.066 & -23.566 & 0.258 & 0.984 & 2.535 & 0.224\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.007 & 1.116 & 0.024 & 0.935 & 0.585 & 0.000\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -1.202 & 0.000 & 0.939 & 0.017 & 0.001\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.041 & -1.782 & 0.018 & 0.988 & 0.706 & 0.009\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.096 & -33.989 & 0.262 & 0.991 & 3.394 & 0.511\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.008 & 1.226 & 0.024 & 0.934 & 0.585 & 0.002\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.150 & 0.000 & 0.940 & 0.017 & 0.005\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.036 & -1.573 & 0.020 & 0.986 & 0.738 & 0.023\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.174 & -61.685 & 0.380 & 0.991 & 4.350 & 0.669\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.010 & 1.639 & 0.025 & 0.937 & 0.598 & 0.005\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.961 & 0.000 & 0.949 & 0.018 & 0.024\\
+\cline{1-9}
+ &  & $\gamma_0$ & 0.041 & -1.790 & 0.018 & 0.989 & 0.703 & 0.005\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.084 & -29.806 & 0.242 & 0.994 & 2.967 & 0.423\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.007 & 1.141 & 0.024 & 0.936 & 0.585 & 0.001\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -1.100 & 0.000 & 0.940 & 0.017 & 0.002\\
+\cline{2-9}
+ &  & $\gamma_0$ & 0.031 & -1.347 & 0.018 & 0.992 & 0.739 & 0.046\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.112 & -39.818 & 0.246 & 0.988 & 3.491 & 0.722\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.008 & 1.269 & 0.024 & 0.936 & 0.588 & 0.005\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.499 & 0.000 & 0.944 & 0.017 & 0.024\\
+\cline{2-9}
+ &  & $\gamma_0$ & -0.003 & 0.133 & 0.022 & 0.996 & 0.985 & 0.237\\
+\cline{3-9}
+ &  & $\beta_1$ & -0.094 & -33.488 & 0.233 & 0.988 & 3.875 & 0.887\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.010 & 1.616 & 0.025 & 0.941 & 0.608 & 0.033\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & -0.001 & -3.529 & 0.000 & 0.964 & 0.021 & 0.160\\
+\hline
+\end{tabular}}
+\end{table}
+
+\end{knitrout}
 
@@
 In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$.
-The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:table6}.
-\par
+The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:hightime}.
+\par
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[!h]
+
+\caption{\label{tab:hightime}High Time Results (N = 60)}
+\centering
+\resizebox{\linewidth}{!}{\begin{tabular}[t]{l|l|l|r|r|r|r|r|r}
+\hline
+Design & Level & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
+\hline
+ &  & $\gamma_0$ & -0.023 & 0.498 & 0.120 & 0.968 & 1.414 & 0.018\\
+\cline{3-9}
+ &  & $\beta_1$ & 0.604 & 429.053 & 0.669 & 0.973 & 4.812 & 0.271\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.010 & 3.263 & 0.048 & 0.955 & 0.827 & 0.003\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -2.671 & 0.000 & 0.945 & 0.039 & 0.004\\
+\cline{2-9}
+ &  & $\gamma_0$ & -0.048 & 1.060 & 0.128 & 0.972 & 1.506 & 0.059\\
+\cline{3-9}
+ &  & $\beta_1$ & 0.724 & 513.940 & 0.898 & 0.988 & 5.933 & 0.499\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.025 & 7.927 & 0.047 & 0.958 & 0.834 & 0.013\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -2.867 & 0.000 & 0.938 & 0.039 & 0.017\\
+\cline{2-9}
+ &  & $\gamma_0$ & -0.178 & 3.882 & 0.370 & 0.984 & 2.050 & 0.132\\
+\cline{3-9}
+ &  & $\beta_1$ & 0.997 & 708.287 & 1.573 & 0.955 & 6.822 & 0.610\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.044 & 13.650 & 0.060 & 0.965 & 0.966 & 0.036\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.787 & 0.000 & 0.955 & 0.048 & 0.060\\
+\cline{1-9}
+ &  & $\gamma_0$ & -0.019 & 0.415 & 0.119 & 0.966 & 1.401 & 0.011\\
+\cline{3-9}
+ &  & $\beta_1$ & 0.603 & 428.601 & 0.638 & 0.966 & 4.616 & 0.239\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.014 & 4.254 & 0.048 & 0.956 & 0.827 & 0.002\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -3.004 & 0.000 & 0.944 & 0.039 & 0.003\\
+\cline{2-9}
+ &  & $\gamma_0$ & -0.045 & 0.988 & 0.124 & 0.978 & 1.493 & 0.053\\
+\cline{3-9}
+ &  & $\beta_1$ & 0.728 & 517.389 & 0.879 & 0.974 & 5.976 & 0.504\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.024 & 7.437 & 0.051 & 0.954 & 0.838 & 0.011\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & -0.001 & -4.550 & 0.000 & 0.946 & 0.039 & 0.018\\
+\cline{2-9}
+ &  & $\gamma_0$ & -0.117 & 2.557 & 0.196 & 0.984 & 1.759 & 0.112\\
+\cline{3-9}
+ &  & $\beta_1$ & 0.876 & 622.327 & 1.305 & 0.968 & 6.913 & 0.650\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.026 & 8.265 & 0.051 & 0.963 & 0.892 & 0.034\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & -0.001 & -5.340 & 0.000 & 0.949 & 0.043 & 0.055\\
+\cline{1-9}
+ &  & $\gamma_0$ & -0.057 & 1.249 & 0.127 & 0.968 & 1.454 & 0.038\\
+\cline{3-9}
+ &  & $\beta_1$ & 0.853 & 606.148 & 1.003 & 0.974 & 5.629 & 0.510\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.006 & 1.804 & 0.046 & 0.959 & 0.831 & 0.006\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -3.051 & 0.000 & 0.945 & 0.039 & 0.011\\
+\cline{2-9}
+ &  & $\gamma_0$ & -0.182 & 3.981 & 0.166 & 0.979 & 1.813 & 0.183\\
+\cline{3-9}
+ &  & $\beta_1$ & 0.979 & 695.352 & 1.325 & 0.967 & 6.758 & 0.782\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.020 & 6.425 & 0.050 & 0.956 & 0.871 & 0.037\\
+\cline{3-9}
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & -0.001 & -4.466 & 0.000 & 0.955 & 0.042 & 0.068\\
+\cline{2-9}
+ &  & $\gamma_0$ & -0.403 & 8.803 & 0.345 & 0.987 & 2.789 & 0.440\\
+\cline{3-9}
+ &  & $\beta_1$ & 1.050 & 745.735 & 1.504 & 0.951 & 7.357 & 0.887\\
+\cline{3-9}
+ &  & $\beta_2$ & 0.019 & 5.848 & 0.050 & 0.973 & 0.960 & 0.099\\
+\cline{3-9}
+\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & -0.003 & -18.904 & 0.000 & 0.975 & 0.052 & 0.200\\
+\hline
+\end{tabular}}
+\end{table}
+
+\end{knitrout}
 

### 2018-05-22 Documentation/ogtablesandtest.Rnw
Manuscript edits.

--- 2018-05-22 Documentation/manuscript.Rnw
@@
-% Predefine some figures
-
-<<echo = FALSE>>=
-# Creating dataframe to visualize - one subject's questions for 5 days
-split.form <- function(set, nrem = 2, bound = 0){
-
-set[set$Day >= bound, paste0("Q",1:8)] <- t(apply(set[set$Day >= bound,paste0("Q",1:8)], 1, function(x){
-    ind <- sample(1:8, nrem)
-    x[ind] <- NA
-    as.numeric(x)
-  }))
-
-  return(set)
-}
-@
-
-<<echo = FALSE>>=
-wave.des <- function(set, nmiss, ...) { # nmiss is the number of days each person would miss? 11?? Like, miss a fourth of the days?
-  id <- sample(2:45, size=nmiss)
-  for (i in 1:nmiss) {
-    set[set$Day %in% id[i], c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')] <- NA
-  }
-  return(set)
-}
-@
-
-<<warning=FALSE, echo = FALSE>>=
-cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
-fill <- matrix(1, 45, 8)
-dat <- data.frame(fill)
-colnames(dat) <- cols
-dat$Day <- seq.int(nrow(dat))
-set.seed(1234)
-split.dat <- split.form(dat)[1:8]
-#split.dat
-@
-
-<<warning=FALSE,message=FALSE,echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- split.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-
-#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
-fill <- matrix(1, 45, 8)
-dat <- data.frame(fill)
-colnames(dat) <- cols
-dat$Day <- seq.int(nrow(dat))
-set.seed(1234)
-alternate.split.dat <- split.form(dat, bound = 3)[1:8]
-#alternate.split.dat
-@
-
-<<warning=FALSE,message=FALSE,echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- alternate.split.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<warning=FALSE,echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-
-#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
-@
-
-<<echo=FALSE>>=
-set.seed(1234)
-wave.dat <- wave.des(dat,11)
-#wave.dat
-@
-
-<<echo=FALSE>>=
-library(ggplot2)
-library(dplyr)
-library(reshape2)
-datmelt <- wave.dat[1:8] %>% is.na %>% melt
-colnames(datmelt) <- c("Day","Question","Missing")
-#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
-datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")
-
-  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
-@
-
-<<echo=FALSE>>=
-cols <- c("Missing" = "red", "Observed" = "skyblue3")
-waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-@
-
-\RequirePackage{fix-cm}
-
-\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-
+\documentclass{article}
 \usepackage{graphicx}
@@
 \usepackage{tabu}
-% \usepackage{threeparttable}
-% \usepackage{threeparttablex}
-% \usepackage[normalem]{ulem}
-% \usepackage{makecell}
+\begin{document}
 
-\raggedbottom
+% Original Tables and Figures
 
-\journalname{Sankhya B}
+% Table 10
 
-\begin{document}
-%\SweaveOpts{concordance=TRUE}
+% \begin{table}[h!]
+% 	\centering
+% 	\caption{The Three Form PM Design}
+% 	\label{tab:table10}
+% 	\setlength{\tabcolsep}{1cm}
+% 	\begin{tabular}{c|cccc}
+% 		\toprule
+% 		& \multicolumn{4}{c}{Block} \\
+% 		Form & X & A & B & C \\
+% 		\midrule
+% 		1 & 1 & 1 & 1 & 0 \\
+% 		2 & 1 & 1 & 0 & 1 \\
+% 		3 & 1 & 0 & 1 & 1 \\
+% 		\bottomrule
+% 	\end{tabular}
+% \end{table}
+
+% Table 11
+
+% \begin{table}[!h]
+% 	\centering
+% 	\caption{The Wave Missingness PM Design}
+% 	\label{tab:table11}
+% 	\setlength{\tabcolsep}{0.75cm}
+% 	\begin{tabular}{c|ccccc}
+% 		\toprule
+% 		& \multicolumn{5}{c}{Month} \\
+% 		Participant & 1 & 2 & 3 & 4 & 5 \\
+% 		\midrule
+% 		1 & 1 & 0 & 1 & 0 & 1 \\
+% 		2 & 1 & 1 & 0 & 1 & 0 \\
+% 		3 & 0 & 0 & 1 & 1 & 1 \\
+% 		4 & 1 & 1 & 1 & 0 & 0 \\
+% 		\bottomrule
+% 	\end{tabular}
+% \end{table}
+
+Tables for paper
 
@@
   collapse_rows(columns = 1:2, latex_hline = "full") %>%
-  kable_styling(latex_options = c("scale_down","hold_position"))
+  kable_styling(latex_options = c("scale_down","HOLD_position"))
 @
@@
   collapse_rows(columns = 1:2, latex_hline = "full") %>%
-  kable_styling(latex_options = c("scale_down","hold_position"))
+  kable_styling(latex_options = c("scale_down","HOLD_position"))
 @
 
-\title{Comparing Different Planned Missingness Designs in Longitudinal Studies}
-
-\author{Josephine Wood \and Gregory J. Matthews \and Nicholas Illenberger \and Jennifer Pellowski \and Ofer Harel}
-
-\institute{J. Wood \and G. J. Matthews
-          \at Loyola University Chicago \\
-          1032 W. Sheridan Rd.\\
-          Chicago IL, 60660 USA\\
-          Tel: (773)508-3558
-          \and
-          N. Illenberger \and O. Harel 
-				\at University of Connecticut \\
-						215 Glennbrook Rd. Unit 420\\
-						Storrs CT, 06269-4120 USA
-              Tel: (860)486-6989 \\
-		      \email{ofer.harel@uconn.edu}  
-					\and
-					J. Pellowski
-					\at International Health Institute\\ 
-					Brown School of Public Health 
-					\and J. Pellowski 
-					\at Department of Psychiatry and Human Behavior\\
-					The Warren Alpert Medical School of Brown University.  
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-Planned Missingness (PM) designs, in which researchers deliberately collect only partial data, have enjoyed a recent growth in popularity.
-Among other benefits these designs have been proven capable of reducing the study costs and alleviating participant burden.
-Past research has shown that Split Form PM designs can be effective in simplifying complex surveys while Wave Missingness PM designs act similarly for Longitudinal studies.
-However, less work has been done to inform how to implement PM structures into studies which incorporate elements of both survey and longitudinal designs.
-Specifically, in studies where a questionnaire is given to participants at multiple measurement occasions the best way to design missingness is still unclear.
-To address this deficiency, data in this hybrid format was simulated under both Split Form and Wave Missingness PM structures.
-Multiple Imputation techniques were applied to estimate a multilevel logistic model in each of the simulations.
-Estimated parameters were compared to the true values to see which PM design allowed us to best capture the true model.
-The results of this study indicate that, compared to the Split Form Design, the Wave Missingness design consistently performed less effectively in capturing the multilevel model.
-Thus, in the context of longitudinal surveys this study recommends the use of Split Form missingness designs, which performs well under a number of different conditions.
-
-\keywords{Planned Missingness \and Split Form \and Multiform \and Wave Missingness \and Multiple Imputation \and Missing Data.}
-\end{abstract}
-
-\section{Introduction}
-\label{intro}
-Planned Missingness (PM) designs are a type of experimental design in which some of the data is predetermined to be missing.
-While it may seem counterproductive to deliberately omit data from the collection process, PM designs have been shown to reduce both participant burden \citep{graham2006planned, saris20048} and the costs of a study \citep{graham2001planned}.
-Moreover, PM designs can actually increase the quality of collected data by increasing the breadth of a study \citep{little2013planned} as well as decreasing the effects of assessment reactivity and rates of unplanned missingness \cite{harel2015designed}.
-We further note that while PM designs decrease the efficiency of estimators \citep{rhemtulla2016asymptotic}, decreasing the cost per participant may allow researchers to enroll more participants in a study, offsetting some of the efficiency loss.
-\par
-
-There have been many different incarnations of the PM design, each crafted to best suit the study at hand.
-For example, PM designs have been used in the study of longitudinal growth curves \citep{graham2001planned, mcardle1997expanding}, business research \citep{shoemaker1973principles}, behavioral studies \citep{harel2015designed}, biostatistics \citep{andres2006partial, wacholder1994partial}, and educational assessments \citep{zeger1997efficient, sirotnik1977incidence}.
-This paper focuses on two of the simplest and most applicable PM designs; the Split Form design \citep{raghunathan1995split} and the Wave Missingness design \citep{little2013planned}.
-While this paper covers these designs in more detail later, broadly speaking, the Split Form design entails measuring fewer points on a single measurement occasion \citep{raghunathan1995split}.
-The Wave Missingness design, on the other hand, requires missing an entire measurement occasion within a longitudinal study \citep{graham2001planned}.
-
-The issue we concern ourselves with arises when a longitudinal study requires multiple items to be collected at each measurement occasion.
-When implementing a multi-level regression model in this situation, we investigate which planned missingess design is more efficient and accurate.
-Previous research indicates that for the estimation of correlated latent growth curve models use of the three-form PM design, a special case of Split Form designs \citep{raghunathan1995split}, resulted in low bias on parameter estimates or standard error and high efficiency when compared with wave missingness designs \citep{rhemtulla2014planned}.
-As our model of interest is a mixed effects model, however, we can not be sure that this result will hold.
-\par
-
-To answer our question we performed a simulation study from data obtained in longitudinal research on HIV medication adherence and alcohol-interactivity beliefs \citep{pellowski2016alcohol}.
-For the PM designs mentioned we simulated sample data and then used multiple imputation (MI) \citep{little2014statistical}  techniques to analyze the data.
-The PM methods were subsequently evaluated through the assessmemt of the average bias, percent bias, mean squared error, coverage rates, confidence interval length, and estimated fraction of missing information (FMI) \citep{little2014statistical} for parameter estimates in a multilevel model.
-To make the results generalizable, the experiment was repeated under multiple scenarios: increased sample size, low inter-survey correlation, and high time effect.
-\par
-
-To delineate the remainder of this paper, in Section 2 we go into more depth on the two PM designs previously mentioned and then move into a discussion on the modern Multiple Imputation technique for dealing with missing data.
-Next, in Section 3 we briefly describe the dataset we worked with and our method of simulation before moving on to the results of our analyses in Section 4 and a discussion in the final section.
-\par
-
-\section{Designs and Methods}
-\label{sec:1}
-\subsection{Split Form Design}
-\label{sec:1.1}
-
-Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are very aptly named.
-Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions.
-How these subsets are chosen varies.
-A common form setup is three-form Block Design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C.
-Each form of the survey includes the X block as well as two of the remaining blocks.
-A participant is then given a different form each day of the study.
-Designing the forms in this manner allows researchers to estimate the relationship between any chosen items, regardless of their blocks.
-For example, this allows the relationship between an item in block A and another in block C to be estimated and examined.
-\par
-
-An important consideration here is question distribution. The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
-Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}.
-On the other hand, placing the most predictive variables in the X-block allows Multiple Imputation to more effectively impute missing values from the other blocks \citep{gottschall2012comparison}.
-Similarly, it is good practice to place variables which are predictive of each other in separate blocks \citep{gottschall2012comparison}.
-While this approach provides researchers more freedom when forming the surveys, the puzzle of question distribution introduces new concerns.
-When the question groupings are not obvious, pilot studies may be necessary to determine the predictive potential of and relationships between variables.
-The cost and burden associated with an item must also be considered when deciding which block to place it in.
-For example, if a critical item is overly expensive or difficult to obtain we may be better off excluding it from the X-block \citep{little2013planned}.
-\par
-
-In addition, the number of blocks must be determined.
-Including more blocks in the design allows further increased missingness \citep{graham2006planned}.
-While increasing missingness may allow for further reductions in burden and cost, researchers must consider the disadvantages of more blocks.
-As more blocks are added, the number of possible forms increases.
-For example, consider two research teams.
-The first team divides their survey into an X-block and three other blocks of equal size, each containing 25\% of the survey.
-The second uses an X-block and nine others with 10\% of the items each.
-If the teams decide that each form will contain the X-block and two of the other blocks, then the second team will have 36 \textbf{(28?
-8 choose 2?)} total forms while the first team can proceed with 3.
-\textbf{This is all assuming that the blocks represent the optimal question grouping.
-If this is not known, to account for possible relationships and correlation between questions, the teams would need to consider all possible blocks and create forms for every block configuration.
-For a 7 question survey, with any one question X block and the other 6 split into three blocks, there are 75 possible block configurations.
-For each configuration, there are 3 possible forms.
-So, a team would need to consider 225 different forms.
-Instead of creating 225 distinct forms, a research team can follow a alternative Split Form method.} \par
-
-\textbf{This method, hereafter referred to as Split Form planned missingness and illustrated in \ref{fig:formillustration}, involves meaningfully selecting an X block of $n$ questions and then randomly excluding $k$ questions on each day.
-In a way treating each item as its own block \citep{silvia2014planned}.
-This is simple in theory, but for traditional paper surveys this is very difficult to execute.
-Fortunately, recent technological advances have made the use of electronic questionaires more readily accessible.
-In this environment form randomization can be automated and the creation of numerous unique forms is no longer an issue.} Using this method, researchers reap the benefits of including all possible variable relationships through increased forms without the difficulty caused by manually building these forms.
-\par
-
-\subsection{Wave Missingness Design}
-\label{sec:1.2}
-While Split Form missingness can be applied to many experimental designs, the Wave Missingness design \citep{little2013planned} is unique to studies with multiple measurement occasions, or "waves".
-Unlike the Split Form design, where participants miss a subset of items in a single measurement occasion, the Wave Design entails randomizing participants to miss a measurement occasion entirely.
-An example of a Wave Missing design is shown in Figure \ref{fig:formillustration} where data is collected monthly over the course of 5 months.
-However, each participant is only measured at three of these occasions.
-\par
-
-A relative advantage of the Wave Missingness design over the Split form design is increased control over the level of missingness.
-For studies with many measurement occasions, it is easy to make small changes to the amount of missing data.
-For example, the data described by \citet{pellowski2016alcohol} records measurements for 45 days.
-Missing eleven days here would result in 24.4\% missingness while missing twelve gives us 26.7\%.
-Further, Wave Missingness designs eclipse Split Form designs in terms of cost reduction \citep{little2013planned}.
-\par
-
-Another advantage of this design is many longitudinal study designs already use the Wave Missingness structure \citep{little2013planned}.
-Cohort Sequential Designs require cohorts of different ages to be followed longitudinally in such a way that the information from one cohort can be used to impute values for another \citep{little2013longitudinal, duncan2013introduction}.
-For example, there were three cohorts of ages 10, 11, and 12 at baseline and measured annually for four years.
-Although measurement only occurs at four waves we can frame this as a six-wave study where the 10-year old cohort has missing values at waves five and six, the 11-year old cohort at waves one and six, and the 12-year old cohort at waves one and two.
-Because the 10-year old cohort is the only group observed at the first wave, the missing values for the other groups are imputed using this information.
-By continuing in this manner the data that was collected over a four year period is extended it to cover six years, accelerating the study.
-The setup of this type of study is demonstrated in Table \ref{tab:cohort}, where "1" and "0" respectively indicate an included and excluded wave.
-\par
-
-\begin{table}[H]
-	\centering
-	\caption{Cohort Sequential Design}
-	\label{tab:cohort}
-	\setlength{\tabcolsep}{0.5cm}
-	\begin{tabular}{c|cccccc}
-		\toprule
-		& \multicolumn{6}{c}{Age} \\
-		Participant & 10 & 11 & 12 & 13 & 14 & 15 \\
-		\midrule
-		1 & 1 & 1 & 1 & 1 & 0 & 0\\
-		2 & 0 & 1 & 1 & 1 & 1 & 0\\
-		3 & 0 & 0 & 1 & 1 & 1 & 1\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Developmental time-lag models \citep{mcardle1997expanding} use the Wave Missingness structure, as well.
-As shown in Table \ref{tab:devtimelag}, researchers observe participants at only two measurement occasions, varying the length between occasions for each participant, and then treat this two-time-point data as multi-time-point data with missing values.
-Under this framework they impute these missing values and estimate growth curve models.
-Estimating this type of model would normally require measuring participants at many time points.
-However, under the Wave Missingness design this is accomplished with only two measurement occasions per participant.
-These designs exemplify how useful the Wave Missingness structure is in accelerating longitudinal studies.
-\par
-
-\begin{table}[H]
-	\centering
-	\caption{Developmental Time-Lag Setup}
-	\label{tab:devtimelag}
-	\setlength{\tabcolsep}{0.75cm}
-	\begin{tabular}{c|cccc}
-		\toprule
-		& \multicolumn{4}{c}{Wave} \\
-		Participant & 1 & 2 & 3 & 4 \\
-		\midrule
-		1 & 1 & 1 & 0 & 0 \\
-		2 & 1 & 0 & 1 & 0 \\
-		3 & 1 & 0 & 0 & 1 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\subsection{Altered Split Form}
-
-The Split Form planned missingness method can be modified to include the benefits of complete cases seen in Wave Missingness in what may be called Altered Split Form.
-In this method, the researcher asks participants all questions on the first $n$ days of the study.
-Thereafter, the survey design reverts to regular Split Form.
-This method allows the researcher to collect $n$ complete cases from each participant, aiding in the imputation process after surveys are administered.
-Altered Split Form, and the other planned missingness methods, is illustrated in Figure \ref{fig:formillustration} below.
-
-<<formillustration, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig.keep = TRUE, fig.pos = "H">>=
-require(gridExtra)
-grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
-@
-
-\subsection{Multiple Imputation}
-\label{sec:1.3}
-\subsubsection{Missing Data Mechanisms}
-\label{sec:1.3.1}
-Before describing Multiple Imputation and how it can be applied to PM designs it is important to first understand how data become incomplete.
-Suppose we have a dataset, $Y_{com}$, with some missing values.
-We define the missingness, $R$, to be an indicator variable which equals 0 where $Y_{com}$ is observed and 1 where the corresponding value in $Y_{com}$ is missing.
-Missing data mechanisms describe the proposed probabilistic relationship between $R$ and the values in $Y_{com}$, observed or unobserved \citep{little2014statistical}.
-\par
-
-The first missing data mechanism, missing at random (MAR), was defined by \citet{rubin1976inference}.
-Data are considered MAR when the missingness does not depend on unobserved values but may depend upon other observed variables.
-For instance, if men are less likely to report their incomes than women but the level of income itself does not affect the probability of reporting, then we can say the missingness govern income is MAR.
-\par
-
-Later, \citet{little2014statistical} described two additional mechanisms which lead to missing values: missing completely at random (MCAR) and missing not at random (MNAR) \citep{little2014statistical}.
-The first, MCAR, is used to describe a situation in which the missingness is independent of the observed or unobserved data.
-That is, the missing values are simply a random subset of the full data.
-On the other hand, data is said to be MNAR when the missingness is related to the unobserved data; in a survey people may be less willing to provide their income if it is extremely high or low, for example.
-\par
-
-If we have prior knowledge concerning the relationship between unobserved values, indicated by $R$, and the observed values, then Multiple Imputation can yield efficient estimates even under MNAR \citep{harel2007multiple}.
-However, because this is not typically the case, MI is most often implemented when data is MCAR or MAR \citep{little2014statistical}.
-\par
-
-As a consequence of allowing researchers to decide which values in a dataset are observed and unobserved, PM designs grant control over the missing data mechanism.
-Because of this, MI is an appealing option for researchers utilizing a PM design.
-If implemented properly, data should conform to either the MCAR or MAR assumption.
-For instance, if medical researchers decide not to collect blood pressure on a completely random subset of patients there is no reason to believe the missing blood pressures differ significantly from the observed ones.
-This fact allows for the use of MI and other modern missing data techniques such as the Full Information Maximum Likelihood approach \citep{dempster1977maximum} \par
-
-\subsubsection{The Multiple Imputation Procedure}
-\label{sec:1.3.2}
-Multiple Imputation is used to obtain statistically valid inferences in spite of missing data.
-MI works by replacing unobserved values with a set of plausible values in a way which allows us to account for uncertainty in the imputation process.
-Repeatedly using an imputation technique, every missing value in the incomplete dataset is replaced with a fixed number of imputed values.
-This process allows for the creation of multiple complete datasets, on which users can run complete-data procedures.
-If, for instance, we imputed $M$ possible values for every missing value we would obtain $M$ different completed datasets.
-Once created, the analysis of interest can be performed on each of them and, using rules defined by \citet{little2014statistical} and \citet{rubin2004multiple}, combine the results to obtain a single inference.
-\par
-
-Suppose we are interested in estimating a certain parameter such as the mean of a variable or a regression coefficient.
-If $\theta$ is the parameter of interest, let $\widehat{\theta_1}, \widehat{\theta_2}, ...
-\widehat{\theta_M}$ be the estimates of $\theta$ and let $S_1, S_2, ...
-S_M$ be the corresponding estimated standard errors from the $M$ imputed datasets.
-We can aggregate these results using the combining rules specified by \citet{little2014statistical} and \citet{rubin2004multiple}.
-\par
-The overall MI estimate of $\theta$ is defined as,
-
-\begin{equation}
-\widehat{\theta} = \sum_{n=1}^{M} \widehat{\theta_n}.
-\end{equation}
-
-From here we can compute the sample variance of this estimate by calculating the between-imputation component, $B_M = \frac{1}{(M-1)}\sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2$, and the within-imputation component, $W_M = \frac{1}{(M)}\sum_{n=1}^{M} S_n^2$.
-These components are combined to obtain the overall sample variance of our MI estimate as follows:
-
-\begin{equation}
-T_M = W_M + \frac{M+1}{(M)}B_M.
-\end{equation}
-
-These equations form the basis of Rubin's combining rules and provide unbiased parameter estimates accounting for the inherent uncertainty in the imputation process \citep{raghunathan2015missing}.
-For a more in depth explanation of these methods we refer readers to \citet{little2014statistical}.
-\par
-
-When using Multiple Imputation, researchers must decide on the number of imputations, $M$, to use.
-Generally, as the level of missingness decreases the number of imputations needed does as well.
-If less than 20\% of the requisite data is missing, for instance, five or tien imputations will suffice \citep{raghunathan2015missing}.
-However, at its roots, MI is a simulation technique and thus, the greater $M$ is the more stable our estimates become \citep{harel2007inferences}.
-\citet{graham2007many} recommend that if computational power is not a limiting factor, then setting $M=100$ is good practice.
-\par
-
-\section{Data and Simulations}
-\label{sec:2}
-\subsection{Data}
-\label{sec:2.1}
-The dataset the simulations are based on originated in a study by \citet{pellowski2016alcohol}.
-The data was collected in an attempt to determine the day-level relationship between alcohol use, its interactive toxicity beliefs, and adherence to antiretroviral therapy (ART) amongst patients with HIV.
-Previous studies note that alcohol use combined with the perception that mixing alcohol and ARTs can cause adverse effects, correlated with non-adherence to ARTs \citep{kalichman2009prevalence, kalichman2012alcohol}.
-However, \citet{pellowski2016alcohol} pointed out that past research collected data over extended periods of time, preventing the identification a day-level interaction.
-Unlike others, this study was able to determine whether alcohol use and missed medication doses occurred on the same day.
-\par
-
-The study employed an observational cohort design, following sixty participants over forty-five consequtive days via a daily questionnaire.
-Questions in the survey concerned livelihood insecurities from the previous day as well as alcohol use.
-The analysis included eight particular questions: two binary questions on housing insecurity, four binary questions on food insecurity, and two questions concerning alcohol use (one binary variable and one count variable).
-The exact questions can be found in Table \ref{tab:survey_qs}.
-\par
-
-\begin{table}[H]
-	\centering
-	\caption{Survey Questions}
-	\label{tab:survey_qs}
-	\begin{tabular}{cp{6.5cm}c}
-		\toprule
-		Item Number & Question & Responses\\
-		\midrule
-		1 & I worried about having a place to stay yesterday. & 1.Yes $\>$ 2.No \\
-		2 & I could not get to where I needed to go yesterday. & 1.Yes $\>$ 2.No \\
-		3 & I worried about my food running out yesterday. & 1.Yes $\>$ 2.No \\
-		4 & I ate less than I needed to yesterday. & 1.Yes $\>$ 2.No \\
-		5 & I was hungry, but did not eat because I couldn't afford food. & 1.Yes $\>$ 2.No \\
-		6 & I got food from a pantry, church, agency, friend or the street yesterday. & 1.Yes $\>$ 2.No \\
-		7 & Did you drink alcohol yesterday? & 1.Yes $\>$ 2.No \\
-		8 & How many alcohol drinks did you have yesterday? & 0-20 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Beyond the daily questionnaire, data was also collected through a computer-assisted interview on behavioral, psychosocial, and cognitive factors (ex.
-Income, alcohol-toxicity beliefs, education, etc.) which have been shown to be associated with medication adherence.
-These values were only collected at baseline and are considered time independent.
-The variables from this assessment used in our analysis concerned education level, income, age, beliefs about the interactivity of alcohol with ART medication, depression, and alcohol abuse.
-\par
-
-\subsection{Simulations}
-\label{sec:2.2}
-The first step in the process of creating the simulated datasets was to obtain parameter estimates from \citet{pellowski2016alcohol} and to quantify the relationships between variables.
-These estimated relationships were treated as the "true" relationships and \textbf{one thousand (number or no???)} samples were drawn using these parameters.
-The purpose of simulating these datasets was to see how well they captured the true relationship between daily medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score).
-Specifically, \\
-
-Let $Y_{ij} \sim binomial(n_{ij},p_{ij})$ be whether the $j$th person missed their medication dose on the $i$th day.
-Then the model of interest is the random intercept model with time effect described as follows:
-\begin{align*}
-logit(p_{ij}) &= \beta_{0j} + \beta_1DrinkYN_i + \beta_2ZAlcTox_i +\beta_3Day
-\end{align*}
-where $\beta_{0j} = \gamma_0 + \alpha_j$ and $\alpha_j \sim \mathcal{N}(0,\sigma_\alpha^2)$. \\ \\ 
-Additionally, note: \\ \\
-$p_{ij} = 1$ when participant $p$ did not adhere to the ART on day $i$, 0 otherwise. \\
-$DrinkYN = 1$ if participant $p$  drank on day $i$, 0 otherwise.\\
-$ZAlcTox =$ participant $p$'s Z-transformed score on an alcohol-antiretroviral interactive toxicity scale developed by Kalichman \cite{kalichman2009prevalence}. \\
-$Day =$ Day $i$ of the study, 0-44. \\
-$j =$ participant index, 1-60. \\
-
-Based on the observed data, the true values of the parameters, $\gamma_0$, $\beta_1$, $\beta_2$, $\beta_3$, and $\sigma_\alpha^2$ were found to be -2.29, 0.28, 0.64, 0.01, and \textbf{1.0???} respectively.
-\par
-Once the samples were drawn, they were transformed under the three different missingness structures.
-These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed.
-To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in \textbf{Table \ref{tab:table14} (do we want the illustration here instead?
-or in both places?)}.
-As in the previous tables, "1" indicates an observed occasion while "0" indicates a missing one.
-We see that the Split Form design entails missing two items on each of the days.
-The altered Split Form, while similar, is fully measured on two of the measurement occasions.
-Because there are days which are fully observed, the relationships between variables may be clearer, allowing the imputation procedure to run more effectively.
-On the other hand, the Wave Missingness design shows two days in which no questions are asked but the full questionnaire is given on the remaining days.
-\par
-
-\begin{table}[H]
-	\centering
-	\caption{Different Planned Missingness Designs}
-	\setlength{\tabcolsep}{0.45cm}
-	\label{tab:table14}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|ccccc}
-		\toprule
-		Design & Day & Q1 & Q2 & Q3 & Q4 & Q5 \\
-		\midrule
-		\multirow{5}{*}{Split Form}
-		& 1 & 1 & 1 & 0 & 0 & 1 \\
-		& 2 & 0 & 0 & 1 & 1 & 1 \\
-		& 3 & 0 & 1 & 1 & 0 & 1 \\
-		& 4 & 1 & 0 & 1 & 1 & 0 \\
-		& 5 & 1 & 1 & 0 & 1 & 1 \\
-		\midrule
-		\midrule
-		\multirow{5}{*}{Altered Split Form}
-		& 1 & 1 & 1 & 1 & 1 & 1 \\
-		& 2 & 1 & 1 & 1 & 1 & 1 \\
-		& 3 & 0 & 0 & 1 & 1 & 1 \\
-		& 4 & 1 & 1 & 0 & 1 & 0 \\
-		& 5 & 0 & 1 & 1 & 0 & 1 \\
-		\midrule
-		\midrule
-		\multirow{5}{*}{Wave Missingness}
-		& 1 & 1 & 1 & 1 & 1 & 1 \\
-		& 2 & 0 & 0 & 0 & 0 & 0 \\
-		& 3 & 1 & 1 & 1 & 1 & 1 \\
-		& 4 & 1 & 1 & 1 & 1 & 1 \\
-		& 5 & 0 & 0 & 0 & 0 & 0 \\
-		\bottomrule
-	\end{tabular}
-	\hspace*{-1cm}	
-\end{table}
-
-Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions.
-Previous work by \citet{rhemtulla2014planned} found that for low levels of missingness Split Form design outperforms the Wave Missingness design in capturing latent growth curve model parameters.
-However, because only low-levels of missingness are tested it is unknown whether this relationship holds at moderate or high levels.
-By including these different levels of missingness the performance at all levels of the missingness spectrum will be measured.
-\par
-Once missingness was created, Multiple Imputation techniques were applied to estimate the relationship between medication adherence and the other variables in our model.
-Because the missing data mechanism is controled, the data is known to be MCAR.
-This fact allows for the principled use of MI techniques.
-Using the R package $\{$mice$\}$ \citep{mice2011imputation} the binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching \textbf{was it???
-i don't think so, it was in the X block originally but double check!}.
-\par
-
-After imputing, a logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}.
-From here, the results from each PM design were evaluated based on bias, percent bias, mean squared error (MSE), coverage, confidence interval (CI) length, and the fraction of missing information (FMI).
-The FMI is a measure of how much of the MI sample variance comes from differences between imputations.
-In addition to comparing the results between each of the PM designs, the same analyses were also performed before missingness was imposed.
-\par
-
-When determining if the PM designs are performing sufficiently, it is important to consider how well the simulated samples performed before adding a missingness structure.
-For example, consider two full data samples with respective biases on the $\beta_1$ estimate of 0.13 and 0.15.
-Further, after imposing different PM design structures on these samples, the average biases are 0.14 and 0.15 respectively.
-It would be unfair to claim that the first PM design performed better than the second because, by chance, it was based off of a more representative sample.
-This fact was considered when determining the evaluation criteria.
-\par
-
-For bias, percent bias, and MSE we claimed that an increase of more than 40\% in these measurements after imposing missingness indicates that the PM design is inappropriate.
-For instance, if the complete data shows a percent bias of 10\%, anything higher than 14\% would be unacceptable.
-An increase of this size has the ability to negatively effect efficiency of our estimation.
-Based on the work of \citet{collins2001comparison} we also regard coverages of less than 90\% as unacceptable.
-If a 95\% CI has a true coverage of 90\% than the Type I error rate is double what it should be.
-Because MI accounts for uncertainty in the imputation process, coverages should be similar despite the added missingness.
-In terms of confidence interval lengths, if one PM design provides similar rates of coverage to another while maintaining shorter intervals than this is considered the better of the two methods.
-For equal coverage rates, shorter intervals imply more power.
-The FMI, which quantifies the uncertainty in our imputation process, is simply reported for each PM design.
-While less uncertainty in the imputations can be beneficial, less variation does not necessarily imply accuracy.
-Thus, FMI should be taken in the context of the other measurements.
-\par
-
-This process was repeated under the three modified simulation scenarios mentioned in the following sections.
-Note that while typically these PM designs would be compared against the results obtained using a complete case analysis \citep{rhemtulla2016asymptotic}, this approach was avoided as it would fundamentally alter the form of the data.
-Specifically, complete case analysis removes any observation with any missing values.
-Then, for the Split Form design this would remove all observations.
-In the Wave Missingness setup, complete case analysis would shorten the length of the longitudinal study.
-If a participant was missing values on 11 of the 45 days, then complete case analysis would have made the data resemble a longitudinal study held over 34 days.
-Hence, this comparison is invalid.
-\par
-
-\subsubsection{Increased Sample Size}
-In order to evaluate the impact of sample size on estimation, the original sample size of 60 participants was expanded to 120.
-The rest of the simulation process was carried out as before.
-As noted earlier, the cost savings gleaned from the PM designs could allow us to enroll more participants.
-Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, researchers can design missingness in whichever method is most convenient.
-Furthermore, because Wave Missingness allows for greater savings, an increase in sample size is more reasonable for that type of missingness.
-\par
-\subsubsection{Low Inter-Survey Correlation}
-For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best.
-To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days.
-While this fact was accounted for in the original simulations, it was not in this set of simulations.
-If the probability of answering "yes" on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables.
-This implies that each of the questions are conditionally independent of each other given the baseline variables.
-If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal.
-To investigate this, the correlation of the variables was scaled by 0.5.\par
-\subsubsection{High Time Effect}
-In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable.
-To do this we changed the value of the parameters $\gamma_0$, $\beta_1$, $\beta_2$, and $\beta_3$ to -4.56, 0.14, 0.32, and 0.01 respectively.
-Note that instead of increasing the value of $\beta_3$, the slope for time effect, all the other parameters were decreased.
-This was done because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1.
-Decreasing the other variables effects ensured that time has a disproportionate effect without this problem.
-The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point.
-\par
-
-\section{Results}
-\label{sec:3}
-\subsection{Primary Simulation}
-\label{sec:3.1}
-The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.28$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.01$.
-The effects of the variables here are comparable to those found in the original dataset.
-This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design.
-Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:prelim} \textbf{not here yet}.
-Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
-
-<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
-#prelim
-@
-
-Of note in the complete-data primary analysis is that the coverage of the 95\% CIs is larger than expected for the parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large.
-This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}.
-Nevertheless, this must be kept in mind when analyzing the results from the PM designs provided in Table \ref{tab:primary}.
-\textbf{In Table \ref{tab:primary} as in Tables \ref{tab:sampsize}, \ref{tab:lowcorr}, and \ref{tab:hightime} bold values indicate ``unacceptable" results.} That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
+Table \ref{tab:primary}
 
@@
 
-For the Split Form and Altered Split Form designs seen in Table \ref{tab:table3}, note that the greatest loss in efficiency was on the $\beta_1$ estimate.
-While the CI coverage remained high at all levels of missingness for the two designs, the bias, percent bias, and MSE reached unacceptable levels at the high missingness level.
-We also point out that the Altered Split Form design did not perform significantly better than the regular Split Form design.
-While some individual measurements outperformed those from the Split Form design, bias on $\beta_1$ for example, it underperformed in others, such as percent bias on $\beta_3$.
-In reference to the FMI on the $\beta_1$ estimate, we can see that at low and medium missingness both Split Form designs performed well.
-That is, there was less variance in the results from th imputed datasets than we expected given the amount of missing data.\par
-
-Towards the bottom of Table \ref{tab:primary}, the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at both medium and high levels of missingness.
-Moreover, at high levels of missingness coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.
-Additionally, we see that CI length for the $\beta_1$ estimate was roughly equal across all designs, despite the fact that the Wave Missingness design provided more biased estimates.
-\par
-
-\subsection{Increased Sample Size}
-\label{sec:3.2}
-In the next simulation scenario the sample size was increased to 120 participants.
-All parameter values were held the same as in the original simulation.
-Table \ref{tab:prelim} \textbf{not here yet}, again, contains the results of the analysis before applying any PM design.
-The results of the full-data simulations are compared to those obtained from the PM designs, shown in Table \ref{tab:sampsize}.
-\par
+Table \ref{tab:sampsize}
 
@@
 
-First notice the bias of all parameters is lower than in the smaller sample size simulations.
-Next, the Split Form design performed similarly well as in the first.
-At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable.
-However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:prelim} \textbf{not here yet}.
-The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088.
-Furthermore, the percent bias on the $\beta_1$ estimate is not seriously different from that obtained in the small sample scenario.
-For example, at medium levels of missingness the percent bias on $\beta_1$ is 23.86\% while for the smaller sample it was 23.75\%.
-Similarly to the Split Form design, the Altered Split Form Design also provided unacceptable results for the MSE of the $\beta_1$ estimate at medium missingness and unacceptable bias, percent bias, and MSE at high levels.
-\par
-For the Wave Missingness design we continue to see the issues observed in the small sample simulations.
-That is, for the $\beta_1$ estimate the measurements at medium and high levels of missingness are unacceptable and a steep drop off in coverage probability occurs for the 95\% CIs.
-In fact, at medium and high levels of missingness the coverages drop to 85.5\% and 82.0\%.
-The $\gamma_0$ parameter also continues to be estimated poorly at high levels of missing data under the Wave Missingness design.
-\par
+Table \ref{tab:hightime}
 
-\subsection{Low Inter-Survey Correlation}
-\label{sec:3.3}
-For the next set of simulations sample size returned to 60 participants but the level of inter-survey correlation decreased.
-The results obtained from the full data simulations are provided in Table \ref{tab:prelim} \textbf{not here yet} while the results from the PM designs are given in Table \ref{tab:lowcorr}.
-\par
+<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
+hightime
+@
+
+Table \ref{tab:lowcorr}
 
@@
 
-For the Split Form design it is important to notice that the efficiency of the $\beta_1$ estimate decreases much more rapidly than in the original simulations where survey questions were predictive of one another.
-For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be 0.150 and 0.276 at high levels.
-This left us with an increase in average bias of 0.126.
-Looking at the same increase in the original simulations, note that the bias only increased by 0.071.
-This loss in efficiency is seen in the other measurements on the $\beta_1$ estimate as well.
-Moreover, note that the Split Form design performs unacceptably in terms of bias, percent bias, and MSE at medium levels of missingness.
-This was not the case in the other missingness scenarios.
-\par
-
-The Altered Split Form design at medium levels of missingness yielded an MSE outside of the acceptable range and at high levels bias, the percent bias are unacceptable as well.
-Additionally, the coverage of the $\beta_1$ CIs was quite a bit higher than in the full-data simulations.
-That is, while the coverage probability obtained in the full-data simulations was 94.5\%, under this Altered Split Form design the coverages are 95.5\%, 97.0\%, and 96.0\% at low, medium, and high levels of missingness respectively.
-\par
-
-Under Wave Missingness the issues of unacceptable bias, percent bias and MSE occur.
-However, at low levels of missingness, the coverage of the $\beta_1$ estimate was fairly good (96.5\% compared to 94.5\% in the full data).
-Sufficient coverage did not hold through increased missingness as coverage dropped to 89.5\% in the high missingness scenario.
-As in other scenarios, the CI lengths produced under the Wave Missingness design are similar to those produced in the Split Form designs despite an increase in bias.
-However, here the increase in bias is less dramatic than in other scenarios.
-For example, at high levels of missingness in the original simulations the average bias on the $\beta_1$ estimate was 0.065 higher for the Wave Missingness design (at 0.290) than in the Split Form design (0.225).
-In this simulation scenario that same difference was only 0.027.
-Moreover, while the estimation of $\gamma_0$ was unacceptable at high levels of missingness in the other simulation scenarios, here it was in the acceptable range.\par
-
-\subsection{High Time Effect}
-\label{sec:3.4}
-In the final scenario we tested to see how the PM designs would capture a model where time had a disproportionately large effect on Missed Dose.
-In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$.
-The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:hightime}.
-\par
-
-<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
-hightime
-@
-
-The effects of imposing Split Form missingness in this high time effect scenario are similar to those under the low inter-survey correlation scenario.
-At low levels of missingness bias, percent bias, MSE, and coverage for $\beta_1$ are all within the acceptable range.
-At medium and high levels of missingness bias, percent bias, and MSE are unacceptably high.
-\par
-
-The Altered Split Form design performed slightly better than the normal Split Form design under this simulation scenario.
-Note, however, that while the normal Split Form design provided unacceptable bias and percent bias for the $\beta_1$ estimate at medium levels of missingness, this was not true of the Altered Split Form design.
-Additionally, observe that at medium and high levels of missingness there was an improvement under the Split Form design in the CI lengths for the $\beta_1$ estimate.
-In the Split Form design the CI lengths were recorded as 0.981 and 1.433 at medium and high missingness.
-Under the Altered Split Form design these measurements were 0.903 and 1.381.
-\par
-
-In this simulation scenario, the Wave Missingness Design performs similarly to the Split Form and Altered Split Form designs at low levels of missingness.
-The bias, percent bias, MSE, and CI coverage for $\beta_1$ all performed acceptably using the Wave Missingness design at low levels of missingness.
-However, as missingness increases this design shows itself to be unsuitable in terms of estimating $\beta_1$ for the same reasons noted in the other scenarios.
-\par
-
-\subsection{Interpretation}
-\label{sec:3.5}
-We note two commonalities throughout our simulation scenarios.
-The first is that the Altered Split Form design consistently failed to produce better results than the normal Split Form design.
-Secondly, the Wave Missingness Design resulted in unacceptably poor estimation for anything but low levels of missingness.
-\par
-
-This first result, the lack of improvement seen in the Altered Split form design is surprising.
-By keeping a small number of measurement occasions fully observed we would have expected the imputation process to perform more effectively and improve our estimates.
-However, even factoring in the slight decrease in overall missingness, this design performed only equally as well as the normal Split Form design.
-This may be a result of the fact that the number of observations we left fully observed was small; only two out of the forty-five days (approximately 4.4\% of days).
-While it may be interesting to see if the inclusion of more fully observed days is capable of improving our estimates, perhaps keeping five days (11.1\%) fully observed, we would need to be careful about raising this number too high.
-If the cost or burden of observations is a limiting factor, then collecting full data on even 10\% of the days may be unnecessarily burdensome.
-\par
-
-Of larger concern, however, is the steep drop-off in estimating quality of the Wave Missingness design as missingness increased.
-In every scenario tested, the Wave Missingness design produced unacceptable bias, percent bias, and MSE at medium and high levels of missingness.
-In addition, despite increased bias on estimates with missing values, the length of confidence intervals for these estimates remained the same as in the Split Form design.
-This implies that there is an underestimation of the variances occurring at some point in the imputation process.
-This is supported by the fact that, generally, the fraction of missing information estimated in the Wave Missingness design tended to be smaller than that of the corresponding Split Form design.
-This can also explain the lower confidence interval coverages obtained using this design.
-At high levels of missingness none of the scenarios allowed the Wave Missingness design to obtain coverages above 90\%.
-This leads to the belief that many of the imputations are producing datasets which are similar in terms of the relationships between variables but that are not representative of the true relationships.
-Because of this, the use of Wave Missingness designs for anything but small levels of missing data cannot be recommended.
-\par
-
-Additionally, all PM designs under all scenarios performed within acceptable ranges when measuring the effects of variables which had no missing values ($\gamma_0, \beta_2, \beta_3$).
-This fact makes the increased sample size scenario promising for researchers.
-While our estimation of $\beta_1$ was similar in this scenario as in others, the estimation of the other model parameters improved by leaps and bounds.
-If a PM design is able to reduce costs by 50\% by introducing missingness, using these extra funds to recruit more participants may be a good idea for researchers whose analysis of interest involves variables that will not have missing values.
-\par
-
-\section{Discussion}
-\label{4}
-In this paper we performed a simulation study to test the ability of different PM designs to capture a multilevel logistic model under a longitudinal framework.
-We found that for low levels of planned missing data (about 25\% missingness), variations of the Split Form design and the Wave Missingness designs are all capable of estimating the parameters of the multilevel model reasonably well.
-As the level of missing data increases to 50\% and 75\%, however, the quality of estimates in all of the tested PM designs become unacceptable as we see rising parameter biases and confidence interval lengths.
-Moreover, we found that the quality of the Wave Missingness design depreciates much more rapidly than the other PM designs, providing higher parameter biases than the corresponding Split Form estimates and low confidence interval coverages (95\% confidence intervals with less than 90\% coverage in some cases).
-\par
-
-These facts warn against the use of Wave Missingness designs when the Split Form design can be easily substituted.
-If Wave Missingness must be used, as in the cohort sequential and developmental timelLag designs, the design must minimize the amount of missing data.
-For instance, in a cohort sequential design which attempts to stretch four-year data to cover a span of six years each cohort will have missing values at two of the six measurement occasions.
-This would result in about 33.3\% missingness.
-To ensure that the researcher's analyses are accurate, we would recommend an increase in the amount of time they follow participants, using five-year data instead of four-year data to cover the same period.
-While the recommendation to use low levels of missing data is especially true for Wave Missingness designs it also holds for the Split Form designs.
-While these designs tended to perform well for all parameters in the multilevel model at low levels of missingness this was not true when missingness was increased to around 50\%.
-\par
-
-For future research it may be useful to test a wider range of missingness.
-That is, while this study showed that the PM designs performed well when missingness was around 25\% and sometimes performed poorly when it was around 50\% it is unknown exactly when the estimation procedure breaks down.
-While only 25\% missing data is suggested here, if it was shown that these designs performed well at 40\% missingness, then researchers could substantially increase cost reduction and decrease participant burden beyond what our recommendations allow.
-Another worthwhile pursuit may be to see how hybrid PM designs perform.
-While it was found that Wave Missingness designs performed underwhelmingly, it would be interesting to investigatte a design containing fully missing days with the remaining days missing on some values would perform.
-This investigation may be particularly useful to researchers who wish to implement an accelerated longitudinal design but also have measures that are costly or burdensome which they would like to limit the collection of.
-\par
-
-To conclude we discuss the limitations of this analysis. DIFFERENT LIMITATIONS. NOT COMPUTING POWER.
-
-Hopefully, the results of this paper will serve to help researchers decide which PM design is most appropriate for their studies' needs.
-By illuminating the weaknesses of the Wave Missingness design, it is hoped that, unless it is explicitly required, researchers will opt instead to use a Split Form design.
-Furthermore, when researchers do implement a PM design we hope they follow our recommendation to err on the side of caution and keep the amount of missing data relatively low.
-\par
-
-%\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-\bibliographystyle{plainnat}
-\bibliography{citations}   % name your BibTeX data base
-
 \end{document}

### 2018-05-29 Documentation/manuscript.Rnw
Fixed the hard coded path problem.

@@
+\RequirePackage{fix-cm}
+
+\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+
+\usepackage{graphicx}
+\usepackage{mathptmx}      
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{cite}
+\usepackage{caption}
+\usepackage{natbib}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage[table]{xcolor}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+% \usepackage{threeparttable}
+% \usepackage{threeparttablex}
+% \usepackage[normalem]{ulem}
+% \usepackage{makecell}
+
+\raggedbottom
+
+\journalname{Sankhya B}
+
+\begin{document}
+%\SweaveOpts{concordance=TRUE}
+
+<<echo=FALSE>>=
+if (Sys.info()["user"] == "gregorymatthews") {
+  root <- "/Users/gregorymatthews/Dropbox/designedMissingnessGit/Results/"
+}
+
+if (Sys.info()["user"] != "gregorymatthews") {
+  root <- "~/GitHub/designedmissingness/Results/"
+}
+@
+
 % Predefine some figures
@@
 
-\RequirePackage{fix-cm}
+<<primary, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
 
-\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-
-\usepackage{graphicx}
-\usepackage{mathptmx}      
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{cite}
-\usepackage{caption}
-\usepackage{natbib}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage[table]{xcolor}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-% \usepackage{threeparttable}
-% \usepackage{threeparttablex}
-% \usepackage[normalem]{ulem}
-% \usepackage{makecell}
-
-\raggedbottom
-
-\journalname{Sankhya B}
-
-\begin{document}
-%\SweaveOpts{concordance=TRUE}
-
-<<primary, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
 library(kableExtra)
 library(dplyr)
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime0.RData")
+load(paste0(root,"tables20180509_60_1_high_hightime0.RData"))
 high <- d
 
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime0.RData")
+load(paste0(root,"tables20180509_60_1_med_hightime0.RData"))
 med <- d
 
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime0.RData")
+load(paste0(root,"tables20180509_60_1_low_hightime0.RData"))
 low <- d
@@
 library(dplyr)
-load("~/GitHub/designedmissingness/Results/tables20180509_120_1_high_hightime0.RData")
+load(paste0(root,"tables20180509_120_1_high_hightime0.RData"))
 high <- d
 
-load("~/GitHub/designedmissingness/Results/tables20180509_120_1_med_hightime0.RData")
+load(paste0(root,"tables20180509_120_1_med_hightime0.RData"))
 med <- d
 
-load("~/GitHub/designedmissingness/Results/tables20180509_120_1_low_hightime0.RData")
+load(paste0(root,"tables20180509_120_1_low_hightime0.RData"))
 low <- d
@@
 library(dplyr)
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime1.RData")
+load(paste0(root,"tables20180509_60_1_high_hightime1.RData"))
 high <- d
 
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime1.RData")
+load(paste0(root,"tables20180509_60_1_med_hightime1.RData"))
 med <- d
 
-load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime1.RData")
+load(paste0(root,"tables20180509_60_1_low_hightime1.RData"))
 low <- d
@@
 library(dplyr)
-load("~/GitHub/designedmissingness/Results/tables20180509_60_0.5_high_hightime0.RData")
+load(paste0(root,"tables20180509_60_0.5_high_hightime0.RData"))
 high <- d
 
-load("~/GitHub/designedmissingness/Results/tables20180509_60_0.5_med_hightime0.RData")
+load(paste0(root,"tables20180509_60_0.5_med_hightime0.RData"))
 med <- d
 
-load("~/GitHub/designedmissingness/Results/tables20180509_60_0.5_low_hightime0.RData")
+load(paste0(root,"tables20180509_60_0.5_low_hightime0.RData"))
 low <- d

### 2018-05-29 Documentation/manuscript.Rnw
Fixed Ofer typos suggestions.

@@
           \and
-          N. Illenberger \and O. Harel 
+          O. Harel 
 				\at University of Connecticut \\
@@
 					\at International Health Institute\\ 
-					Brown School of Public Health 
-					\and J. Pellowski 
-					\at Department of Psychiatry and Human Behavior\\
+					Brown School of Public Health\\
+					Department of Psychiatry and Human Behavior\\
 					The Warren Alpert Medical School of Brown University.  
@@
 While it may seem counterproductive to deliberately omit data from the collection process, PM designs have been shown to reduce both participant burden \citep{graham2006planned, saris20048} and the costs of a study \citep{graham2001planned}.
-Moreover, PM designs can actually increase the quality of collected data by increasing the breadth of a study \citep{little2013planned} as well as decreasing the effects of assessment reactivity and rates of unplanned missingness \cite{harel2015designed}.
+Moreover, PM designs can actually increase the quality of collected data by increasing the breadth of a study \citep{little2013planned} as well as decreasing the effects of assessment reactivity and rates of unplanned missingness \citep{harel2015designed}.
 We further note that while PM designs decrease the efficiency of estimators \citep{rhemtulla2016asymptotic}, decreasing the cost per participant may allow researchers to enroll more participants in a study, offsetting some of the efficiency loss.
@@
 
-Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are very aptly named.
+Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are aptly named.
 Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions.
@@
 An important consideration here is question distribution. The X-block, being included in every form, should contain either the variables of greatest interest or those with the most predictive ability.
+
 Placing central items in the X-block ensures they are always collected and minimizes the efficiency loss of our analyses \citep{thomas2006evaluation}.
@@
 If we have prior knowledge concerning the relationship between unobserved values, indicated by $R$, and the observed values, then Multiple Imputation can yield efficient estimates even under MNAR \citep{harel2007multiple}.
-However, because this is not typically the case, MI is most often implemented when data is MCAR or MAR \citep{little2014statistical}.
+However, because this is not typically the case, MI is most often implemented under MCAR or MAR assumptions \citep{little2014statistical}.
 \par
@@
 For instance, if medical researchers decide not to collect blood pressure on a completely random subset of patients there is no reason to believe the missing blood pressures differ significantly from the observed ones.
-This fact allows for the use of MI and other modern missing data techniques such as the Full Information Maximum Likelihood approach \citep{dempster1977maximum} \par
+This fact allows for the use of MI and other modern missing data techniques such as the Full Information Maximum Likelihood approach \citep{dempster1977maximum}.
+\par
 
@@
 If, for instance, we imputed $M$ possible values for every missing value we would obtain $M$ different completed datasets.
-Once created, the analysis of interest can be performed on each of them and, using rules defined by \citet{little2014statistical} and \citet{rubin2004multiple}, combine the results to obtain a single inference.
+Once created, the analysis of interest can be performed on each of them and, using Rubin's rules detailed in \citet{rubin2004multiple}, combine the results to obtain a single inference.
 \par
@@
 S_M$ be the corresponding estimated standard errors from the $M$ imputed datasets.
-We can aggregate these results using the combining rules specified by \citet{little2014statistical} and \citet{rubin2004multiple}.
+We can aggregate these results using the combining rules specified in \citet{rubin2004multiple}.
 \par
@@
 \begin{equation}
-\widehat{\theta} = \sum_{n=1}^{M} \widehat{\theta_n}.
+\widehat{\theta} = \sum_{n=1}^{M} \frac{1}{M} \widehat{\theta_n}.
 \end{equation}
@@
 Generally, as the level of missingness decreases the number of imputations needed does as well.
-If less than 20\% of the requisite data is missing, for instance, five or tien imputations will suffice \citep{raghunathan2015missing}.
+(IS THIS TRUE?) If less than 20\% of the requisite data are missing, for instance, five or ten imputations will suffice \citep{raghunathan2015missing}.
 However, at its roots, MI is a simulation technique and thus, the greater $M$ is the more stable our estimates become \citep{harel2007inferences}.
@@
 \par
-Once the samples were drawn, they were transformed under the three different missingness structures.
+Once the samples were drawn, missingness was added under three different structures.
 These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed.
@@
 
+FIX THIS: THIS SOUNDS LIKE WE ADDED MORE MISSINGNESS.
 Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions.
@@
 These facts warn against the use of Wave Missingness designs when the Split Form design can be easily substituted.
-If Wave Missingness must be used, as in the cohort sequential and developmental timelLag designs, the design must minimize the amount of missing data.
+If Wave Missingness must be used, as in the cohort sequential and developmental time lag designs, the design must minimize the amount of missing data.
 For instance, in a cohort sequential design which attempts to stretch four-year data to cover a span of six years each cohort will have missing values at two of the six measurement occasions.
@@
 
+\begin{acknowledgements}
+Nick Illenberger
+\end{acknowledgements}
+
 %\bibliographystyle{spbasic}      % basic style, author-year citations

### 2018-05-29 Documentation/manuscript.Rnw
Updated Manuscript.

@@
 % Predefine some figures
+<<echo = FALSE, message=FALSE>>=
+library(dplyr)
+library(kableExtra)
+load(paste0(root,"fullmods_60_1_high_hightime0.RData"))
+beta <- do.call(rbind,fullmods$beta)
+se <- do.call(rbind,fullmods$se) 
+se <- se[abs(beta[,2])<=10,]
+beta <- beta[abs(beta[,2])<=10,]
+
+#bias, percent bias, MSE, coverage, CI length
+bias <- apply(beta,2,mean) - pop.mod.coeffs[,1]
+pctbias <- (apply(beta,2,mean) - pop.mod.coeffs[,1])/pop.mod.coeffs[,1]
+mse <- apply(apply(beta,1,function(x){(x- pop.mod.coeffs[,1])^2}),1,mean)
+upper <- beta + qnorm(0.975)*se
+lower <- beta - qnorm(0.975)*se
+coverage <- rep(NA, 4)
+for (i in 1:4){
+coverage[i] <- sum(upper[,i] > pop.mod.coeffs[i,1] & lower[,i] < pop.mod.coeffs[i,1])/nrow(beta)
+}
+CIlength <- apply(upper - lower, 2 , mean)
+
+res60 <- data.frame(bias, pctbias, mse, coverage, CIlength)
+
+load(paste0(root,"fullmods_120_1_high_hightime0.RData"))
+
+#bias, percent bias, MSE, coverage, CI length
+beta <- do.call(rbind,fullmods$beta)
+se <- do.call(rbind,fullmods$se) 
+se <- se[abs(beta[,2])<=10,]
+beta <- beta[abs(beta[,2])<=10,]
+
+#bias, percent bias, MSE, coverage, CI length
+bias <- apply(beta,2,mean) - pop.mod.coeffs[,1]
+pctbias <- (apply(beta,2,mean) - pop.mod.coeffs[,1])/pop.mod.coeffs[,1]
+mse <- apply(apply(beta,1,function(x){(x- pop.mod.coeffs[,1])^2}),1,mean)
+upper <- beta + qnorm(0.975)*se
+lower <- beta - qnorm(0.975)*se
+coverage <- rep(NA, 4)
+for (i in 1:4){
+coverage[i] <- sum(upper[,i] > pop.mod.coeffs[i,1] & lower[,i] < pop.mod.coeffs[i,1])/nrow(beta)
+}
+CIlength <- apply(upper - lower, 2 , mean)
+
+res120 <- data.frame(bias, pctbias, mse, coverage, CIlength)
+
+load(paste0(root,"fullmods_60_1_high_hightime1.RData"))
+
+#bias, percent bias, MSE, coverage, CI length
+beta <- do.call(rbind,fullmods$beta)
+se <- do.call(rbind,fullmods$se) 
+ind <- abs(beta[,2])<=10
+se <- se[ind,]
+beta <- beta[ind,]
+
+#bias, percent bias, MSE, coverage, CI length
+bias <- apply(beta,2,mean) - pop.mod.coeffs[,1]
+pctbias <- (apply(beta,2,mean) - pop.mod.coeffs[,1])/pop.mod.coeffs[,1]
+mse <- apply(apply(beta,1,function(x){(x- pop.mod.coeffs[,1])^2}),1,mean)
+upper <- beta + qnorm(0.975)*se
+lower <- beta - qnorm(0.975)*se
+coverage <- rep(NA, 4)
+for (i in 1:4){
+coverage[i] <- sum(upper[,i] > pop.mod.coeffs[i,1] & lower[,i] < pop.mod.coeffs[i,1])/nrow(beta)
+}
+CIlength <- apply(upper - lower, 2 , mean)
+
+reshightime <- data.frame(bias, pctbias, mse, coverage, CIlength)
+
+load(paste0(root,"fullmods_60_0.5_high_hightime0.RData"))
+
+#bias, percent bias, MSE, coverage, CI length
+beta <- do.call(rbind,fullmods$beta)
+se <- do.call(rbind,fullmods$se) 
+se <- se[abs(beta[,2])<=10,]
+beta <- beta[abs(beta[,2])<=10,]
+
+#bias, percent bias, MSE, coverage, CI length
+bias <- apply(beta,2,mean) - pop.mod.coeffs[,1]
+pctbias <- (apply(beta,2,mean) - pop.mod.coeffs[,1])/pop.mod.coeffs[,1]
+mse <- apply(apply(beta,1,function(x){(x- pop.mod.coeffs[,1])^2}),1,mean)
+upper <- beta + qnorm(0.975)*se
+lower <- beta - qnorm(0.975)*se
+coverage <- rep(NA, 4)
+for (i in 1:4){
+coverage[i] <- sum(upper[,i] > pop.mod.coeffs[i,1] & lower[,i] < pop.mod.coeffs[i,1])/nrow(beta)
+}
+CIlength <- apply(upper - lower, 2 , mean)
+
+reslowcorr <- data.frame(bias, pctbias, mse, coverage, CIlength)
+
+dat <- rbind(res60,res120,reslowcorr,reshightime)
+dat$pctbias <- paste0(round(100*dat$pctbias,2), "\\%")
+dat$coverage <- paste0(round(100*dat$coverage,1), "\\%")
+
+df <- data.frame(Scenario = rep(c("Primary Analysis (n = 60)","Increased Sample Size (n = 120)", "Low Inter-Survey Correlation (n = 60)", "High Time Effect (n = 60)"), each = 4), Parameter = rep(c("$\\gamma_0$", "$\\beta_1$", "$\\beta_2$", "$\\beta_3$"),4),dat)
+row.names(df) <- NULL
+
+names(df) <- c("Scenario","Parameter","Bias","Pct Bias", "MSE", "Coverage","CI Length")
+
+df[,c(3,5,7)] <- apply(df[,c(3,5,7)], 2, round, digits = 3)
+
+prelim <- kable(df, escape = FALSE, format ="latex", caption = "\\label{tab:prelim} Primary Results (N = 60)") %>%
+  collapse_rows(columns = 1:2, latex_hline = "major") %>%
+  kable_styling(latex_options = c("scale_down","hold_position"))
+@
 
@@
 row.names(df) <- NULL
-primary <- kable(df, escape = FALSE, format ="latex", caption = "Primary Results (N = 60)") %>%
-  collapse_rows(columns = 1:2, latex_hline = "full") %>%
+
+df$`Pct Bias` <- paste0(round(df$`Pct Bias`,2),"\\%")
+df$Coverage <- paste0(round(100*df$Coverage,1),"\\%")
+
+primary <- kable(df, escape = FALSE, format ="latex", caption = "\\label{} Primary Results (N = 60)") %>%
+  collapse_rows(columns = 1:2, latex_hline = "major") %>%
   kable_styling(latex_options = c("scale_down","hold_position"))
@@
 row.names(df) <- NULL
+
+df$`Pct Bias` <- paste0(round(df$`Pct Bias`,2),"\\%")
+df$Coverage <- paste0(round(100*df$Coverage,1),"\\%")
+
 sampsize <- kable(df, escape = FALSE, format ="latex", caption = "Increased Sample Size Results (N = 120)") %>%
-  collapse_rows(columns = 1:2, latex_hline = "full") %>%
+  collapse_rows(columns = 1:2, latex_hline = "major") %>%
   kable_styling(latex_options = c("scale_down","hold_position"))
@@
 row.names(df) <- NULL
+
+df$`Pct Bias` <- paste0(round(df$`Pct Bias`,2),"\\%")
+df$Coverage <- paste0(round(100*df$Coverage,1),"\\%")
+
 hightime <- kable(df, escape = FALSE, format ="latex", caption = "High Time Results (N = 60)") %>%
-  collapse_rows(columns = 1:2, latex_hline = "full") %>%
+  collapse_rows(columns = 1:2, latex_hline = "major") %>%
   kable_styling(latex_options = c("scale_down","hold_position"))
@@
 row.names(df) <- NULL
+
+df$`Pct Bias` <- paste0(round(df$`Pct Bias`,2),"\\%")
+df$Coverage <- paste0(round(100*df$Coverage,1),"\\%")
+
 lowcorr <- kable(df, escape = FALSE, format ="latex", caption = "Low Inter-Survey Correlation Results (N = 60)") %>%
-  collapse_rows(columns = 1:2, latex_hline = "full") %>%
+  collapse_rows(columns = 1:2, latex_hline = "major") %>%
   kable_styling(latex_options = c("scale_down","hold_position"))
@@
 
-\author{Josephine Wood \and Gregory J. Matthews \and Nicholas Illenberger \and Jennifer Pellowski \and Ofer Harel}
+\author{Josephine Wood \and Gregory J. Matthews \and Jennifer Pellowski \and Ofer Harel}
 
@@
 The second uses an X-block and nine others with 10\% of the items each.
-If the teams decide that each form will contain the X-block and two of the other blocks, then the second team will have 36 \textbf{(28?
-8 choose 2?)} total forms while the first team can proceed with 3.
-\textbf{This is all assuming that the blocks represent the optimal question grouping.
+If the teams decide that each form will contain the X-block and two of the other blocks, then the second team will have 36 %\textbf{(28?
+8 choose 2?)} %No.
+9 choose 2 = 36.
+total forms while the first team can proceed with 3. 
+%\textbf{This is all assuming that the blocks represent the optimal question grouping.
 If this is not known, to account for possible relationships and correlation between questions, the teams would need to consider all possible blocks and create forms for every block configuration.
@@
 
-\textbf{This method, hereafter referred to as Split Form planned missingness and illustrated in \ref{fig:formillustration}, involves meaningfully selecting an X block of $n$ questions and then randomly excluding $k$ questions on each day.
+\textbf{This method, hereafter referred to as Split Form planned missingness and illustrated in \ref{fig:formillustration}, involves meaningfully selecting an X block of $p$ questions and then randomly excluding $k$ questions on each day.
 In a way treating each item as its own block \citep{silvia2014planned}.
@@
 \label{sec:1.2}
-While Split Form missingness can be applied to many experimental designs, the Wave Missingness design \citep{little2013planned} is unique to studies with multiple measurement occasions, or "waves".
+While Split Form missingness can be applied to many experimental designs, the Wave Missingness design \citep{little2013planned} is unique to studies with multiple measurement occasions, or ``waves".
 Unlike the Split Form design, where participants miss a subset of items in a single measurement occasion, the Wave Design entails randomizing participants to miss a measurement occasion entirely.
@@
 
-From here we can compute the sample variance of this estimate by calculating the between-imputation component, $B_M = \frac{1}{(M-1)}\sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2$, and the within-imputation component, $W_M = \frac{1}{(M)}\sum_{n=1}^{M} S_n^2$.
+From here we can compute the sample variance of this estimate by calculating the between-imputation component, $B_M = \frac{1}{(M-1)}\sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2$, and the within-imputation component, $W_M = \frac{1}{M}\sum_{n=1}^{M} S_n^2$.
 These components are combined to obtain the overall sample variance of our MI estimate as follows:
@@
 \begin{equation}
-T_M = W_M + \frac{M+1}{(M)}B_M.
+T_M = W_M + \frac{M+1}{M}B_M.
 \end{equation}
@@
 Generally, as the level of missingness decreases the number of imputations needed does as well.
-(IS THIS TRUE?) If less than 20\% of the requisite data are missing, for instance, five or ten imputations will suffice \citep{raghunathan2015missing}.
+\textbf{Greg: IS THIS TRUE?} If less than 20\% of the requisite data are missing, for instance, five or ten imputations will suffice \citep{raghunathan2015missing}.
 However, at its roots, MI is a simulation technique and thus, the greater $M$ is the more stable our estimates become \citep{harel2007inferences}.
@@
 The first step in the process of creating the simulated datasets was to obtain parameter estimates from \citet{pellowski2016alcohol} and to quantify the relationships between variables.
-These estimated relationships were treated as the "true" relationships and \textbf{one thousand (number or no???)} samples were drawn using these parameters.
+These estimated relationships were treated as the "true" relationships and one thousand samples were drawn using these parameters.
 The purpose of simulating these datasets was to see how well they captured the true relationship between daily medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score).
@@
 \end{align*}
-where $\beta_{0j} = \gamma_0 + \alpha_j$ and $\alpha_j \sim \mathcal{N}(0,\sigma_\alpha^2)$. \\ \\ 
+where $\beta_{0j} = \gamma_0 + \alpha_j$ and $\alpha_j \sim N(0,\sigma_\alpha^2)$. \\ \\ 
 Additionally, note: \\ \\
-$p_{ij} = 1$ when participant $p$ did not adhere to the ART on day $i$, 0 otherwise. \\
-$DrinkYN = 1$ if participant $p$  drank on day $i$, 0 otherwise.\\
-$ZAlcTox =$ participant $p$'s Z-transformed score on an alcohol-antiretroviral interactive toxicity scale developed by Kalichman \cite{kalichman2009prevalence}. \\
-$Day =$ Day $i$ of the study, 0-44. \\
-$j =$ participant index, 1-60. \\
+\begin{itemize}
+\item $p_{ij} = 1$ when participant $p$ did not adhere to the ART on day $i$, 0 otherwise \\
+\item $DrinkYN = 1$ if participant $p$  drank on day $i$, 0 otherwise\\
+\item $ZAlcTox =$ participant $p$'s Z-transformed score on an alcohol-antiretroviral interactive toxicity scale developed by Kalichman \cite{kalichman2009prevalence} \\
+\item $Day =$ Day $i$ of the study, 0-44 \\
+\item $j =$ participant index, 1-60 \\
+\end{itemize}.
 
-Based on the observed data, the true values of the parameters, $\gamma_0$, $\beta_1$, $\beta_2$, $\beta_3$, and $\sigma_\alpha^2$ were found to be -2.29, 0.28, 0.64, 0.01, and \textbf{1.0???} respectively.
-\par
+Based on the observed data, the true values of the parameters, $\gamma_0$, $\beta_1$, $\beta_2$, $\beta_3$, and $\sigma_\alpha^2$ were found to be -2.29, 0.28, 0.64, 0.01, and 1.12, respectively. \par
 Once the samples were drawn, missingness was added under three different structures.
 These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed.
-To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in \textbf{Table \ref{tab:table14} (do we want the illustration here instead?
-or in both places?)}.
+To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Table \ref{tab:table14} \textbf{Greg: I think we need either only the table or only the illustration.
+Not sure we need both.}.
 As in the previous tables, "1" indicates an observed occasion while "0" indicates a missing one.
@@
 
-FIX THIS: THIS SOUNDS LIKE WE ADDED MORE MISSINGNESS.
-Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions.
+%FIX THIS: THIS SOUNDS LIKE WE ADDED MORE MISSINGNESS. FIXED
+For each different designed missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions.
 Previous work by \citet{rhemtulla2014planned} found that for low levels of missingness Split Form design outperforms the Wave Missingness design in capturing latent growth curve model parameters.
@@
 This fact allows for the principled use of MI techniques.
-Using the R package $\{$mice$\}$ \citep{mice2011imputation} the binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching \textbf{was it???
-i don't think so, it was in the X block originally but double check!}.
+Using the R package \texttt{mice} \citep{mice2011imputation} the binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching %\textbf{was it???
+i don't think so, it was in the X block originally but double check!Greg: Yes it was}.
 \par
@@
 Note that instead of increasing the value of $\beta_3$, the slope for time effect, all the other parameters were decreased.
-This was done because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1.
-Decreasing the other variables effects ensured that time has a disproportionate effect without this problem.
 The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point.
@@
 This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design.
-Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:prelim} \textbf{not here yet}.
+Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:prelim}.
 Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
 
-<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
-#prelim
+<<tab:prelim,echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
+prelim
 @
@@
 Nevertheless, this must be kept in mind when analyzing the results from the PM designs provided in Table \ref{tab:primary}.
-\textbf{In Table \ref{tab:primary} as in Tables \ref{tab:sampsize}, \ref{tab:lowcorr}, and \ref{tab:hightime} bold values indicate ``unacceptable" results.} That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
+%\textbf{In Table \ref{tab:primary} as in Tables \ref{tab:sampsize}, \ref{tab:lowcorr}, and \ref{tab:hightime} bold values indicate ``unacceptable" results.} That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
 
@@
 
-For the Split Form and Altered Split Form designs seen in Table \ref{tab:table3}, note that the greatest loss in efficiency was on the $\beta_1$ estimate.
+For the Split Form and Altered Split Form designs seen in Table \ref{tab:primary}, note that the greatest loss in efficiency was on the $\beta_1$ estimate.
 While the CI coverage remained high at all levels of missingness for the two designs, the bias, percent bias, and MSE reached unacceptable levels at the high missingness level.
@@
 All parameter values were held the same as in the original simulation.
-Table \ref{tab:prelim} \textbf{not here yet}, again, contains the results of the analysis before applying any PM design.
+Table \ref{tab:prelim}, again, contains the results of the analysis before applying any PM design.
 The results of the full-data simulations are compared to those obtained from the PM designs, shown in Table \ref{tab:sampsize}.
@@
 At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable.
-However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:prelim} \textbf{not here yet}.
+However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:prelim}.
 The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088.
@@
 For the next set of simulations sample size returned to 60 participants but the level of inter-survey correlation decreased.
-The results obtained from the full data simulations are provided in Table \ref{tab:prelim} \textbf{not here yet} while the results from the PM designs are given in Table \ref{tab:lowcorr}.
+The results obtained from the full data simulations are provided in Table \ref{tab:prelim} while the results from the PM designs are given in Table \ref{tab:lowcorr}.
 \par
@@
 In the final scenario we tested to see how the PM designs would capture a model where time had a disproportionately large effect on Missed Dose.
-In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$.
-The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:hightime}.
+The results from our full-data analyses are provided in Table \ref{tab:prelim} while the corresponding PM design results are in Table \ref{tab:hightime}.
 \par
@@
 We found that for low levels of planned missing data (about 25\% missingness), variations of the Split Form design and the Wave Missingness designs are all capable of estimating the parameters of the multilevel model reasonably well.
-As the level of missing data increases to 50\% and 75\%, however, the quality of estimates in all of the tested PM designs become unacceptable as we see rising parameter biases and confidence interval lengths.
-Moreover, we found that the quality of the Wave Missingness design depreciates much more rapidly than the other PM designs, providing higher parameter biases than the corresponding Split Form estimates and low confidence interval coverages (95\% confidence intervals with less than 90\% coverage in some cases).
+As the level of missing data increases to 50\% and 75\% the quality of estimates in all of the tested PM designs degrades we see generally rising parameter biases and confidence interval lengths.
+This occurs most dramatically in the Wave Missingness design, which suggest the use of Split Form designs over Wave Missingness when Split form can be easily implemented.
 \par
 
-These facts warn against the use of Wave Missingness designs when the Split Form design can be easily substituted.
-If Wave Missingness must be used, as in the cohort sequential and developmental time lag designs, the design must minimize the amount of missing data.
+If Wave Missingness must be used, as in the cohort sequential and developmental time lag designs, the design should attempt to minimize the amount of missing data.
 For instance, in a cohort sequential design which attempts to stretch four-year data to cover a span of six years each cohort will have missing values at two of the six measurement occasions.
-This would result in about 33.3\% missingness.
 To ensure that the researcher's analyses are accurate, we would recommend an increase in the amount of time they follow participants, using five-year data instead of four-year data to cover the same period.
@@
 
-For future research it may be useful to test a wider range of missingness.
+For future research it may be useful to test a wider range of missingness rates.
 That is, while this study showed that the PM designs performed well when missingness was around 25\% and sometimes performed poorly when it was around 50\% it is unknown exactly when the estimation procedure breaks down.
 While only 25\% missing data is suggested here, if it was shown that these designs performed well at 40\% missingness, then researchers could substantially increase cost reduction and decrease participant burden beyond what our recommendations allow.
-Another worthwhile pursuit may be to see how hybrid PM designs perform.
-While it was found that Wave Missingness designs performed underwhelmingly, it would be interesting to investigatte a design containing fully missing days with the remaining days missing on some values would perform.
+Another worthwhile pursuit may be to examine how hybrid PM designs perform.
+While it was found that Wave Missingness designs performed worse than Split Form, it would be interesting to investigate a design containing fully missing days with the remaining days missing on some values would perform (i.e.
+Wave Missingness/Split Form hybrid).
 This investigation may be particularly useful to researchers who wish to implement an accelerated longitudinal design but also have measures that are costly or burdensome which they would like to limit the collection of.
@@
 
-To conclude we discuss the limitations of this analysis. DIFFERENT LIMITATIONS. NOT COMPUTING POWER.
+%To conclude we discuss the limitations of this analysis. DIFFERENT LIMITATIONS. NOT COMPUTING POWER.
 
@@
 By illuminating the weaknesses of the Wave Missingness design, it is hoped that, unless it is explicitly required, researchers will opt instead to use a Split Form design.
-Furthermore, when researchers do implement a PM design we hope they follow our recommendation to err on the side of caution and keep the amount of missing data relatively low.
+Furthermore, when researchers do implement a PM design we hope they follow our recommendation to err on the side of caution and take steps to keep the amount of missing data relatively low.
 \par

### 2018-05-30 Code/Code Rework.R
Modified the high time setting.  Now time is multiplied by 10 and everything else is held at 1.

@@ -123,7 +123,8 @@ pop.mod.coeffs <- summary(pop.mod)$coef[,1:2]
 no.var <- nrow(pop.mod.coeffs)
 
 if (hightime == 1){
-  pop.mod.coeffs[,1] <- pop.mod.coeffs[,1] * c(2,0.5,0.5,1)
+  #pop.mod.coeffs[,1] <- pop.mod.coeffs[,1] * c(2,0.5,0.5,1)
+  pop.mod.coeffs[,1] <- pop.mod.coeffs[,1] * c(1,1,1,10)#new test
 }
 
 # Correlation Matrix
@@ -179,7 +180,7 @@ for (i in 1:no.sim) {print(i)
   sigmaPID <- MD@theta
   
   if (hightime == 1){
-    MD@beta <- MD@beta * c(2,0.5,0.5,1)
+    MD@beta <- MD@beta * c(1,1,1,10)
   }
   
   X$groupErr <- rnorm(no.pid, mean=0, sd=sigmaPID)[X$PID]
@@ -194,7 +195,7 @@ for (i in 1:no.sim) {print(i)
 mod.maker.nomiss <- function(dat){ #
   modbetas <- list()
   modse <- list()
-  for (i in 1:length(dat)){
+  for (i in 1:length(dat)){print(i)
     try(model <- glmer(MissedDose ~ Q7 + ZAlcTox + Day + (1|PID), data = dat[[i]], family=binomial(link=logit)))
     try(modbetas[[i]] <- summary(model)$coef[,1]) # only take the coefficients of the variables, not the intercept
     try(modse[[i]] <- summary(model)$coef[,2])
@@ -204,6 +205,7 @@ mod.maker.nomiss <- function(dat){ #
 
 #Get results for the data with no missingess.
 fullmods <- mod.maker.nomiss(sim.data)
+#save(pop.mod.coeffs,fullmods,file = paste0("fullmods_",no.pid,"_",corr.scale,"_",howmuch,"_hightime",hightime,".RData"))
 
 #Analysis for models with no missing data
 #Bias

### 2018-05-31 Code/Code Rework.R
Updated code.

@@ -205,7 +205,7 @@ mod.maker.nomiss <- function(dat){ #
 
 #Get results for the data with no missingess.
 fullmods <- mod.maker.nomiss(sim.data)
-#save(pop.mod.coeffs,fullmods,file = paste0("fullmods_",no.pid,"_",corr.scale,"_",howmuch,"_hightime",hightime,".RData"))
+save(pop.mod.coeffs,fullmods,file = paste0("fullmods_",no.pid,"_",corr.scale,"_",howmuch,"_hightime",hightime,".RData"))
 
 #Analysis for models with no missing data
 #Bias

### 2018-05-31 Documentation/manuscript.Rnw
updated manuscript.  Re-write of the high time section.  And updated high time tables.  (i.e. table 5 bottom part and table 9).

@@
 se <- do.call(rbind,fullmods$se)
-se <- se[abs(beta[,2])<=10,]
-beta <- beta[abs(beta[,2])<=10,]
 
@@
 se <- do.call(rbind,fullmods$se)
-ind <- abs(beta[,2])<=10
-se <- se[ind,]
-beta <- beta[ind,]
 
@@
 In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable.
-To do this we changed the value of the parameters $\gamma_0$, $\beta_1$, $\beta_2$, and $\beta_3$ to -4.56, 0.14, 0.32, and 0.01 respectively.
-Note that instead of increasing the value of $\beta_3$, the slope for time effect, all the other parameters were decreased.
+To do this held the values of $\gamma_0$, $\beta_1$, $\beta_2$ the same and increaed the effect of time (i.e.
+$\beta_3$) by ten times.
 The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point.
@@
 
+With the Split Form and Altered Split Form designs we observed coverage rates for $\beta_1$ paramter estimate that are slightly higher than the nominal level of 95\% coverage in the high, medium, and low levels of missingness.
+The percentage of bias in these desgined is relatively low in the -30\% to -50\% range across low, medium, and high missingness.
+As for Wave Missingness, the percent bias increases from about -40\% for low missingness all the way up to about -92\% for high missingness.
+\par
+
+It is interesting to note that the FMI seems the be relatively unaffected by the level of missingness in the Split Form and Altered Split Form designs, but in Wave Missingness the FMI increases steadily as the level of missingess increases.
+We also observe this in the confidence interval length, which is relatively stable around 4 for Split Form and Altered Split Form across the three different levels of missingness whereas the confidence interval length in Wave Missingness increases steadily and the amount of missing information increases.
+\par
+
 <<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
@@
 
-The effects of imposing Split Form missingness in this high time effect scenario are similar to those under the low inter-survey correlation scenario.
-At low levels of missingness bias, percent bias, MSE, and coverage for $\beta_1$ are all within the acceptable range.
-At medium and high levels of missingness bias, percent bias, and MSE are unacceptably high.
-\par
-
+%The effects of imposing Split Form missingness in this high time effect scenario are similar to those under the low inter-survey correlation scenario.
 The Altered Split Form design performed slightly better than the normal Split Form design under this simulation scenario.
@@
 
-In this simulation scenario, the Wave Missingness Design performs similarly to the Split Form and Altered Split Form designs at low levels of missingness.
+%In this simulation scenario, the Wave Missingness Design performs similarly to the Split Form and Altered Split Form designs at low levels of missingness.
 The bias, percent bias, MSE, and CI coverage for $\beta_1$ all performed acceptably using the Wave Missingness design at low levels of missingness.
@@
 Of larger concern, however, is the steep drop-off in estimating quality of the Wave Missingness design as missingness increased.
-In every scenario tested, the Wave Missingness design produced unacceptable bias, percent bias, and MSE at medium and high levels of missingness.
+In every scenario tested, the Wave Missingness design produced high bias, percent bias, and MSE at medium and high levels of missingness.
 In addition, despite increased bias on estimates with missing values, the length of confidence intervals for these estimates remained the same as in the Split Form design.

### 2018-06-02 Documentation/PointByPointResponse4.tex
Reviewer response document.

%% This file is to be used as a template for your submission. 
%% Rename this file and replace the text with the text of 
%% your manuscript.
%%
%% The standard LaTeX document class "article" is recommended. 
%% Use options letterpaper and 12pt.
\documentclass[letterpaper,12pt]{article}

\newdimen\bibsep

\newdimen\bibhang
%% This is the recommended preamble for your document.
\usepackage{setspace}
%% Load De Gruyter specific settings 
\usepackage{dgjournal}          
\usepackage{color,soul}
%% The mathptmx package is recommended for Times compatible math symbols.
%% Use mtpro2 or mathtime instead of mathptmx if you have the commercially
%% available MathTime fonts.
%% Other options are txfonts (free) or belleek (free) or TM-Math (commercial)
\usepackage{amssymb,amsmath}
\usepackage{multirow}
%% Use the graphics package to include figures
\usepackage{graphics}
%% Use natbib with these recommended options
\usepackage[authoryear,comma,longnamesfirst,sectionbib]{natbib} 
\usepackage{lscape}
\usepackage{graphicx}

\setstretch{1}
\setlength{\bibsep}{10pt}
\usepackage{booktabs}
%% Start your document body here
\begin{document}

 We would again like to thank the reviewers for their helpful comments on our manuscript.  We have addressed each of these comments in our revised manuscript, as well as provided a point-by-point response below. Reviewer comments are in normal font and our responses are bold-faced.

\section{Referee 1}
\subsection{Comments to the Author}
\begin{itemize}
\item [Issues] that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs. Further, there is no justification for an inherent interest in a multilevel model. Why is this of greater interest than a latent growth curve or a simple repeated measures model?\\

{\bf This sentence now reads ``Support vector machines (SVM) perform classification by constructing linear boundaries in a transformed version of the feature space." }\\

\item  The level of detail is more than readers need to get the essentials and pointing out that researchers have to choose how many blocks to include in any design is extraneous information and distracts from the larger argument.

{\bf Our response goes here.}

\item Similarly, there is little mention about the mechanics behind multiple imputation - this is an important aspect of the study that deserves more attention than what is included. As a case in point, the authors mention that the choice of imputations is important but never mention why (e.g., improved efficiency). They also fail to mention the importance of the imputation model.

{\bf Our response goes here.}

\item [The] empirical example is so specific that I am not sure one can generalize beyond the limited set of simulations that were examined here.  For example, can we reasonably assume that these findings would generalize to a continuous outcome? What about different parameters for the covariates? Are these sample sizes typical? And is there good reason to believe that a different design would have produced the same results? For example, is it reasonable to assume that there are no context or order effects in these questions that might play out in at least the split form designs?  Of course, this is a flaw of any simulation; however, the highly specific nature of this study stands out. As an aside, why is there only one omitted response for day 5 (Q3)?

{\bf Our response goes here.}

\item In table 7 it would be useful to have the true parameter values next to the parameter.

{\bf Our response goes here.}

\item I was troubled by the seemingly arbitrary thresholds for what were unacceptable criteria. How was "Bias, Percent Bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90%" determined?

{\bf Our response goes here.}

\item In section 4.3, the authors seem to confuse the idea of bias and efficiency.

{\bf Our response goes here.}
\end{itemize}

\section{Referee 2}
\subsection{Comments to the Author}
\begin{itemize}
\item  The authors compare their model with the one investigated by Rhemtulla et al. (2014), writing that "because our model of interest is a mixed effects model, though, we cannot be sure that this result will hold." It might be useful to spell out the differences between the two models, because a latent growth curve model can be specified as a mixed effects model. I believe there are three differences in the models: (1) we included a random slope, whereas yours is fixed; (2) we used a "latent basis" model in which the slope coefficients were estimated, whereas yours are fixed to specify linear change, and (3) you included observed predictors whereas we did not. It may be interesting to consider any differences in the results in light of these model differences, in particular, I would have predicted that a linear slope (and especially a fixed linear slope) is less affected by wave-level missingness than a random basis slope, which would seem to require more information at each time point in order to estimate.

{\bf Our response goes here.}

\itemThe model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!

{\bf Our response goes here.}

\item I'm quite confused about the relation between the survey questions and the analysis model. Table 5 presents the survey questions, which I presumed to be the basis for the planned missing design, but the analysis model doesn't seem to include any of those items except "did you drink today" as a predictor. How is the split form design relevant to the variables included in the model? What was the missingness pattern of those items? More generally, I'd like to see the full model of the complete data that were generated and the details of all the missingness patterns that were imposed (i.e., which variables were missing data on which days in the 25\%, 50\%, and 75\% missing conditions)

{\bf Our response goes here.}

\item In the split form design, is Day 5 / Q5 supposed to be missing? It's otherwise strange that Q5 is answered on 4/5 days and that Day 5 as 4/5 questions, as opposed to all the other days/questions being 3/5.

{\bf Our response goes here.}

\item Further, please clarify whether that Table 6 presents the PM designs for a single participant. That is, I think another participant would be missing different questions on different days in the Split Form design, or missing different waves in the Wave Missingness design. Normally these design tables (like Tables 1-4) have a column for participants/forms, but Table 6 does not.

{\bf Our response goes here.}

\item "The FMI is a measure of how much of the MI sampling variance comes from differences between imputations." That is how it is computed, but it is more generally a measure of the proportion of information that is lost as a result of missing data (e.g., see Savalei & Rhemtulla, 2012 "On obtaining estimates of the fraction of missing information from FIML") "When determining if the PM designs are performing sufficiently...three possible PM designs." If different missingness structures are applied to the very same data sets, then the results are perfectly comparable. Further, it's not clear what "bias" and "average biases" refer to here - an estimate cannot be said to be biased based on a single data set, and it's not clear what's being averaged over.

{\bf Our response goes here.}

\item "If a 95\% CI has a true coverage of 90\% then the Type I error rate is double what it should be." That's only true if the true parameter value is 0 and you're testing the hypothesis that the estimated parameter is different from 0. Otherwise these measures get at different things. (Indeed, there is no Type I error rate if the parameter value is not 0).

{\bf Our response goes here.}

\item "While this fact was accounted for in the original simulations, it was not in this set of simulations." This sentence makes it sound as though the second simulation design somehow failed to model the correlations among variables, rather than that low correlations were imposed. Am I right that the actual inter-item correlations are not presented anywhere in the paper? This is relevant information that is missing.

{\bf Our response goes here.}

\item Results are presented for the main effects in the model, but not for the variance of the random intercept - it would be interesting to see these results as well.

{\bf Our response goes here.}

\item It is impossible to understand the results of the low inter-survey correlation condition without a clearer presentation of the design. If survey items were predictable from "baseline items" but not from each other, what were the correlations between these items and the baseline items? Were the baseline items used in imputation? And again, since the survey items don't seem to be in the model anywhere, how are these relationships expected to affect parameter estimation?

{\bf Our response goes here.}

\item In section 4.3, the authors seem to confuse the idea of bias and efficiency.

{\bf Our response goes here.}

\end{itemize}

\bibliographystyle{plos2015}
\bibliography{brophyTeeth}

\end{document}

### 2018-06-02 Documentation/response.Rnw
Reviewer response document.

--- 2018-06-02 Documentation/PointByPointResponse4.tex
@@
 
-\newdimen\bibsep
+%\newdimen\bibsep
 
-\newdimen\bibhang
+%\newdimen\bibhang
 %% This is the recommended preamble for your document.
@@
 \begin{itemize}
-\item [Issues] that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs.
-Further, there is no justification for an inherent interest in a multilevel model.
-Why is this of greater interest than a latent growth curve or a simple repeated measures model?\\
 
-{\bf This sentence now reads ``Support vector machines (SVM) perform classification by constructing linear boundaries in a transformed version of the feature space." }\\
+\item {[Issues]} that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs.\\
 
-\item  The level of detail is more than readers need to get the essentials and pointing out that researchers have to choose how many blocks to include in any design is extraneous information and distracts from the larger argument.
+{\bf Our response goes here.}\\
 
-{\bf Our response goes here.}
+\item {[There]} is no justification for an inherent interest in a multilevel model. Why is this of greater interest than a latent growth curve or a simple repeated measures model?\\
+
+{\bf Our response goes here.}\\
+
+\item  The level of detail is more than readers need to get the essentials and pointing out that researchers have to choose how many blocks to include in any design is extraneous information and distracts from the larger argument.\\
+
+{\bf Our response goes here.}\\
 
@@
 As a case in point, the authors mention that the choice of imputations is important but never mention why (e.g., improved efficiency).
-They also fail to mention the importance of the imputation model.
+They also fail to mention the importance of the imputation model.\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
-\item [The] empirical example is so specific that I am not sure one can generalize beyond the limited set of simulations that were examined here.
+\item {[The]} empirical example is so specific that I am not sure one can generalize beyond the limited set of simulations that were examined here.
 For example, can we reasonably assume that these findings would generalize to a continuous outcome?
@@
 Of course, this is a flaw of any simulation; however, the highly specific nature of this study stands out.
-As an aside, why is there only one omitted response for day 5 (Q3)?
+As an aside, why is there only one omitted response for day 5 (Q3)?\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
-\item In table 7 it would be useful to have the true parameter values next to the parameter.
+\item In table 7 it would be useful to have the true parameter values next to the parameter.\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
 \item I was troubled by the seemingly arbitrary thresholds for what were unacceptable criteria.
-How was "Bias, Percent Bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90%" determined?
+How was "Bias, Percent Bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%" determined?\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
-\item In section 4.3, the authors seem to confuse the idea of bias and efficiency.
+\item In section 4.3, the authors seem to confuse the idea of bias and efficiency.\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 \end{itemize}
@@
 \begin{itemize}
+
 \item  The authors compare their model with the one investigated by Rhemtulla et al.
@@
 I believe there are three differences in the models: (1) we included a random slope, whereas yours is fixed; (2) we used a "latent basis" model in which the slope coefficients were estimated, whereas yours are fixed to specify linear change, and (3) you included observed predictors whereas we did not.
-It may be interesting to consider any differences in the results in light of these model differences, in particular, I would have predicted that a linear slope (and especially a fixed linear slope) is less affected by wave-level missingness than a random basis slope, which would seem to require more information at each time point in order to estimate.
+It may be interesting to consider any differences in the results in light of these model differences, in particular, I would have predicted that a linear slope (and especially a fixed linear slope) is less affected by wave-level missingness than a random basis slope, which would seem to require more information at each time point in order to estimate.\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
-\itemThe model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!
+\itemThe model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
@@
 What was the missingness pattern of those items?
-More generally, I'd like to see the full model of the complete data that were generated and the details of all the missingness patterns that were imposed (i.e., which variables were missing data on which days in the 25\%, 50\%, and 75\% missing conditions)
+More generally, I'd like to see the full model of the complete data that were generated and the details of all the missingness patterns that were imposed (i.e., which variables were missing data on which days in the 25\%, 50\%, and 75\% missing conditions).\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
 \item In the split form design, is Day 5 / Q5 supposed to be missing?
-It's otherwise strange that Q5 is answered on 4/5 days and that Day 5 as 4/5 questions, as opposed to all the other days/questions being 3/5.
+It's otherwise strange that Q5 is answered on 4/5 days and that Day 5 as 4/5 questions, as opposed to all the other days/questions being 3/5.\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
@@
 That is, I think another participant would be missing different questions on different days in the Split Form design, or missing different waves in the Wave Missingness design.
-Normally these design tables (like Tables 1-4) have a column for participants/forms, but Table 6 does not.
+Normally these design tables (like Tables 1-4) have a column for participants/forms, but Table 6 does not.\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
 \item "The FMI is a measure of how much of the MI sampling variance comes from differences between imputations." That is how it is computed, but it is more generally a measure of the proportion of information that is lost as a result of missing data (e.g., see Savalei & Rhemtulla, 2012 "On obtaining estimates of the fraction of missing information from FIML") "When determining if the PM designs are performing sufficiently...three possible PM designs." If different missingness structures are applied to the very same data sets, then the results are perfectly comparable.
-Further, it's not clear what "bias" and "average biases" refer to here - an estimate cannot be said to be biased based on a single data set, and it's not clear what's being averaged over.
+Further, it's not clear what "bias" and "average biases" refer to here - an estimate cannot be said to be biased based on a single data set, and it's not clear what's being averaged over.\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
@@
 Otherwise these measures get at different things.
-(Indeed, there is no Type I error rate if the parameter value is not 0).
+(Indeed, there is no Type I error rate if the parameter value is not 0).\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
@@
 Am I right that the actual inter-item correlations are not presented anywhere in the paper?
-This is relevant information that is missing.
+This is relevant information that is missing.\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
-\item Results are presented for the main effects in the model, but not for the variance of the random intercept - it would be interesting to see these results as well.
+\item Results are presented for the main effects in the model, but not for the variance of the random intercept - it would be interesting to see these results as well.\\
 
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 
@@
 Were the baseline items used in imputation?
-And again, since the survey items don't seem to be in the model anywhere, how are these relationships expected to affect parameter estimation?
+And again, since the survey items don't seem to be in the model anywhere, how are these relationships expected to affect parameter estimation?\\
 
-{\bf Our response goes here.}
-
-\item In section 4.3, the authors seem to confuse the idea of bias and efficiency.
-
-{\bf Our response goes here.}
+{\bf Our response goes here.}\\
 

### 2018-06-02 Documentation/response.tex
Reviewer response document.

--- 2018-06-02 Documentation/response.Rnw
@@
 %% Use options letterpaper and 12pt.
-\documentclass[letterpaper,12pt]{article}
+\documentclass[letterpaper,12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 %% Start your document body here
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
-\item {[Issues]} that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs.\\
-
-{\bf Our response goes here.}\\
-
-\item {[There]} is no justification for an inherent interest in a multilevel model. Why is this of greater interest than a latent growth curve or a simple repeated measures model?\\
+\item {[Issues]} that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs.
+Further, there is no justification for an inherent interest in a multilevel model.
+Why is this of greater interest than a latent growth curve or a simple repeated measures model?\\
 

### 2018-06-07 Documentation/manuscript.Rnw
Updated a few things.

@@
 
-df <- data.frame(Scenario = rep(c("Primary Analysis (n = 60)","Increased Sample Size (n = 120)", "Low Inter-Survey Correlation (n = 60)", "High Time Effect (n = 60)"), each = 4), Parameter = rep(c("$\\gamma_0$", "$\\beta_1$", "$\\beta_2$", "$\\beta_3$"),4),dat)
+df <- data.frame(Scenario = rep(c("Primary Analysis (n = 60)","Increased Sample Size (n = 120)", "Low Inter-Survey Correlation (n = 60)", "High Time Effect (n = 60)"), each = 4), Parameter = c(rep(c("$\\gamma_0$ (-2.287)", "$\\beta_1$ (0.282)", "$\\beta_2$ (0.637)", "$\\beta_3$ (0.0147)"),3),c("$\\gamma_0$ (-2.287)", "$\\beta_1$ (0.282)", "$\\beta_2$ (0.637)", "$\\beta_3$ (0.147)")),dat)
 row.names(df) <- NULL
@@
 		& 4 & 1 & 0 & 1 & 1 & 0 \\
-		& 5 & 1 & 1 & 0 & 1 & 1 \\
+		& 5 & 0 & 1 & 0 & 1 & 1 \\
 		\midrule
@@
 
-For the Split Form design it is important to notice that the efficiency of the $\beta_1$ estimate decreases much more rapidly than in the original simulations where survey questions were predictive of one another.
-For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be 0.150 and 0.276 at high levels.
-This left us with an increase in average bias of 0.126.
-Looking at the same increase in the original simulations, note that the bias only increased by 0.071.
-This loss in efficiency is seen in the other measurements on the $\beta_1$ estimate as well.
-Moreover, note that the Split Form design performs unacceptably in terms of bias, percent bias, and MSE at medium levels of missingness.
-This was not the case in the other missingness scenarios.
+For the Split Form design it is important to notice that the bias of the $\beta_1$ estimate decreases much more than in the original simulations when moving from low to high missingess.
+For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be -0.041 and -0.145 at high levels.
+Looking at the same increase in the original simulations, note that the bias only changed from -0.071 to -0.107.
 \par
@@
 Additionally, the coverage of the $\beta_1$ CIs was quite a bit higher than in the full-data simulations.
-That is, while the coverage probability obtained in the full-data simulations was 94.5\%, under this Altered Split Form design the coverages are 95.5\%, 97.0\%, and 96.0\% at low, medium, and high levels of missingness respectively.
+That is, while the coverage probability obtained in the full-data simulations was 95.4\%, under this Altered Split Form design the coverages are 98.4\%, 99.1\%, and 99.1\% at low, medium, and high levels of missingness, respectively.
 \par

### 2018-06-07 Documentation/response.Rnw
Response document.

@@
 
- We would again like to thank the reviewers for their helpful comments on our manuscript.
+ We would like to thank the reviewers for their helpful comments on our manuscript.
 We have addressed each of these comments in our revised manuscript, as well as provided a point-by-point response below.
-Reviewer comments are in normal font and our responses are bold-faced.
+Reviewer comments are in regular font and our responses are bold-faced.
+
+ We should also note that this revision is a little bit unusual in that the main author of the first submission has been dropped from this manuscript.
+Since then two other authors have been added to this manuscript, which has had parts largely re-written and the simulation study has been completely overhauled to conform to  standards of reproducible research.
 
@@
 
-{\bf Our response goes here.}\\
+{\bf With any high frequency longitudinal study, there is a high probability of dropout.
+Using planned missingness reduces the burden on the participants, which often lowers the probability of drop out due to survey fatigue.
+It can also lower the cost of a longitudinal study.
+We believe this is addressed in the second sentence of the first paragraph of the new draft of the manuscript.
+}\\
+
+%With a high frequency longitudinal there is is a high probabilty of dropout.  Using planned missingesns reduces the burden on participants.  CITE where we talk about this in the paper.
 
@@
 
-{\bf Our response goes here.}\\
+{\bf We chose to work with a multi-level model in this case because that was the analysis model of interest in Pellowski et.
+al.
+(2016).
+The data used in the aforementioned paper was used a basis for our simulation study, and so we wanted to continue to use the analysis model that was of interest in the original paper.
+The justification for using that model can be found in Pellowski et.
+al.
+(2016).
+}\\
+%In the paper by Pellofski YEAR, that was the origianl model of interest.  We are simply using that model of interest in our simulation, now with the addition of planned missingess.
 
@@
 
-{\bf Our response goes here.}\\
+{\bf We believe that we have addressed this issue by re-writing and cleaning up large sections of the manuscript, which we believe now contain the appropriate level of detail.  }\\
+%We have re-written this whole section and we believe it now has the appropriate level of detail.
 
@@
 
-{\bf Our response goes here.}\\
+{\bf }\\
+Complete case analysis is highly inefficient here because we would be removing nearly all of the observations.
+Multiple imputation gets around this and allows for more efficient estiamtion of the parameters.
 
@@
 
-{\bf Our response goes here.}\\
+{\bf Certainly any simulation study suffers from the flaw that it is difficult to determined how generalizable the results are beyond the specific settings of the particular simulation study.
+However, the study design in Pellowski et.
+al.
+(2016) is a common design and the planned missingness designs studied here are also common desgined.
+\\
+
+That being said, we believe that results would be similar if the response was continuous and / or different parameters were chosen for the covariates.
+The sample size of this study is relatively small, but we still see reasonable results.
+In Pellowski et.
+al.
+(2016) the number of participants was 59.
+Sample sizes can be this low when attempting to collect data longitudinally at high frequencies such as daily (or even more often) due to the fact the participants need to be highly engaged in the study.\\
+
+There should have been two omitted responses for Day 5 in the Split Form example in Table 4.  This correction has been made.\\  
+}\\
+
+How to respond to this: ``Are these sample sizes typical?
+And is there good reason to believe that a different design would have produced the same results?
+For example, is it reasonable to assume that there are no context or order effects in these questions that might play out in at least the split form designs?"
 
@@
 
-{\bf Our response goes here.}\\
+{\bf The true parameter values have been added to this table, which is now Table 5. }\\
 
@@
 {\bf Our response goes here.}\\
+These threshholds are identified in Collins, Cam, and Schafer.
 
@@
 {\bf Our response goes here.}\\
+CHECK THIS.
+
 \end{itemize}
@@
 {\bf Our response goes here.}\\
+The complete data structure is best fit with mixed effects model and mimic the original data.
+We now exgend it to the scenario where we have missing by design.
+For the structure of this data, we believe this is the best model.
 
-\itemThe model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!\\
+We're using different data! That's why we didn't use a latent growth curve model.  It's not a comparison.  It's in addition to.
+
+\item The model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!\\
 
 {\bf Our response goes here.}\\
+The model has been specified correctly this time.  The reviewer is correct.
 
@@
 {\bf Our response goes here.}\\
+This has been addressed.  Please see the new figures that are red and blue.  Tables INSERT NUMBERS!.
 
@@
 {\bf Our response goes here.}\\
+The reviewer is correct.  We have replaced those tables with new figures.....
 
@@
 {\bf Our response goes here.}\\
+Yes this is for one participant.
+We have removed this table.
+We have replaced these with figures.
+The figure give an example of what it would look like for one individual, but each individual will have a different set of missing questions.
 
@@
 {\bf Our response goes here.}\\
+We agree with the description of FMI.  In spirit it is accounting for how much missing data there is.  CHANGE IN TEXT.
+
+Let me read the FMI section and see what they are talkin gabout here.
+
+If you mean that they are all the same for different planned missingness patterns that is not correct.  We don't fully understan this statement from the reviewer.
 
@@
 {\bf Our response goes here.}\\
+We disagree politely.  Here is why........
 
@@
 {\bf Our response goes here.}\\
+We are using inter-item correlation.  Just specify.
 
@@
 {\bf Our response goes here.}\\
+1.) Either add this if it's easy.
+
+OR
+
+2.) The main interest of this paper was the fixed effects.  So we excluded the variance of the random intercept.
 
@@
 {\bf Our response goes here.}\\
+There was a major change to this section.  We have added more information that hopefully satisfies the reviewer.
 
@@
 
-\bibliographystyle{plos2015}
-\bibliography{brophyTeeth}
+%\bibliographystyle{plos2015}
+%\bibliography{brophyTeeth}
 

### 2018-06-07 Documentation/response.Rnw
f

@@
 
-{\bf Our response goes here.}\\
-These threshholds are identified in Collins, Cam, and Schafer.
+{\bf We have removed the mention of these cut-offs.  However, they are based on suggestions put forth in Collins, L. M., Schafer, J. L., & Kam, C.-M. (2001)}\\
 
 \item In section 4.3, the authors seem to confuse the idea of bias and efficiency.\\
-
-{\bf Our response goes here.}\\
-CHECK THIS.
+{\bf That is correct.  The mentions of efficiency have been removed from this section.  }\\
 

### 2018-06-07 Documentation/response.Rnw
updates more.

@@
 
-{\bf Our response goes here.}\\
-The model has been specified correctly this time.  The reviewer is correct.
+{\bf The model was indeed written incorrectly.  The model is now written as $$
+logit (p_{ij}) = \beta_{0j} + \beta_1DrinkYN_i + \beta_2ZAlcTox_i +\beta_3Day
+$$
+where $\beta_{0j} = \gamma_0 + \alpha_j$ and $\alpha_j \sim N(0,\sigma_\alpha^2)$.}\\
 

### 2018-06-07 Documentation/manuscript.Rnw
updates more.

@@
 
-\begin{table}[H]
-	\centering
-	\caption{Different Planned Missingness Designs}
-	\setlength{\tabcolsep}{0.45cm}
-	\label{tab:table14}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|ccccc}
-		\toprule
-		Design & Day & Q1 & Q2 & Q3 & Q4 & Q5 \\
-		\midrule
-		\multirow{5}{*}{Split Form}
-		& 1 & 1 & 1 & 0 & 0 & 1 \\
-		& 2 & 0 & 0 & 1 & 1 & 1 \\
-		& 3 & 0 & 1 & 1 & 0 & 1 \\
-		& 4 & 1 & 0 & 1 & 1 & 0 \\
-		& 5 & 0 & 1 & 0 & 1 & 1 \\
-		\midrule
-		\midrule
-		\multirow{5}{*}{Altered Split Form}
-		& 1 & 1 & 1 & 1 & 1 & 1 \\
-		& 2 & 1 & 1 & 1 & 1 & 1 \\
-		& 3 & 0 & 0 & 1 & 1 & 1 \\
-		& 4 & 1 & 1 & 0 & 1 & 0 \\
-		& 5 & 0 & 1 & 1 & 0 & 1 \\
-		\midrule
-		\midrule
-		\multirow{5}{*}{Wave Missingness}
-		& 1 & 1 & 1 & 1 & 1 & 1 \\
-		& 2 & 0 & 0 & 0 & 0 & 0 \\
-		& 3 & 1 & 1 & 1 & 1 & 1 \\
-		& 4 & 1 & 1 & 1 & 1 & 1 \\
-		& 5 & 0 & 0 & 0 & 0 & 0 \\
-		\bottomrule
-	\end{tabular}
-	\hspace*{-1cm}	
-\end{table}
+% \begin{table}[H]
+% 	\centering
+% 	\caption{Different Planned Missingness Designs}
+% 	\setlength{\tabcolsep}{0.45cm}
+% 	\label{tab:table14}
+% 	\hspace*{-1cm}
+% 	\begin{tabular}{c|c|ccccc}
+% 		\toprule
+% 		Design & Day & Q1 & Q2 & Q3 & Q4 & Q5 \\
+% 		\midrule
+% 		\multirow{5}{*}{Split Form}
+% 		& 1 & 1 & 1 & 0 & 0 & 1 \\
+% 		& 2 & 0 & 0 & 1 & 1 & 1 \\
+% 		& 3 & 0 & 1 & 1 & 0 & 1 \\
+% 		& 4 & 1 & 0 & 1 & 1 & 0 \\
+% 		& 5 & 0 & 1 & 0 & 1 & 1 \\
+% 		\midrule
+% 		\midrule
+% 		\multirow{5}{*}{Altered Split Form}
+% 		& 1 & 1 & 1 & 1 & 1 & 1 \\
+% 		& 2 & 1 & 1 & 1 & 1 & 1 \\
+% 		& 3 & 0 & 0 & 1 & 1 & 1 \\
+% 		& 4 & 1 & 1 & 0 & 1 & 0 \\
+% 		& 5 & 0 & 1 & 1 & 0 & 1 \\
+% 		\midrule
+% 		\midrule
+% 		\multirow{5}{*}{Wave Missingness}
+% 		& 1 & 1 & 1 & 1 & 1 & 1 \\
+% 		& 2 & 0 & 0 & 0 & 0 & 0 \\
+% 		& 3 & 1 & 1 & 1 & 1 & 1 \\
+% 		& 4 & 1 & 1 & 1 & 1 & 1 \\
+% 		& 5 & 0 & 0 & 0 & 0 & 0 \\
+% 		\bottomrule
+% 	\end{tabular}
+% 	\hspace*{-1cm}	
+% \end{table}
 
@@
 \par
+measure of the proportion of information that is lost as a result of missing data
 
@@
 From here, the results from each PM design were evaluated based on bias, percent bias, mean squared error (MSE), coverage, confidence interval (CI) length, and the fraction of missing information (FMI).
-The FMI is a measure of how much of the MI sample variance comes from differences between imputations.
+The FMI is a measure of the fraction of information that is lost due to missing data.
 In addition to comparing the results between each of the PM designs, the same analyses were also performed before missingness was imposed.
@@
 To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days.
-While this fact was accounted for in the original simulations, it was not in this set of simulations.
+This set of simulations reduced the correlations between survey questions to study the impact lower correlation between survey question answers.
+This was done to simulate a scenario where researchers have a questionnaire that they do not expect any of the answers to be obviously related.
+To investigate this, the correlation betwen the variables was reduced by half.\par
+
+% While this fact was accounted for in the original simulations, it was not in this set of simulations.
 If the probability of answering "yes" on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables.
 This implies that each of the questions are conditionally independent of each other given the baseline variables.
-If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal.
-To investigate this, the correlation of the variables was scaled by 0.5.\par
 \subsubsection{High Time Effect}

### 2018-06-07 Documentation/response.Rnw
f

@@
 
-{\bf Our response goes here.}\\
-This has been addressed.  Please see the new figures that are red and blue.  Tables INSERT NUMBERS!.
+{\bf The analysis model contains only one of the survey questions, but the other survey questions are used in the imputation model to impute the missing values of the question used in the analysis model.
+An example of the missingness pattern fo rlow levels of missingness for split design can be seen in figure 1 in the left-most image.
+}\\
 
@@
 
-{\bf Our response goes here.}\\
-The reviewer is correct.  We have replaced those tables with new figures.....
+{\bf We have removed this table from the manuscript and replaced with this Figure 1.  Figure 1 shows an example of the missingness patterns for one single participant.  }\\
 
@@
 
-{\bf Our response goes here.}\\
-Yes this is for one participant.
-We have removed this table.
-We have replaced these with figures.
-The figure give an example of what it would look like for one individual, but each individual will have a different set of missing questions.
+{\bf The table that the reviewer is referring to has been removed from the manuscript.
+It has been replaced by figure 1 and it is indeed and example of the missingness design for one single individual.
+}\\
 
@@
 
-{\bf Our response goes here.}\\
-We agree with the description of FMI.  In spirit it is accounting for how much missing data there is.  CHANGE IN TEXT.
+{\bf We have changed this sentence to now read: ``The FMI is a measure of the fraction of information that is lost due to missing data."\\
 
-Let me read the FMI section and see what they are talkin gabout here.
+We have changed this sentence to read ``In addition to comparing the results between each of the PM designs, the same analyses were also performed before missingness was imposed." We believe this addresses the reveiwers concern.
+\\
 
-If you mean that they are all the same for different planned missingness patterns that is not correct.  We don't fully understan this statement from the reviewer.
+Finally, the bias and average bias are found by averaging across the different simulations.  }\\
 
@@
 
-{\bf Our response goes here.}\\
-We disagree politely.  Here is why........
+{\bf Type I error rate refers to the rate at which the null hypothesis is rejected given that the null hypothesis is true.
+In this case, we are implicitly testing the null hypothesis that each regression coefficient is equal to the known value.
+(e.g.
+$\beta_1 = 0.28$).
+Since we know the true values of our population parameters, and we are generating simulated data sets based on those values our coverage rates are in fact estimating $1 - \alpha$, where $\alpha$ is the probability of making a type I error.
+There is always a type I error rate, even for parameter values different than 0.
+It is simply calculated by measuring how often the test is rejected (i.e.
+how often a confidence interval misses the true parameter value) conditional on the null hypothesis being true.}\\
 
@@
 {\bf Our response goes here.}\\
-We are using inter-item correlation.  Just specify.
+The correlation matrix used needs to be added to the paper.
 
@@
 
-{\bf Our response goes here.}\\
-1.) Either add this if it's easy.
-
-OR
-
-2.) The main interest of this paper was the fixed effects.  So we excluded the variance of the random intercept.
+{\bf The main interest of this paper was the fixed effects coefficients, so we excluded analysis of the variance of the random intercept.  }\\
+% 1.) Either add this if it's easy.  
+% 
+% OR
+% 
+% 2.) The main interest of this paper was the fixed effects.  So we excluded the variance of the random intercept.
 

### 2018-06-08 Documentation/response.Rnw
Had to commit

--- 2018-06-07 Documentation/response.Rnw
@@
 
- We would like to thank the reviewers for their helpful comments on our manuscript.
-We have addressed each of these comments in our revised manuscript, as well as provided a point-by-point response below.
-Reviewer comments are in regular font and our responses are bold-faced.
-
- We should also note that this revision is a little bit unusual in that the main author of the first submission has been dropped from this manuscript.
-Since then two other authors have been added to this manuscript, which has had parts largely re-written and the simulation study has been completely overhauled to conform to  standards of reproducible research.
+We would again like to thank the reviewers for their helpful comments on the manuscript.
+As the study was reexamined and reworked, they served as very helpful guidelines.
+We have addressed each of these comments in the revised manuscript, as well as provided a point-by-point response below.
+Reviewer comments are in normal font and our responses are bold-faced.
 
@@
 
-{\bf With any high frequency longitudinal study, there is a high probability of dropout.
-Using planned missingness reduces the burden on the participants, which often lowers the probability of drop out due to survey fatigue.
-It can also lower the cost of a longitudinal study.
-We believe this is addressed in the second sentence of the first paragraph of the new draft of the manuscript.
-}\\
-
-%With a high frequency longitudinal there is is a high probabilty of dropout.  Using planned missingesns reduces the burden on participants.  CITE where we talk about this in the paper.
+{\bf This first iteration of this paper did not provide adequate context. This particular concern is addressed in the addition of an introductory paragraph.}\\
 
@@
 
-{\bf We chose to work with a multi-level model in this case because that was the analysis model of interest in Pellowski et.
-al.
-(2016).
-The data used in the aforementioned paper was used a basis for our simulation study, and so we wanted to continue to use the analysis model that was of interest in the original paper.
-The justification for using that model can be found in Pellowski et.
-al.
-(2016).
-}\\
-%In the paper by Pellofski YEAR, that was the origianl model of interest.  We are simply using that model of interest in our simulation, now with the addition of planned missingess.
+{\bf Our interest in studying a multi-level regression model stems from a lack of attention in recent literature. This is now addressed in the paper.}\\
 
@@
 
-{\bf We believe that we have addressed this issue by re-writing and cleaning up large sections of the manuscript, which we believe now contain the appropriate level of detail.  }\\
-%We have re-written this whole section and we believe it now has the appropriate level of detail.
+{\bf Much of this section was edited out and restructured for brevity and to avoid redundancies.}\\
 
@@
 
-{\bf }\\
-Complete case analysis is highly inefficient here because we would be removing nearly all of the observations.
-Multiple imputation gets around this and allows for more efficient estiamtion of the parameters.
+{\bf We felt that as Sankhya B is an applied journal, some technical details could be omitted here. That said, this section has been rewritten with your comment in mind.}\\
 
@@
 
-{\bf Certainly any simulation study suffers from the flaw that it is difficult to determined how generalizable the results are beyond the specific settings of the particular simulation study.
-However, the study design in Pellowski et.
-al.
-(2016) is a common design and the planned missingness designs studied here are also common desgined.
-\\
-
-That being said, we believe that results would be similar if the response was continuous and / or different parameters were chosen for the covariates.
-The sample size of this study is relatively small, but we still see reasonable results.
-In Pellowski et.
-al.
-(2016) the number of participants was 59.
-Sample sizes can be this low when attempting to collect data longitudinally at high frequencies such as daily (or even more often) due to the fact the participants need to be highly engaged in the study.\\
-
-There should have been two omitted responses for Day 5 in the Split Form example in Table 4.  This correction has been made.\\  
-}\\
-
-How to respond to this: ``Are these sample sizes typical?
-And is there good reason to believe that a different design would have produced the same results?
-For example, is it reasonable to assume that there are no context or order effects in these questions that might play out in at least the split form designs?"
+{\bf Dr. Matthews??? As for only one response being omitted for day 5 the first iteration had an inaccurate representation of the designs.}\\
 
@@
 
-{\bf The true parameter values have been added to this table, which is now Table 5. }\\
+{\bf This would be very useful, and has been added! DR. MATTHEWS CAN WE ADD THIS IS THE TABLES}\\
 
@@
 
-{\bf We have removed the mention of these cut-offs.  However, they are based on suggestions put forth in Collins, L. M., Schafer, J. L., & Kam, C.-M. (2001)}\\
+{\bf DR. MATTHEWS???}\\
 
 \item In section 4.3, the authors seem to confuse the idea of bias and efficiency.\\
-{\bf That is correct.  The mentions of efficiency have been removed from this section.  }\\
 
+{\bf This mistake has been corrected, thank you!}\\
 \end{itemize}
@@
 
-{\bf Our response goes here.}\\
-The complete data structure is best fit with mixed effects model and mimic the original data.
-We now exgend it to the scenario where we have missing by design.
-For the structure of this data, we believe this is the best model.
+{\bf DR. MATTHEWS??? I can rewrite to address.}\\
 
-We're using different data! That's why we didn't use a latent growth curve model.  It's not a comparison.  It's in addition to.
+\itemThe model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!\\
 
-\item The model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!\\
-
-{\bf Our response goes here.}\\
-The model has been specified correctly this time.  The reviewer is correct.
+{\bf The model equation has been rewritten to address this, and other concer}\\
 
@@
 {\bf Our response goes here.}\\
-This has been addressed.  Please see the new figures that are red and blue.  Tables INSERT NUMBERS!.
 
@@
 {\bf Our response goes here.}\\
-The reviewer is correct.  We have replaced those tables with new figures.....
 
@@
 {\bf Our response goes here.}\\
-Yes this is for one participant.
-We have removed this table.
-We have replaced these with figures.
-The figure give an example of what it would look like for one individual, but each individual will have a different set of missing questions.
 
@@
 {\bf Our response goes here.}\\
-We agree with the description of FMI.  In spirit it is accounting for how much missing data there is.  CHANGE IN TEXT.
-
-Let me read the FMI section and see what they are talkin gabout here.
-
-If you mean that they are all the same for different planned missingness patterns that is not correct.  We don't fully understan this statement from the reviewer.
 
@@
 {\bf Our response goes here.}\\
-We disagree politely.  Here is why........
 
@@
 {\bf Our response goes here.}\\
-We are using inter-item correlation.  Just specify.
 
@@
 {\bf Our response goes here.}\\
-1.) Either add this if it's easy.
-
-OR
-
-2.) The main interest of this paper was the fixed effects.  So we excluded the variance of the random intercept.
 
@@
 {\bf Our response goes here.}\\
-There was a major change to this section.  We have added more information that hopefully satisfies the reviewer.
 
@@
 
-%\bibliographystyle{plos2015}
-%\bibliography{brophyTeeth}
+\bibliographystyle{plos2015}
+\bibliography{brophyTeeth}
 

### 2018-06-08 Documentation/response.tex
Had to commit

@@
 
- We would again like to thank the reviewers for their helpful comments on our manuscript.
-We have addressed each of these comments in our revised manuscript, as well as provided a point-by-point response below.
+We would again like to thank the reviewers for their helpful comments on the manuscript.
+As the study was reexamined and reworked, they served as very helpful guidelines.
+We have addressed each of these comments in the revised manuscript, as well as provided a point-by-point response below.
 Reviewer comments are in normal font and our responses are bold-faced.
@@
 
-\item {[Issues]} that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs.
-Further, there is no justification for an inherent interest in a multilevel model.
-Why is this of greater interest than a latent growth curve or a simple repeated measures model?\\
+\item {[Issues]} that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs.\\
 
-{\bf Our response goes here.}\\
+{\bf This first iteration of this paper did not provide adequate context. This particular concern is addressed in the addition of an introductory paragraph.}\\
+
+\item {[There]} is no justification for an inherent interest in a multilevel model. Why is this of greater interest than a latent growth curve or a simple repeated measures model?\\
+
+{\bf Our interest in studying a multi-level regression model stems from a lack of attention in recent literature. This is now addressed in the paper.}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf Much of this section was edited out and restructured for brevity and to avoid redundancies.}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf We felt that as Sankhya B is an applied journal, some technical details could be omitted here. That said, this section has been rewritten with your comment in mind.}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf Dr. Matthews??? As for only one response being omitted for day 5 the first iteration had an inaccurate representation of the designs.}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf This would be very useful, and has been added! DR. MATTHEWS CAN WE ADD THIS IS THE TABLES}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf DR. MATTHEWS???}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf This mistake has been corrected, thank you!}\\
 \end{itemize}
@@
 
-{\bf Our response goes here.}\\
+{\bf DR. MATTHEWS??? I can rewrite to address.}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf The model equation has been rewritten to address this, and other concer}\\
 

### 2018-06-08 Documentation/manuscript.Rnw
Had to commit

--- 2018-05-31 Documentation/manuscript.Rnw
@@
 \label{intro}
-Planned Missingness (PM) designs are a type of experimental design in which some of the data is predetermined to be missing.
+
+Often, studies are conducted longitudinally; measuring participants on numerous separate occasions.
+This allows researchers to observe how a measurement may change over time.
+In theory, administering a survey once a month would be successful.
+However, in practice, as surveys become longer and more frequent, participants may begin to provide ingenuine responses or drop out of the study entirely.
+To combat this issue, researchers may attempt to shorten the survey or decrease the measurement frequency.
+Merely truncating a survey results in lost information and infrequent administration does not provide a clear picture of participants' evolution over time.
+In answer to a difficult question, many researchers have turned to planned missingness when designing experiments.
+
+Planned missingness (PM) designs are a type of experimental design in which some of the data is predetermined to be missing.
 While it may seem counterproductive to deliberately omit data from the collection process, PM designs have been shown to reduce both participant burden \citep{graham2006planned, saris20048} and the costs of a study \citep{graham2001planned}.
@@
 For example, PM designs have been used in the study of longitudinal growth curves \citep{graham2001planned, mcardle1997expanding}, business research \citep{shoemaker1973principles}, behavioral studies \citep{harel2015designed}, biostatistics \citep{andres2006partial, wacholder1994partial}, and educational assessments \citep{zeger1997efficient, sirotnik1977incidence}.
-This paper focuses on two of the simplest and most applicable PM designs; the Split Form design \citep{raghunathan1995split} and the Wave Missingness design \citep{little2013planned}.
+This paper focuses on two of the simplest and most applicable PM designs; the Split Form design \citep{raghunathan1995split} and the Wave Missingness design \citep{little2013planned} and their application in a longitudinal study utilizing a multi-level regression model, as it lacks coverage in recent literature.
 While this paper covers these designs in more detail later, broadly speaking, the Split Form design entails measuring fewer points on a single measurement occasion \citep{raghunathan1995split}.
@@
 The second uses an X-block and nine others with 10\% of the items each.
-If the teams decide that each form will contain the X-block and two of the other blocks, then the second team will have 36 %\textbf{(28?
-8 choose 2?)} %No.
-9 choose 2 = 36.
-total forms while the first team can proceed with 3. 
+If the teams decide that each form will contain the X-block and two of the other blocks, then the second team will have 36 total forms while the first team can proceed with 3.
 %\textbf{This is all assuming that the blocks represent the optimal question grouping.
@@
 
-\textbf{This method, hereafter referred to as Split Form planned missingness and illustrated in \ref{fig:formillustration}, involves meaningfully selecting an X block of $p$ questions and then randomly excluding $k$ questions on each day.
-In a way treating each item as its own block \citep{silvia2014planned}.
 This is simple in theory, but for traditional paper surveys this is very difficult to execute.
 Fortunately, recent technological advances have made the use of electronic questionaires more readily accessible.
-In this environment form randomization can be automated and the creation of numerous unique forms is no longer an issue.} Using this method, researchers reap the benefits of including all possible variable relationships through increased forms without the difficulty caused by manually building these forms.
+In this environment form randomization can be automated and the creation of numerous unique forms is no longer an issue.
+This ability allows another method, hereafter referred to as Split Form planned missingness and illustrated in Figure \ref{fig:formillustration}, to be implemented.
+Split Form is the random exclusion of $k$ questions on a given day, treating each item as its own block \citep{silvia2014planned}.
+Using this method, researchers reap the benefits of including all possible variable relationships through increased forms without the difficulty caused by manually building these forms.
 \par

### 2018-06-08 Documentation/manuscript.tex
Had to commit

@@
-% Predefine some figures
-
 \RequirePackage{fix-cm}
@@
 
+% Predefine some figures
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'dplyr' was built under R version 3.4.3}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'kableExtra' was built under R version 3.4.4}}\end{kframe}
+\end{knitrout}
+
 \title{Comparing Different Planned Missingness Designs in Longitudinal Studies}
 
-\author{Josephine Wood \and Gregory J. Matthews \and Nicholas Illenberger \and Jennifer Pellowski \and Ofer Harel}
+\author{Josephine Wood \and Gregory J. Matthews \and Jennifer Pellowski \and Ofer Harel}
 
@@
 \label{intro}
-Planned Missingness (PM) designs are a type of experimental design in which some of the data is predetermined to be missing.
+
+Often, studies are conducted longitudinally; measuring participants on numerous separate occasions.
+This allows researchers to observe how a measurement may change over time.
+In theory, administering a survey once a month would be successful.
+However, in practice, as surveys become longer and more frequent, participants may begin to provide ingenuine responses or drop out of the study entirely.
+To combat this issue, researchers may attempt to shorten the survey or decrease the measurement frequency.
+Merely truncating a survey results in lost information and infrequent administration does not provide a clear picture of participants' evolution over time.
+In answer to a difficult question, many researchers have turned to planned missingness when designing experiments.
+
+Planned missingness (PM) designs are a type of experimental design in which some of the data is predetermined to be missing.
 While it may seem counterproductive to deliberately omit data from the collection process, PM designs have been shown to reduce both participant burden \citep{graham2006planned, saris20048} and the costs of a study \citep{graham2001planned}.
-Moreover, PM designs can actually increase the quality of collected data by increasing the breadth of a study \citep{little2013planned} as well as decreasing the effects of assessment reactivity and rates of unplanned missingness \cite{harel2015designed}.
+Moreover, PM designs can actually increase the quality of collected data by increasing the breadth of a study \citep{little2013planned} as well as decreasing the effects of assessment reactivity and rates of unplanned missingness \citep{harel2015designed}.
 We further note that while PM designs decrease the efficiency of estimators \citep{rhemtulla2016asymptotic}, decreasing the cost per participant may allow researchers to enroll more participants in a study, offsetting some of the efficiency loss.
@@
 The second uses an X-block and nine others with 10\% of the items each.
-If the teams decide that each form will contain the X-block and two of the other blocks, then the second team will have 36 \textbf{(28?
-8 choose 2?)} total forms while the first team can proceed with 3.
-\textbf{This is all assuming that the blocks represent the optimal question grouping.
+If the teams decide that each form will contain the X-block and two of the other blocks, then the second team will have 36 total forms while the first team can proceed with 3.
+%\textbf{This is all assuming that the blocks represent the optimal question grouping.
 If this is not known, to account for possible relationships and correlation between questions, the teams would need to consider all possible blocks and create forms for every block configuration.
@@
 
-\textbf{This method, hereafter referred to as Split Form planned missingness and illustrated in \ref{fig:formillustration}, involves meaningfully selecting an X block of $n$ questions and then randomly excluding $k$ questions on each day.
-In a way treating each item as its own block \citep{silvia2014planned}.
 This is simple in theory, but for traditional paper surveys this is very difficult to execute.
 Fortunately, recent technological advances have made the use of electronic questionaires more readily accessible.
-In this environment form randomization can be automated and the creation of numerous unique forms is no longer an issue.} Using this method, researchers reap the benefits of including all possible variable relationships through increased forms without the difficulty caused by manually building these forms.
+In this environment form randomization can be automated and the creation of numerous unique forms is no longer an issue.
+This ability allows another method, hereafter referred to as Split Form planned missingness and illustrated in Figure \ref{fig:formillustration}, to be implemented.
+Split Form is the random exclusion of $k$ questions on a given day, treating each item as its own block \citep{silvia2014planned}.
+Using this method, researchers reap the benefits of including all possible variable relationships through increased forms without the difficulty caused by manually building these forms.
 \par
@@
 \begin{equation}
-\widehat{\theta} = \sum_{n=1}^{M} \widehat{\theta_n}.
+\widehat{\theta} = \sum_{n=1}^{M} \frac{1}{M} \widehat{\theta_n}.
 \end{equation}
 
-From here we can compute the sample variance of this estimate by calculating the between-imputation component, $B_M = \frac{1}{(M-1)}\sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2$, and the within-imputation component, $W_M = \frac{1}{(M)}\sum_{n=1}^{M} S_n^2$.
+From here we can compute the sample variance of this estimate by calculating the between-imputation component, $B_M = \frac{1}{(M-1)}\sum_{n=1}^{M} (\widehat{\theta_n} - \widehat{\theta})^2$, and the within-imputation component, $W_M = \frac{1}{M}\sum_{n=1}^{M} S_n^2$.
 These components are combined to obtain the overall sample variance of our MI estimate as follows:
@@
 Generally, as the level of missingness decreases the number of imputations needed does as well.
-If less than 20\% of the requisite data is missing, for instance, five or tien imputations will suffice \citep{raghunathan2015missing}.
+\textbf{Greg: IS THIS TRUE?} If less than 20\% of the requisite data are missing, for instance, five or ten imputations will suffice \citep{raghunathan2015missing}.
 However, at its roots, MI is a simulation technique and thus, the greater $M$ is the more stable our estimates become \citep{harel2007inferences}.
@@
 \end{align*}
-where $\beta_{0j} = \gamma_0 + \alpha_j$ and $\alpha_j \sim \mathcal{N}(0,\sigma_\alpha^2)$. \\ \\ 
+where $\beta_{0j} = \gamma_0 + \alpha_j$ and $\alpha_j \sim N(0,\sigma_\alpha^2)$. \\ \\ 
 Additionally, note: \\ \\
-$p_{ij} = 1$ when participant $p$ did not adhere to the ART on day $i$, 0 otherwise. \\
-$DrinkYN = 1$ if participant $p$  drank on day $i$, 0 otherwise.\\
-$ZAlcTox =$ participant $p$'s Z-transformed score on an alcohol-antiretroviral interactive toxicity scale developed by Kalichman \cite{kalichman2009prevalence}. \\
-$Day =$ Day $i$ of the study, 0-44. \\
-$j =$ participant index, 1-60. \\
-
-Based on the observed data, the true values of the parameters, $\gamma_0$, $\beta_1$, $\beta_2$, $\beta_3$, and $\sigma_\alpha^2$ were found to be -2.29, 0.28, 0.64, 0.01, and \textbf{1.0???} respectively.
-\par
-Once the samples were drawn, they were transformed under the three different missingness structures.
+\begin{itemize}
+\item $p_{ij} = 1$ when participant $p$ did not adhere to the ART on day $i$, 0 otherwise \\
+\item $DrinkYN = 1$ if participant $p$  drank on day $i$, 0 otherwise\\
+\item $ZAlcTox =$ participant $p$'s Z-transformed score on an alcohol-antiretroviral interactive toxicity scale developed by Kalichman \cite{kalichman2009prevalence} \\
+\item $Day =$ Day $i$ of the study, 0-44 \\
+\item $j =$ participant index, 1-60 \\
+\end{itemize}.
+
+Based on the observed data, the true values of the parameters, $\gamma_0$, $\beta_1$, $\beta_2$, $\beta_3$, and $\sigma_\alpha^2$ were found to be -2.29, 0.28, 0.64, 0.01, and 1.12, respectively. \par
+Once the samples were drawn, missingness was added under three different structures.
 These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed.
-To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in \textbf{Table \ref{tab:table14} (do we want the illustration here instead?
-or in both places?)}.
+To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Table \ref{tab:table14} \textbf{Greg: I think we need either only the table or only the illustration.
+Not sure we need both.}.
 As in the previous tables, "1" indicates an observed occasion while "0" indicates a missing one.
@@
 
-Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions.
+%FIX THIS: THIS SOUNDS LIKE WE ADDED MORE MISSINGNESS. FIXED
+For each different designed missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions.
 Previous work by \citet{rhemtulla2014planned} found that for low levels of missingness Split Form design outperforms the Wave Missingness design in capturing latent growth curve model parameters.
@@
 In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable.
-To do this we changed the value of the parameters $\gamma_0$, $\beta_1$, $\beta_2$, and $\beta_3$ to -4.56, 0.14, 0.32, and 0.01 respectively.
-Note that instead of increasing the value of $\beta_3$, the slope for time effect, all the other parameters were decreased.
-This was done because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1.
-Decreasing the other variables effects ensured that time has a disproportionate effect without this problem.
+To do this held the values of $\gamma_0$, $\beta_1$, $\beta_2$ the same and increaed the effect of time (i.e.
+$\beta_3$) by ten times.
 The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point.
@@
 This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design.
-Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:prelim} \textbf{not here yet}.
+Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:prelim}.
 Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[!h]
+
+\caption{\label{tab:unnamed-chunk-2}\label{tab:prelim} Primary Results (N = 60)}
+\centering
+\resizebox{\linewidth}{!}{\begin{tabular}[t]{l|l|r|l|r|l|r}
+\hline
+Scenario & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length\\
+\hline
+ & $\gamma_0$ & 0.042 & -1.86\% & 0.018 & 98.8\% & 0.700\\
+
+ & $\beta_1$ & -0.103 & -36.45\% & 0.871 & 95.4\% & 3.040\\
+
+ & $\beta_2$ & 0.008 & 1.26\% & 0.024 & 93.4\% & 0.585\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash Primary Analysis (n = 60)} & $\beta_3$ & 0.000 & -0.83\% & 0.000 & 94.2\% & 0.017\\
+\cline{1-7}
+ & $\gamma_0$ & 0.014 & -0.59\% & 0.008 & 98.4\% & 0.424\\
+
+ & $\beta_1$ & -0.038 & -13.5\% & 0.135 & 95.2\% & 1.384\\
+
+ & $\beta_2$ & 0.006 & 0.86\% & 0.007 & 94.4\% & 0.319\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash Increased Sample Size (n = 120)} & $\beta_3$ & 0.000 & -0.87\% & 0.000 & 95.3\% & 0.012\\
+\cline{1-7}
+ & $\gamma_0$ & 0.044 & -1.91\% & 0.018 & 98.8\% & 0.700\\
+
+ & $\beta_1$ & -0.067 & -23.67\% & 0.298 & 95.8\% & 2.001\\
+
+ & $\beta_2$ & 0.007 & 1.11\% & 0.024 & 93.5\% & 0.585\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash Low Inter-Survey Correlation (n = 60)} & $\beta_3$ & 0.000 & -1.17\% & 0.000 & 94\% & 0.017\\
+\cline{1-7}
+ & $\gamma_0$ & -0.020 & 0.44\% & 0.114 & 96.2\% & 1.368\\
+
+ & $\beta_1$ & -6.781 & -4815.84\% & 136.550 & 96.6\% & 88815.966\\
+
+ & $\beta_2$ & 0.014 & 4.54\% & 0.047 & 95.7\% & 0.832\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash High Time Effect (n = 60)} & $\beta_3$ & 0.000 & -0.98\% & 0.000 & 94.5\% & 0.039\\
+\hline
+\end{tabular}}
+\end{table}
+
+\end{knitrout}
 
@@
 
-\caption{\label{tab:primary}Primary Results (N = 60)}
+\caption{\label{tab:primary}\label{} Primary Results (N = 60)}
 \centering
-\resizebox{\linewidth}{!}{\begin{tabular}[t]{l|l|l|r|r|r|r|r|r}
+\resizebox{\linewidth}{!}{\begin{tabular}[t]{l|l|l|r|l|r|l|r|r}
 \hline
@@
 \hline
- &  & $\gamma_0$ & 0.042 & -1.817 & 0.018 & 0.988 & 0.702 & 0.002\\
-\cline{3-9}
- &  & $\beta_1$ & -0.071 & -25.122 & 0.269 & 0.983 & 2.534 & 0.236\\
-\cline{3-9}
- &  & $\beta_2$ & 0.008 & 1.253 & 0.024 & 0.932 & 0.585 & 0.000\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.886 & 0.000 & 0.944 & 0.017 & 0.001\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.039 & -1.684 & 0.018 & 0.990 & 0.709 & 0.011\\
-\cline{3-9}
- &  & $\beta_1$ & -0.102 & -36.186 & 0.271 & 0.998 & 3.500 & 0.534\\
-\cline{3-9}
- &  & $\beta_2$ & 0.008 & 1.207 & 0.024 & 0.933 & 0.586 & 0.002\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.419 & 0.000 & 0.946 & 0.017 & 0.007\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.028 & -1.242 & 0.027 & 0.985 & 0.791 & 0.030\\
-\cline{3-9}
- &  & $\beta_1$ & -0.107 & -38.054 & 0.418 & 0.988 & 4.268 & 0.630\\
-\cline{3-9}
- &  & $\beta_2$ & 0.012 & 1.869 & 0.027 & 0.932 & 0.613 & 0.005\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.471 & 0.000 & 0.946 & 0.020 & 0.020\\
+ &  & $\gamma_0$ & 0.042 & -1.82\% & 0.018 & 98.8\% & 0.702 & 0.002\\
+
+ &  & $\beta_1$ & -0.071 & -25.12\% & 0.269 & 98.3\% & 2.534 & 0.236\\
+
+ &  & $\beta_2$ & 0.008 & 1.25\% & 0.024 & 93.2\% & 0.585 & 0.000\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.89\% & 0.000 & 94.4\% & 0.017 & 0.001\\
+
+ &  & $\gamma_0$ & 0.039 & -1.68\% & 0.018 & 99\% & 0.709 & 0.011\\
+
+ &  & $\beta_1$ & -0.102 & -36.19\% & 0.271 & 99.8\% & 3.500 & 0.534\\
+
+ &  & $\beta_2$ & 0.008 & 1.21\% & 0.024 & 93.3\% & 0.586 & 0.002\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.42\% & 0.000 & 94.6\% & 0.017 & 0.007\\
+
+ &  & $\gamma_0$ & 0.028 & -1.24\% & 0.027 & 98.5\% & 0.791 & 0.030\\
+
+ &  & $\beta_1$ & -0.107 & -38.05\% & 0.418 & 98.8\% & 4.268 & 0.630\\
+
+ &  & $\beta_2$ & 0.012 & 1.87\% & 0.027 & 93.2\% & 0.613 & 0.005\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.47\% & 0.000 & 94.6\% & 0.020 & 0.020\\
 \cline{1-9}
- &  & $\gamma_0$ & 0.042 & -1.832 & 0.018 & 0.990 & 0.701 & 0.001\\
-\cline{3-9}
- &  & $\beta_1$ & -0.069 & -24.401 & 0.283 & 0.983 & 2.508 & 0.218\\
-\cline{3-9}
- &  & $\beta_2$ & 0.008 & 1.272 & 0.024 & 0.933 & 0.585 & 0.000\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.949 & 0.000 & 0.944 & 0.017 & 0.001\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.040 & -1.760 & 0.018 & 0.988 & 0.704 & 0.007\\
-\cline{3-9}
- &  & $\beta_1$ & -0.117 & -41.573 & 0.277 & 0.990 & 3.385 & 0.508\\
-\cline{3-9}
- &  & $\beta_2$ & 0.008 & 1.286 & 0.024 & 0.931 & 0.585 & 0.002\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.986 & 0.000 & 0.945 & 0.017 & 0.005\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.036 & -1.592 & 0.021 & 0.989 & 0.742 & 0.022\\
-\cline{3-9}
- &  & $\beta_1$ & -0.158 & -56.111 & 0.394 & 0.992 & 4.336 & 0.662\\
-\cline{3-9}
- &  & $\beta_2$ & 0.012 & 1.809 & 0.026 & 0.934 & 0.601 & 0.006\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.487 & 0.000 & 0.941 & 0.018 & 0.021\\
+ &  & $\gamma_0$ & 0.042 & -1.83\% & 0.018 & 99\% & 0.701 & 0.001\\
+
+ &  & $\beta_1$ & -0.069 & -24.4\% & 0.283 & 98.3\% & 2.508 & 0.218\\
+
+ &  & $\beta_2$ & 0.008 & 1.27\% & 0.024 & 93.3\% & 0.585 & 0.000\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.95\% & 0.000 & 94.4\% & 0.017 & 0.001\\
+
+ &  & $\gamma_0$ & 0.040 & -1.76\% & 0.018 & 98.8\% & 0.704 & 0.007\\
+
+ &  & $\beta_1$ & -0.117 & -41.57\% & 0.277 & 99\% & 3.385 & 0.508\\
+
+ &  & $\beta_2$ & 0.008 & 1.29\% & 0.024 & 93.1\% & 0.585 & 0.002\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.99\% & 0.000 & 94.5\% & 0.017 & 0.005\\
+
+ &  & $\gamma_0$ & 0.036 & -1.59\% & 0.021 & 98.9\% & 0.742 & 0.022\\
+
+ &  & $\beta_1$ & -0.158 & -56.11\% & 0.394 & 99.2\% & 4.336 & 0.662\\
+
+ &  & $\beta_2$ & 0.012 & 1.81\% & 0.026 & 93.4\% & 0.601 & 0.006\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.49\% & 0.000 & 94.1\% & 0.018 & 0.021\\
 \cline{1-9}
- &  & $\gamma_0$ & 0.040 & -1.765 & 0.018 & 0.988 & 0.703 & 0.005\\
-\cline{3-9}
- &  & $\beta_1$ & -0.094 & -33.425 & 0.238 & 0.993 & 2.995 & 0.433\\
-\cline{3-9}
- &  & $\beta_2$ & 0.008 & 1.251 & 0.024 & 0.934 & 0.585 & 0.001\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.875 & 0.000 & 0.943 & 0.017 & 0.002\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.028 & -1.223 & 0.018 & 0.995 & 0.744 & 0.051\\
-\cline{3-9}
- &  & $\beta_1$ & -0.088 & -31.121 & 0.240 & 0.992 & 3.497 & 0.718\\
-\cline{3-9}
- &  & $\beta_2$ & 0.009 & 1.436 & 0.024 & 0.933 & 0.588 & 0.006\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.326 & 0.000 & 0.946 & 0.017 & 0.025\\
-\cline{2-9}
- &  & $\gamma_0$ & -0.004 & 0.194 & 0.020 & 0.995 & 0.962 & 0.224\\
-\cline{3-9}
- &  & $\beta_1$ & -0.080 & -28.263 & 0.234 & 0.985 & 3.791 & 0.886\\
-\cline{3-9}
- &  & $\beta_2$ & 0.011 & 1.700 & 0.024 & 0.938 & 0.607 & 0.032\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -3.304 & 0.000 & 0.970 & 0.020 & 0.148\\
+ &  & $\gamma_0$ & 0.040 & -1.76\% & 0.018 & 98.8\% & 0.703 & 0.005\\
+
+ &  & $\beta_1$ & -0.094 & -33.42\% & 0.238 & 99.3\% & 2.995 & 0.433\\
+
+ &  & $\beta_2$ & 0.008 & 1.25\% & 0.024 & 93.4\% & 0.585 & 0.001\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.88\% & 0.000 & 94.3\% & 0.017 & 0.002\\
+
+ &  & $\gamma_0$ & 0.028 & -1.22\% & 0.018 & 99.5\% & 0.744 & 0.051\\
+
+ &  & $\beta_1$ & -0.088 & -31.12\% & 0.240 & 99.2\% & 3.497 & 0.718\\
+
+ &  & $\beta_2$ & 0.009 & 1.44\% & 0.024 & 93.3\% & 0.588 & 0.006\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.33\% & 0.000 & 94.6\% & 0.017 & 0.025\\
+
+ &  & $\gamma_0$ & -0.004 & 0.19\% & 0.020 & 99.5\% & 0.962 & 0.224\\
+
+ &  & $\beta_1$ & -0.080 & -28.26\% & 0.234 & 98.5\% & 3.791 & 0.886\\
+
+ &  & $\beta_2$ & 0.011 & 1.7\% & 0.024 & 93.8\% & 0.607 & 0.032\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -3.3\% & 0.000 & 97\% & 0.020 & 0.148\\
 \hline
@@
 \centering
-\resizebox{\linewidth}{!}{\begin{tabular}[t]{l|l|l|r|r|r|r|r|r}
+\resizebox{\linewidth}{!}{\begin{tabular}[t]{l|l|l|r|l|r|l|r|r}
 \hline
@@
 \hline
- &  & $\gamma_0$ & 0.013 & -0.577 & 0.008 & 0.985 & 0.424 & 0.001\\
-\cline{3-9}
- &  & $\beta_1$ & -0.041 & -14.633 & 0.134 & 0.975 & 1.690 & 0.183\\
-\cline{3-9}
- &  & $\beta_2$ & 0.006 & 0.867 & 0.007 & 0.944 & 0.319 & 0.000\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.868 & 0.000 & 0.954 & 0.012 & 0.000\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.012 & -0.544 & 0.008 & 0.985 & 0.429 & 0.009\\
-\cline{3-9}
- &  & $\beta_1$ & -0.073 & -25.973 & 0.148 & 0.991 & 2.366 & 0.449\\
-\cline{3-9}
- &  & $\beta_2$ & 0.006 & 0.875 & 0.007 & 0.944 & 0.320 & 0.002\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.832 & 0.000 & 0.953 & 0.012 & 0.002\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.004 & -0.179 & 0.011 & 0.973 & 0.465 & 0.025\\
-\cline{3-9}
- &  & $\beta_1$ & -0.145 & -51.616 & 0.304 & 0.983 & 3.281 & 0.649\\
-\cline{3-9}
- &  & $\beta_2$ & 0.007 & 1.136 & 0.008 & 0.939 & 0.332 & 0.005\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & 0.243 & 0.000 & 0.944 & 0.013 & 0.010\\
+ &  & $\gamma_0$ & 0.013 & -0.58\% & 0.008 & 98.5\% & 0.424 & 0.001\\
+
+ &  & $\beta_1$ & -0.041 & -14.63\% & 0.134 & 97.5\% & 1.690 & 0.183\\
+
+ &  & $\beta_2$ & 0.006 & 0.87\% & 0.007 & 94.4\% & 0.319 & 0.000\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.87\% & 0.000 & 95.4\% & 0.012 & 0.000\\
+
+ &  & $\gamma_0$ & 0.012 & -0.54\% & 0.008 & 98.5\% & 0.429 & 0.009\\
+
+ &  & $\beta_1$ & -0.073 & -25.97\% & 0.148 & 99.1\% & 2.366 & 0.449\\
+
+ &  & $\beta_2$ & 0.006 & 0.88\% & 0.007 & 94.4\% & 0.320 & 0.002\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.83\% & 0.000 & 95.3\% & 0.012 & 0.002\\
+
+ &  & $\gamma_0$ & 0.004 & -0.18\% & 0.011 & 97.3\% & 0.465 & 0.025\\
+
+ &  & $\beta_1$ & -0.145 & -51.62\% & 0.304 & 98.3\% & 3.281 & 0.649\\
+
+ &  & $\beta_2$ & 0.007 & 1.14\% & 0.008 & 93.9\% & 0.332 & 0.005\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & 0.24\% & 0.000 & 94.4\% & 0.013 & 0.010\\
 \cline{1-9}
- &  & $\gamma_0$ & 0.013 & -0.576 & 0.008 & 0.984 & 0.425 & 0.002\\
-\cline{3-9}
- &  & $\beta_1$ & -0.032 & -11.186 & 0.129 & 0.980 & 1.677 & 0.173\\
-\cline{3-9}
- &  & $\beta_2$ & 0.006 & 0.875 & 0.007 & 0.944 & 0.319 & 0.000\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.883 & 0.000 & 0.952 & 0.012 & 0.000\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.013 & -0.553 & 0.008 & 0.983 & 0.426 & 0.005\\
-\cline{3-9}
- &  & $\beta_1$ & -0.058 & -20.672 & 0.145 & 0.996 & 2.250 & 0.414\\
-\cline{3-9}
- &  & $\beta_2$ & 0.006 & 0.879 & 0.007 & 0.944 & 0.319 & 0.001\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.917 & 0.000 & 0.951 & 0.012 & 0.002\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.011 & -0.465 & 0.008 & 0.986 & 0.434 & 0.017\\
-\cline{3-9}
- &  & $\beta_1$ & -0.112 & -39.796 & 0.228 & 0.994 & 3.245 & 0.691\\
-\cline{3-9}
- &  & $\beta_2$ & 0.006 & 0.886 & 0.007 & 0.940 & 0.321 & 0.004\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.054 & 0.000 & 0.952 & 0.012 & 0.009\\
+ &  & $\gamma_0$ & 0.013 & -0.58\% & 0.008 & 98.4\% & 0.425 & 0.002\\
+
+ &  & $\beta_1$ & -0.032 & -11.19\% & 0.129 & 98\% & 1.677 & 0.173\\
+
+ &  & $\beta_2$ & 0.006 & 0.88\% & 0.007 & 94.4\% & 0.319 & 0.000\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.88\% & 0.000 & 95.2\% & 0.012 & 0.000\\
+
+ &  & $\gamma_0$ & 0.013 & -0.55\% & 0.008 & 98.3\% & 0.426 & 0.005\\
+
+ &  & $\beta_1$ & -0.058 & -20.67\% & 0.145 & 99.6\% & 2.250 & 0.414\\
+
+ &  & $\beta_2$ & 0.006 & 0.88\% & 0.007 & 94.4\% & 0.319 & 0.001\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.92\% & 0.000 & 95.1\% & 0.012 & 0.002\\
+
+ &  & $\gamma_0$ & 0.011 & -0.46\% & 0.008 & 98.6\% & 0.434 & 0.017\\
+
+ &  & $\beta_1$ & -0.112 & -39.8\% & 0.228 & 99.4\% & 3.245 & 0.691\\
+
+ &  & $\beta_2$ & 0.006 & 0.89\% & 0.007 & 94\% & 0.321 & 0.004\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.05\% & 0.000 & 95.2\% & 0.012 & 0.009\\
 \cline{1-9}
- &  & $\gamma_0$ & 0.013 & -0.575 & 0.008 & 0.985 & 0.426 & 0.004\\
-\cline{3-9}
- &  & $\beta_1$ & -0.064 & -22.793 & 0.137 & 0.987 & 2.064 & 0.342\\
-\cline{3-9}
- &  & $\beta_2$ & 0.005 & 0.832 & 0.007 & 0.944 & 0.319 & 0.001\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.906 & 0.000 & 0.952 & 0.012 & 0.001\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.010 & -0.453 & 0.008 & 0.984 & 0.435 & 0.023\\
-\cline{3-9}
- &  & $\beta_1$ & -0.082 & -29.029 & 0.184 & 0.994 & 2.979 & 0.630\\
-\cline{3-9}
- &  & $\beta_2$ & 0.006 & 0.890 & 0.007 & 0.943 & 0.320 & 0.004\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.959 & 0.000 & 0.954 & 0.012 & 0.008\\
-\cline{2-9}
- &  & $\gamma_0$ & -0.010 & 0.428 & 0.010 & 0.988 & 0.554 & 0.179\\
-\cline{3-9}
- &  & $\beta_1$ & -0.059 & -21.087 & 0.297 & 0.970 & 3.760 & 0.859\\
-\cline{3-9}
- &  & $\beta_2$ & 0.008 & 1.204 & 0.007 & 0.952 & 0.334 & 0.040\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -2.426 & 0.000 & 0.955 & 0.014 & 0.105\\
+ &  & $\gamma_0$ & 0.013 & -0.57\% & 0.008 & 98.5\% & 0.426 & 0.004\\
+
+ &  & $\beta_1$ & -0.064 & -22.79\% & 0.137 & 98.7\% & 2.064 & 0.342\\
+
+ &  & $\beta_2$ & 0.005 & 0.83\% & 0.007 & 94.4\% & 0.319 & 0.001\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.91\% & 0.000 & 95.2\% & 0.012 & 0.001\\
+
+ &  & $\gamma_0$ & 0.010 & -0.45\% & 0.008 & 98.4\% & 0.435 & 0.023\\
+
+ &  & $\beta_1$ & -0.082 & -29.03\% & 0.184 & 99.4\% & 2.979 & 0.630\\
+
+ &  & $\beta_2$ & 0.006 & 0.89\% & 0.007 & 94.3\% & 0.320 & 0.004\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.96\% & 0.000 & 95.4\% & 0.012 & 0.008\\
+
+ &  & $\gamma_0$ & -0.010 & 0.43\% & 0.010 & 98.8\% & 0.554 & 0.179\\
+
+ &  & $\beta_1$ & -0.059 & -21.09\% & 0.297 & 97\% & 3.760 & 0.859\\
+
+ &  & $\beta_2$ & 0.008 & 1.2\% & 0.007 & 95.2\% & 0.334 & 0.040\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -2.43\% & 0.000 & 95.5\% & 0.014 & 0.105\\
 \hline
@@
 \hline
- &  & $\gamma_0$ & 0.042 & -1.856 & 0.018 & 0.990 & 0.702 & 0.002\\
-\cline{3-9}
- &  & $\beta_1$ & -0.067 & -23.958 & 0.265 & 0.981 & 2.537 & 0.230\\
-\cline{3-9}
- &  & $\beta_2$ & 0.007 & 1.122 & 0.024 & 0.938 & 0.585 & 0.000\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -1.108 & 0.000 & 0.940 & 0.017 & 0.001\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.041 & -1.774 & 0.018 & 0.992 & 0.708 & 0.010\\
-\cline{3-9}
- &  & $\beta_1$ & -0.103 & -36.645 & 0.281 & 0.991 & 3.492 & 0.535\\
-\cline{3-9}
- &  & $\beta_2$ & 0.008 & 1.183 & 0.024 & 0.934 & 0.586 & 0.002\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.031 & 0.000 & 0.939 & 0.017 & 0.006\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.034 & -1.488 & 0.026 & 0.990 & 0.794 & 0.030\\
-\cline{3-9}
- &  & $\beta_1$ & -0.148 & -52.475 & 0.425 & 0.991 & 4.285 & 0.621\\
-\cline{3-9}
- &  & $\beta_2$ & 0.011 & 1.791 & 0.028 & 0.935 & 0.613 & 0.005\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.870 & 0.000 & 0.941 & 0.020 & 0.020\\
+ &  & $\gamma_0$ & 0.042 & -1.86\% & 0.018 & 99\% & 0.702 & 0.002\\
+
+ &  & $\beta_1$ & -0.067 & -23.96\% & 0.265 & 98.1\% & 2.537 & 0.230\\
+
+ &  & $\beta_2$ & 0.007 & 1.12\% & 0.024 & 93.8\% & 0.585 & 0.000\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -1.11\% & 0.000 & 94\% & 0.017 & 0.001\\
+
+ &  & $\gamma_0$ & 0.041 & -1.77\% & 0.018 & 99.2\% & 0.708 & 0.010\\
+
+ &  & $\beta_1$ & -0.103 & -36.65\% & 0.281 & 99.1\% & 3.492 & 0.535\\
+
+ &  & $\beta_2$ & 0.008 & 1.18\% & 0.024 & 93.4\% & 0.586 & 0.002\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.03\% & 0.000 & 93.9\% & 0.017 & 0.006\\
+
+ &  & $\gamma_0$ & 0.034 & -1.49\% & 0.026 & 99\% & 0.794 & 0.030\\
+
+ &  & $\beta_1$ & -0.148 & -52.48\% & 0.425 & 99.1\% & 4.285 & 0.621\\
+
+ &  & $\beta_2$ & 0.011 & 1.79\% & 0.028 & 93.5\% & 0.613 & 0.005\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.87\% & 0.000 & 94.1\% & 0.020 & 0.020\\
 \cline{1-9}
- &  & $\gamma_0$ & 0.043 & -1.874 & 0.018 & 0.989 & 0.701 & 0.001\\
-\cline{3-9}
- &  & $\beta_1$ & -0.066 & -23.566 & 0.258 & 0.984 & 2.535 & 0.224\\
-\cline{3-9}
- &  & $\beta_2$ & 0.007 & 1.116 & 0.024 & 0.935 & 0.585 & 0.000\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -1.202 & 0.000 & 0.939 & 0.017 & 0.001\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.041 & -1.782 & 0.018 & 0.988 & 0.706 & 0.009\\
-\cline{3-9}
- &  & $\beta_1$ & -0.096 & -33.989 & 0.262 & 0.991 & 3.394 & 0.511\\
-\cline{3-9}
- &  & $\beta_2$ & 0.008 & 1.226 & 0.024 & 0.934 & 0.585 & 0.002\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.150 & 0.000 & 0.940 & 0.017 & 0.005\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.036 & -1.573 & 0.020 & 0.986 & 0.738 & 0.023\\
-\cline{3-9}
- &  & $\beta_1$ & -0.174 & -61.685 & 0.380 & 0.991 & 4.350 & 0.669\\
-\cline{3-9}
- &  & $\beta_2$ & 0.010 & 1.639 & 0.025 & 0.937 & 0.598 & 0.005\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.961 & 0.000 & 0.949 & 0.018 & 0.024\\
+ &  & $\gamma_0$ & 0.043 & -1.87\% & 0.018 & 98.9\% & 0.701 & 0.001\\
+
+ &  & $\beta_1$ & -0.066 & -23.57\% & 0.258 & 98.4\% & 2.535 & 0.224\\
+
+ &  & $\beta_2$ & 0.007 & 1.12\% & 0.024 & 93.5\% & 0.585 & 0.000\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -1.2\% & 0.000 & 93.9\% & 0.017 & 0.001\\
+
+ &  & $\gamma_0$ & 0.041 & -1.78\% & 0.018 & 98.8\% & 0.706 & 0.009\\
+
+ &  & $\beta_1$ & -0.096 & -33.99\% & 0.262 & 99.1\% & 3.394 & 0.511\\
+
+ &  & $\beta_2$ & 0.008 & 1.23\% & 0.024 & 93.4\% & 0.585 & 0.002\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.15\% & 0.000 & 94\% & 0.017 & 0.005\\
+
+ &  & $\gamma_0$ & 0.036 & -1.57\% & 0.020 & 98.6\% & 0.738 & 0.023\\
+
+ &  & $\beta_1$ & -0.174 & -61.69\% & 0.380 & 99.1\% & 4.350 & 0.669\\
+
+ &  & $\beta_2$ & 0.010 & 1.64\% & 0.025 & 93.7\% & 0.598 & 0.005\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.96\% & 0.000 & 94.9\% & 0.018 & 0.024\\
 \cline{1-9}
- &  & $\gamma_0$ & 0.041 & -1.790 & 0.018 & 0.989 & 0.703 & 0.005\\
-\cline{3-9}
- &  & $\beta_1$ & -0.084 & -29.806 & 0.242 & 0.994 & 2.967 & 0.423\\
-\cline{3-9}
- &  & $\beta_2$ & 0.007 & 1.141 & 0.024 & 0.936 & 0.585 & 0.001\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -1.100 & 0.000 & 0.940 & 0.017 & 0.002\\
-\cline{2-9}
- &  & $\gamma_0$ & 0.031 & -1.347 & 0.018 & 0.992 & 0.739 & 0.046\\
-\cline{3-9}
- &  & $\beta_1$ & -0.112 & -39.818 & 0.246 & 0.988 & 3.491 & 0.722\\
-\cline{3-9}
- &  & $\beta_2$ & 0.008 & 1.269 & 0.024 & 0.936 & 0.588 & 0.005\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.499 & 0.000 & 0.944 & 0.017 & 0.024\\
-\cline{2-9}
- &  & $\gamma_0$ & -0.003 & 0.133 & 0.022 & 0.996 & 0.985 & 0.237\\
-\cline{3-9}
- &  & $\beta_1$ & -0.094 & -33.488 & 0.233 & 0.988 & 3.875 & 0.887\\
-\cline{3-9}
- &  & $\beta_2$ & 0.010 & 1.616 & 0.025 & 0.941 & 0.608 & 0.033\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & -0.001 & -3.529 & 0.000 & 0.964 & 0.021 & 0.160\\
+ &  & $\gamma_0$ & 0.041 & -1.79\% & 0.018 & 98.9\% & 0.703 & 0.005\\
+
+ &  & $\beta_1$ & -0.084 & -29.81\% & 0.242 & 99.4\% & 2.967 & 0.423\\
+
+ &  & $\beta_2$ & 0.007 & 1.14\% & 0.024 & 93.6\% & 0.585 & 0.001\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -1.1\% & 0.000 & 94\% & 0.017 & 0.002\\
+
+ &  & $\gamma_0$ & 0.031 & -1.35\% & 0.018 & 99.2\% & 0.739 & 0.046\\
+
+ &  & $\beta_1$ & -0.112 & -39.82\% & 0.246 & 98.8\% & 3.491 & 0.722\\
+
+ &  & $\beta_2$ & 0.008 & 1.27\% & 0.024 & 93.6\% & 0.588 & 0.005\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.5\% & 0.000 & 94.4\% & 0.017 & 0.024\\
+
+ &  & $\gamma_0$ & -0.003 & 0.13\% & 0.022 & 99.6\% & 0.985 & 0.237\\
+
+ &  & $\beta_1$ & -0.094 & -33.49\% & 0.233 & 98.8\% & 3.875 & 0.887\\
+
+ &  & $\beta_2$ & 0.010 & 1.62\% & 0.025 & 94.1\% & 0.608 & 0.033\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & -0.001 & -3.53\% & 0.000 & 96.4\% & 0.021 & 0.160\\
 \hline
@@
 In the final scenario we tested to see how the PM designs would capture a model where time had a disproportionately large effect on Missed Dose.
-In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$.
-The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:hightime}.
+The results from our full-data analyses are provided in Table \ref{tab:prelim} while the corresponding PM design results are in Table \ref{tab:hightime}.
+\par
+
+With the Split Form and Altered Split Form designs we observed coverage rates for $\beta_1$ paramter estimate that are slightly higher than the nominal level of 95\% coverage in the high, medium, and low levels of missingness.
+The percentage of bias in these desgined is relatively low in the -30\% to -50\% range across low, medium, and high missingness.
+As for Wave Missingness, the percent bias increases from about -40\% for low missingness all the way up to about -92\% for high missingness.
+\par
+
+It is interesting to note that the FMI seems the be relatively unaffected by the level of missingness in the Split Form and Altered Split Form designs, but in Wave Missingness the FMI increases steadily as the level of missingess increases.
+We also observe this in the confidence interval length, which is relatively stable around 4 for Split Form and Altered Split Form across the three different levels of missingness whereas the confidence interval length in Wave Missingness increases steadily and the amount of missing information increases.
 \par
@@
 \hline
- &  & $\gamma_0$ & -0.023 & 0.498 & 0.120 & 0.968 & 1.414 & 0.018\\
-\cline{3-9}
- &  & $\beta_1$ & 0.604 & 429.053 & 0.669 & 0.973 & 4.812 & 0.271\\
-\cline{3-9}
- &  & $\beta_2$ & 0.010 & 3.263 & 0.048 & 0.955 & 0.827 & 0.003\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -2.671 & 0.000 & 0.945 & 0.039 & 0.004\\
-\cline{2-9}
- &  & $\gamma_0$ & -0.048 & 1.060 & 0.128 & 0.972 & 1.506 & 0.059\\
-\cline{3-9}
- &  & $\beta_1$ & 0.724 & 513.940 & 0.898 & 0.988 & 5.933 & 0.499\\
-\cline{3-9}
- &  & $\beta_2$ & 0.025 & 7.927 & 0.047 & 0.958 & 0.834 & 0.013\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -2.867 & 0.000 & 0.938 & 0.039 & 0.017\\
-\cline{2-9}
- &  & $\gamma_0$ & -0.178 & 3.882 & 0.370 & 0.984 & 2.050 & 0.132\\
-\cline{3-9}
- &  & $\beta_1$ & 0.997 & 708.287 & 1.573 & 0.955 & 6.822 & 0.610\\
-\cline{3-9}
- &  & $\beta_2$ & 0.044 & 13.650 & 0.060 & 0.965 & 0.966 & 0.036\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.787 & 0.000 & 0.955 & 0.048 & 0.060\\
+ &  & $\gamma_0$ & -0.023 & 0.5\% & 0.120 & 96.8\% & 1.414 & 0.018\\
+
+ &  & $\beta_1$ & 0.604 & 429.05\% & 0.669 & 97.3\% & 4.812 & 0.271\\
+
+ &  & $\beta_2$ & 0.010 & 3.26\% & 0.048 & 95.5\% & 0.827 & 0.003\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -2.67\% & 0.000 & 94.5\% & 0.039 & 0.004\\
+
+ &  & $\gamma_0$ & -0.048 & 1.06\% & 0.128 & 97.2\% & 1.506 & 0.059\\
+
+ &  & $\beta_1$ & 0.724 & 513.94\% & 0.898 & 98.8\% & 5.933 & 0.499\\
+
+ &  & $\beta_2$ & 0.025 & 7.93\% & 0.047 & 95.8\% & 0.834 & 0.013\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -2.87\% & 0.000 & 93.8\% & 0.039 & 0.017\\
+
+ &  & $\gamma_0$ & -0.178 & 3.88\% & 0.370 & 98.4\% & 2.050 & 0.132\\
+
+ &  & $\beta_1$ & 0.997 & 708.29\% & 1.573 & 95.5\% & 6.822 & 0.610\\
+
+ &  & $\beta_2$ & 0.044 & 13.65\% & 0.060 & 96.5\% & 0.966 & 0.036\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.79\% & 0.000 & 95.5\% & 0.048 & 0.060\\
 \cline{1-9}
- &  & $\gamma_0$ & -0.019 & 0.415 & 0.119 & 0.966 & 1.401 & 0.011\\
-\cline{3-9}
- &  & $\beta_1$ & 0.603 & 428.601 & 0.638 & 0.966 & 4.616 & 0.239\\
-\cline{3-9}
- &  & $\beta_2$ & 0.014 & 4.254 & 0.048 & 0.956 & 0.827 & 0.002\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -3.004 & 0.000 & 0.944 & 0.039 & 0.003\\
-\cline{2-9}
- &  & $\gamma_0$ & -0.045 & 0.988 & 0.124 & 0.978 & 1.493 & 0.053\\
-\cline{3-9}
- &  & $\beta_1$ & 0.728 & 517.389 & 0.879 & 0.974 & 5.976 & 0.504\\
-\cline{3-9}
- &  & $\beta_2$ & 0.024 & 7.437 & 0.051 & 0.954 & 0.838 & 0.011\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & -0.001 & -4.550 & 0.000 & 0.946 & 0.039 & 0.018\\
-\cline{2-9}
- &  & $\gamma_0$ & -0.117 & 2.557 & 0.196 & 0.984 & 1.759 & 0.112\\
-\cline{3-9}
- &  & $\beta_1$ & 0.876 & 622.327 & 1.305 & 0.968 & 6.913 & 0.650\\
-\cline{3-9}
- &  & $\beta_2$ & 0.026 & 8.265 & 0.051 & 0.963 & 0.892 & 0.034\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & -0.001 & -5.340 & 0.000 & 0.949 & 0.043 & 0.055\\
+ &  & $\gamma_0$ & -0.019 & 0.42\% & 0.119 & 96.6\% & 1.401 & 0.011\\
+
+ &  & $\beta_1$ & 0.603 & 428.6\% & 0.638 & 96.6\% & 4.616 & 0.239\\
+
+ &  & $\beta_2$ & 0.014 & 4.25\% & 0.048 & 95.6\% & 0.827 & 0.002\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -3\% & 0.000 & 94.4\% & 0.039 & 0.003\\
+
+ &  & $\gamma_0$ & -0.045 & 0.99\% & 0.124 & 97.8\% & 1.493 & 0.053\\
+
+ &  & $\beta_1$ & 0.728 & 517.39\% & 0.879 & 97.4\% & 5.976 & 0.504\\
+
+ &  & $\beta_2$ & 0.024 & 7.44\% & 0.051 & 95.4\% & 0.838 & 0.011\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & -0.001 & -4.55\% & 0.000 & 94.6\% & 0.039 & 0.018\\
+
+ &  & $\gamma_0$ & -0.117 & 2.56\% & 0.196 & 98.4\% & 1.759 & 0.112\\
+
+ &  & $\beta_1$ & 0.876 & 622.33\% & 1.305 & 96.8\% & 6.913 & 0.650\\
+
+ &  & $\beta_2$ & 0.026 & 8.27\% & 0.051 & 96.3\% & 0.892 & 0.034\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & -0.001 & -5.34\% & 0.000 & 94.9\% & 0.043 & 0.055\\
 \cline{1-9}
- &  & $\gamma_0$ & -0.057 & 1.249 & 0.127 & 0.968 & 1.454 & 0.038\\
-\cline{3-9}
- &  & $\beta_1$ & 0.853 & 606.148 & 1.003 & 0.974 & 5.629 & 0.510\\
-\cline{3-9}
- &  & $\beta_2$ & 0.006 & 1.804 & 0.046 & 0.959 & 0.831 & 0.006\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -3.051 & 0.000 & 0.945 & 0.039 & 0.011\\
-\cline{2-9}
- &  & $\gamma_0$ & -0.182 & 3.981 & 0.166 & 0.979 & 1.813 & 0.183\\
-\cline{3-9}
- &  & $\beta_1$ & 0.979 & 695.352 & 1.325 & 0.967 & 6.758 & 0.782\\
-\cline{3-9}
- &  & $\beta_2$ & 0.020 & 6.425 & 0.050 & 0.956 & 0.871 & 0.037\\
-\cline{3-9}
- & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & -0.001 & -4.466 & 0.000 & 0.955 & 0.042 & 0.068\\
-\cline{2-9}
- &  & $\gamma_0$ & -0.403 & 8.803 & 0.345 & 0.987 & 2.789 & 0.440\\
-\cline{3-9}
- &  & $\beta_1$ & 1.050 & 745.735 & 1.504 & 0.951 & 7.357 & 0.887\\
-\cline{3-9}
- &  & $\beta_2$ & 0.019 & 5.848 & 0.050 & 0.973 & 0.960 & 0.099\\
-\cline{3-9}
-\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & -0.003 & -18.904 & 0.000 & 0.975 & 0.052 & 0.200\\
+ &  & $\gamma_0$ & -0.057 & 1.25\% & 0.127 & 96.8\% & 1.454 & 0.038\\
+
+ &  & $\beta_1$ & 0.853 & 606.15\% & 1.003 & 97.4\% & 5.629 & 0.510\\
+
+ &  & $\beta_2$ & 0.006 & 1.8\% & 0.046 & 95.9\% & 0.831 & 0.006\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -3.05\% & 0.000 & 94.5\% & 0.039 & 0.011\\
+
+ &  & $\gamma_0$ & -0.182 & 3.98\% & 0.166 & 97.9\% & 1.813 & 0.183\\
+
+ &  & $\beta_1$ & 0.979 & 695.35\% & 1.325 & 96.7\% & 6.758 & 0.782\\
+
+ &  & $\beta_2$ & 0.020 & 6.42\% & 0.050 & 95.6\% & 0.871 & 0.037\\
+
+ & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & -0.001 & -4.47\% & 0.000 & 95.5\% & 0.042 & 0.068\\
+
+ &  & $\gamma_0$ & -0.403 & 8.8\% & 0.345 & 98.7\% & 2.789 & 0.440\\
+
+ &  & $\beta_1$ & 1.050 & 745.74\% & 1.504 & 95.1\% & 7.357 & 0.887\\
+
+ &  & $\beta_2$ & 0.019 & 5.85\% & 0.050 & 97.3\% & 0.960 & 0.099\\
+
+\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & -0.003 & -18.9\% & 0.000 & 97.5\% & 0.052 & 0.200\\
 \hline
@@
 We found that for low levels of planned missing data (about 25\% missingness), variations of the Split Form design and the Wave Missingness designs are all capable of estimating the parameters of the multilevel model reasonably well.
-As the level of missing data increases to 50\% and 75\%, however, the quality of estimates in all of the tested PM designs become unacceptable as we see rising parameter biases and confidence interval lengths.
-Moreover, we found that the quality of the Wave Missingness design depreciates much more rapidly than the other PM designs, providing higher parameter biases than the corresponding Split Form estimates and low confidence interval coverages (95\% confidence intervals with less than 90\% coverage in some cases).
-\par
-
-These facts warn against the use of Wave Missingness designs when the Split Form design can be easily substituted.
-If Wave Missingness must be used, as in the cohort sequential and developmental timelLag designs, the design must minimize the amount of missing data.
+As the level of missing data increases to 50\% and 75\% the quality of estimates in all of the tested PM designs degrades we see generally rising parameter biases and confidence interval lengths.
+This occurs most dramatically in the Wave Missingness design, which suggest the use of Split Form designs over Wave Missingness when Split form can be easily implemented.
+\par
+
+If Wave Missingness must be used, as in the cohort sequential and developmental time lag designs, the design should attempt to minimize the amount of missing data.
 For instance, in a cohort sequential design which attempts to stretch four-year data to cover a span of six years each cohort will have missing values at two of the six measurement occasions.
-This would result in about 33.3\% missingness.
 To ensure that the researcher's analyses are accurate, we would recommend an increase in the amount of time they follow participants, using five-year data instead of four-year data to cover the same period.
@@
 By illuminating the weaknesses of the Wave Missingness design, it is hoped that, unless it is explicitly required, researchers will opt instead to use a Split Form design.
-Furthermore, when researchers do implement a PM design we hope they follow our recommendation to err on the side of caution and keep the amount of missing data relatively low.
-\par
+Furthermore, when researchers do implement a PM design we hope they follow our recommendation to err on the side of caution and take steps to keep the amount of missing data relatively low.
+\par
+
+\begin{acknowledgements}
+Nick Illenberger
+\end{acknowledgements}
 

### 2018-06-09 Documentation/response.Rnw
Manuscript and response edits.

--- 2018-06-07 Documentation/response.Rnw
@@
 
+{\bf This first iteration of this paper did not provide adequate context. This particular concern is addressed in the addition of an introductory paragraph.}\\
+
 {\bf With any high frequency longitudinal study, there is a high probability of dropout.
@@
 It can also lower the cost of a longitudinal study.
-We believe this is addressed in the second sentence of the first paragraph of the new draft of the manuscript.
-}\\
+We believe this is addressed in the second sentence of the first paragraph of the new draft of the manuscript.}\\
 
@@
 
-{\bf }\\
-Complete case analysis is highly inefficient here because we would be removing nearly all of the observations.
-Multiple imputation gets around this and allows for more efficient estiamtion of the parameters.
+{\bf Complete case analysis is highly inefficient here because we would be removing nearly all of the observations.
+Multiple imputation gets around this and allows for more efficient estiamtion of the parameters.}\\
 
@@
 And is there good reason to believe that a different design would have produced the same results?
-For example, is it reasonable to assume that there are no context or order effects in these questions that might play out in at least the split form designs?"
+For example, is it reasonable to assume that there are no context or order effects in these questions that might play out in at least the split form designs?"\\
 
@@
 \item In section 4.3, the authors seem to confuse the idea of bias and efficiency.\\
+
 {\bf That is correct.  The mentions of efficiency have been removed from this section.  }\\
@@
 
-{\bf Our response goes here.}\\
-The complete data structure is best fit with mixed effects model and mimic the original data.
+{\bf The complete data structure is best fit with mixed effects model and mimic the original data.
 We now exgend it to the scenario where we have missing by design.
-For the structure of this data, we believe this is the best model.
+For the structure of this data, we believe this is the best model.}\\
 
-We're using different data! That's why we didn't use a latent growth curve model.  It's not a comparison.  It's in addition to.
+%We're using different data! That's why we didn't use a latent growth curve model.  It's not a comparison.  It's in addition to.
 
@@
 {\bf The analysis model contains only one of the survey questions, but the other survey questions are used in the imputation model to impute the missing values of the question used in the analysis model.
-An example of the missingness pattern fo rlow levels of missingness for split design can be seen in figure 1 in the left-most image.
+An example of the missingness pattern for low levels of missingness for split design can be seen in figure 1 in the left-most image.
 }\\
@@
 {\bf The table that the reviewer is referring to has been removed from the manuscript.
-It has been replaced by figure 1 and it is indeed and example of the missingness design for one single individual.
+It has been replaced by figure 1 and it is indeed an example of the missingness design for one single individual.
 }\\

### 2018-06-09 Documentation/response.tex
Manuscript and response edits.

--- 2018-06-02 Documentation/response.tex
@@
 
- We would again like to thank the reviewers for their helpful comments on our manuscript.
+ We would like to thank the reviewers for their helpful comments on our manuscript.
 We have addressed each of these comments in our revised manuscript, as well as provided a point-by-point response below.
-Reviewer comments are in normal font and our responses are bold-faced.
+Reviewer comments are in regular font and our responses are bold-faced.
+
+ We should also note that this revision is a little bit unusual in that the main author of the first submission has been dropped from this manuscript.
+Since then two other authors have been added to this manuscript, which has had parts largely re-written and the simulation study has been completely overhauled to conform to standards of reproducible research.
 
@@
 
-\item {[Issues]} that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs.
-Further, there is no justification for an inherent interest in a multilevel model.
-Why is this of greater interest than a latent growth curve or a simple repeated measures model?\\
+\item {[Issues]} that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs.\\
 
-{\bf Our response goes here.}\\
+{\bf This first iteration of this paper did not provide adequate context. This particular concern is addressed in the addition of an introductory paragraph.}\\
+
+{\bf With any high frequency longitudinal study, there is a high probability of dropout.
+Using planned missingness reduces the burden on the participants, which often lowers the probability of drop out due to survey fatigue.
+It can also lower the cost of a longitudinal study.
+We believe this is addressed in the second sentence of the first paragraph of the new draft of the manuscript.}\\
+
+%With a high frequency longitudinal there is is a high probabilty of dropout.  Using planned missingesns reduces the burden on participants.  CITE where we talk about this in the paper.
+
+\item {[There]} is no justification for an inherent interest in a multilevel model. Why is this of greater interest than a latent growth curve or a simple repeated measures model?\\
+
+{\bf We chose to work with a multi-level model in this case because that was the analysis model of interest in Pellowski et.
+al.
+(2016).
+The data used in the aforementioned paper was used a basis for our simulation study, and so we wanted to continue to use the analysis model that was of interest in the original paper.
+The justification for using that model can be found in Pellowski et.
+al.
+(2016).
+}\\
+%In the paper by Pellofski YEAR, that was the origianl model of interest.  We are simply using that model of interest in our simulation, now with the addition of planned missingess.
 
@@
 
-{\bf Our response goes here.}\\
+{\bf Complete case analysis is highly inefficient here because we would be removing nearly all of the observations.
+Multiple imputation gets around this and allows for more efficient estiamtion of the parameters.}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf Certainly any simulation study suffers from the flaw that it is difficult to determined how generalizable the results are beyond the specific settings of the particular simulation study.
+However, the study design in Pellowski et.
+al.
+(2016) is a common design and the planned missingness designs studied here are also common desgined.
+\\
+
+That being said, we believe that results would be similar if the response was continuous and / or different parameters were chosen for the covariates.
+The sample size of this study is relatively small, but we still see reasonable results.
+In Pellowski et.
+al.
+(2016) the number of participants was 59.
+Sample sizes can be this low when attempting to collect data longitudinally at high frequencies such as daily (or even more often) due to the fact the participants need to be highly engaged in the study.\\
+
+There should have been two omitted responses for Day 5 in the Split Form example in Table 4.  This correction has been made.\\  
+}\\
+
+How to respond to this: ``Are these sample sizes typical?
+And is there good reason to believe that a different design would have produced the same results?
+For example, is it reasonable to assume that there are no context or order effects in these questions that might play out in at least the split form designs?"\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf We have removed the mention of these cut-offs.  However, they are based on suggestions put forth in Collins, L. M., Schafer, J. L., & Kam, C.-M. (2001)}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf That is correct.  The mentions of efficiency have been removed from this section.  }\\
+
 \end{itemize}
@@
 
-{\bf Our response goes here.}\\
+{\bf The complete data structure is best fit with mixed effects model and mimic the original data.
+We now exgend it to the scenario where we have missing by design.
+For the structure of this data, we believe this is the best model.}\\
 
-\itemThe model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!\\
+%We're using different data! That's why we didn't use a latent growth curve model.  It's not a comparison.  It's in addition to.
 
-{\bf Our response goes here.}\\
+\item The model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!\\
+
+{\bf The model was indeed written incorrectly.  The model is now written as $$
+logit (p_{ij}) = \beta_{0j} + \beta_1DrinkYN_i + \beta_2ZAlcTox_i +\beta_3Day
+$$
+where $\beta_{0j} = \gamma_0 + \alpha_j$ and $\alpha_j \sim N(0,\sigma_\alpha^2)$.}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf The analysis model contains only one of the survey questions, but the other survey questions are used in the imputation model to impute the missing values of the question used in the analysis model.
+An example of the missingness pattern for low levels of missingness for split design can be seen in figure 1 in the left-most image.
+}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf We have removed this table from the manuscript and replaced with this Figure 1.  Figure 1 shows an example of the missingness patterns for one single participant.  }\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf The table that the reviewer is referring to has been removed from the manuscript.
+It has been replaced by figure 1 and it is indeed an example of the missingness design for one single individual.
+}\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf We have changed this sentence to now read: ``The FMI is a measure of the fraction of information that is lost due to missing data."\\
+
+We have changed this sentence to read ``In addition to comparing the results between each of the PM designs, the same analyses were also performed before missingness was imposed." We believe this addresses the reveiwers concern.
+\\
+
+Finally, the bias and average bias are found by averaging across the different simulations.  }\\
 
@@
 
-{\bf Our response goes here.}\\
+{\bf Type I error rate refers to the rate at which the null hypothesis is rejected given that the null hypothesis is true.
+In this case, we are implicitly testing the null hypothesis that each regression coefficient is equal to the known value.
+(e.g.
+$\beta_1 = 0.28$).
+Since we know the true values of our population parameters, and we are generating simulated data sets based on those values our coverage rates are in fact estimating $1 - \alpha$, where $\alpha$ is the probability of making a type I error.
+There is always a type I error rate, even for parameter values different than 0.
+It is simply calculated by measuring how often the test is rejected (i.e.
+how often a confidence interval misses the true parameter value) conditional on the null hypothesis being true.}\\
 
@@
 {\bf Our response goes here.}\\
+The correlation matrix used needs to be added to the paper.
 
@@
 
-{\bf Our response goes here.}\\
+{\bf The main interest of this paper was the fixed effects coefficients, so we excluded analysis of the variance of the random intercept.  }\\
+% 1.) Either add this if it's easy.  
+% 
+% OR
+% 
+% 2.) The main interest of this paper was the fixed effects.  So we excluded the variance of the random intercept.
 

### 2018-06-09 Documentation/manuscript.Rnw
Manuscript and response edits.

@@
 
-prelim <- kable(df, escape = FALSE, format ="latex", caption = "\\label{tab:prelim} Primary Results (N = 60)") %>%
+prelim <- kable(df, escape = FALSE, format ="latex", caption = "\\label{tab:prelim} Preliminary Results (N = 60)") %>%
   collapse_rows(columns = 1:2, latex_hline = "major") %>%
@@
 waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
+@
+
+<<echo=FALSE>>=
+grid_arrange_shared_legend <- function(...) {
+    plots <- list(...)
+    g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
+    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+    lheight <- sum(legend$height)
+    grid.arrange(
+        do.call(arrangeGrob, lapply(plots, function(x)
+            x + theme(legend.position="none"))),
+        legend,
+        ncol = 1,
+        heights = unit.c(unit(1, "npc") - lheight, lheight))
+}
 @
@@
 require(gridExtra)
+require(grid)
+require(ggplot2)
+
+# plots <- list(splitplot, alternatesplitplot, waveplot)
+# g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
+# legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+# lheight <- sum(legend$height)
+# tmp <- arrangeGrob(splitplot + theme(legend.position = "none"), alternatesplitplot + theme(legend.position = "none"), layout_matrix = matrix(c(1, 3), nrow = 1))
+# grid.arrange(legend, tmp, ncol = 2, heights = c(10,1))
+
 grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@@
 These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed.
-To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Table \ref{tab:table14} \textbf{Greg: I think we need either only the table or only the illustration.
-Not sure we need both.}.
-As in the previous tables, "1" indicates an observed occasion while "0" indicates a missing one.
-We see that the Split Form design entails missing two items on each of the days.
-The altered Split Form, while similar, is fully measured on two of the measurement occasions.
-Because there are days which are fully observed, the relationships between variables may be clearer, allowing the imputation procedure to run more effectively.
-On the other hand, the Wave Missingness design shows two days in which no questions are asked but the full questionnaire is given on the remaining days.
-\par
-
-% \begin{table}[H]
-% 	\centering
-% 	\caption{Different Planned Missingness Designs}
-% 	\setlength{\tabcolsep}{0.45cm}
-% 	\label{tab:table14}
-% 	\hspace*{-1cm}
-% 	\begin{tabular}{c|c|ccccc}
-% 		\toprule
-% 		Design & Day & Q1 & Q2 & Q3 & Q4 & Q5 \\
-% 		\midrule
-% 		\multirow{5}{*}{Split Form}
-% 		& 1 & 1 & 1 & 0 & 0 & 1 \\
-% 		& 2 & 0 & 0 & 1 & 1 & 1 \\
-% 		& 3 & 0 & 1 & 1 & 0 & 1 \\
-% 		& 4 & 1 & 0 & 1 & 1 & 0 \\
-% 		& 5 & 0 & 1 & 0 & 1 & 1 \\
-% 		\midrule
-% 		\midrule
-% 		\multirow{5}{*}{Altered Split Form}
-% 		& 1 & 1 & 1 & 1 & 1 & 1 \\
-% 		& 2 & 1 & 1 & 1 & 1 & 1 \\
-% 		& 3 & 0 & 0 & 1 & 1 & 1 \\
-% 		& 4 & 1 & 1 & 0 & 1 & 0 \\
-% 		& 5 & 0 & 1 & 1 & 0 & 1 \\
-% 		\midrule
-% 		\midrule
-% 		\multirow{5}{*}{Wave Missingness}
-% 		& 1 & 1 & 1 & 1 & 1 & 1 \\
-% 		& 2 & 0 & 0 & 0 & 0 & 0 \\
-% 		& 3 & 1 & 1 & 1 & 1 & 1 \\
-% 		& 4 & 1 & 1 & 1 & 1 & 1 \\
-% 		& 5 & 0 & 0 & 0 & 0 & 0 \\
-% 		\bottomrule
-% 	\end{tabular}
-% 	\hspace*{-1cm}	
-% \end{table}
-
-%FIX THIS: THIS SOUNDS LIKE WE ADDED MORE MISSINGNESS. FIXED
+To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Figure \ref{fig:formillustration}.
+\par
+
 For each different designed missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions.
@@
 This fact allows for the principled use of MI techniques.
-Using the R package \texttt{mice} \citep{mice2011imputation} the binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching %\textbf{was it???
-i don't think so, it was in the X block originally but double check!Greg: Yes it was}.
-\par
-measure of the proportion of information that is lost as a result of missing data
+Using the R package \texttt{mice} \citep{mice2011imputation} the binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching measure of the proportion of information that is lost as a result of missing data.
+\par
 
@@
 \par
+
 \subsubsection{Low Inter-Survey Correlation}
@@
 
-% While this fact was accounted for in the original simulations, it was not in this set of simulations.
-If the probability of answering "yes" on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables.
-This implies that each of the questions are conditionally independent of each other given the baseline variables.
 \subsubsection{High Time Effect}
@@
 Nevertheless, this must be kept in mind when analyzing the results from the PM designs provided in Table \ref{tab:primary}.
-%\textbf{In Table \ref{tab:primary} as in Tables \ref{tab:sampsize}, \ref{tab:lowcorr}, and \ref{tab:hightime} bold values indicate ``unacceptable" results.} That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.
 
@@
 However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:prelim}.
-The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088.
-Furthermore, the percent bias on the $\beta_1$ estimate is not seriously different from that obtained in the small sample scenario.
-For example, at medium levels of missingness the percent bias on $\beta_1$ is 23.86\% while for the smaller sample it was 23.75\%.
+The CI length from the complete-data simulations was 1.384 while at high levels of missingness the CI length reaches 3.281.
+However, the percent bias on the $\beta_1$ estimate is seriously different from that obtained in the small sample scenario.
+For example, at medium levels of missingness the percent bias on $\beta_1$ is -25.97\% while for the smaller sample it was -36.19\%.
 Similarly to the Split Form design, the Altered Split Form Design also provided unacceptable results for the MSE of the $\beta_1$ estimate at medium missingness and unacceptable bias, percent bias, and MSE at high levels.
@@
 That is, for the $\beta_1$ estimate the measurements at medium and high levels of missingness are unacceptable and a steep drop off in coverage probability occurs for the 95\% CIs.
-In fact, at medium and high levels of missingness the coverages drop to 85.5\% and 82.0\%.
+In fact, at medium and high levels of missingness the coverages remain steady at 99.4\% and 97\%.
 The $\gamma_0$ parameter also continues to be estimated poorly at high levels of missing data under the Wave Missingness design.
@@
 For the Split Form design it is important to notice that the bias of the $\beta_1$ estimate decreases much more than in the original simulations when moving from low to high missingess.
-For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be -0.041 and -0.145 at high levels.
+For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be -0.067 and -0.148 at high levels.
 Looking at the same increase in the original simulations, note that the bias only changed from -0.071 to -0.107.
@@
 With the Split Form and Altered Split Form designs we observed coverage rates for $\beta_1$ paramter estimate that are slightly higher than the nominal level of 95\% coverage in the high, medium, and low levels of missingness.
-The percentage of bias in these desgined is relatively low in the -30\% to -50\% range across low, medium, and high missingness.
+The percentage of bias in these designs is relatively low in the -30\% to -50\% range across low, medium, and high missingness.
 As for Wave Missingness, the percent bias increases from about -40\% for low missingness all the way up to about -92\% for high missingness.

### 2018-06-09 Documentation/manuscript.tex
Manuscript and response edits.

@@
 These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed.
-To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Table \ref{tab:table14} \textbf{Greg: I think we need either only the table or only the illustration.
-Not sure we need both.}.
-As in the previous tables, "1" indicates an observed occasion while "0" indicates a missing one.
-We see that the Split Form design entails missing two items on each of the days.
-The altered Split Form, while similar, is fully measured on two of the measurement occasions.
-Because there are days which are fully observed, the relationships between variables may be clearer, allowing the imputation procedure to run more effectively.
-On the other hand, the Wave Missingness design shows two days in which no questions are asked but the full questionnaire is given on the remaining days.
-\par
-
-\begin{table}[H]
-	\centering
-	\caption{Different Planned Missingness Designs}
-	\setlength{\tabcolsep}{0.45cm}
-	\label{tab:table14}
-	\hspace*{-1cm}
-	\begin{tabular}{c|c|ccccc}
-		\toprule
-		Design & Day & Q1 & Q2 & Q3 & Q4 & Q5 \\
-		\midrule
-		\multirow{5}{*}{Split Form}
-		& 1 & 1 & 1 & 0 & 0 & 1 \\
-		& 2 & 0 & 0 & 1 & 1 & 1 \\
-		& 3 & 0 & 1 & 1 & 0 & 1 \\
-		& 4 & 1 & 0 & 1 & 1 & 0 \\
-		& 5 & 1 & 1 & 0 & 1 & 1 \\
-		\midrule
-		\midrule
-		\multirow{5}{*}{Altered Split Form}
-		& 1 & 1 & 1 & 1 & 1 & 1 \\
-		& 2 & 1 & 1 & 1 & 1 & 1 \\
-		& 3 & 0 & 0 & 1 & 1 & 1 \\
-		& 4 & 1 & 1 & 0 & 1 & 0 \\
-		& 5 & 0 & 1 & 1 & 0 & 1 \\
-		\midrule
-		\midrule
-		\multirow{5}{*}{Wave Missingness}
-		& 1 & 1 & 1 & 1 & 1 & 1 \\
-		& 2 & 0 & 0 & 0 & 0 & 0 \\
-		& 3 & 1 & 1 & 1 & 1 & 1 \\
-		& 4 & 1 & 1 & 1 & 1 & 1 \\
-		& 5 & 0 & 0 & 0 & 0 & 0 \\
-		\bottomrule
-	\end{tabular}
-	\hspace*{-1cm}	
-\end{table}
-
-%FIX THIS: THIS SOUNDS LIKE WE ADDED MORE MISSINGNESS. FIXED
+To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Figure \ref{fig:formillustration}.
+\par
+
 For each different designed missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions.
@@
 This fact allows for the principled use of MI techniques.
-Using the R package \texttt{mice} \citep{mice2011imputation} the binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching %\textbf{was it???
-i don't think so, it was in the X block originally but double check!Greg: Yes it was}.
+Using the R package \texttt{mice} \citep{mice2011imputation} the binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching measure of the proportion of information that is lost as a result of missing data.
 \par
@@
 To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days.
-While this fact was accounted for in the original simulations, it was not in this set of simulations.
-If the probability of answering "yes" on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables.
-This implies that each of the questions are conditionally independent of each other given the baseline variables.
-If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal.
-To investigate this, the correlation of the variables was scaled by 0.5.\par
+This set of simulations reduced the correlations between survey questions to study the impact lower correlation between survey question answers.
+This was done to simulate a scenario where researchers have a questionnaire that they do not expect any of the answers to be obviously related.
+To investigate this, the correlation betwen the variables was reduced by half.\par
+
 \subsubsection{High Time Effect}
@@
 
-\caption{\label{tab:unnamed-chunk-2}\label{tab:prelim} Primary Results (N = 60)}
+\caption{\label{tab:unnamed-chunk-2}\label{tab:prelim} Preliminary Results (N = 60)}
 \centering
@@
 \hline
- & $\gamma_0$ & 0.042 & -1.86\% & 0.018 & 98.8\% & 0.700\\
-
- & $\beta_1$ & -0.103 & -36.45\% & 0.871 & 95.4\% & 3.040\\
-
- & $\beta_2$ & 0.008 & 1.26\% & 0.024 & 93.4\% & 0.585\\
-
-\multirow{-4}{*}{\raggedright\arraybackslash Primary Analysis (n = 60)} & $\beta_3$ & 0.000 & -0.83\% & 0.000 & 94.2\% & 0.017\\
+ & $\gamma_0$ (-2.287) & 0.042 & -1.86\% & 0.018 & 98.8\% & 0.700\\
+
+ & $\beta_1$ (0.282) & -0.103 & -36.45\% & 0.871 & 95.4\% & 3.040\\
+
+ & $\beta_2$ (0.637) & 0.008 & 1.26\% & 0.024 & 93.4\% & 0.585\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash Primary Analysis (n = 60)} & $\beta_3$ (0.0147) & 0.000 & -0.83\% & 0.000 & 94.2\% & 0.017\\
 \cline{1-7}
- & $\gamma_0$ & 0.014 & -0.59\% & 0.008 & 98.4\% & 0.424\\
-
- & $\beta_1$ & -0.038 & -13.5\% & 0.135 & 95.2\% & 1.384\\
-
- & $\beta_2$ & 0.006 & 0.86\% & 0.007 & 94.4\% & 0.319\\
-
-\multirow{-4}{*}{\raggedright\arraybackslash Increased Sample Size (n = 120)} & $\beta_3$ & 0.000 & -0.87\% & 0.000 & 95.3\% & 0.012\\
+ & $\gamma_0$ (-2.287) & 0.014 & -0.59\% & 0.008 & 98.4\% & 0.424\\
+
+ & $\beta_1$ (0.282) & -0.038 & -13.5\% & 0.135 & 95.2\% & 1.384\\
+
+ & $\beta_2$ (0.637) & 0.006 & 0.86\% & 0.007 & 94.4\% & 0.319\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash Increased Sample Size (n = 120)} & $\beta_3$ (0.0147) & 0.000 & -0.87\% & 0.000 & 95.3\% & 0.012\\
 \cline{1-7}
- & $\gamma_0$ & 0.044 & -1.91\% & 0.018 & 98.8\% & 0.700\\
-
- & $\beta_1$ & -0.067 & -23.67\% & 0.298 & 95.8\% & 2.001\\
-
- & $\beta_2$ & 0.007 & 1.11\% & 0.024 & 93.5\% & 0.585\\
-
-\multirow{-4}{*}{\raggedright\arraybackslash Low Inter-Survey Correlation (n = 60)} & $\beta_3$ & 0.000 & -1.17\% & 0.000 & 94\% & 0.017\\
+ & $\gamma_0$ (-2.287) & 0.044 & -1.91\% & 0.018 & 98.8\% & 0.700\\
+
+ & $\beta_1$ (0.282) & -0.067 & -23.67\% & 0.298 & 95.8\% & 2.001\\
+
+ & $\beta_2$ (0.637) & 0.007 & 1.11\% & 0.024 & 93.5\% & 0.585\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash Low Inter-Survey Correlation (n = 60)} & $\beta_3$ (0.0147) & 0.000 & -1.17\% & 0.000 & 94\% & 0.017\\
 \cline{1-7}
- & $\gamma_0$ & -0.020 & 0.44\% & 0.114 & 96.2\% & 1.368\\
-
- & $\beta_1$ & -6.781 & -4815.84\% & 136.550 & 96.6\% & 88815.966\\
-
- & $\beta_2$ & 0.014 & 4.54\% & 0.047 & 95.7\% & 0.832\\
-
-\multirow{-4}{*}{\raggedright\arraybackslash High Time Effect (n = 60)} & $\beta_3$ & 0.000 & -0.98\% & 0.000 & 94.5\% & 0.039\\
+ & $\gamma_0$ (-2.287) & -0.020 & 0.44\% & 0.114 & 96.2\% & 1.368\\
+
+ & $\beta_1$ (0.282) & -6.781 & -4815.84\% & 136.550 & 96.6\% & 88815.966\\
+
+ & $\beta_2$ (0.637) & 0.014 & 4.54\% & 0.047 & 95.7\% & 0.832\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash High Time Effect (n = 60)} & $\beta_3$ (0.147) & 0.000 & -0.98\% & 0.000 & 94.5\% & 0.039\\
 \hline

### 2018-06-10 Documentation/manuscript.Rnw
Manuscript
Common legend for illustration!!!

@@
 cols <- c("Missing" = "red", "Observed" = "skyblue3")
-splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
+splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.title.x = element_blank(),panel.background = element_rect(fill = NA)) + labs(y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
 
@@
 cols <- c("Missing" = "red", "Observed" = "skyblue3")
-alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
+alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.title.y = element_blank(), axis.title.x = element_blank(),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
 
@@
 cols <- c("Missing" = "red", "Observed" = "skyblue3")
-waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
-@
-
-<<echo=FALSE>>=
-grid_arrange_shared_legend <- function(...) {
-    plots <- list(...)
-    g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
-    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
-    lheight <- sum(legend$height)
-    grid.arrange(
-        do.call(arrangeGrob, lapply(plots, function(x)
-            x + theme(legend.position="none"))),
-        legend,
-        ncol = 1,
-        heights = unit.c(unit(1, "npc") - lheight, lheight))
-}
+waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.title.x = element_blank(), axis.title.y = element_blank(),panel.background = element_rect(fill = NA)) + labs(fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
 @
@@
 require(ggplot2)
+require(lemon)
 
@@
 
-grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
+#plots <- grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3, bottom=textGrob("x axis title", gp=gpar(fontsize=22)))
+
+#grid_arrange_shared_legend(plots,position="bottom")
+
+gg <- grid_arrange_shared_legend(splitplot, alternatesplitplot, waveplot, ncol=3, position="top")
+grid.arrange(gg,bottom=textGrob("Questions Asked"))
+#grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
 @
@@
 
-<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
+<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=X
 sampsize
